### 2015-12-29 Paper.tex
Complete referee requests for resubmission

\documentclass[11pt]{article}
\usepackage{amsfonts}
\usepackage{amsmath,amsthm,amssymb,graphicx,setspace,url,booktabs,tabularx,slantsc}
\usepackage[T1]{fontenc}

% \usepackage[yyyymmdd,hhmmss]{datetime}
% \usepackage{fancyhdr}
% \pagestyle{fancy}
% \lfoot{Page \thepage. Typeset on \today\ at \currenttime}
% \cfoot{}
% \rfoot{}

\usepackage[sort,round]{natbib}
\usepackage[multiple]{footmisc}
\usepackage{geometry}
\usepackage[small]{caption}

\bibliographystyle{abbrvnat}
\newcommand\citepos[2][]{\citeauthor{#2}'s \citeyearpar[#1]{#2}}

\newtheorem{thm}{Theorem}
\newtheorem{lem}{Lemma}
\newtheorem{claim}{Claim}
\newtheorem{cor}{Corollary}
\newtheorem{res}{Result}

\theoremstyle{definition}

\newtheorem{example}{Example}
\newtheorem{defn}{Definition}
\newtheorem{rem}{Remark}

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\plim}{plim}

\DeclareMathOperator{\dist}{d}
\DeclareMathOperator{\const}{const}
\DeclareMathOperator{\cov}{cov}
\DeclareMathOperator{\E}{E}
\DeclareMathOperator{\eqd}{\overset{d}{=}}
\DeclareMathOperator{\ind}{1}
\DeclareMathOperator{\pr}{Pr}
\DeclareMathOperator{\sgn}{sgn}
\DeclareMathOperator{\var}{var}
\DeclareMathOperator{\vech}{vech}

\renewcommand{\mod}{\operatorname{mod}}

\newcommand{\clt}{\textsc{clt}}
\newcommand{\fclt}{\textsc{fclt}}
\newcommand{\hac}{\textsc{hac}}
\newcommand{\lln}{\textsc{lln}}
\newcommand{\mds}{\textsc{mds}}
\newcommand{\ned}{\textsc{ned}}

\frenchspacing

\begin{document}

\author{Gray Calhoun\thanks{Economics Department, Iowa State
    University, Ames, IA 50011. Telephone: (515) 294-6271.  Email:
    \texttt{gcalhoun@iastate.edu}. Web: \texttt{http://gray.clhn.co}.
    I would like to thank Helle Bunzel, Dimitris Politis, Robert
    Taylor, and three anonymous referees for their comments and
    feedback on earlier versions of this paper.}}

\title{Block bootstrap consistency\\under weak assumptions}

\date{March 25, 2013}
\maketitle

\begin{abstract}\noindent
  This paper weakens the size and moment conditions needed for typical
  block bootstrap methods (i.e. the Moving Blocks, Circular Blocks,
  and Stationary Bootstraps) to be valid for the sample mean of
  Near-Epoch-Dependent (\ned) functions of mixing processes; they are
  consistent under the weakest conditions that ensure the original
  \ned\ process obeys a Central Limit Theorem \citep[those
    of][\textit{Econometric Theory}]{Jon:97}.  In doing so, this paper
  extends de Jong's method of proof, a blocking argument, to hold with
  random and unequal block lengths.  This paper also proves that
  bootstrapped partial sums satisfy a Functional CLT under the same
  conditions.

  \noindent \textsc{jel} Classification: C12, C15

  \noindent Keywords: Resampling, Time Series, Near Epoch Dependence,
  Functional Central Limit Theorem
\end{abstract}

\newpage
\noindent Block bootstraps, e.g. the Moving Blocks
\citep{Kun:89,LiS:92}, Circular Block \citep{PoR:92}, and Stationary
Bootstraps \citep{PoR:94}, have become popular in Economics, partly
because they do not require the researcher to make parametric
assumptions about the data generating process.  They are valid under
general weak dependence and moment conditions.  Some recent papers
(\citealp{GoW:02}; \citealp{GoJ:03}) relax the dependence and moment
conditions of the original papers to fit with those commonly used in
Econometrics based on Near-Epoch-Dependence
(\ned).\footnote{\citet{GoW:02} show that these bootstrap methods can
  be applied to heterogeneous $L_{2+\delta}$-\ned\ processes of size
  $-2(r-1)/(r-2)$ on a strong mixing sequence of size
  $-r(2+\delta)/(r-2)$, where $r > 2$ and $\delta >0$, when the
  original series has uniformly bounded $3r$-moments.  \citet{GoJ:03}
  relax these conditions to $L_{2+\delta}$-\ned\ of size $-1$ and
  $r+\delta$ moments for the original series, and size
  $-(2+\delta)(r+\delta)/(r-2)$ for the underlying mixing series.
  Both papers require that the expected block length grow with $n$ and
  be $o(n^{1/2})$.  \cite{GoP:11} discuss these issues
  further.}\footnote{An array $\{X_{nt}\}$ is an $L_{\rho}$-\ned\
  process on a mixing array $\{V_{nt}\}$ if
  \begin{equation}
    \| X_{nt} - \E(X_{nt}
    \mid V_{n,t-m},\dots,V_{n,t+m}) \|_{\rho} \leq d_{nt} v_m
  \end{equation} 
  with $v_m \to 0$ as $m \to \infty$ and $\{d_{nt}\}$ an array of
  positive constants.  It is of size $-\gamma$ if $v_m = O(m^{-\gamma
    - \delta})$ for all $\delta>0$.  Dropping the index ``$n$'' gives
  the series definition.  Note that strong and uniform mixing arrays are
  not required to be stationary.} But these conditions are still stronger than
required for a \clt\ to hold; \citet{Jon:97} has established the \clt\
under $L_2$-\ned\ with smaller size and moment
restrictions.\footnote{\citet{Jon:97} proves that the \clt\ holds for
  averages of $L_2$-\ned\ processes of size $-1/2$ on a strong mixing
  series of size $-r/(r-2)$, $r > 2$ and the original series having
  bounded $r$-moments.}  This paper shows that these block bootstrap
methods consistently estimate the distribution of the sample mean
under \citepos{Jon:97} assumptions, and show that an \fclt\ holds as
well.\footnote{\citet{Rad:96} proves consistency for the Moving Blocks
  Bootstrap for any stationary strong mixing sequence that satisfies
  the \clt. This paper uses a similar method of proof to his, but also
  accommodates nonstationary sequences and the Stationary Bootstrap.}
It also relaxes \citepos{GoW:02} and \citepos{GoJ:03} requirement that
the expected block length be $o(n^{1/2})$ to the original papers'
requirement that it be $o(n)$.

The proof exploits the conditional independence of the blocks in each
bootstrap.  Each bootstrap proceeds by drawing blocks of $M$
consecutive observations from the original time series, and then
pasting these blocks together to create the new bootstrap time series.
The Moving Blocks bootstrap does exactly that; the Circular Block
bootstrap ``wraps'' the observations, so that $(X_{n-1}, X_n, X_1,
X_2)$, for example, is a possible block of length four (letting $X_t$
denote the original time series).  The Stationary Bootstrap wraps the
observations and also draws $M$ at random for each block;
\citet{PoR:94} suggest drawing $M$ from the geometric distribution.
As the name suggests, the series produced by the Stationary Bootstrap
are strictly stationary, while those produced by the other methods are
not.  Although the Stationary Bootstrap was believed to be much less
efficient than other block bootstrap methods due to results of
\citet{Lah:99}, \citet{Nor:09} has shown that it is only slightly less
efficient than the other block-bootstrap methods discussed in this
paper, and has efficiency identical to that of the non-overlapping
block bootstrap.  Consequently, there has been renewed interest in the
Stationary Bootstrap since stationarity of the bootstrap samples can
be a useful property in theoretical research.  \cite{KrP:11} provides
a recent review of the bootstrap for time-series
processes,\footnote{Also see the discussion papers:
  \citet{Dah:11,GoP:11,Hor:11,JeM:11,KrP:11b}.} and \citet{GoP:11}
further discuss recent developments in block-bootstraps.

Theorem~\ref{thm:1} presents the main result, asymptotic normality of
the distribution of bootstrapped partial sums.  This paper adopts the
standard notation that $\E^{*}$, $\var^{*}$, etc. are the usual
operators with respect to the probability measure induced by the
bootstrap and will use explicit stochastic array notation 
for precision.  Also note that all results are presented for the
scalar case but generalize immediately to random vectors.  All of the
proofs are presented in the appendix; only proofs for the Stationary
Bootstrap are presented, since proofs for the other methods are
similar and easier to follow.  All limits are taken as $n \to \infty$
unless otherwise noted and $\lVert \cdot \rVert_r$ denotes the
$L_r$-norm.

\begin{thm}\label{thm:1}
  Suppose the following conditions hold.
  \begin{enumerate}
  \item $X_{nt}$ is $L_2$-\ned\ of size $-1/2$ on an array
    $V_{nt}$ that is either strong mixing of size $-r/(r-2)$ or
    uniform mixing of size $-r/2(r-1)$, with $r > 2$.  The
    \ned\ magnitude indices are denoted $\{d_{nt}\}$.
  \item The array $\mu_{nt} - \bar \mu_n$ is uniformly bounded where
    $\E X_{nt} = \mu_{nt}$ and $\bar{\mu}_n = n^{-1} \sum_{t=1}^n
    \mu_{nt}$.  Moreover, $\sqrt{n} \| \bar{X}_{n} - \bar\mu_n \|_2
    \to \sigma > 0$.
  \item There exists an array of positive real numbers $\{c_{nt}\}$
    such that $(X_{nt} - \mu_{nt})/c_{nt}$ is uniformly $L_r$-bounded
    and $c_{nt}$ and $d_{nt}/c_{nt}$ are uniformly bounded in $n$
    and~$t$.
  \item $X_{nt}^{*}$ is generated by the Stationary Bootstrap with
    geometric block lengths with success probability $p_n$, $p_n = c
    n^{-a}$ and $a,c \in (0,1)$, or by the Moving or Circular Block
    bootstrap with block length $M_n$ such that $M_n \sim n^a$ for 
    $a \in (0,1)$.  Let $M_{ni}$ be the block length of the $i$th
    block, $i=1,\dots,J_n$, and define $K_{n0} = 0$ and $K_{nj} =
    \sum_{i=1}^j M_{ni}$.
  \end{enumerate}
  Then
  \begin{equation}\label{eq:30}
    \sup_x \big\lvert \pr^{*}\big[\sqrt{n}(\bar X_{n}^{*} - \mu_{n}^{*}) \big/
    \sigma_n^{*} \leq x \big] - \Phi(x) \big\rvert \to^p 0,
  \end{equation}
  and
  \begin{equation}
    \label{eq:9}
    \sup_x \big\lvert \pr^{*}\big[
    \sqrt{n}(\bar X_{n}^{*} - \mu_{n}^{*}) \big/ \hat\sigma_n^{*}
    \leq x \big] - \Phi(x) \big\rvert \to^p 0,
  \end{equation}
  where $\Phi$ is the \textsc{cdf} of the Standard Normal
  distribution, $\sigma_n^{*2} = \var^{*}(\sqrt{n} \bar X_n^{*})$, and
    \begin{equation}
      \label{eq:12}
      \hat{\sigma}_n^{*2} = \tfrac{1}{n} \sum_{j=1}^{J_n}
      \Big\{\sum_{t=K_{n,j-1}+1}^{K_{nj}} (X_{nt}^{*} - \bar X_{n}^{*})\Big\}^2.
    \end{equation}
\end{thm}

Note that \citet{Jon:97} allows a little bit more flexibility in his
conditions on the array $\{c_{nt}\}$ \citep[see also][]{Dav:93};
essentially, he allows for a single set of blocks with the
maximal $\{c_{nt}\}$ over each block well-behaved, while this
paper requires this condition to hold for every possible partition of
blocks.  This additional restriction is required because the
Stationary Bootstrap will select the blocks randomly and is similar to
\citepos{JoD:00b} for the \fclt.

Consistency for the distribution of the sample mean follows as an
immediate corollary of Theorem~\ref{thm:1} and \citet[Theorem~2]{Jon:97}.

\begin{cor}\label{cor:1} 
  If the conditions of Theorem~\ref{thm:1} hold and $\hat{\sigma}^2_n$
  is a consistent estimator of $\sigma^2$ then
  \begin{equation}
    \label{eq:31}
    \sup_{x} \big\lvert \pr^{*}\big[
    \sqrt{n}(\bar X_{n}^{*} - \mu_{n}^{*}) / \sigma_{n}^{*}
    \leq x \big]
    - \pr\big[\sqrt{n}(\bar X_n - \bar{\mu}_n)/\hat{\sigma}_n \leq x \big] \big\rvert \to^p 0.
  \end{equation}
  and
  \begin{equation}
    \label{eq:11}
    \sup_{x} \big\lvert \pr^{*}\big[
    \sqrt{n} (\bar X_{n}^{*} - \mu_{n}^{*}) \big/ \hat\sigma^{*}_{n}
    \leq x \big]
    - \pr\big[\sqrt{n}(\bar X_n - \bar{\mu}_n)/\hat{\sigma}_n \leq x \big] \big\rvert \to^p 0.
  \end{equation}
\end{cor}

Corollary~\ref{cor:1} justifies using the Stationary Bootstrap to
conduct inference about $\bar \mu_n$ even though there may be
considerable heterogeneity.  Unlike \citet{GoW:02} and \citet{GoJ:03},
we are able to achieve consistency without
additional assumptions that ensure the heterogeneity is asymptotically
irrelevant, either because the deviations of $\mu_{nt}$ from $\bar
\mu_n$ are small or because there are a finite number of breaks that
occur in a neighborhood of the first observation.
The additional cost is the assumption that there must be an estimator
$\hat\sigma^2$ of $\sigma^2$ that is known to be consistent, and such an
estimator will typically require the heterogeneity in the mean to be
approximately known.

If the mean \textit{is} approximately constant, we can get a result
directly comparable to \citepos{GoW:02} and \citet{GoJ:03}, but with
the weaker size and moment conditions of Theorem~\ref{thm:1}.
Corollary~\ref{cor:2} formalizes this result and follows from
Corollary~\ref{cor:1} and Lemma~\ref{res:B}.
\begin{cor}\label{cor:2}
  Suppose that the conditions of Theorem~\ref{thm:1} hold and that
  $\sum_{t=1}^n (\mu_{nt} - \bar{\mu}_n)^2$ is $o(n^{1/2})$.  
  Then $\sigma_n^{*2} \to^p
  \sigma^2$, $\hat{\sigma}_n^{*2} \to^p \sigma^2$, and
\end{cor}
  \begin{equation}
    \sup_{x} \big\lvert \pr^{*}\big[
    \sqrt{n}(\bar X_{n}^{*} - \mu_{n}^{*})
    \leq x \big]
    - \pr\big[\sqrt{n}(\bar X_n - \bar{\mu}_n) \leq x \big] \big\rvert \to^p 0.
  \end{equation}

For some uses, a \clt\ is not enough and an \fclt\ is desired.
Theorem~\ref{thm:1} can be extended to give an \fclt\ (using
arguments from \citealp{JoD:00b}), but we will see that extending 
Corollaries~\ref{cor:1} and~\ref{cor:2} is more problematic.
Theorem~\ref{thm:2} proves a version of Theorem~\ref{thm:1} for the
partial sum; under the same assumptions as Theorem~\ref{thm:1}, the
partial sum of the bootstrapped process obeys an \fclt\ and can be
used to derive critical values for other test statistics.

\begin{thm}\label{thm:2}
  Suppose that the conditions of Theorem~\ref{thm:1} hold, let $W$ be
  standard Brownian Motion, and define
  \begin{equation}
    \label{eq:7}
    W_n^{*}(\gamma) = \tfrac{1}{\sqrt{n}}
    \sum_{t=1}^{\lfloor \gamma n \rfloor} (X^*_{nt} - \mu_n^{*}) / \sigma_{n}^{*}
  \end{equation}
  and 
  \begin{equation}
    \label{eq:7}
    \hat{W}_n^{*}(\gamma) = \tfrac{1}{\sqrt{n}}
    \sum_{t=1}^{\lfloor \gamma n \rfloor} (X^*_{nt} - \mu_n^{*}) / \hat\sigma_n^{*}.
  \end{equation}
  Then $\pr^{*}[\dist(W_n^{*}, W) > \delta] \to 0$ i.p. and
  $\pr^{*}[\dist(\hat{W}_n^{*}, W) > \delta] \to 0$ i.p. for any
  positive $\delta$ and distance $\dist$ that metricizes weak
  convergence.
\end{thm}

Just as with Theorem~\ref{thm:1}, we have natural corollaries using
Theorem~\ref{thm:2} to approximate the behavior of partial sums of the
original series.  But applying this corollary requires much stronger
assumptions.  In Corollary~\ref{cor:1}, the
heterogeneity in $X_{nt}$ affects inference through the estimator of
the asymptotic variance, $\hat{\sigma}_n^2$; but if the researcher
has a consistent estimator of the variance, inference on the grand
mean, $\bar{\mu}_{n}$, can proceed as normal.
Assuming negligible heterogeneity in the means was unnecessary unless
we want to avoid estimating $\sigma^2$ directly.

But for the partial sum, a consistent estimator of the variance is not
enough.  If the mean is not approximately constant then only the full
summation is centered at the grand mean---the partial sums are
centered at partial averages of the $\mu_{nt}$ terms.  If the research
question concerns the individual $\mu_{nt}$'s then the bootstrap
approximation can be used, but otherwise it can not.

A second difference is that, if the $\mu_{nt}$ terms are approximately
constant as in Corollary~\ref{cor:2}, the covariance process must
still be consistently estimated.  The bootstrapped processes are
(essentially) homoskedastic, so they are unable to match patterns of
heteroskedasticity in the original series.  Those patterns must be
removed by studentizing both the original and bootstrap partial sums.
Other methods, such
as the Local Block Bootstrap \citep{PaP:02,DPP:03}, may be able to
capture this additional heterogeneity, but we do not pursue that
possibility further.

\begin{cor}
  Suppose the conditions of Theorem~\ref{thm:1} hold, define
  \begin{equation}
    \label{eq:14}
    \sigma_n^2(\gamma) = \tfrac{1}{n}
    \sum_{s,t=1}^{\lfloor \gamma n \rfloor} \cov(X_{ns}, X_{nt}),
  \end{equation}
  let $\hat\sigma_n^2(\cdot)$ be an estimator of $\sigma_n^2(\cdot)$
  such that $\sup_{\gamma} |\sigma_n^2(\gamma) /
  \hat{\sigma}_n^2(\gamma) - 1| \to^p 0$, and let
  \begin{equation}
    \label{eq:8}
    \hat{W}_n(\gamma) = \tfrac{1}{\sqrt{n}} \sum_{t=1}^{\lfloor \gamma
      n \rfloor} (X_{nt} - \mu_{nt}) / \hat{\sigma}_{n}(\gamma).
  \end{equation}
  Then $\pr^{*}[\dist(W_n^{*}, \hat{W}_n) > \delta] \to^p 0$ and
  $\pr^{*}[\dist(\hat{W}_n^{*}, \hat{W}_n) > \delta] \to^p 0$ for any
  positive $\delta$ and any distance $\dist$ that metricizes weak
  convergence.

  Moreover, define 
  \begin{align*}
    \tilde W_n(\gamma) &= \tfrac{1}{\sqrt{n}} \sum_{t=1}^{\lfloor \gamma
      n \rfloor} (X_{nt} - \bar \mu_{n}) / \hat{\sigma}_{n}(\gamma),
&    \bar W_n(\gamma) &= \tfrac{1}{\sqrt{n}} \sum_{t=1}^{\lfloor \gamma
      n \rfloor} (X_{nt} - \bar \mu_{n}) / \hat\sigma_n.
  \end{align*}
  If $\sup_t \mu_{nt}$ is $o(n^{-1/2})$ then
  $\pr^{*}[\dist(\hat{W}_n^{*}, \tilde{W}_n) > \delta] \to^p 0$ and, if 
  $\sup_\gamma | \sigma_n(\gamma) / \gamma \sigma - 1 | \to 0$, then
  $\pr^{*}[\dist(\hat{W}_n^{*}, \bar{W}_n) > \delta] \to^p 0$.
\end{cor}

The rest of the paper presents the mathematical proof in detail.
The key insight in these proofs is for the Stationary Bootstrap (other
block bootstraps arise as a special case).  After conditioning on the
block lengths, proving that the partial sums obey an \fclt\ reduces to
proving consistency of the bootstrap variance (conditional on the
block lengths), and the conditional bootstrap variance can be
expressed in terms of blocks of consecutive observations of the
original series.\footnote{Although this paper focuses on the Moving Blocks,
Circular, and Stationary Bootstraps, I expect that the results can be
extended to other recent block bootstrap methods such as the Tapered Block
Bootstrap \citep{PaP:01,PaP:02b} and the Extended Tapered Block Bootstrap
\citep{Sha:10}.  Those extensions are left for future research.}
Since convergence of these blocks is essential to
the \clt\ in general,\footnote{See, for example, \citet{Mcl:74},
  \citet[Chapter 3]{HaH:80}, and \citet[Chapter 24]{Dav:94}.} I
conjecture that the same approach will hold under most forms of
dependence that allow for a \clt\ or \fclt.

\appendix

\subsection*{Proof of Theorem~\ref{thm:1}}
I will only present the proof for the Stationary Bootstrap, since it
is the more difficult of the three.
We can rewrite the sum of $X_{nt}^{*} - \mu_n^{*}$ as a sum of blocks:
\begin{equation}\label{eq:1}
  \tfrac{1}{\sqrt{n}} \sum_{t=1}^n (X_{nt}^{*} - \mu_n^{*}) = \sum_{j=1}^{J_n} \Big\{\tfrac{1}{\sqrt{n}} \sum_{t = K_{n,j-1} +
    1}^{K_{nj}} (X_{nt}^{*} - \bar X_n)\Big\} \equiv 
  \sum_{j=1}^{J_n} Z_{nj}^{*}.
\end{equation}
Now define $\mathcal{M}_{n}=\sigma(J_{n}, M_{n1},\dots,M_{nJ_n})$,
$\mathcal{G}_{nj} = \sigma(Z_{n1}^{*},\dots, Z_{nj}^{*},
X_{n1},\dots,X_{nn}, \mathcal{M}_n)$,
  \begin{equation}\label{eq:18}
    Z_n(\tau, m) = \tfrac{1}{\sqrt{n}} \sum_{t\in I_n(\tau, m)} (X_{nt} - \bar \mu_n),
  \end{equation}
$\nu_{nj}^2(\tau) = \E(Z_n(\tau, M_{nj})^2 \mid \mathcal M_n)$, and
  \begin{equation}\label{eq:26}
    \eta_n^{2} = \tfrac{1}{n} \sum_{\tau=0}^{n-1} \sum_{j=1}^{J_n} \nu_{nj}^2(\tau),
  \end{equation}
with
\begin{equation}
  \label{eq:3}
  I_n(\tau, m) = \begin{cases}
    \{\tau + 1,\dots, \tau + m\} & 0 \leq \tau \leq n - m \\
    \{1,\dots, m - n + \tau\} \cup \{\tau + 1,\dots, n\} & n - m < \tau \leq n.
  \end{cases}
\end{equation}
  Consequently $\{Z_{nj}^{*} / \eta_n, \mathcal{G}_{nj}\}$ is a martingale
  difference array and
\begin{equation}
  \label{eq:6}
  \pr^{*} \Big[ \sum_{j=1}^{J_n}
  Z_{nj}^{*} / \eta_n \leq x \ \Big|\ \mathcal{M}_{n}\Big] - \Phi(x) \to^p 0
\end{equation}
for all $x$ if the following two conditions hold:
\begin{equation}
  \label{eq:13}
  \sum_{j=1}^{J_n} \E^{*}\big( (Z_{nj}^{*2}/\eta_n^{2}) 1\{Z_{nj}^{*2}/\eta_n^{2}  >
  \epsilon\} \ \big|\ \mathcal{M}_n\big) \to^p 0 \qquad \forall \epsilon > 0
\end{equation}
and 
\begin{equation}
  \label{eq:4}
  \pr^{*}\Big[\ \Big|\sum_{j=1}^{J_n} Z_{nj}^{*2}/ \eta_n^{2} - 1
  \Big|\ > \epsilon \ \Big|\ \mathcal{M}_n \Big] \to^p 0 \qquad \forall \epsilon > 0,
\end{equation}
since~\eqref{eq:13} and~\eqref{eq:4} ensure that $Z_{nj}^{*}/\eta_n$ obeys a
martingale difference \clt\ \citep[e.g.][Theorem
3.3]{HaH:80}.

First we will prove
\begin{equation}\label{eq:41}
  \E\Big[ \sum_{j=1}^{J_n} \E^{*}\big((Z_{nj}^{*2} / \eta_n^2) 1\{
  Z_{nj}^{*2} / \eta_n^2 > \epsilon\} \mid \mathcal{M}_n\big) \ \Big|\
  \mathcal{M}_n\Big] \to^p 0,
\end{equation}
which implies~\eqref{eq:13}.  Note that
\begin{equation*}
  \E^{*}(g(Z_{nj}^{*}) \mid \mathcal{M}_n) = \tfrac{1}{n}
  \sum_{\tau=0}^{n-1} g(Z_n(\tau, M_{nj}))
\end{equation*}
almost surely for any function $g$.  As a consequence, we can write
\begin{multline}\label{eq:32}
  \E\Big( \sum_{j=1}^{J_n} \E^{*}\big( (Z_{nj}^{*2}/\eta_n^{2})
  1\{Z_{nj}^{*2}/\eta_n^{2} > \epsilon\} \ \big|\ \mathcal{M}_n\big)
  \ \Big|\ \mathcal{M}_{n} \Big)
  \\\begin{split}= \tfrac{1}{n} \sum_{\tau=0}^{n-1} \sum_{j=1}^{J_n} &
     \frac{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n}{\eta_n^2}
  \E\Bigg( \frac{Z_n(\tau, M_{nj})^2}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n} 
  \\ & \times 1\Bigg\{\frac{Z_n(\tau, M_{nj})^2}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n} 
  > \frac{\eta_n^2 \epsilon}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n}\Bigg\} 
  \ \Bigg|\ \mathcal{M}_n \Bigg)
\end{split}
\end{multline}
almost surely.  Lemma~\ref{res:L} implies that there exists a finite,
monotone function $B(\cdot)$ such that $B(x) \to 0$ as $x \to \infty$
and
\begin{multline*}
\E\Bigg( \frac{Z_n(\tau, M_{nj})^2}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n}
  \times 1\Bigg\{\frac{Z_n(\tau, M_{nj})^2}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n} > \frac{\eta_n^2 \epsilon}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n}\Bigg\} 
  \ \Bigg|\ \mathcal{M}_n \Bigg) \\
  \leq B\Bigg(\frac{\eta_n^2\epsilon}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n}\Bigg)
\end{multline*}
almost surely for all $n$, $j$, and $\tau$.  Consequently, the right
side of~\eqref{eq:32} is bounded by
\begin{equation*}
\tfrac{1}{n} \sum_{\tau=0}^{n-1} \sum_{j=1}^{J_n} 
\frac{\nu_{nj}^2(\tau) + \sigma^2 M_{nj}/n}{\eta_n^2} B\Bigg(\frac{\eta_n^2
  \epsilon}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n}\Bigg)
\end{equation*}
a.s., and this quantity is a.s. less than
\begin{equation*}
  O_{a.s.}(1) \max_{\tau = 0,\dots,n-1} \max_{j=1,\dots,J_n} B\Bigg(\frac{\eta_n^2\epsilon}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n}\Bigg)
\end{equation*}
by definition.  Moreover
\[\max_{\tau=0,\dots,n-1} \max_{j=1,\dots,J_n} B\Bigg(\frac{\eta_n^2 \epsilon}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n}\Bigg)
= B\Bigg(\min_{\tau=0,\dots,n-1} \min_{j=1,\dots,J_n} \frac{\eta_n^2 \epsilon}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n}\Bigg)\]
a.s. by monotonicity, and
\begin{equation*}
  \min_{\tau=0,\dots,n-1} \min_{j=1,\dots,J_n} \frac{\eta_n^2}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n} \to^p \infty
\end{equation*}
by Lemmas~\ref{res:a1}, \ref{res:16},
and~\ref{res:B}, completing the proof of \eqref{eq:41}.
For~\eqref{eq:4},
\begin{equation*}
  \sum_{j=1}^{J_n} Z_{nj}^{*2} = \eta_n^2 + \sum_{j=1}^{J_n}
  \big(Z_{nj}^{*2} - \E^*(Z_{nj}^{*2} \mid \mathcal{M}_n)\big) +
  \tfrac{1}{n} \sum_{\tau=0}^{n-1} \sum_{j=1}^{J_n} \big(Z_{n}(\tau,
  M_{nj})^2 - \nu_{nj}^2(\tau)\big) \qquad
  \text{a.s.}.
\end{equation*}
The first summation on the right is $o_p(\eta_n^2)$ by
Lemma~\ref{res:H} and the second is $o_p(\eta_n^2)$ by
Lemma~\ref{res:B}.

The Dominated Convergence Theorem then ensures that
\begin{equation}\label{eq:39}
  \pr^{*} \Big[\sum_{j=1}^{J_n}
  Z_{nj}^{*} / \eta_n \leq x \Big] - \Phi(x) \to^p 0.
\end{equation}
Lemma~\ref{res:B} proves that $\sigma_n^{*}/\eta_n \to^p 1$ and
$\hat{\sigma}_n^{*}/\eta_n \to^p 1$, so
\begin{equation}
  \label{eq:17}
  \pr^{*}\big[\sqrt{n}(\bar X_{n}^{*} - \mu_{n}^{*}) / \sigma_n^{*}
  \leq x\big] \to^p \Phi(x)
\end{equation}
and
\begin{equation}
  \label{eq:17}
  \pr^{*}\big[\sqrt{n}(\bar X_{n}^{*} - \mu_{n}^{*}) / \hat\sigma_n^{*}
  \leq x\big] \to^p \Phi(x)
\end{equation}
for any $x$.  These results are sufficient for~\eqref{eq:30}
and~\eqref{eq:9} since the Normal distribution is continuous
\citep[see, for example,][Lemma 2.11]{Vaa:00}.\qed

\subsection*{Proof of Theorem~\ref{thm:2}}
Again, I will only present a proof for the Stationary Bootstrap.
The proof follows that of \citet{JoD:00b} closely and notation is reused from the
proof of Theorem~\ref{thm:1}.  Lemma~\ref{res:B} implies that
$\pr^{*}[\dist(W_n^{*}, W) > \delta] \to^p 0$ is sufficient for all of Theorem~\ref{thm:2}'s
conclusions
  \begin{equation*}
    W_n^{*}(\gamma) = \tfrac{1}{\sqrt{n}} \sum_{t=1}^{\lfloor \gamma n
      \rfloor} (X^{*}_{nt} - \mu_n^{*})/\eta_{n}.
  \end{equation*}
  From Theorem~\ref{thm:1}, we know that
  \begin{equation*}
    (W^{*}_n(\gamma_1),\dots, W^{*}_n(\gamma_l)) \to^d
    (W(\gamma_1),\dots,W(\gamma_l))
  \end{equation*}
  in probability for any finite $l$ and $\gamma_1,\dots,\gamma_l \in
  [0,1]$, so the result holds if $W_n^{*}(\gamma)$ is stochastically
  equicontinuous and if the increments of $W^{*}_n(\cdot)$ are
  independent in the limit \citep[Theorems~15.4 and~15.5]{Bil:68}.

  Stochastic equicontinuity requires that
  \begin{equation}\label{eq:22} 
    \lim_{\delta \to 0} \limsup_{n \to \infty} \E\Big( \pr^{*}\Big[\sup_{\gamma
    \in [0,1]} \sup_{\gamma' \in (\gamma-\delta, \gamma+\delta) \cap
    [0,1]]} |W_n^{*}(\gamma) - W_n^{*}(\gamma')| >
  \epsilon \ \Big|\ \mathcal{M}_n \Big]\Big) = 0.
  \end{equation}
  By construction,
  \begin{equation*}
    W_n^*(\gamma) = \sum_{j=1}^{\lfloor \gamma J_n \rfloor} Z_{nj}^*  +
    \big(1 - 2 \times 1\{ \gamma n \leq K_{n, \lfloor \gamma J_n \rfloor}\}\big)
    \sum_{t \in L_n(\gamma)} (X_{nt}^* - \mu_{nt}^*)
  \end{equation*}
  where 
  \[L_n(\gamma) =
  \{\min(K_{n,\lfloor \gamma J_n \rfloor}, \lfloor n \gamma \rfloor) + 1,\dots,
  \max(K_{n,\lfloor \gamma J_n \rfloor}, \lfloor n \gamma \rfloor)\},
  \]
  so we have the upper bound
  \begin{align}\label{eq:27}
    \E \Big(\pr^{*}\Big[&\sup_{\gamma \in [0,1]} \sup_{\gamma' \in
      (\gamma-\delta, \gamma+\delta) \cap [0,1]]}
    |W_n^{*}(\gamma) - W_n^{*}(\gamma')| > \epsilon \
    \Big|\ \mathcal{M}_n \Big]\Big) \nonumber \\
    &\leq \E \Big(\pr^{*} \Big[\sup_{\gamma \in [0,1]} \sup_{\gamma' \in
      (\gamma, \gamma+2\delta) \cap [0,1]]} \Big\lvert
    \sum_{j={\lfloor \gamma J_n \rfloor}}^{\lfloor \gamma'J_n \rfloor}
    Z_{nj}^{*}/ \eta_n \Big\rvert > \epsilon \
    \Big|\ \mathcal{M}_n \Big]\Big) \nonumber \\
    &\quad+ 2 \E \Big(\pr^{*} \Big[\sup_{\gamma \in [0,1]} \Big\lvert
    \tfrac{1}{\sqrt{n}} \sum_{t \in L_n(\gamma)} (X_{nt}^{*} -
    \mu_n^{*}) / \eta_{n}\Big\rvert > \epsilon \ \Big|\ \mathcal{M}_n \Big]\Big).
  \end{align}
  Just as in Theorem~\ref{thm:1}, $Z_{nj}^{*}/\eta_n$ is a martingale
  difference array conditional on $\mathcal{M}_n$, and so
  \begin{equation*}
    \E \Big(\pr^{*} \Big[\sup_{\gamma \in [0,1]} \sup_{\gamma' \in
      (\gamma, \gamma+2\delta) \cap [0,1]]} \Big\lvert 
    \sum_{j={\lfloor \gamma J_n \rfloor}}^{\lfloor \gamma'J_n \rfloor}
    Z_{nj}^{*} / \eta_n \Big\rvert > \epsilon \
    \Big|\ \mathcal{M}_n \Big]\Big) \leq \tfrac{C \delta}{\epsilon} \E\big(\sigma_n^{*2}/\eta_n^2\big)
  \end{equation*}
  for some finite $C$ that does not depend on $n$ \citep[using,
  e.g.][Theorem~15.14]{Dav:94}. And Lemmas~\ref{res:L} and~\ref{res:B}
  imply that
  \begin{equation*}
    \lim_{\delta \to 0}\limsup_{n\to\infty}  \tfrac{C \delta}{\epsilon} \E(\sigma_n^{*} /
    \eta_n) = 0.
  \end{equation*}

  The second term in \eqref{eq:27} is a.s. equal to
  \begin{equation*}
    \E\Big( \tfrac{2}{n} \sum_{\tau=0}^{n-1} \pr\Big[\sup_{\gamma \in
      [0,1]} \Big\lvert \tfrac{1}{\eta_n \sqrt{n}} \sum_{t \in I(\tau, |\lfloor
      \gamma n \rfloor - K_{n,\lfloor \gamma J_n \rfloor}|)} (X_{nt} -
    \bar X_n) \Big\rvert > \epsilon \ \Big|\ \mathcal{M}_n\Big]\Big)
  \end{equation*}
  since the $X_{nt}^{*}$'s are all in the same ``block'' by
  construction, and this quantity is a.s. bounded by
  \begin{multline}\label{eq:24}
    2 \max_{\tau=0,\dots,n-1} \E \Big(\pr\Big[\sup_{\gamma \in [0,1]} \Big\lvert
    \tfrac{1}{\eta_n \sqrt{n}} \sum_{t \in I(\tau, |\lfloor \gamma n
      \rfloor - K_{n,\lfloor \gamma J_n \rfloor}|)} (X_{nt} -
    \mu_{nt}) \Big\rvert > \epsilon \ \Big|\ \mathcal{M}_n\Big]\Big) \\+ 2
    \max_{\tau=0,\dots,n-1}\E \Big(\pr\Big[\sup_{\gamma \in [0,1]} \Big\lvert
    \tfrac{1}{\eta_n \sqrt{n}} \sum_{t \in I(\tau, |\lfloor \gamma n
      \rfloor - K_{n,\lfloor \gamma J_n \rfloor}|)} (\mu_{nt} - \bar
    \mu_n) \Big\rvert > \epsilon \ \Big|\ \mathcal{M}_n\Big]\Big) \\+ 2
    \max_{\tau=0,\dots,n-1}\E\Big( \pr\Big[\sup_{\gamma \in [0,1]} \Big\lvert
    \tfrac{1}{\eta_n \sqrt{n}} \sum_{t \in I(\tau, |\lfloor \gamma n
      \rfloor - K_{n,\lfloor \gamma J_n \rfloor}|)} (\bar \mu_{n} -
    \bar X_n) \Big\rvert > \epsilon \ \Big|\ \mathcal{M}_n\Big]\Big).
  \end{multline}
  Lemma~\ref{res:B} implies that $\eta_n^{-1} = O_p(n^{-1/2})$ and the
  \lln\ implies that $K_{n,\lfloor \gamma J_n\rfloor}/n$ converges
  i.p.  to $\gamma$.  Consequently, the first term converges to zero
  i.p. since the partial sums of $X_{nt} - \mu_{nt}$ obey an \fclt, the
  second term converges to zero i.p. since $\mu_{nt}-\bar{\mu}_n$ is
  bounded, and the third term converges to zero i.p. since $\bar{X}_n
  - \bar{\mu}_n = O_p(n^{-1/2})$, proving~\eqref{eq:22}.

  Since the increments of $W_n^{*}$ are asymptotically normal, we can
  prove asymptotic independence by proving that the covariance between
  any two distinct increments converges to zero.  Take $i < j$ and
  define $i'$, $j'$, $i''$, and $j''$ so that
  \begin{align*}
    \gamma_{i-1} n &\in [K_{n,i'-1}+1,K_{n,i'}] & \gamma_{i} n &\in [K_{n,i''-1}+1,K_{n,i''}]\\
    \gamma_{j-1} n &\in [K_{n,j'-1}+1,K_{n,j'}] & \gamma_{j} n &\in [K_{n,j''-1}+1,K_{n,j''}].
  \end{align*}
  Then the covariance between $W_n^*(\gamma_i) - W_n^*(\gamma_{i-1})$
  and $W_n^*(\gamma_j) - W_n^*(\gamma_{j-1})$ equals
  \begin{multline}\label{eq:15}
    \E^*((W_n^*(\gamma_i) - W_n^*(\gamma_{i-1}))
    (W_n^*(\gamma_j) - W_n^*(\gamma_{j-1}))\mid \mathcal{M}_n) =\\
    \begin{split}
      \E^*\Big(&\Big(\tfrac{1}{\eta_n\sqrt{n}} \sum_{t=\lfloor \gamma_{i-1} n \rfloor + 1}^{K_{ni'}} (X_{nt}^{*} - \mu_n^{*}) 
    + \tfrac{1}{\eta_n} \sum_{k=i'+1}^{i''-1} Z_{nk}^{*} + \tfrac{1}{\eta_n \sqrt{n}} \sum_{t=K_{n,i''-1}+1}^{\lfloor \gamma_i n \rfloor} (X_{nt}^{*} - \mu_n^{*})\Big) \\
    &
      \times \Big(\tfrac{1}{\eta_n\sqrt{n}} \sum_{t=\lfloor \gamma_{j-1} n \rfloor + 1}^{K_{nj'}} (X_{nt}^{*} - \mu_n^{*}) 
    + \tfrac{1}{\eta_n} \sum_{k=j'+1}^{j''-1} Z_{nk}^{*} 
  \end{split}\\
  + \tfrac{1}{\eta_n \sqrt{n}} \sum_{t=K_{n,j''-1}+1}^{\lfloor
    \gamma_j n \rfloor} (X_{nt}^{*} - \mu_n^{*})\Big) \ \Big|\
  \mathcal{M}_n \Big)
\end{multline}
  almost surely (with obvious modifications if $i' = i''$ or $j' =
  j''$).  Since the blocks are independent under the bootstrap-induced
  probability measure, the right side of~\eqref{eq:15} equals
  \begin{equation*}
    \E^{*}\Big( \tfrac{1}{\eta_n^2 n} \sum_{s=K_{n,i''-1}+1}^{\lfloor \gamma_i n \rfloor} (X_{ns}^{*} - \mu_n^{*})
    \sum_{t=\lfloor \gamma_{j-1} n \rfloor + 1}^{K_{nj'}} (X_{nt}^{*} - \mu_n^{*}) \ \Big|\ \mathcal{M}_n\Big) 1\{K_{ni''} = K_{nj'} \}
  \end{equation*}
  which is almost surely bounded in absolute value by
  \begin{equation*}
     \E^{*}\Big(\Big( \tfrac{1}{\eta_n \sqrt{n}} \sum_{s=K_{n,i''-1}+1}^{\lfloor \gamma_i n \rfloor} (X_{ns}^{*} - \mu_n^{*})\Big)^2 \ \Big|\ \mathcal{M}_n\Big)^{1/2}
     \E^{*}\Big(\Big( \tfrac{1}{\eta_n \sqrt{n}} \sum_{t=\lfloor \gamma_{j-1} n \rfloor+1}^{K_{n,j'}} (X_{nt}^{*} - \mu_n^{*})\Big)^2 \ \Big|\ \mathcal{M}_n\Big)^{1/2}.
  \end{equation*}
  Each of these terms converges to zero in probability as before, completing the proof.
 \qed

\section{Supplemental results}
As in the proofs of Theorems~\ref{thm:1} and~\ref{thm:2}, we only
present the proofs for the Stationary Bootstrap as those for the
Circular and Moving Block bootstraps are similar but less complicated.

\begin{lem}\label{res:a1}
  Suppose that $M_{n1}, M_{n2},\dots$ are i.i.d. geometric random
  variables with success parameter $p_n = c n^{-a}$ with $a, c \in
  (0,1)$, and that $\ell_n = (p_n \log p_n^{-1})^{-1}$ and define
  $J_n$ so that $\sum_{i=1}^{J_n-1} < n \leq \sum_{i=1}^{J_n} M_{ni} $
  Then 
  \begin{enumerate}
  \item $\max_{i=1,\dots,\lfloor C n p_n \rfloor} M_{ni} / n \to^p 0$
    for any positive $C$,
  \item $\max_{i=1,\dots,J_n} M_{ni} / n \to^p 0$,
  \item $\max_{i=1,\dots,  \lfloor C n p_n \rfloor} M_{ni} /
  \ell_n^{1+\epsilon} \to^p 0$ as $n \to \infty$ for any positive
  $\epsilon$ and $C$, and
  \item $\max_{i=1,\dots,J_n} M_{ni} /
  \ell_n^{1+\epsilon} \to^p 0$ as $n \to \infty$ for any positive
  $\epsilon$.
  \end{enumerate}
\end{lem}

\begin{proof}[Proof of Lemma~\ref{res:a1}]
  To prove part 1, observe that, for any increasing positive sequence
  $x_n$ such that $x_n p_n \to \infty$,
  \begin{equation*}
    \pr\Big[\max_{i=1,\dots, \lfloor C n p_n \rfloor} M_{ni} \leq x_n\Big] =
    (1 - (1 - p_n)^{x_n})^{\lfloor C n p_n \rfloor} \to \lim \exp(-C n p_n (1 - p_n)^{x_n})
  \end{equation*}
  and $C n p_n (1 - p_n)^{x_n} \to \lim C n p_n e^{-x_n p_n}$. Now, let
  $x_n = n x$ for any positive number $x$.  Then
  \begin{equation*}
    \pr\Big[\max_{i=1,\dots,\lfloor C n p_n \rfloor} M_{ni}/n \leq x \Big] \to
    \lim \exp(-C n p_n e^{-n p_n x}) =
    \exp(0) = 1.
  \end{equation*}
  Since $x$ is arbitrary, $\max_{i=1,\dots,\lfloor C n p_n \rfloor} M_{ni} / n \to^p 0$.

  For part 2, take $C$ to be an arbitrary constant strictly greater
  than one. For any $x$,
  \begin{align*}
    \pr\Big[\max_{i=1,\dots,J_n} M_{ni} > x\Big] & \leq
    \pr\Big[\max_{i=1,\dots,\lfloor C n p_n \rfloor} M_{ni} > x \text{ or
    } J_n > \lfloor C n p_n \rfloor\Big] \\
    & \leq \pr\Big[\max_{i=1,\dots,\lfloor C n p_n \rfloor} M_{ni} > x\Big]
    + \pr\Big[\sum\nolimits_{i=1}^{\lfloor C n
      p_n \rfloor} M_{ni} < n \Big]
  \end{align*}
  The first term converges to zero by part 1 and the second term by
  the \lln.

  For part 3, let $x_n = \ell_n^{1 + \epsilon} x$ and note that 
  \begin{equation*}
    p_n \ell_n^{1+\epsilon} \geq p_n^{-(\epsilon-\delta-\epsilon\delta)} =
    c^{-(\epsilon-\delta-\epsilon\delta)}
    n^{a(\epsilon-\delta-\epsilon\delta)} \equiv b n^{a(\epsilon
      - \delta - \epsilon\delta)}
  \end{equation*}
  for any $\delta > 0$ and large enough $n$.  Choose $\delta$ small
  enough that $\epsilon > \delta(1 +\epsilon)$. Then
  \begin{equation*}
    n p_n \exp(-\ell_n^{1+\epsilon} p_n) \leq n p_n
    \exp(-b n^{a(\epsilon -
      \delta - \epsilon\delta)}) = c
    v_n^{\frac{1-a}{a(\epsilon-\delta-\epsilon\delta)}}
    \exp(-b v_n) \to 0,
  \end{equation*}
  with $v_n = n^{a(\epsilon-\delta-\epsilon\delta)}$.  Consequently,
  \begin{equation*}
    \pr[\max_i M_{ni}/\ell_n^{1+\epsilon} \leq x ] \to \exp(0) = 1
  \end{equation*}
  as well.

  The proof of part 4 is the same as part 2, making the obvious
  substitutions.
\end{proof}

The next result is identical to \citepos{Mcl:75} Theorem~1.6, but is
stated for conditional expectations so that it is relevant for our
bootstrap results. The proof is identical to the original.
\begin{lem}\label{res:16}
  Let $\{\mathcal{G}_n\}$ be a sequence of $\sigma$-fields,
  $\{\mathcal{F}_{nt}\}$ an array of $\sigma$-fields such that
  $\mathcal{G}_n \subset \mathcal{F}_{nt}$ for each $n$ and $t$, and
  suppose that $\{X_{nt}\}$ is an array such that
  \begin{equation*}
    \E\big(\big( \E( X_{nt} \mid \mathcal{F}_{n,t-m} \big)^2 \ \big|\
    \mathcal{G}_n\big)^{1/2} \leq \psi_m c_{nt}
  \end{equation*}
  and
\begin{equation*}
  \E\big(\big(X_{nt} - \E( X_{nt}\mid F_{n,t+m}) \big)^2 \ \big|\
  \mathcal{G}_n\big)^{1/2} \leq \psi_{m+1} c_{nt}  
\end{equation*}
almost surely, with $\psi_m = O(m^{-1/2-\delta})$ for some positive
$\delta$ and $c_{nt} \in \mathcal{G}_n$ for every $n$ and $t$.  Then
there exists a sequence of random variables $\Delta_n \in
\mathcal{G}_n$ such that $\Delta_n = O_p(1)$ and
\begin{equation}\label{eq:40}
  \E\Big( \max_{u \leq s, t \leq v} \Big(\sum_{w=s}^t X_{nw}\Big)^2 \ \Big|\
  \mathcal{G}_n\Big) \leq \Delta_n \sum_{t=u}^v c_{nt}^2
\end{equation}
almost surely.
\end{lem}

\begin{lem}\label{res:L}
  Define $Z_n(\tau,m)$ as in Equation~\eqref{eq:18}.  Under the
  conditions of Theorem~\ref{thm:1}, the family
  \begin{equation*}
    \Bigg\{\frac{Z_{n}(\tau,m)^2}{\E
  Z_n(\tau,m)^2 + \sigma^2 m / n}\ ;\quad \tau, m, n\Bigg\}
  \end{equation*}
 is uniformly integrable.
\end{lem}
\begin{proof}
  We can write 
  \begin{multline}\label{eq:35}
    Z_n(\tau, m)^2 = \big(Y_n(\tau, m) + \tfrac{m}{\sqrt{n}}
    (\bar{\mu}_n - \bar{X}_n) \big)^2 + \Big(\tfrac{1}{\sqrt{n}}\sum_{t \in I_n(\tau,m)} (\mu_{nt} - \bar{\mu}_n)\Big)^2\\
    + 2 \big(Y_n(\tau, m) + \tfrac{m}{\sqrt{n}} (\bar{\mu}_n - \bar{X}_n)\big)
    \Big(\tfrac{1}{\sqrt{n}}\sum_{t \in I_n(\tau,m)} (\mu_{nt} - \bar{\mu}_n)\Big)
  \end{multline}
  almost surely, with 
  \begin{equation}\label{eq:28}
    Y_n(\tau, m) = \tfrac{1}{\sqrt{n}} \sum_{t \in
      I_n(\tau, m)} (X_{nt} - \mu_{nt}).
  \end{equation}
  Then the conclusion holds if
  \begin{equation}\label{eq:34}
    \frac{\big(\sqrt{n} Y_n(\tau, m) + m (\bar{\mu}_n - \bar{X}_n) \big)^2}
    {\E \big(\sqrt{n} Y_n(\tau,m) + m (\bar{\mu}_n - \bar{X}_n)\big)^2  
    + \big(\sum_{t \in I_n(\tau,m)} (\mu_{nt} - \bar{\mu}_n)\big)^2 + m \sigma^2},
  \end{equation}
  and
  \begin{equation}\label{eq:33}
    \frac{\big(\sum_{t \in I_n(\tau,m)} (\mu_{nt} - \bar{\mu}_n)\big)^2}
    {\E \big(\sqrt{n} Y_n(\tau,m) + m (\bar{\mu}_n - \bar{X}_n) \big)^2  +\big(\sum_{t \in I_n(\tau,m)} (\mu_{nt} - \bar{\mu}_n)\big)^2 + \sigma^2}
  \end{equation}
  are all uniformly integrable.  But $\tfrac{n}{m} Y_n(\tau, m)^2$ and
  $n (\bar{\mu_n} - \bar X_n)^2$ are uniformly integrable by existing
  results \citep{Dav:92,Dav:93,Jon:97} and~\eqref{eq:33} is bounded
  above by construction, completing the proof.
\end{proof}

\begin{lem}\label{res:H}
  Suppose the conditions of Theorem~\ref{thm:1} hold and define
  $Z_{nj}^{*}$ and $\eta_n^2$ as in Equations~\eqref{eq:18}
  and~\eqref{eq:26}. Then
  \begin{equation}
    \label{eq:2}
    \pr^{*}\Big[\Big| \sum_{j=1}^{J_n} \big(Z_{nj}^{*2} -
    \E^{*}(Z_{nj}^{*2} \mid \mathcal{M}_n)\big) \Big| \Big/ \eta_n^2
    > \delta \ \Big|\ \mathcal{M}_n \Big] \to^p 0
  \end{equation}
  for any positive $\delta$.
\end{lem}

\begin{proof}
  The proof follows the steps of, for example, Davidson's Theorem 19.7
  using Lemma~\ref{res:L} to establish the necessary inequalities.
  The same argument behind Lemma~\ref{res:L} ensures that, for any
  positive $\epsilon$, there exists a constant $B_{\epsilon}$ such
  that
  \begin{equation}
    \label{eq:21}
    \sup_{\tau, m, n} \big\| \big(Y_n(\tau,m)^2 n / \sigma^2 m \big)
    1\{Y_n(\tau,m)^2 n/ \sigma^2 m  > B_{\epsilon}^2\}\ \big\|_1 \leq \epsilon
  \end{equation}
  with $Y_n(\tau, m)$ defined in~\eqref{eq:28}.  Let $u_{nj}$ be the
  discrete uniform$(1,\dots,n)$ indicating the beginning of the $j$th
  block, so that
  \begin{equation*}
    (X_{n,u_{nj}},\dots,X_{n,u_{nj} + M_{n,j} - 1}) = (X_{n,K_{n,j-1}+1}^{*},\dots,X_{n,K_{n,j}}^{*})
  \end{equation*}
  almost surely, and define
  \begin{equation*}
    U_{nj} = Y_{nj}^{*2} \, 1\{Y_{nj}^{*2} \leq B_{\epsilon}^2 \sigma^2 M_{nj} / n d \}
  \end{equation*}
  and
  \begin{equation*}
    V_{nj} = Y_{nj}^{*2} - U_{nj},
  \end{equation*}
  so
  \begin{multline*}
    Z_{nj}^{*2} - \E^{*}(Z_{nj}^{*2} \mid \mathcal{G}_{n,j-1}) 
    = U_{nj} - \E^{*}(U_{nj} \mid \mathcal{G}_{n,j-1}) + V_{nj} - \E^{*}(V_{nj} \mid \mathcal{G}_{n,j-1}) \\ 
    + \big(Z_{nj}^{*2} - \E^{*}(Z_{nj}^{*2} \mid \mathcal{G}_{n,j-1})\big) - \big(Y_{nj}^{*2} - \E^{*}(Y_{nj}^{*2} \mid \mathcal{G}_{n,j-1})\big)
  \end{multline*}
  almost surely.

  Now, just as in Davidson's proof, we have (with all relationships
  understood to hold almost surely)
  \begin{align*}
    \E\Big(\Big|\tfrac{1}{\eta_n^2} \sum_{j=1}^{J_n} \big(U_{nj} - \E^{*}& (U_{nj} \mid \mathcal{G}_{n,j-1})\big) \Big| \ \Big|\ \mathcal{M}_n\Big)\\
    &\leq \tfrac{1}{\eta_n^2}\Big[\E\Big( \E^{*} \Big( \Big|\sum_{j=1}^{J_n} \big(U_{nj} 
     - \E^{*}(U_{nj} \mid \mathcal{G}_{n,j-1})\big) \Big|^2 \ \Big|\ \mathcal{M}_n\Big)\ \Big|\ \mathcal{M}_n\Big)\Big]^{1/2}
    \\ &= \tfrac{1}{\eta_n^2} \Big(\sum_{j=1}^{J_n} \E\big(\E^{*}\big([U_{nj} - \E^{*}(U_{nj} \mid \mathcal{G}_{n,j-1})]^2\mid \mathcal{M}_{n} \big) \mid \mathcal{M}_n\big) \Big)^{1/2} 
    \\ &\leq \tfrac{1}{\eta_n^2} \Big(\sum_{j=1}^{J_n} \E \E^{*}(U_{nj}^2 \mid \mathcal{M}_n) \Big)^{1/2} 
    \\ & \leq \tfrac{B_{\epsilon}}{\eta_n^2} \Big(\sum_{j=1}^{J_n} \tfrac{1}{n} \sum_{\tau=0}^{n-1} \Big[\E(Y_n(\tau, M_{nj})^2 \mid \mathcal{M}_n)\Big]^2\Big)^{1/2}
    \\ & \leq \tfrac{C_n}{\eta_n^2} \Big(\sum_{j=1}^{J_n} M_{nj}^2 / n^2\Big)^{1/2} \to^{L_1} 0
  \end{align*}
  for some $C_n$, with the last inequality a consequence of Lemma~\ref{res:16}
  and convergence a consequence of Lemma~\ref{res:a1}.  Also,
  \begin{align*}
    \E \E^{*}\Big(\Big\lvert &\tfrac{1}{\eta_n^2} \sum_{j=1}^{J_n} (V_{nj} -
      \E^{*}(V_{nj} \mid \mathcal{G}_{n,j-1})) \Big\rvert \ \Big|\ \mathcal{M}_n \Big)
    \\ & \leq 2 \E \sum_{j=1}^{J_n} \tfrac{1}{\eta_n^2} \E^{*}(\lvert V_{nj} \rvert \mid \mathcal{M}_n)
    \\ & \leq 2 \E \sum_{j=1}^{J_n} \tfrac{1}{\eta_n^2} Y_n(u_{nj}, M_{nj})^2
    1\big\{Y_n(u_{nj}, M_{nj})^2 > B^2_{\epsilon} \sigma^2 M_{nj}/n \big\}
    \\ & \leq 2 \epsilon \E \sum_{j=1}^{J_n} \tfrac{\sigma^2}{\eta_n^2} M_{nj} / n
    \\ & \leq \tfrac{2\sigma^2}{\eta_n^2} \epsilon
  \end{align*}
  with the second to last inequality holding by the choice of
  $B_{\epsilon}$ and all of these relationships understood to hold
  almost surely.

  Finally, 
  \begin{multline*}
    \tfrac{1}{\eta_n^2} \sum_{j=1}^{J_n} \big[(Z_{nj}^{*2} - \E(Z_{nj}^{*2} \mid \mathcal{G}_{n,j-1}) - (Y_{nj}^{*2} - \E(Y_{nj}^{*2} \mid \mathcal{G}_{n,j-1}))\big] \\
    = \tfrac{2}{\eta_n^2} \sum_{j=1}^{J_n} \big[Y_{nj}^{*} - \E^{*}(Y_{nj}^{*} \mid \mathcal{G}_{n,j-1})]
    \Big[\tfrac{M_{nj}}{\sqrt{n}} (\bar{X}_n - \bar{\mu}_n) + \tfrac{1}{\sqrt{n}} \sum_{t \in I_n(\tau, M_{nj})} (\mu_{nt} - \bar{\mu}_n)\Big]
  \end{multline*}
  almost surely, which converges to zero in $L_1$ by the usual arguments, completing the proof.
\end{proof}

\begin{lem}\label{res:B}
  If the conditions of Theorem~\ref{thm:1} hold then
  \begin{equation}
    \label{eq:38}
    \eta_n^2 - \sigma^2 - \tfrac{1}{n^2} \sum_{j=1}^{J_n} \sum_{\tau=0}^{n-1} \Big(\sum_{t \in I_n(\tau, M_{nj})} (\mu_{nt} - \bar{\mu}_n) \Big)^2 = o_p(1),
  \end{equation}
  \begin{equation}
    \label{eq:19}
    \tfrac{1}{n} \sum_{\tau=0}^{n-1} \sum_{j=1}^{J_n} Z_n(\tau,
    M_{nj})^2 -\eta_n^2 = o_p(\eta_n^2),
  \end{equation}
  \begin{equation}\label{eq:37}
    \sigma_n^{*2} - \eta_n^2 = o_p(\eta_n^2),
  \end{equation}
  and
  \begin{equation}
    \label{eq:36}
    \hat\sigma_n^{*2} - \eta_n^2 = o_p(\eta_n^2).
  \end{equation}
\end{lem}

\begin{proof} 
  Equation~\eqref{eq:35}, along with Theorem~2 of \citet{Jon:97} and
  Lemma~\ref{res:a1}, implies that
  \begin{multline*}
    \label{eq:52}
    \sum_{j=1}^{J_n} \tfrac{1}{n} \sum_{\tau=0}^{n-1} Z_n(\tau,
    M_{nj})^2 = \tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau=0}^{n-1}
    Y_n(\tau, M_{nj})^2 + \tfrac{1}{n^2} \sum_{j=1}^{J_n}
    \sum_{\tau=0}^{n-1} \Big(\sum_{t \in I_n(\tau, M_{nj})} (\mu_{nt} - \bar{\mu}_n)\Big)^2 \\
    + \tfrac{2}{n^{3/2}} \sum_{j=1}^{J_n} \sum_{\tau=0}^{n-1}
    Y_n(\tau, M_{nj}) \sum_{t\in I_n(\tau, M_{nj})} (\mu_{nt} -
    \bar{\mu}_n) + o_p(1).
  \end{multline*}
  So~\eqref{eq:38} follows directly from Lemma~\ref{res:7}.
  For~\eqref{eq:19}, it suffices to prove that
  \begin{equation}
    \label{eq:20}
    \tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau=0}^{n-1} \big\{Y_n(\tau,
    M_{nj})^2 - \E(Y_n(\tau, M_{nj})^2 \mid \mathcal{M}_n) \big\} \to^p 0,
  \end{equation}
  and
  \begin{equation}
    \label{eq:51}
    \tfrac{1}{n^{3/2}} \sum_{j=1}^{J_n} \sum_{\tau=0}^{n-1}
    Y_{n}(\tau, M_{nj})\sum_{t\in I_n(\tau, M_{nj})}(\mu_{nt} -
    \bar{\mu}_n) = o_p(\eta_n).
  \end{equation}
  Observe that we can express the summation in~\eqref{eq:20} as
  \begin{multline}\label{eq:47}
    \tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau=0}^{n-1} \big\{Y_n(\tau,
    M_{nj})^2 - \E(Y_n(\tau, M_{nj})^2 \mid \mathcal{M}_n) \big\} \\ =
    \tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau=0}^{M_{nj}-1}
    \sum_{i=1}^{L_{nj}}\big\{ Y_n(\tau+(i-1)M_{nj}, M_{nj})^2
    - \E(Y_n(\tau+(i-1)M_{nj}, M_{nj})^2 \mid
    \mathcal{M}_n)\big\} \\ + \tfrac{1}{n} \sum_{j=1}^{J_n}
    \sum_{\tau= M_{nj}L_{nj}}^{n-1} \big\{Y_{n}(\tau, M_{nj})^2 -
    \E(Y_n(\tau, M_{nj})^2 \mid \mathcal{M}_n)\big\}
  \end{multline}
  almost surely, where $L_{nj} = \lfloor n/ M_{nj} \rfloor$.  The
  advantage of this representation is that each summation over
  $i=1,\dots,L_{nj}$ is formed from adjacent blocks of the original
  series, so standard blocking arguments can be applied.  Now let
  $\ell_n = (p_n \log p_n^{-1})^{-1}$. By Lemma~\ref{res:7}, for any
  $\delta > 0$ there exist positive $C$ and $\epsilon$ such that
  \begin{multline*}
    \Big\lVert\tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau=1}^{M_{nj}}
    \sum_{i=1}^{L_{nj}}\big\{ Y_n(\tau+(i-1)M_{nj}, M_{nj})^2 -
    \E(Y_n(\tau+(i-1)M_{nj}, M_{nj})^2 \mid
    \mathcal{M}_n)\big\}\Big\rVert_1 \\ \leq C \tfrac{\ell_n}{n} + 2
    \delta + C\, \Big\lVert \max_{j =
      1,\dots,J_n}\big(\tfrac{M_{nj}}{n}\big)^{1/2} \max_{j =
      1,\dots,J_n}\big(1,
    \tfrac{M_{nj}}{\ell_n^{1+\epsilon}}\big)^{1/2} \Big\rVert_1
  \end{multline*} 
  which converges to $2 \delta$ by Lemma~\ref{res:a1}.  The second
  term of~\eqref{eq:47} is $O_{p}(1 - M_{nj}/n)$ by Lemma~\ref{res:16},
  proving~\eqref{eq:20}.

  For~\eqref{eq:51}, the Cauchy-Schwarz inequality implies that
  \begin{multline*}
    \tfrac{1}{n^{3/2}} \sum_{j=1}^{J_n} \sum_{\tau=0}^{n-1}
    \Big\lvert Y_{n}(\tau, M_{nj})\sum_{t\in I_n(\tau, M_{nj})}(\mu_{nt} -
    \bar{\mu}_n)\Big\rvert \\\leq \Big\{\tfrac{1}{n} \sum_{j=1}^{J_n}
    \sum_{\tau=0}^{n-1} \big(\tfrac{1}{\sqrt{n}} Y_n(\tau,
    M_{nj})^2\big)\Big\}^{1/2} \Big\{\tfrac{1}{n} \sum_{j=1}^{J_n}
    \sum_{\tau=0}^{n-1} \Big(\tfrac{1}{\sqrt{n}} \sum_{t \in I_n(\tau,
      M_{nj})} (\mu_{nt} - \bar{\mu}_{n} )\Big)^2\Big\}^{1/2}.
  \end{multline*}
  Lemma~\ref{res:16} implies that
  \begin{equation}
    \label{eq:23}
    \tfrac{1}{n} \sum_{j=1}^{J_n}
    \sum_{\tau=0}^{n-1} \big(\tfrac{1}{\sqrt{n}} Y_n(\tau,
    M_{nj})^2\big) \to^p 0
  \end{equation}
  and Equation~\eqref{eq:38} that
  \begin{equation*}
    \tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau=0}^{n-1}
    \Big(\tfrac{1}{\sqrt{n}} \sum_{t \in I_n(\tau, M_{nj})} (\mu_{nt} -
    \bar{\mu}_{n} )\Big)^2 = O_p(\eta_n^2).
  \end{equation*}
  completing the proof of~\eqref{eq:19}.

  Result~\eqref{eq:37} is an immediate consequence of~\eqref{eq:19}
  and Lemma~\ref{res:L}.  Finally, for~\eqref{eq:36}, observe that
  \begin{equation*}
    \hat{\sigma}_n^{*2} = \eta_n^2 + (\sigma_n^{*2} - \eta_n^2) + \sum_{j=1}^{J_n}\Big[
    Z_{nj}^{*2} - \E^*(Z_{nj}^{*2} \mid \mathcal{M}_n)
    + \tfrac{2 M_{nj}}{\sqrt{n}} (\mu_n^{*} - \bar{X}_n^{*})
    Z_{nj}^{*} + \tfrac{M_{nj}^2}{n} (\mu_n^{*} - \bar{X}_n^{*})^2 \Big]
  \end{equation*}
  implying that $\hat{\sigma}_n^{*2}/\eta_n^2 \to^p 1$
  by~\eqref{eq:37} along with Lemmas~\ref{res:a1},~\ref{res:L},
  and~\ref{res:H}.
\end{proof}

\begin{lem}\label{res:7}
  Define $Y_n(\tau, m)$ as in Equation~\eqref{eq:28} and $L_{nj} =
  \lfloor n/M_{nj}\rfloor$. For any positive $\delta$, there exist
  positive and finite constants $C$, $N$, and $\epsilon$ such that
\begin{multline}\label{eq:29}
  \E\Big(\Big\lvert\sum_{i=1}^{L_n} \big[Y_{n}(\tau + (i-1) M_{nj},
  M_{nj})^2 -  Y_{n}(\tau + (i-1) M_{nj}, M_{nj} -
  \ell)^2\big]\Big\rvert \ \Big|\
  \mathcal{M}_n\Big) \leq C \tfrac{\ell}{n},
\end{multline}
\begin{multline}\label{eq:16}
  \E\Big(\Big\lvert\sum_{i=1}^{L_n} \big[Y_{n}(\tau + (i-1) M_{nj},
  M_{nj} - \ell)^2 \\- \E(Y_{n}(\tau + (i-1) M_{nj}, M_{nj} -
  \ell)^2 \mid \mathcal{M}_n)\big]\Big\rvert \ \Big|\
  \mathcal{M}_n\Big)\\ \leq 2 \delta + C \cdot \big(\tfrac{M_{nj}}{n}\big)^{1/2}
  \max\big(1, \tfrac{M_{nj}}{\ell^{1+\epsilon}}\big)^{1/2},
\end{multline}
and
  \begin{multline}
    \label{eq:5}
    \E\Big(\Big\lvert \sum_{i=1}^{L_{n}} \E(Y_n(\tau + (i-1) M_{nj}, M_{nj} - \ell)^2 \mid
    \mathcal{M}_n) - \sigma^2 \Big\rvert \ \Big|\ \mathcal{M}_n\Big) \leq 
    \\ C\,  \nu_n^2(0, n) \Big(\ell \log(\ell)^2 \psi(\ell)^2 
     + \sum_{m=\ell}^{\infty} \log(m)^2 \psi(m)^2 \Big)^{1/2} \Big( \psi(0)^2 + \sum_{v=1}^{\infty} \log(v)^2 \psi(v)^2 \Big)^{1/2}
  \end{multline}
  almost surely for all $j = 1,\dots,J_n$, $\tau= 0,\dots,n-1$,
  $\ell=1,\dots,M_{nj}-1$, and $n > N$.  Moreover, if $\ell_n =
  (p_n^{-1} \log p_n^{-1})^{-1}$ then
  \begin{equation}
    \label{eq:46}
    \sup_{\tau=0,\dots,n-1} \E\Big(\Big\lvert \sum_{j=1}^{L_{n}} \E(Y_n(\tau + (i-1) M_{nj}, M_{nj} - \ell_n)^2 \mid
    \mathcal{M}_n) - \sigma^2 \Big\rvert \ \Big|\ \mathcal{M}_n\Big) \to^{L_1} 0.
  \end{equation}
\end{lem}
\begin{proof}
  Result~\eqref{eq:29} is immediate from Lemma~\ref{res:16}
  and~\eqref{eq:46} follows directly from~\eqref{eq:5}.
  Results~\eqref{eq:16} and~\eqref{eq:5} are direct extensions of
  \citepos[Lemmas 5 and 4, respectively]{Jon:97}, replacing de Jong's
  implicit use of inequalities with explicit inequalities.
\end{proof}
\bibliography{texextra/AllRefs}
\end{document}

% LocalWords:  CLT Kun LiS PoR GoW GoJ nt indices eq studentized JoD reindex nj
% LocalWords:  de Jong's ns Mcl AllRefs nn th nm ni HaH formulae jn gcalhoun nN
% LocalWords:  jel PaP DPP np Ames Resampling nonstationary cdf

### 2015-12-29 Paper.tex
Write initial version of block bootstrap theory paper

@@
-\documentclass[11pt]{article}
+\documentclass[12pt]{article}
 \usepackage{amsfonts}
-\usepackage{amsmath,amsthm,amssymb,graphicx,setspace,url,booktabs,tabularx,slantsc}
-\usepackage[T1]{fontenc}
-
-% \usepackage[yyyymmdd,hhmmss]{datetime}
-% \usepackage{fancyhdr}
-% \pagestyle{fancy}
-% \lfoot{Page \thepage. Typeset on \today\ at \currenttime}
-% \cfoot{}
-% \rfoot{}
-
+\usepackage{amsmath,amsthm,amssymb,graphicx,setspace,url,booktabs,tabularx}
 \usepackage[sort,round]{natbib}
-\usepackage[multiple]{footmisc}
-\usepackage{geometry}
+\usepackage[margin=1.25in]{geometry}
 \usepackage[small]{caption}
@@
 \newtheorem{thm}{Theorem}
-\newtheorem{lem}{Lemma}
-\newtheorem{claim}{Claim}
-\newtheorem{cor}{Corollary}
-\newtheorem{res}{Result}
+\newtheorem{lem}[thm]{Lemma}
+\newtheorem{claim}[thm]{Claim}
+\newtheorem{cor}[thm]{Corollary}
+\newtheorem{res}[thm]{Result}
+\newtheorem{lema}{Lemma}[section]
+\newtheorem{alg}{Algorithm}
+\newtheorem{asmp}{Assumption}[section]
 
@@
 
-\DeclareMathOperator{\dist}{d}
 \DeclareMathOperator{\const}{const}
@@
 \newcommand{\lln}{\textsc{lln}}
-\newcommand{\mds}{\textsc{mds}}
 \newcommand{\ned}{\textsc{ned}}
@@
 \frenchspacing
+\onehalfspacing
 
@@
     University, Ames, IA 50011. Telephone: (515) 294-6271.  Email:
-    \texttt{gcalhoun@iastate.edu}. Web: \texttt{http://gray.clhn.co}.
-    I would like to thank Helle Bunzel, Dimitris Politis, Robert
-    Taylor, and three anonymous referees for their comments and
-    feedback on earlier versions of this paper.}}
-
+    \texttt{gcalhoun@iastate.edu}. Web: \texttt{http://www.econ.iastate.edu/$\sim$gcalhoun}.}}
 \title{Block bootstrap consistency\\under weak assumptions}
-
-\date{March 25, 2013}
+\date{\today}
 \maketitle
@@
   This paper weakens the size and moment conditions needed for typical
-  block bootstrap methods (i.e. the Moving Blocks, Circular Blocks,
-  and Stationary Bootstraps) to be valid for the sample mean of
-  Near-Epoch-Dependent (\ned) functions of mixing processes; they are
+  block bootstrap methods (i.e. the moving blocks, circular blocks,
+  and stationary bootstraps) to be valid for the sample mean of
+  Near-Epoch-Dependent functions of mixing processes; they are
   consistent under the weakest conditions that ensure the original
-  \ned\ process obeys a Central Limit Theorem \citep[those
+  process obeys a Central Limit Theorem \citep[those
     of][\textit{Econometric Theory}]{Jon:97}.  In doing so, this paper
@@
 
-\newpage
-\noindent Block bootstraps, e.g. the Moving Blocks
-\citep{Kun:89,LiS:92}, Circular Block \citep{PoR:92}, and Stationary
-Bootstraps \citep{PoR:94}, have become popular in Economics, partly
+\newpage\noindent Block bootstraps, e.g. the moving blocks
+\citep{Kun:89,LiS:92}, circular block \citep{PoR:92}, and stationary
+bootstraps \citep{PoR:94}, have become popular in Economics, partly
 because they do not require the researcher to make parametric
@@
   Both papers require that the expected block length grow with $n$ and
-  be $o(n^{1/2})$.  \cite{GoP:11} discuss these issues
-  further.}\footnote{An array $\{X_{nt}\}$ is an $L_{\rho}$-\ned\
-  process on a mixing array $\{V_{nt}\}$ if
+  be $o(n^{1/2})$.}\footnote{An array $\{X_{nt}\}$ is an
+  $L_{\rho}$-\ned\ process on a mixing array $\{V_{nt}\}$ if
   \begin{equation}
@@
     - \delta})$ for all $\delta>0$.  Dropping the index ``$n$'' gives
-  the series definition.  Note that strong and uniform mixing arrays are
-  not required to be stationary.} But these conditions are still stronger than
+  the series definition.} But these conditions are still stronger than
 required for a \clt\ to hold; \citet{Jon:97} has established the \clt\
@@
   series of size $-r/(r-2)$, $r > 2$ and the original series having
-  bounded $r$-moments.}  This paper shows that these block bootstrap
-methods consistently estimate the distribution of the sample mean
-under \citepos{Jon:97} assumptions, and show that an \fclt\ holds as
-well.\footnote{\citet{Rad:96} proves consistency for the Moving Blocks
-  Bootstrap for any stationary strong mixing sequence that satisfies
-  the \clt. This paper uses a similar method of proof to his, but also
-  accommodates nonstationary sequences and the Stationary Bootstrap.}
-It also relaxes \citepos{GoW:02} and \citepos{GoJ:03} requirement that
-the expected block length be $o(n^{1/2})$ to the original papers'
-requirement that it be $o(n)$.
+  bounded $r$-moments.}  In this paper, I'll show that these block
+bootstrap methods consistently estimate the distribution of the sample
+mean under \citepos{Jon:97} assumptions, and show that an \fclt\ holds
+as well.  I also relax \citepos{GoW:02} and \citepos{GoJ:03}
+requirement that the expected block length be $o(n^{1/2})$ to the
+original papers' requirement that it be $o(n)$.
 
-The proof exploits the conditional independence of the blocks in each
-bootstrap.  Each bootstrap proceeds by drawing blocks of $M$
+The proof will exploit the conditional independence of the blocks in
+each bootstrap.  Each bootstrap proceeds by drawing blocks of $M$
 consecutive observations from the original time series, and then
 pasting these blocks together to create the new bootstrap time series.
-The Moving Blocks bootstrap does exactly that; the Circular Block
+The moving blocks bootstrap does exactly that; the circular block
 bootstrap ``wraps'' the observations, so that $(X_{n-1}, X_n, X_1,
 X_2)$, for example, is a possible block of length four (letting $X_t$
-denote the original time series).  The Stationary Bootstrap wraps the
+denote the original time series).  The stationary bootstrap wraps the
 observations and also draws $M$ at random for each block;
 \citet{PoR:94} suggest drawing $M$ from the geometric distribution.
-As the name suggests, the series produced by the Stationary Bootstrap
+As the name suggests, the series produced by the stationary bootstrap
 are strictly stationary, while those produced by the other methods are
-not.  Although the Stationary Bootstrap was believed to be much less
-efficient than other block bootstrap methods due to results of
-\citet{Lah:99}, \citet{Nor:09} has shown that it is only slightly less
-efficient than the other block-bootstrap methods discussed in this
-paper, and has efficiency identical to that of the non-overlapping
-block bootstrap.  Consequently, there has been renewed interest in the
-Stationary Bootstrap since stationarity of the bootstrap samples can
-be a useful property in theoretical research.  \cite{KrP:11} provides
-a recent review of the bootstrap for time-series
-processes,\footnote{Also see the discussion papers:
-  \citet{Dah:11,GoP:11,Hor:11,JeM:11,KrP:11b}.} and \citet{GoP:11}
-further discuss recent developments in block-bootstraps.
+not.
 
-Theorem~\ref{thm:1} presents the main result, asymptotic normality of
-the distribution of bootstrapped partial sums.  This paper adopts the
+Theorem~\ref{res:C} presents our main result, asymptotic normality of
+the distribution of bootstrapped partial sums.  This paper adopt the
 standard notation that $\E^{*}$, $\var^{*}$, etc. are the usual
 operators with respect to the probability measure induced by the
-bootstrap and will use explicit stochastic array notation 
-for precision.  Also note that all results are presented for the
-scalar case but generalize immediately to random vectors.  All of the
-proofs are presented in the appendix; only proofs for the Stationary
-Bootstrap are presented, since proofs for the other methods are
-similar and easier to follow.  All limits are taken as $n \to \infty$
-unless otherwise noted and $\lVert \cdot \rVert_r$ denotes the
-$L_r$-norm.
+bootstrap and will use explicit stochastic array notation in this
+paper for precision.  Also note that all results are presented for the
+scalar case but generalize immediately to vector-valued random
+variables.  All of the proofs are presented in the appendix; I only
+present proofs for the stationary bootstrap, since proofs for the
+other methods are similar and easier.  All limits are taken as $n \to
+\infty$ unless otherwise noted.
 
-\begin{thm}\label{thm:1}
+\begin{thm}\label{res:C}
   Suppose the following conditions hold.
   \begin{enumerate}
-  \item $X_{nt}$ is $L_2$-\ned\ of size $-1/2$ on an array
-    $V_{nt}$ that is either strong mixing of size $-r/(r-2)$ or
-    uniform mixing of size $-r/2(r-1)$, with $r > 2$.  The
-    \ned\ magnitude indices are denoted $\{d_{nt}\}$.
-  \item The array $\mu_{nt} - \bar \mu_n$ is uniformly bounded where
-    $\E X_{nt} = \mu_{nt}$ and $\bar{\mu}_n = n^{-1} \sum_{t=1}^n
-    \mu_{nt}$.  Moreover, $\sqrt{n} \| \bar{X}_{n} - \bar\mu_n \|_2
-    \to \sigma > 0$.
+  \item $X_{nt}$ is $L_2$-\ned\ of size $-1/2$ on an array $V_{nt}$
+    that is either strong mixing of size $-r/(r-2)$ or uniform mixing
+    of size $-r/2(r-1)$, with $r > 2$.  The \ned\ magnitude indices
+    are denoted $\{d_{nt}\}$.
+  \item $\E X_{nt} = \mu_{nt}$, $\mu_{nt} - \bar \mu_n$ is uniformly
+    bounded, and $\sqrt{n} \| \bar{X}_{n} - \bar\mu_n \|_2 \to 1$.
   \item There exists an array of positive real numbers $\{c_{nt}\}$
-    such that $(X_{nt} - \mu_{nt})/c_{nt}$ is uniformly $L_r$-bounded
-    and $c_{nt}$ and $d_{nt}/c_{nt}$ are uniformly bounded in $n$
-    and~$t$.
-  \item $X_{nt}^{*}$ is generated by the Stationary Bootstrap with
+    such that $\max_t c_{nt}$ is uniformly finite, $(X_{nt} -
+    \mu_{nt})/c_{nt}$ is uniformly $L_r$-bounded, and $d_{nt}/c_{nt}$
+    is uniformly bounded.
+  \item $X_{nt}^{*}$ is generated by the stationary bootstrap with
     geometric block lengths with success probability $p_n$, $p_n = c
-    n^{-a}$ and $a,c \in (0,1)$, or by the Moving or Circular Block
-    bootstrap with block length $M_n$ such that $M_n \sim n^a$ for 
-    $a \in (0,1)$.  Let $M_{ni}$ be the block length of the $i$th
-    block, $i=1,\dots,J_n$, and define $K_{n0} = 0$ and $K_{nj} =
-    \sum_{i=1}^j M_{ni}$.
+    n^{-a}$ and $a,c \in (0,1)$, or by the moving or circular block
+    bootstrap with block length $M_n$ such that $M_n \to \infty$ and
+    $M_n/n \to 0$.
   \end{enumerate}
-  Then
-  \begin{equation}\label{eq:30}
-    \sup_x \big\lvert \pr^{*}\big[\sqrt{n}(\bar X_{n}^{*} - \mu_{n}^{*}) \big/
-    \sigma_n^{*} \leq x \big] - \Phi(x) \big\rvert \to^p 0,
-  \end{equation}
-  and
-  \begin{equation}
-    \label{eq:9}
-    \sup_x \big\lvert \pr^{*}\big[
-    \sqrt{n}(\bar X_{n}^{*} - \mu_{n}^{*}) \big/ \hat\sigma_n^{*}
-    \leq x \big] - \Phi(x) \big\rvert \to^p 0,
-  \end{equation}
-  where $\Phi$ is the \textsc{cdf} of the Standard Normal
-  distribution, $\sigma_n^{*2} = \var^{*}(\sqrt{n} \bar X_n^{*})$, and
-    \begin{equation}
-      \label{eq:12}
-      \hat{\sigma}_n^{*2} = \tfrac{1}{n} \sum_{j=1}^{J_n}
-      \Big\{\sum_{t=K_{n,j-1}+1}^{K_{nj}} (X_{nt}^{*} - \bar X_{n}^{*})\Big\}^2.
-    \end{equation}
+  Define $\mathcal{B}$ as Brownian Motion and
+  $\mathbb{B}_n^{*}(\gamma) = n^{-1/2} \sum_{t=1}^{\lfloor n \gamma
+    \rfloor} (X_{nt}^{*} - \mu_{n}^{*})$.  Then
+  $\sqrt{n}(\bar{X}_n^{*} - \mu_n^{*}) \to^d N(0,1)$ and
+  $\mathbb{B}_n^{*} \to^d \mathcal{B}$.
 \end{thm}
+
+Theorem~\ref{res:C} assumes that the series have been normalized by
+dividing by the square root of the (population) second moment of
+$\sqrt{n} (\bar{X}_n - \bar{\mu}_n)$.  Sometimes, though, it's useful
+to treat the variance of $X_{nt}$ as a random variable (call it
+$\eta^2_n$).  In such cases the dependence and moment conditions
+listed in Theorem~\ref{res:C} apply to the original array and not the
+normalized array $\eta^{-1}_n X_{nt}$ as is clear from inspecting the
+proofs in this paper and \citet{Jon:97}.\footnote{See also
+  \citepos{HaH:80} Theorem 3.2, Corollary 3.1, and following remarks.}
+Deriving bounds for $\eta_n^{-1} X_{nt}$ from primitive conditions on
+$X_{nt}$ would be difficult.
 
@@
 conditions on the array $\{c_{nt}\}$ \citep[see also][]{Dav:93};
-essentially, he allows for a single set of blocks with the
+essentially, he allows there to be a single set of blocks with the
 maximal $\{c_{nt}\}$ over each block well-behaved, while this
-paper requires this condition to hold for every possible partition of
+paper requires that his condition hold for every possible partition of
 blocks.  This additional restriction is required because the
-Stationary Bootstrap will select the blocks randomly and is similar to
-\citepos{JoD:00b} for the \fclt.
+stationary bootstrap will select the blocks randomly.
 
-Consistency for the distribution of the sample mean follows as an
-immediate corollary of Theorem~\ref{thm:1} and \citet[Theorem~2]{Jon:97}.
+Consistency for the sample mean follows as an immediate corollary of
+Theorem~\ref{res:C} and \citet[Theorem~2]{Jon:97}.
 
-\begin{cor}\label{cor:1} 
-  If the conditions of Theorem~\ref{thm:1} hold and $\hat{\sigma}^2_n$
-  is a consistent estimator of $\sigma^2$ then
-  \begin{equation}
-    \label{eq:31}
-    \sup_{x} \big\lvert \pr^{*}\big[
-    \sqrt{n}(\bar X_{n}^{*} - \mu_{n}^{*}) / \sigma_{n}^{*}
-    \leq x \big]
-    - \pr\big[\sqrt{n}(\bar X_n - \bar{\mu}_n)/\hat{\sigma}_n \leq x \big] \big\rvert \to^p 0.
-  \end{equation}
-  and
-  \begin{equation}
-    \label{eq:11}
-    \sup_{x} \big\lvert \pr^{*}\big[
-    \sqrt{n} (\bar X_{n}^{*} - \mu_{n}^{*}) \big/ \hat\sigma^{*}_{n}
-    \leq x \big]
-    - \pr\big[\sqrt{n}(\bar X_n - \bar{\mu}_n)/\hat{\sigma}_n \leq x \big] \big\rvert \to^p 0.
-  \end{equation}
+\begin{cor}\label{res:E} 
+  Define $\bar{\mu}_n = n^{-1} \sum_{t=1}^n \mu_{nt}$.  If the
+  conditions of Theorem~\ref{res:C} hold then $\sqrt{n}(\bar{X}_n^{*}
+  - \mu_n^{*})$ and $\sqrt{n}(\bar{X}_n - \bar{\mu}_n)$ converge in
+  distribution to the same limit.
 \end{cor}
 
-Corollary~\ref{cor:1} justifies using the Stationary Bootstrap to
-conduct inference about $\bar \mu_n$ even though there may be
-considerable heterogeneity.  Unlike \citet{GoW:02} and \citet{GoJ:03},
-we are able to achieve consistency without
+Corollary~\ref{res:E} justifies using the stationary bootstrap to
+conduct inference about $\bar \mu_n$ even though there is considerable
+heterogeneity.  This conclusion is also present in \citepos{GoW:02}
+and \citepos{GoJ:03} papers, but those authors introduce and emphasize
 additional assumptions that ensure the heterogeneity is asymptotically
@@
 \mu_n$ are small or because there are a finite number of breaks that
-occur in a neighborhood of the first observation.
-The additional cost is the assumption that there must be an estimator
-$\hat\sigma^2$ of $\sigma^2$ that is known to be consistent, and such an
-estimator will typically require the heterogeneity in the mean to be
-approximately known.
+occur in a neighborhood of the first observation.  Such assumptions
+are unnecessary.
 
-If the mean \textit{is} approximately constant, we can get a result
-directly comparable to \citepos{GoW:02} and \citet{GoJ:03}, but with
-the weaker size and moment conditions of Theorem~\ref{thm:1}.
-Corollary~\ref{cor:2} formalizes this result and follows from
-Corollary~\ref{cor:1} and Lemma~\ref{res:B}.
-\begin{cor}\label{cor:2}
-  Suppose that the conditions of Theorem~\ref{thm:1} hold and that
-  $\sum_{t=1}^n (\mu_{nt} - \bar{\mu}_n)^2$ is $o(n^{1/2})$.  
-  Then $\sigma_n^{*2} \to^p
-  \sigma^2$, $\hat{\sigma}_n^{*2} \to^p \sigma^2$, and
+But heterogeneity rules out a version of Corollary~\ref{res:E} for the
+partial sum.  It is not hard to see that under the
+assumptions of Theorem~\ref{res:C},
+\begin{equation}
+  n^{-1/2} \sum_{t=1}^{\lfloor \gamma n \rfloor} \Big(X_{nt}
+  - (\gamma n)^{-1} \sum_{s=1}^{\lfloor \gamma n \rfloor}
+  \mu_{nt}\Big) \to^d \mathcal{B}_{\xi},
+\end{equation}
+where $\mathcal{B}_{\xi}$ is a Gaussian process and $\xi$ captures the
+asymptotic variance of the partial sums.  It would be uncommon for a
+researcher to be interested in these particular random variables; one
+would typically be more interested in $\bar \mu_n$ than $(\gamma
+n)^{-1} \sum_{s=1}^{\lfloor \gamma n \rfloor} \mu_{nt}$, but these
+bootstrap methods do not allow us to approximate the distribution of
+$(\gamma n)^{-1/2} \sum_{t=1}^{\lfloor \gamma n \rfloor} (X_{nt} -
+\bar \mu_n)$.  The same discussion applies if $\mu_{nt} = \bar{\mu}_n$
+for all $t$ but $\mathcal{B}_{\xi} \neq \mathcal{B}$.  Other methods,
+such as the local block bootstrap \citep{PaP:02,DPP:03}, may be able to
+capture this heterogeneity, but we do not pursue that possibility
+further.
+
+For completeness, I'll present a consistency result under the
+additional condition that the heterogeneity vanishes asymptotically
+\citep[similar to Assumption 2.2 of][]{GoW:02}.  This result is a
+corollary of Theorem~\ref{res:C} and \citet[Theorem 3.1]{JoD:00b}.
+
+\begin{cor}\label{res:F} Let $\mathbb{B}_n(\gamma) = n^{-1/2} \sum_{t=1}^{\lfloor n \gamma \rfloor} (X_{nt} -
+  \bar{\mu}_{n})$ and suppose the conditions of Theorem~\ref{res:C}
+  hold, $\sup_t |\mu_{nt} - \bar{\mu}_n| \to 0$, and
+  \begin{equation}
+    n^{-1} \sum_{s,t=1}^{\lfloor \gamma n \rfloor} \E (X_{ns} -
+    \mu_{ns}) (X_{nt} - \mu_{nt}) \to \gamma
+  \end{equation}
+  for all $\gamma \in [0,1]$.  Then $\mathbb{B}_n$ and
+  $\mathbb{B}_n^{*}$ converge in distribution to the same limit.
 \end{cor}
+
+We can develop some more intuition by looking at the argument behind
+Theorem~\ref{res:C}.  For concreteness, let $X_{n1},\dots,X_{nn}$
+denote the original array and let $X_{n1}^{*},\dots,X_{nn}^{*}$ a
+hypothetical series generated by the stationary bootstrap.
+Conditional on the number of blocks, $N_n$, and the block lengths,
+$M_{n1},\dots,M_{nN_n}$, we can see that
 \begin{equation}
-    \sup_{x} \big\lvert \pr^{*}\big[
-    \sqrt{n}(\bar X_{n}^{*} - \mu_{n}^{*})
-    \leq x \big]
-    - \pr\big[\sqrt{n}(\bar X_n - \bar{\mu}_n) \leq x \big] \big\rvert \to^p 0.
+  \sqrt{n} \bar{X}^{*}_n = \frac{1}{\sqrt{N_n}} \sum_{i=1}^{N_n}
+  \Bigg\{\sqrt{\frac{N_n}{n}} \sum_{t=K_{n,i-1}+1}^{K_{n,i}} X_{nt}^{*} \Bigg\},\qquad\text{with}\quad K_{n0} = 0,
+  \quad K_{ni} = \sum_{j=1}^i M_{nj},
+\end{equation} 
+is the sum of $N_n$ independent random variables.  So $\sqrt{n}
+(\bar{X}^{*}_n - \bar{X}_n)$ should obey a \clt\ under very weak moment
+conditions and satisfy a relationship like
+\begin{equation}
+  \label{eq:10}
+  \frac{\bar{X}_n^{*} - \mu_n^{*}}{\var^{*}(\bar{X}_n^{*} \mid
+    M_{n1},\dots,M_{n,N_n})} \to^{d^{*}} N(0,1).
 \end{equation}
 
-For some uses, a \clt\ is not enough and an \fclt\ is desired.
-Theorem~\ref{thm:1} can be extended to give an \fclt\ (using
-arguments from \citealp{JoD:00b}), but we will see that extending 
-Corollaries~\ref{cor:1} and~\ref{cor:2} is more problematic.
-Theorem~\ref{thm:2} proves a version of Theorem~\ref{thm:1} for the
-partial sum; under the same assumptions as Theorem~\ref{thm:1}, the
-partial sum of the bootstrapped process obeys an \fclt\ and can be
-used to derive critical values for other test statistics.
+This argument applies directly to the moving blocks and circular
+bootstraps, since $N_n$ and $M_{ni}$ are deterministic.  But they are
+stochastic for the stationary bootstrap and the randomness of $N_n$,
+in particular, complicates a direct argument; conditioning on $N_n$
+would require us to work with the distributions of $M_{nj}$ given
+$M_{n1} + \cdots + M_{n,N_n} = n$.  This information should not matter
+in the limit, though, and so, as a first step, I'll show that we can
+replace $N_n$ with its expected value without affecting the asymptotic
+distribution induced by the bootstrap.
 
-\begin{thm}\label{thm:2}
-  Suppose that the conditions of Theorem~\ref{thm:1} hold, let $W$ be
-  standard Brownian Motion, and define
+\begin{lem}\label{res:A}
+  Consider the following procedure:
+  \begin{enumerate}
+  \item Draw $M_{n1},\dots,M_{n,\lfloor n p_n \rfloor}$ independently from
+    the geometric distribution with success probability $p_n$, let
+    $m_n = \sum_{i=1}^{\lfloor n p_n \rfloor} M_{ni}$, and let
+    $\mathcal{M}_n = (M_{n1},\dots,M_{n,\lfloor n p_n \rfloor})$.
+  \item Draw $\lfloor n p_n \rfloor$ blocks from $X_{n1},\dots,X_{nn}$
+    (with the observations ``wrapped'' as in the stationary
+    bootstrap), with $M_{ni}$ the length of the $i$th block.
+  \end{enumerate}
+  Let $\{X_{nt}^{**}\}$ be a hypothetical array generated by this
+  procedure, let $\{X_{nt}^{*}\}$ be an array generated by the
+  stationary bootstrap, define $\mu^{*}_n = \mu_n^{**} = \bar X_n$,
+  and define $\mathbb{B}_n^{**}(\gamma) = m_n^{-1/2}
+  \sum_{t=1}^{\lfloor \gamma m_n \rfloor} (X_{nt}^{**} - \mu_n^{**})$.
+  Under the conditions of Theorem~\ref{res:C}, $\mathbb{B}_n^{*}$ and
+  $\mathbb{B}_n^{**}$ converge to the same limit.
+\end{lem}
+
+It is easy to see that if $X_{n1}^*,\dots,X_{nn}^*$ is a hypothetical
+sequence generated by the moving or circular blocks bootstrap with
+block length $M_n$ and $X_{n1}^{**},\dots,X_{n,m_n}^{**}$ is a
+bootstrap generated as in Lemma~\ref{res:A} but with $\lfloor n/M_n
+\rfloor$ blocks of length $M_n$, then the conclusion of
+Lemma~\ref{res:A} still holds.
+
+Given Lemma~\ref{res:A} and the preceding discussion, consistency for
+the distribution of the sample mean can be expected to hold if
+\begin{equation}\label{eq:5}
+  \frac{\bar{X}^{**}_n - \mu_n^{**}}{\var^{**}(\bar{X}_n^{**} \mid
+    \mathcal{M}_n)} \to^{d^{**}} N(0,1)
+\end{equation}
+and $\var^{**}(m_{n}^{1/2} \bar X_n^{**} \mid \mathcal
+\mathcal{M}_n) \to^p 1$.  Lemma~\ref{res:B} establishes a stronger
+result necessary for partial sums.
+
+\begin{lem}\label{res:B}  
+  If the conditions of Theorem~\ref{res:C} hold then
+  $\var^{**}(m_n^{-1/2} \sum_{t=1}^{\lfloor \gamma m_n \rfloor}
+  X_{nt}^{**} \mid \mathcal{M}_n) \to^p \gamma$ for all
+  $\gamma \in [0,1]$.
+\end{lem}
+
+The crux of Lemma~\ref{res:B} is the recognition that
+$\var^{**}(m_n^{1/2} \bar{X}_n^{**} \mid \mathcal{M}_n)$ can be written as an
+average over squared blocks of consecutive observations of the
+original series;\footnote{Obviously, this argument needs to hold for
+  the partial sums as well, but I'll just discuss the overall average
+  for a clearer presentation.} i.e.
 \begin{equation}
-    \label{eq:7}
-    W_n^{*}(\gamma) = \tfrac{1}{\sqrt{n}}
-    \sum_{t=1}^{\lfloor \gamma n \rfloor} (X^*_{nt} - \mu_n^{*}) / \sigma_{n}^{*}
+  \var^{**}(m_n^{1/2} \bar{X}^{**}_n \mid \mathcal{M}_n) = n^{-1}
+  \sum_{\tau=1}^n \sum_{j=1}^{\lfloor n p_n \rfloor} Y_{n, \tau, j}^2
 \end{equation}
-  and 
-  \begin{equation}
-    \label{eq:7}
-    \hat{W}_n^{*}(\gamma) = \tfrac{1}{\sqrt{n}}
-    \sum_{t=1}^{\lfloor \gamma n \rfloor} (X^*_{nt} - \mu_n^{*}) / \hat\sigma_n^{*}.
-  \end{equation}
-  Then $\pr^{*}[\dist(W_n^{*}, W) > \delta] \to 0$ i.p. and
-  $\pr^{*}[\dist(\hat{W}_n^{*}, W) > \delta] \to 0$ i.p. for any
-  positive $\delta$ and distance $\dist$ that metricizes weak
-  convergence.
-\end{thm}
+where $Y_{n, \tau, j} = n^{-1/2}\sum_{t=I_{n,\tau,j-1}+1}^{I_{n,\tau,j}}
+(X_{nt} - \bar{X}_n)$ and $0 = I_{n,\tau,0} < I_{n,\tau,1} < \cdots <
+I_{n,\tau,\lfloor n p_n \rfloor} = m_n$ (the specifics are given in the
+proof and use different notation).  Standard arguments from
+\citet{Jon:97} establish that $\sum_j Y_{n,\tau,j}^2 \to^p 1$ for each
+$\tau$.
 
-Just as with Theorem~\ref{thm:1}, we have natural corollaries using
-Theorem~\ref{thm:2} to approximate the behavior of partial sums of the
-original series.  But applying this corollary requires much stronger
-assumptions.  In Corollary~\ref{cor:1}, the
-heterogeneity in $X_{nt}$ affects inference through the estimator of
-the asymptotic variance, $\hat{\sigma}_n^2$; but if the researcher
-has a consistent estimator of the variance, inference on the grand
-mean, $\bar{\mu}_{n}$, can proceed as normal.
-Assuming negligible heterogeneity in the means was unnecessary unless
-we want to avoid estimating $\sigma^2$ directly.
+As a final point, the consistency of the bootstrap variance 
+follows as a corollary to Lemmas~\ref{res:A} and~\ref{res:B}.
 
-But for the partial sum, a consistent estimator of the variance is not
-enough.  If the mean is not approximately constant then only the full
-summation is centered at the grand mean---the partial sums are
-centered at partial averages of the $\mu_{nt}$ terms.  If the research
-question concerns the individual $\mu_{nt}$'s then the bootstrap
-approximation can be used, but otherwise it can not.
-
-A second difference is that, if the $\mu_{nt}$ terms are approximately
-constant as in Corollary~\ref{cor:2}, the covariance process must
-still be consistently estimated.  The bootstrapped processes are
-(essentially) homoskedastic, so they are unable to match patterns of
-heteroskedasticity in the original series.  Those patterns must be
-removed by studentizing both the original and bootstrap partial sums.
-Other methods, such
-as the Local Block Bootstrap \citep{PaP:02,DPP:03}, may be able to
-capture this additional heterogeneity, but we do not pursue that
-possibility further.
-
-\begin{cor}
-  Suppose the conditions of Theorem~\ref{thm:1} hold, define
-  \begin{equation}
-    \label{eq:14}
-    \sigma_n^2(\gamma) = \tfrac{1}{n}
-    \sum_{s,t=1}^{\lfloor \gamma n \rfloor} \cov(X_{ns}, X_{nt}),
-  \end{equation}
-  let $\hat\sigma_n^2(\cdot)$ be an estimator of $\sigma_n^2(\cdot)$
-  such that $\sup_{\gamma} |\sigma_n^2(\gamma) /
-  \hat{\sigma}_n^2(\gamma) - 1| \to^p 0$, and let
-  \begin{equation}
-    \label{eq:8}
-    \hat{W}_n(\gamma) = \tfrac{1}{\sqrt{n}} \sum_{t=1}^{\lfloor \gamma
-      n \rfloor} (X_{nt} - \mu_{nt}) / \hat{\sigma}_{n}(\gamma).
-  \end{equation}
-  Then $\pr^{*}[\dist(W_n^{*}, \hat{W}_n) > \delta] \to^p 0$ and
-  $\pr^{*}[\dist(\hat{W}_n^{*}, \hat{W}_n) > \delta] \to^p 0$ for any
-  positive $\delta$ and any distance $\dist$ that metricizes weak
-  convergence.
-
-  Moreover, define 
-  \begin{align*}
-    \tilde W_n(\gamma) &= \tfrac{1}{\sqrt{n}} \sum_{t=1}^{\lfloor \gamma
-      n \rfloor} (X_{nt} - \bar \mu_{n}) / \hat{\sigma}_{n}(\gamma),
-&    \bar W_n(\gamma) &= \tfrac{1}{\sqrt{n}} \sum_{t=1}^{\lfloor \gamma
-      n \rfloor} (X_{nt} - \bar \mu_{n}) / \hat\sigma_n.
-  \end{align*}
-  If $\sup_t \mu_{nt}$ is $o(n^{-1/2})$ then
-  $\pr^{*}[\dist(\hat{W}_n^{*}, \tilde{W}_n) > \delta] \to^p 0$ and, if 
-  $\sup_\gamma | \sigma_n(\gamma) / \gamma \sigma - 1 | \to 0$, then
-  $\pr^{*}[\dist(\hat{W}_n^{*}, \bar{W}_n) > \delta] \to^p 0$.
+\begin{cor}\label{res:D}
+  If the conditions of Theorem~\ref{res:C} hold then
+  $\var^{*}(n^{1/2} \bar{X}_n^{*}) = \var(n^{1/2} \bar{X}_n) + o_p$.
 \end{cor}
 
-The rest of the paper presents the mathematical proof in detail.
-The key insight in these proofs is for the Stationary Bootstrap (other
+The key insight of this paper is for the stationary bootstrap (other
 block bootstraps arise as a special case).  After conditioning on the
@@
 expressed in terms of blocks of consecutive observations of the
-original series.\footnote{Although this paper focuses on the Moving Blocks,
-Circular, and Stationary Bootstraps, I expect that the results can be
-extended to other recent block bootstrap methods such as the Tapered Block
-Bootstrap \citep{PaP:01,PaP:02b} and the Extended Tapered Block Bootstrap
-\citep{Sha:10}.  Those extensions are left for future research.}
-Since convergence of these blocks is essential to
+original series.  Since convergence of these blocks is essential to
 the \clt\ in general,\footnote{See, for example, \citet{Mcl:74},
@@
 conjecture that the same approach will hold under most forms of
-dependence that allow for a \clt\ or \fclt.
+dependence that allow for a \clt\ or \fclt.  Finally, this result
+allows for considerable heterogeneity in the original process when
+approximating the distribution of a sample mean but not a partial sum.
 
@@
 
-\subsection*{Proof of Theorem~\ref{thm:1}}
-I will only present the proof for the Stationary Bootstrap, since it
-is the more difficult of the three.
-We can rewrite the sum of $X_{nt}^{*} - \mu_n^{*}$ as a sum of blocks:
-\begin{equation}\label{eq:1}
-  \tfrac{1}{\sqrt{n}} \sum_{t=1}^n (X_{nt}^{*} - \mu_n^{*}) = \sum_{j=1}^{J_n} \Big\{\tfrac{1}{\sqrt{n}} \sum_{t = K_{n,j-1} +
-    1}^{K_{nj}} (X_{nt}^{*} - \bar X_n)\Big\} \equiv 
-  \sum_{j=1}^{J_n} Z_{nj}^{*}.
-\end{equation}
-Now define $\mathcal{M}_{n}=\sigma(J_{n}, M_{n1},\dots,M_{nJ_n})$,
-$\mathcal{G}_{nj} = \sigma(Z_{n1}^{*},\dots, Z_{nj}^{*},
-X_{n1},\dots,X_{nn}, \mathcal{M}_n)$,
-  \begin{equation}\label{eq:18}
-    Z_n(\tau, m) = \tfrac{1}{\sqrt{n}} \sum_{t\in I_n(\tau, m)} (X_{nt} - \bar \mu_n),
-  \end{equation}
-$\nu_{nj}^2(\tau) = \E(Z_n(\tau, M_{nj})^2 \mid \mathcal M_n)$, and
-  \begin{equation}\label{eq:26}
-    \eta_n^{2} = \tfrac{1}{n} \sum_{\tau=0}^{n-1} \sum_{j=1}^{J_n} \nu_{nj}^2(\tau),
-  \end{equation}
-with
-\begin{equation}
-  \label{eq:3}
-  I_n(\tau, m) = \begin{cases}
-    \{\tau + 1,\dots, \tau + m\} & 0 \leq \tau \leq n - m \\
-    \{1,\dots, m - n + \tau\} \cup \{\tau + 1,\dots, n\} & n - m < \tau \leq n.
-  \end{cases}
-\end{equation}
-  Consequently $\{Z_{nj}^{*} / \eta_n, \mathcal{G}_{nj}\}$ is a martingale
-  difference array and
-\begin{equation}
-  \label{eq:6}
-  \pr^{*} \Big[ \sum_{j=1}^{J_n}
-  Z_{nj}^{*} / \eta_n \leq x \ \Big|\ \mathcal{M}_{n}\Big] - \Phi(x) \to^p 0
-\end{equation}
-for all $x$ if the following two conditions hold:
-\begin{equation}
-  \label{eq:13}
-  \sum_{j=1}^{J_n} \E^{*}\big( (Z_{nj}^{*2}/\eta_n^{2}) 1\{Z_{nj}^{*2}/\eta_n^{2}  >
-  \epsilon\} \ \big|\ \mathcal{M}_n\big) \to^p 0 \qquad \forall \epsilon > 0
+\section*{Appendix: Proofs and Supporting Results}
+\setcounter{section}{1}
+
+\begin{lema}\label{res:a4}
+  Let $\alpha_n(x)= 1 + ((x-1) \mod n)$, let $\mathcal{N}_n =
+  (M_{n1},\dots,M_{n,N_n})$, and suppose that the conditions of
+  Theorem~\ref{res:C} hold.  For any $t_0$ and $k$ such that the index
+  of the following summations are well defined,
+  \begin{equation}\label{eq:15}
+    \E^*\Bigg(\sum_{t=t_0+1}^{t_0+k} X_{nt}^* \;\Bigg|\;
+    \mathcal{N}_n\Bigg) = \E^{**}\Bigg(\sum_{t=t_0+1}^{t_0+k}
+    X_{nt}^{**} \;\Bigg|\; \mathcal{M}_n\Bigg) = k \bar{X}_n,
   \end{equation}
   and
+  \begin{align}
+    \var^*\Bigg(\sum_{t=t_0+1}^{t_0+k} X_{nt}^* \;\Bigg|\;
+    \mathcal{N}_n\Bigg) &= 
+    \var^{**}\Bigg(\sum_{t=t_0+1}^{t_0+k} X_{nt}^{**} \;\Bigg|\;
+    \mathcal{M}_n\Bigg) \nonumber
+    \\& = 
+    n^{-1} \sum_{\tau=1}^n \Bigg[ \Bigg\{\sum_{t=t_0 + 1}^{K_{n,\kappa_{n0}}}
+       (X_{n,\alpha_n(\tau+t)} - \bar{X}_n)\Bigg\}^2 \nonumber
+    \\ &\quad +  
+      \sum_{j=\kappa_{n0}+1}^{\kappa_{n1}-1}
+       \Bigg\{\sum_{t=K_{n,j -1}+1}^{K_{nj}}
+       (X_{n,\alpha_n(\tau+t)} - \bar{X}_n)\Bigg\}^2 \nonumber
+    \\ &\quad +
+       \Bigg\{\sum_{t=K_{n,\kappa_{n1} - 1} + 1}^{t_0 + k}
+       (X_{n,\alpha_n(\tau + t)} - \bar{X}_n) \Bigg\}^2 \Bigg] \label{eq:16} 
+  \end{align}
+  where $\kappa_{n0}$ and $\kappa_{n1}$ denote the blocks containing $t_0$
+  and $t_0 + k$, so $K_{n,\kappa_{n0} - 1} < t_0 \leq K_{n,\kappa_{n0}}$ and
+  $K_{n,\kappa_{n1} - 1} < t_0 + k \leq K_{n,\kappa_{n1}}$
+\end{lema}
+
+\begin{proof}[Proof of Lemma~\ref{res:a4}]
+  Equation~\eqref{eq:15} is immediate.  For~\eqref{eq:16}, notice that
+  \begin{multline}
+    \var^*\Bigg(\sum_{t=t_0+1}^{t_0+k} X_{nt}^* \;\Bigg|\;
+    \mathcal{N}_n\Bigg) = \var^{*}\Bigg( \sum_{t=t_0+1}^{K_{n,\kappa_{n0}}}
+    X_{nt}^* \;\Bigg|\; \mathcal{N}_n \Bigg) 
+    \\ 
+    + \sum_{j=\kappa_{n0} + 1}^{\kappa_{n1} - 1} \var^{*}\Bigg(
+    \sum_{t=K_{n,j-1}+1}^{K_{nj}} X_{nt}^* \;\Bigg|\; \mathcal{N}_n
+    \Bigg) + \var^{*}\Bigg( \sum_{t=K_{n,\kappa_{n1} - 1}+1}^{t_0 + k}
+    X_{nt}^* \;\Bigg|\; \mathcal{N}_n \Bigg),
+  \end{multline}
+  since the blocks are independent given $\mathcal{N}_n$.  Now, for
+  each block,
   \begin{equation}
-  \label{eq:4}
-  \pr^{*}\Big[\ \Big|\sum_{j=1}^{J_n} Z_{nj}^{*2}/ \eta_n^{2} - 1
-  \Big|\ > \epsilon \ \Big|\ \mathcal{M}_n \Big] \to^p 0 \qquad \forall \epsilon > 0,
+    \var^{*}\Bigg(
+    \sum_{t=K_{n,j-1}+1}^{K_{nj}} X_{nt}^* \;\Bigg|\; \mathcal{N}_n
+    \Bigg) = n^{-1} \sum_{\tau=1}^n 
+    \Bigg\{\sum_{t=K_{n,j -1}+1}^{K_{nj}} (X_{n,\alpha_n(\tau+t)} -
+    \bar{X}_n)\Bigg\}^2,
   \end{equation}
-since~\eqref{eq:13} and~\eqref{eq:4} ensure that $Z_{nj}^{*}/\eta_n$ obeys a
-martingale difference \clt\ \citep[e.g.][Theorem
-3.3]{HaH:80}.
+  with similar formulae for the first and last blocks.
+  The same argument holds for $\var^{**}$, completing the proof.
+\end{proof}
 
-First we will prove
-\begin{equation}\label{eq:41}
-  \E\Big[ \sum_{j=1}^{J_n} \E^{*}\big((Z_{nj}^{*2} / \eta_n^2) 1\{
-  Z_{nj}^{*2} / \eta_n^2 > \epsilon\} \mid \mathcal{M}_n\big) \ \Big|\
-  \mathcal{M}_n\Big] \to^p 0,
-\end{equation}
-which implies~\eqref{eq:13}.  Note that
-\begin{equation*}
-  \E^{*}(g(Z_{nj}^{*}) \mid \mathcal{M}_n) = \tfrac{1}{n}
-  \sum_{\tau=0}^{n-1} g(Z_n(\tau, M_{nj}))
-\end{equation*}
-almost surely for any function $g$.  As a consequence, we can write
-\begin{multline}\label{eq:32}
-  \E\Big( \sum_{j=1}^{J_n} \E^{*}\big( (Z_{nj}^{*2}/\eta_n^{2})
-  1\{Z_{nj}^{*2}/\eta_n^{2} > \epsilon\} \ \big|\ \mathcal{M}_n\big)
-  \ \Big|\ \mathcal{M}_{n} \Big)
-  \\\begin{split}= \tfrac{1}{n} \sum_{\tau=0}^{n-1} \sum_{j=1}^{J_n} &
-     \frac{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n}{\eta_n^2}
-  \E\Bigg( \frac{Z_n(\tau, M_{nj})^2}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n} 
-  \\ & \times 1\Bigg\{\frac{Z_n(\tau, M_{nj})^2}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n} 
-  > \frac{\eta_n^2 \epsilon}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n}\Bigg\} 
-  \ \Bigg|\ \mathcal{M}_n \Bigg)
-\end{split}
-\end{multline}
-almost surely.  Lemma~\ref{res:L} implies that there exists a finite,
-monotone function $B(\cdot)$ such that $B(x) \to 0$ as $x \to \infty$
-and
-\begin{multline*}
-\E\Bigg( \frac{Z_n(\tau, M_{nj})^2}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n}
-  \times 1\Bigg\{\frac{Z_n(\tau, M_{nj})^2}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n} > \frac{\eta_n^2 \epsilon}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n}\Bigg\} 
-  \ \Bigg|\ \mathcal{M}_n \Bigg) \\
-  \leq B\Bigg(\frac{\eta_n^2\epsilon}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n}\Bigg)
-\end{multline*}
-almost surely for all $n$, $j$, and $\tau$.  Consequently, the right
-side of~\eqref{eq:32} is bounded by
-\begin{equation*}
-\tfrac{1}{n} \sum_{\tau=0}^{n-1} \sum_{j=1}^{J_n} 
-\frac{\nu_{nj}^2(\tau) + \sigma^2 M_{nj}/n}{\eta_n^2} B\Bigg(\frac{\eta_n^2
-  \epsilon}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n}\Bigg)
-\end{equation*}
-a.s., and this quantity is a.s. less than
-\begin{equation*}
-  O_{a.s.}(1) \max_{\tau = 0,\dots,n-1} \max_{j=1,\dots,J_n} B\Bigg(\frac{\eta_n^2\epsilon}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n}\Bigg)
-\end{equation*}
-by definition.  Moreover
-\[\max_{\tau=0,\dots,n-1} \max_{j=1,\dots,J_n} B\Bigg(\frac{\eta_n^2 \epsilon}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n}\Bigg)
-= B\Bigg(\min_{\tau=0,\dots,n-1} \min_{j=1,\dots,J_n} \frac{\eta_n^2 \epsilon}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n}\Bigg)\]
-a.s. by monotonicity, and
-\begin{equation*}
-  \min_{\tau=0,\dots,n-1} \min_{j=1,\dots,J_n} \frac{\eta_n^2}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n} \to^p \infty
-\end{equation*}
-by Lemmas~\ref{res:a1}, \ref{res:16},
-and~\ref{res:B}, completing the proof of \eqref{eq:41}.
-For~\eqref{eq:4},
-\begin{equation*}
-  \sum_{j=1}^{J_n} Z_{nj}^{*2} = \eta_n^2 + \sum_{j=1}^{J_n}
-  \big(Z_{nj}^{*2} - \E^*(Z_{nj}^{*2} \mid \mathcal{M}_n)\big) +
-  \tfrac{1}{n} \sum_{\tau=0}^{n-1} \sum_{j=1}^{J_n} \big(Z_{n}(\tau,
-  M_{nj})^2 - \nu_{nj}^2(\tau)\big) \qquad
-  \text{a.s.}.
-\end{equation*}
-The first summation on the right is $o_p(\eta_n^2)$ by
-Lemma~\ref{res:H} and the second is $o_p(\eta_n^2)$ by
-Lemma~\ref{res:B}.
-
-The Dominated Convergence Theorem then ensures that
-\begin{equation}\label{eq:39}
-  \pr^{*} \Big[\sum_{j=1}^{J_n}
-  Z_{nj}^{*} / \eta_n \leq x \Big] - \Phi(x) \to^p 0.
-\end{equation}
-Lemma~\ref{res:B} proves that $\sigma_n^{*}/\eta_n \to^p 1$ and
-$\hat{\sigma}_n^{*}/\eta_n \to^p 1$, so
-\begin{equation}
-  \label{eq:17}
-  \pr^{*}\big[\sqrt{n}(\bar X_{n}^{*} - \mu_{n}^{*}) / \sigma_n^{*}
-  \leq x\big] \to^p \Phi(x)
-\end{equation}
-and
-\begin{equation}
-  \label{eq:17}
-  \pr^{*}\big[\sqrt{n}(\bar X_{n}^{*} - \mu_{n}^{*}) / \hat\sigma_n^{*}
-  \leq x\big] \to^p \Phi(x)
-\end{equation}
-for any $x$.  These results are sufficient for~\eqref{eq:30}
-and~\eqref{eq:9} since the Normal distribution is continuous
-\citep[see, for example,][Lemma 2.11]{Vaa:00}.\qed
-
-\subsection*{Proof of Theorem~\ref{thm:2}}
-Again, I will only present a proof for the Stationary Bootstrap.
-The proof follows that of \citet{JoD:00b} closely and notation is reused from the
-proof of Theorem~\ref{thm:1}.  Lemma~\ref{res:B} implies that
-$\pr^{*}[\dist(W_n^{*}, W) > \delta] \to^p 0$ is sufficient for all of Theorem~\ref{thm:2}'s
-conclusions
-  \begin{equation*}
-    W_n^{*}(\gamma) = \tfrac{1}{\sqrt{n}} \sum_{t=1}^{\lfloor \gamma n
-      \rfloor} (X^{*}_{nt} - \mu_n^{*})/\eta_{n}.
-  \end{equation*}
-  From Theorem~\ref{thm:1}, we know that
-  \begin{equation*}
-    (W^{*}_n(\gamma_1),\dots, W^{*}_n(\gamma_l)) \to^d
-    (W(\gamma_1),\dots,W(\gamma_l))
-  \end{equation*}
-  in probability for any finite $l$ and $\gamma_1,\dots,\gamma_l \in
-  [0,1]$, so the result holds if $W_n^{*}(\gamma)$ is stochastically
-  equicontinuous and if the increments of $W^{*}_n(\cdot)$ are
-  independent in the limit \citep[Theorems~15.4 and~15.5]{Bil:68}.
-
-  Stochastic equicontinuity requires that
-  \begin{equation}\label{eq:22} 
-    \lim_{\delta \to 0} \limsup_{n \to \infty} \E\Big( \pr^{*}\Big[\sup_{\gamma
-    \in [0,1]} \sup_{\gamma' \in (\gamma-\delta, \gamma+\delta) \cap
-    [0,1]]} |W_n^{*}(\gamma) - W_n^{*}(\gamma')| >
-  \epsilon \ \Big|\ \mathcal{M}_n \Big]\Big) = 0.
-  \end{equation}
-  By construction,
-  \begin{equation*}
-    W_n^*(\gamma) = \sum_{j=1}^{\lfloor \gamma J_n \rfloor} Z_{nj}^*  +
-    \big(1 - 2 \times 1\{ \gamma n \leq K_{n, \lfloor \gamma J_n \rfloor}\}\big)
-    \sum_{t \in L_n(\gamma)} (X_{nt}^* - \mu_{nt}^*)
-  \end{equation*}
-  where 
-  \[L_n(\gamma) =
-  \{\min(K_{n,\lfloor \gamma J_n \rfloor}, \lfloor n \gamma \rfloor) + 1,\dots,
-  \max(K_{n,\lfloor \gamma J_n \rfloor}, \lfloor n \gamma \rfloor)\},
-  \]
-  so we have the upper bound
-  \begin{align}\label{eq:27}
-    \E \Big(\pr^{*}\Big[&\sup_{\gamma \in [0,1]} \sup_{\gamma' \in
-      (\gamma-\delta, \gamma+\delta) \cap [0,1]]}
-    |W_n^{*}(\gamma) - W_n^{*}(\gamma')| > \epsilon \
-    \Big|\ \mathcal{M}_n \Big]\Big) \nonumber \\
-    &\leq \E \Big(\pr^{*} \Big[\sup_{\gamma \in [0,1]} \sup_{\gamma' \in
-      (\gamma, \gamma+2\delta) \cap [0,1]]} \Big\lvert
-    \sum_{j={\lfloor \gamma J_n \rfloor}}^{\lfloor \gamma'J_n \rfloor}
-    Z_{nj}^{*}/ \eta_n \Big\rvert > \epsilon \
-    \Big|\ \mathcal{M}_n \Big]\Big) \nonumber \\
-    &\quad+ 2 \E \Big(\pr^{*} \Big[\sup_{\gamma \in [0,1]} \Big\lvert
-    \tfrac{1}{\sqrt{n}} \sum_{t \in L_n(\gamma)} (X_{nt}^{*} -
-    \mu_n^{*}) / \eta_{n}\Big\rvert > \epsilon \ \Big|\ \mathcal{M}_n \Big]\Big).
-  \end{align}
-  Just as in Theorem~\ref{thm:1}, $Z_{nj}^{*}/\eta_n$ is a martingale
-  difference array conditional on $\mathcal{M}_n$, and so
-  \begin{equation*}
-    \E \Big(\pr^{*} \Big[\sup_{\gamma \in [0,1]} \sup_{\gamma' \in
-      (\gamma, \gamma+2\delta) \cap [0,1]]} \Big\lvert 
-    \sum_{j={\lfloor \gamma J_n \rfloor}}^{\lfloor \gamma'J_n \rfloor}
-    Z_{nj}^{*} / \eta_n \Big\rvert > \epsilon \
-    \Big|\ \mathcal{M}_n \Big]\Big) \leq \tfrac{C \delta}{\epsilon} \E\big(\sigma_n^{*2}/\eta_n^2\big)
-  \end{equation*}
-  for some finite $C$ that does not depend on $n$ \citep[using,
-  e.g.][Theorem~15.14]{Dav:94}. And Lemmas~\ref{res:L} and~\ref{res:B}
-  imply that
-  \begin{equation*}
-    \lim_{\delta \to 0}\limsup_{n\to\infty}  \tfrac{C \delta}{\epsilon} \E(\sigma_n^{*} /
-    \eta_n) = 0.
-  \end{equation*}
-
-  The second term in \eqref{eq:27} is a.s. equal to
-  \begin{equation*}
-    \E\Big( \tfrac{2}{n} \sum_{\tau=0}^{n-1} \pr\Big[\sup_{\gamma \in
-      [0,1]} \Big\lvert \tfrac{1}{\eta_n \sqrt{n}} \sum_{t \in I(\tau, |\lfloor
-      \gamma n \rfloor - K_{n,\lfloor \gamma J_n \rfloor}|)} (X_{nt} -
-    \bar X_n) \Big\rvert > \epsilon \ \Big|\ \mathcal{M}_n\Big]\Big)
-  \end{equation*}
-  since the $X_{nt}^{*}$'s are all in the same ``block'' by
-  construction, and this quantity is a.s. bounded by
-  \begin{multline}\label{eq:24}
-    2 \max_{\tau=0,\dots,n-1} \E \Big(\pr\Big[\sup_{\gamma \in [0,1]} \Big\lvert
-    \tfrac{1}{\eta_n \sqrt{n}} \sum_{t \in I(\tau, |\lfloor \gamma n
-      \rfloor - K_{n,\lfloor \gamma J_n \rfloor}|)} (X_{nt} -
-    \mu_{nt}) \Big\rvert > \epsilon \ \Big|\ \mathcal{M}_n\Big]\Big) \\+ 2
-    \max_{\tau=0,\dots,n-1}\E \Big(\pr\Big[\sup_{\gamma \in [0,1]} \Big\lvert
-    \tfrac{1}{\eta_n \sqrt{n}} \sum_{t \in I(\tau, |\lfloor \gamma n
-      \rfloor - K_{n,\lfloor \gamma J_n \rfloor}|)} (\mu_{nt} - \bar
-    \mu_n) \Big\rvert > \epsilon \ \Big|\ \mathcal{M}_n\Big]\Big) \\+ 2
-    \max_{\tau=0,\dots,n-1}\E\Big( \pr\Big[\sup_{\gamma \in [0,1]} \Big\lvert
-    \tfrac{1}{\eta_n \sqrt{n}} \sum_{t \in I(\tau, |\lfloor \gamma n
-      \rfloor - K_{n,\lfloor \gamma J_n \rfloor}|)} (\bar \mu_{n} -
-    \bar X_n) \Big\rvert > \epsilon \ \Big|\ \mathcal{M}_n\Big]\Big).
-  \end{multline}
-  Lemma~\ref{res:B} implies that $\eta_n^{-1} = O_p(n^{-1/2})$ and the
-  \lln\ implies that $K_{n,\lfloor \gamma J_n\rfloor}/n$ converges
-  i.p.  to $\gamma$.  Consequently, the first term converges to zero
-  i.p. since the partial sums of $X_{nt} - \mu_{nt}$ obey an \fclt, the
-  second term converges to zero i.p. since $\mu_{nt}-\bar{\mu}_n$ is
-  bounded, and the third term converges to zero i.p. since $\bar{X}_n
-  - \bar{\mu}_n = O_p(n^{-1/2})$, proving~\eqref{eq:22}.
-
-  Since the increments of $W_n^{*}$ are asymptotically normal, we can
-  prove asymptotic independence by proving that the covariance between
-  any two distinct increments converges to zero.  Take $i < j$ and
-  define $i'$, $j'$, $i''$, and $j''$ so that
-  \begin{align*}
-    \gamma_{i-1} n &\in [K_{n,i'-1}+1,K_{n,i'}] & \gamma_{i} n &\in [K_{n,i''-1}+1,K_{n,i''}]\\
-    \gamma_{j-1} n &\in [K_{n,j'-1}+1,K_{n,j'}] & \gamma_{j} n &\in [K_{n,j''-1}+1,K_{n,j''}].
-  \end{align*}
-  Then the covariance between $W_n^*(\gamma_i) - W_n^*(\gamma_{i-1})$
-  and $W_n^*(\gamma_j) - W_n^*(\gamma_{j-1})$ equals
-  \begin{multline}\label{eq:15}
-    \E^*((W_n^*(\gamma_i) - W_n^*(\gamma_{i-1}))
-    (W_n^*(\gamma_j) - W_n^*(\gamma_{j-1}))\mid \mathcal{M}_n) =\\
-    \begin{split}
-      \E^*\Big(&\Big(\tfrac{1}{\eta_n\sqrt{n}} \sum_{t=\lfloor \gamma_{i-1} n \rfloor + 1}^{K_{ni'}} (X_{nt}^{*} - \mu_n^{*}) 
-    + \tfrac{1}{\eta_n} \sum_{k=i'+1}^{i''-1} Z_{nk}^{*} + \tfrac{1}{\eta_n \sqrt{n}} \sum_{t=K_{n,i''-1}+1}^{\lfloor \gamma_i n \rfloor} (X_{nt}^{*} - \mu_n^{*})\Big) \\
-    &
-      \times \Big(\tfrac{1}{\eta_n\sqrt{n}} \sum_{t=\lfloor \gamma_{j-1} n \rfloor + 1}^{K_{nj'}} (X_{nt}^{*} - \mu_n^{*}) 
-    + \tfrac{1}{\eta_n} \sum_{k=j'+1}^{j''-1} Z_{nk}^{*} 
-  \end{split}\\
-  + \tfrac{1}{\eta_n \sqrt{n}} \sum_{t=K_{n,j''-1}+1}^{\lfloor
-    \gamma_j n \rfloor} (X_{nt}^{*} - \mu_n^{*})\Big) \ \Big|\
-  \mathcal{M}_n \Big)
-\end{multline}
-  almost surely (with obvious modifications if $i' = i''$ or $j' =
-  j''$).  Since the blocks are independent under the bootstrap-induced
-  probability measure, the right side of~\eqref{eq:15} equals
-  \begin{equation*}
-    \E^{*}\Big( \tfrac{1}{\eta_n^2 n} \sum_{s=K_{n,i''-1}+1}^{\lfloor \gamma_i n \rfloor} (X_{ns}^{*} - \mu_n^{*})
-    \sum_{t=\lfloor \gamma_{j-1} n \rfloor + 1}^{K_{nj'}} (X_{nt}^{*} - \mu_n^{*}) \ \Big|\ \mathcal{M}_n\Big) 1\{K_{ni''} = K_{nj'} \}
-  \end{equation*}
-  which is almost surely bounded in absolute value by
-  \begin{equation*}
-     \E^{*}\Big(\Big( \tfrac{1}{\eta_n \sqrt{n}} \sum_{s=K_{n,i''-1}+1}^{\lfloor \gamma_i n \rfloor} (X_{ns}^{*} - \mu_n^{*})\Big)^2 \ \Big|\ \mathcal{M}_n\Big)^{1/2}
-     \E^{*}\Big(\Big( \tfrac{1}{\eta_n \sqrt{n}} \sum_{t=\lfloor \gamma_{j-1} n \rfloor+1}^{K_{n,j'}} (X_{nt}^{*} - \mu_n^{*})\Big)^2 \ \Big|\ \mathcal{M}_n\Big)^{1/2}.
-  \end{equation*}
-  Each of these terms converges to zero in probability as before, completing the proof.
- \qed
-
-\section{Supplemental results}
-As in the proofs of Theorems~\ref{thm:1} and~\ref{thm:2}, we only
-present the proofs for the Stationary Bootstrap as those for the
-Circular and Moving Block bootstraps are similar but less complicated.
-
-\begin{lem}\label{res:a1}
-  Suppose that $M_{n1}, M_{n2},\dots$ are i.i.d. geometric random
-  variables with success parameter $p_n = c n^{-a}$ with $a, c \in
-  (0,1)$, and that $\ell_n = (p_n \log p_n^{-1})^{-1}$ and define
-  $J_n$ so that $\sum_{i=1}^{J_n-1} < n \leq \sum_{i=1}^{J_n} M_{ni} $
-  Then 
-  \begin{enumerate}
-  \item $\max_{i=1,\dots,\lfloor C n p_n \rfloor} M_{ni} / n \to^p 0$
-    for any positive $C$,
-  \item $\max_{i=1,\dots,J_n} M_{ni} / n \to^p 0$,
-  \item $\max_{i=1,\dots,  \lfloor C n p_n \rfloor} M_{ni} /
-  \ell_n^{1+\epsilon} \to^p 0$ as $n \to \infty$ for any positive
-  $\epsilon$ and $C$, and
-  \item $\max_{i=1,\dots,J_n} M_{ni} /
-  \ell_n^{1+\epsilon} \to^p 0$ as $n \to \infty$ for any positive
-  $\epsilon$.
-  \end{enumerate}
-\end{lem}
+\begin{lema}\label{res:a1}
+  Suppose that $M_{n1},\dots,M_{n,\lfloor n p_n \rfloor}$ are
+  i.i.d. geometric random variables with success parameter $p_n = c
+  n^{-a}$ with $a, c \in (0,1)$, and that $\ell_n = (p_n \log
+  p_n^{-1})^{-1}$.  Then (i) $\max_{i=1,\dots,\lfloor n p_n \rfloor}
+  M_{ni} / n \to^p 0$ and (ii) $\max_{i=1,\dots,\lfloor n p_n \rfloor}
+  M_{ni} / \ell_n^{1+\epsilon} \to^p 0$ as $n \to \infty$ for any
+  positive $\epsilon$.
+\end{lema}
 
 \begin{proof}[Proof of Lemma~\ref{res:a1}]
-  To prove part 1, observe that, for any increasing positive sequence
-  $x_n$ such that $x_n p_n \to \infty$,
-  \begin{equation*}
-    \pr\Big[\max_{i=1,\dots, \lfloor C n p_n \rfloor} M_{ni} \leq x_n\Big] =
-    (1 - (1 - p_n)^{x_n})^{\lfloor C n p_n \rfloor} \to \lim \exp(-C n p_n (1 - p_n)^{x_n})
-  \end{equation*}
-  and $C n p_n (1 - p_n)^{x_n} \to \lim C n p_n e^{-x_n p_n}$. Now, let
-  $x_n = n x$ for any positive number $x$.  Then
-  \begin{equation*}
-    \pr\Big[\max_{i=1,\dots,\lfloor C n p_n \rfloor} M_{ni}/n \leq x \Big] \to
-    \lim \exp(-C n p_n e^{-n p_n x}) =
+  We know that, for any increasing positive sequence $x_n$ such that
+  $x_n p_n \to \infty$,
+  \begin{equation}
+    \pr[\max_i M_{ni} \leq x_n] =
+    (1 - (1 - p_n)^{x_n})^{\lfloor n p_n \rfloor} \to \lim \exp(- n p_n (1 - p_n)^{x_n}).
+  \end{equation}
+  Moreover, $n p_n (1 - p_n)^{x_n} \to \lim n p_n e^{-x_n p_n}$.  To
+  prove (i), let $x_n = n x$ for any positive number $x$.  Then
+  \begin{equation}
+    \pr[\max_i M_{ni}/n \leq x ] \to \lim \exp(-n p_n e^{-n p_n x}) =
     \exp(0) = 1.
-  \end{equation*}
-  Since $x$ is arbitrary, $\max_{i=1,\dots,\lfloor C n p_n \rfloor} M_{ni} / n \to^p 0$.
+  \end{equation}
+  Since $x$ is arbitrary, $\max_i M_{ni} / n \to^p 0$.
 
-  For part 2, take $C$ to be an arbitrary constant strictly greater
-  than one. For any $x$,
-  \begin{align*}
-    \pr\Big[\max_{i=1,\dots,J_n} M_{ni} > x\Big] & \leq
-    \pr\Big[\max_{i=1,\dots,\lfloor C n p_n \rfloor} M_{ni} > x \text{ or
-    } J_n > \lfloor C n p_n \rfloor\Big] \\
-    & \leq \pr\Big[\max_{i=1,\dots,\lfloor C n p_n \rfloor} M_{ni} > x\Big]
-    + \pr\Big[\sum\nolimits_{i=1}^{\lfloor C n
-      p_n \rfloor} M_{ni} < n \Big]
-  \end{align*}
-  The first term converges to zero by part 1 and the second term by
-  the \lln.
-
-  For part 3, let $x_n = \ell_n^{1 + \epsilon} x$ and note that 
-  \begin{equation*}
+  For (ii), let $x_n = \ell_n^{1 + \epsilon} x$ and note that 
+  \begin{equation}
     p_n \ell_n^{1+\epsilon} \geq p_n^{-(\epsilon-\delta-\epsilon\delta)} =
@@
       - \delta - \epsilon\delta)}
-  \end{equation*}
+  \end{equation}
   for any $\delta > 0$ and large enough $n$.  Choose $\delta$ small
   enough that $\epsilon > \delta(1 +\epsilon)$. Then
-  \begin{equation*}
+  \begin{equation}
     n p_n \exp(-\ell_n^{1+\epsilon} p_n) \leq n p_n
@@
     \exp(-b v_n) \to 0,
-  \end{equation*}
+  \end{equation}
   with $v_n = n^{a(\epsilon-\delta-\epsilon\delta)}$.  Consequently,
-  \begin{equation*}
+  \begin{equation}
     \pr[\max_i M_{ni}/\ell_n^{1+\epsilon} \leq x ] \to \exp(0) = 1
-  \end{equation*}
+  \end{equation}
   as well.
-
-  The proof of part 4 is the same as part 2, making the obvious
-  substitutions.
 \end{proof}
 
-The next result is identical to \citepos{Mcl:75} Theorem~1.6, but is
-stated for conditional expectations so that it is relevant for our
-bootstrap results. The proof is identical to the original.
-\begin{lem}\label{res:16}
-  Let $\{\mathcal{G}_n\}$ be a sequence of $\sigma$-fields,
-  $\{\mathcal{F}_{nt}\}$ an array of $\sigma$-fields such that
-  $\mathcal{G}_n \subset \mathcal{F}_{nt}$ for each $n$ and $t$, and
-  suppose that $\{X_{nt}\}$ is an array such that
-  \begin{equation*}
-    \E\big(\big( \E( X_{nt} \mid \mathcal{F}_{n,t-m} \big)^2 \ \big|\
-    \mathcal{G}_n\big)^{1/2} \leq \psi_m c_{nt}
-  \end{equation*}
-  and
-\begin{equation*}
-  \E\big(\big(X_{nt} - \E( X_{nt}\mid F_{n,t+m}) \big)^2 \ \big|\
-  \mathcal{G}_n\big)^{1/2} \leq \psi_{m+1} c_{nt}  
-\end{equation*}
-almost surely, with $\psi_m = O(m^{-1/2-\delta})$ for some positive
-$\delta$ and $c_{nt} \in \mathcal{G}_n$ for every $n$ and $t$.  Then
-there exists a sequence of random variables $\Delta_n \in
-\mathcal{G}_n$ such that $\Delta_n = O_p(1)$ and
-\begin{equation}\label{eq:40}
-  \E\Big( \max_{u \leq s, t \leq v} \Big(\sum_{w=s}^t X_{nw}\Big)^2 \ \Big|\
-  \mathcal{G}_n\Big) \leq \Delta_n \sum_{t=u}^v c_{nt}^2
-\end{equation}
-almost surely.
-\end{lem}
+\begin{lema}\label{res:a3}
+  Suppose that the conditions of Lemma~\ref{res:A} hold.  Then the
+  family of random variables $\big\{\big(k^{-1/2} \sum_{t=t_0 + 1}^{t_0+k}
+  X_{nt} \big)^2\big\}_{t_0,k > 0}$ is uniformly integrable.
+\end{lema}
 
-\begin{lem}\label{res:L}
-  Define $Z_n(\tau,m)$ as in Equation~\eqref{eq:18}.  Under the
-  conditions of Theorem~\ref{thm:1}, the family
-  \begin{equation*}
-    \Bigg\{\frac{Z_{n}(\tau,m)^2}{\E
-  Z_n(\tau,m)^2 + \sigma^2 m / n}\ ;\quad \tau, m, n\Bigg\}
-  \end{equation*}
- is uniformly integrable.
-\end{lem}
-\begin{proof}
-  We can write 
-  \begin{multline}\label{eq:35}
-    Z_n(\tau, m)^2 = \big(Y_n(\tau, m) + \tfrac{m}{\sqrt{n}}
-    (\bar{\mu}_n - \bar{X}_n) \big)^2 + \Big(\tfrac{1}{\sqrt{n}}\sum_{t \in I_n(\tau,m)} (\mu_{nt} - \bar{\mu}_n)\Big)^2\\
-    + 2 \big(Y_n(\tau, m) + \tfrac{m}{\sqrt{n}} (\bar{\mu}_n - \bar{X}_n)\big)
-    \Big(\tfrac{1}{\sqrt{n}}\sum_{t \in I_n(\tau,m)} (\mu_{nt} - \bar{\mu}_n)\Big)
-  \end{multline}
-  almost surely, with 
-  \begin{equation}\label{eq:28}
-    Y_n(\tau, m) = \tfrac{1}{\sqrt{n}} \sum_{t \in
-      I_n(\tau, m)} (X_{nt} - \mu_{nt}).
-  \end{equation}
-  Then the conclusion holds if
-  \begin{equation}\label{eq:34}
-    \frac{\big(\sqrt{n} Y_n(\tau, m) + m (\bar{\mu}_n - \bar{X}_n) \big)^2}
-    {\E \big(\sqrt{n} Y_n(\tau,m) + m (\bar{\mu}_n - \bar{X}_n)\big)^2  
-    + \big(\sum_{t \in I_n(\tau,m)} (\mu_{nt} - \bar{\mu}_n)\big)^2 + m \sigma^2},
+\begin{proof}[Proof of Lemma~\ref{res:a3}]
+Follows the same argument as in de Jong (1997) or Davidson's papers.
+Need to fill in later.
+\end{proof}
+
+\begin{lema}\label{res:a4}
+  Let $\alpha_n(x)= 1 + ((x-1) \mod n)$ and suppose that the
+  conditions of Lemma~\ref{res:A} hold.  For any $t_0,k > 0$,
+  \begin{equation}\label{eq:15}
+    \E^*\Bigg(\sum_{t=t_0+1}^{t_0+k} X_{nt}^* \;\Bigg|\;
+    \mathcal{M}_n\Bigg) = \E^{**}\Bigg(\sum_{t=t_0+1}^{t_0+k}
+    X_{nt}^{**} \;\Bigg|\; \mathcal{M}_n\Bigg) = k \bar{X}_n,
   \end{equation}
   and
-  \begin{equation}\label{eq:33}
-    \frac{\big(\sum_{t \in I_n(\tau,m)} (\mu_{nt} - \bar{\mu}_n)\big)^2}
-    {\E \big(\sqrt{n} Y_n(\tau,m) + m (\bar{\mu}_n - \bar{X}_n) \big)^2  +\big(\sum_{t \in I_n(\tau,m)} (\mu_{nt} - \bar{\mu}_n)\big)^2 + \sigma^2}
+  \begin{multline}\label{eq:16} 
+    \var^*\Bigg(\sum_{t=t_0+1}^{t_0+k} X_{nt}^* \;\Bigg|\;
+    \mathcal{M}_n\Bigg) = 
+    \var^{**}\Bigg(\sum_{t=t_0+1}^{t_0+k} X_{nt}^{**} \;\Bigg|\;
+    \mathcal{M}_n\Bigg) 
+    \\
+     = n^{-1} \sum_{\tau=1}^n \Bigg[ \Bigg\{\sum_{t=1}^{K_{\kappa_0}-t_0}
+       (X_{n,\alpha_n(\tau+t)} - \bar{X}_n)\Bigg\}^2 +  \sum_{j=\kappa_0+1}^{\kappa_1-1}
+       \Bigg\{\sum_{t=K_{j -1}-t_0+1}^{K_{j}-t_0}
+       (X_{n,\alpha_n(\tau+t)} - \bar{X}_n)\Bigg\}^2  +
+       \Bigg\{\sum_{t=K_{\kappa_1 - 1} - t_0 + 1}^{K_{\kappa_1}}
+       (X_{nt} - \bar{X}_n) \Bigg\}\Bigg]
+  \end{multline}
+  (the indices need to be worked out better).
+\end{lema}
+
+\begin{proof}[Proof of Lemma~\ref{res:a4}]
+  Equation~\eqref{eq:15} is immediate.  For~\eqref{eq:16}, let
+  $\kappa_0$ and $\kappa_1$ be the indices of the blocks containing
+  $s_0+1$ and $s_0 + k$, i.e. such that $K_{\kappa_0 - 1} < s_0 + 1
+  \leq K_{\kappa_0}$ and $K_{\kappa_1 - 1} < s_0 + k \leq
+  K_{\kappa_1}$.  Then
+  \begin{multline}
+    \var^*\Bigg(\sum_{t=t_0+1}^{t_0+k} X_{nt}^* \;\Bigg|\;
+    \mathcal{M}_n\Bigg) = \var^{*}\Bigg( \sum_{t=t_0+1}^{K_{\kappa_0}}
+    X_{nt}^* \;\Bigg|\; \mathcal{M}_n \Bigg) 
+    \\ 
+    + \sum_{j=\kappa_0 + 1}^{\kappa_1 - 1} \var^{*}\Bigg(
+    \sum_{t=K_{j-1}+1}^{K_{j}} X_{nt}^* \;\Bigg|\; \mathcal{M}_n
+    \Bigg) + \var^{*}\Bigg( \sum_{t=K_{\kappa_1 - 1}+1}^{K_{\kappa_1}}
+    X_{nt}^* \;\Bigg|\; \mathcal{M}_n \Bigg),
+  \end{multline}
+  since the blocks are independent given $\mathcal{M}_n$.  Now, for
+  each block,
+  \begin{equation}
+    \var^{*}\Bigg(
+    \sum_{\tau=K_{j-1}+1}^{K_{j}} X_{nt}^* \;\Bigg|\; \mathcal{M}_n
+    \Bigg) = n^{-1} \sum_{t=1}^n 
+    \Bigg\{\sum_{t=K_{\kappa_j -1}+1}^{K_{\kappa_j}} (X_{n,\alpha_n(\tau+t)} -
+    \bar{X}_n)\Bigg\}^2,
   \end{equation}
-  are all uniformly integrable.  But $\tfrac{n}{m} Y_n(\tau, m)^2$ and
-  $n (\bar{\mu_n} - \bar X_n)^2$ are uniformly integrable by existing
-  results \citep{Dav:92,Dav:93,Jon:97} and~\eqref{eq:33} is bounded
-  above by construction, completing the proof.
+  with similar formulae for the first and last blocks.
+  The same argument holds for $\var^{**}$, completing the proof.
 \end{proof}
 
-\begin{lem}\label{res:H}
-  Suppose the conditions of Theorem~\ref{thm:1} hold and define
-  $Z_{nj}^{*}$ and $\eta_n^2$ as in Equations~\eqref{eq:18}
-  and~\eqref{eq:26}. Then
+\begin{lema}\label{res:a5}
+  Suppose the conditions of Theorem~\ref{res:C} hold, let $\ell_n = (p
+  \log p^{-1})^{-1}$, and define $Z_{nj}^C(\tau, \mathcal{M}_n)$,
+  $M_{nj}(\tau)$, and $K_{nj}(\tau)$ as in the proof of
+  Lemma~\ref{res:B}. Now let $J_n$ be the number of block lengths
+  $M_{nj}(\tau)$ that are greater that $\ell_n$; let $j_{n1},\dots,j_{n,J_n}$
+  be their indices, so that $j_{n1}$ is the index of the first such
+  block, $j_{n2}$ is index of the second, etc.; and define 
+  $W_{ni} = (V_{n,I_{i-1}+1},\dots,V_{n,I_i})$
+  with $I_0 = 0$ and, for $i > 0$,
   \begin{equation}
-    \label{eq:2}
-    \pr^{*}\Big[\Big| \sum_{j=1}^{J_n} \big(Z_{nj}^{*2} -
-    \E^{*}(Z_{nj}^{*2} \mid \mathcal{M}_n)\big) \Big| \Big/ \eta_n^2
-    > \delta \ \Big|\ \mathcal{M}_n \Big] \to^p 0
+    I_i =
+    \begin{cases}
+      K_{n,j_i} & j_{n,i+1} - j_{ni} = 1, \\ 
+      \lfloor (K_{n,j_{n,i+1}} + K_{n,j_{n,i}}) / 2 \rfloor & \text{otherwise.}
+    \end{cases}
   \end{equation}
-  for any positive $\delta$.
-\end{lem}
 
-\begin{proof}
-  The proof follows the steps of, for example, Davidson's Theorem 19.7
-  using Lemma~\ref{res:L} to establish the necessary inequalities.
-  The same argument behind Lemma~\ref{res:L} ensures that, for any
-  positive $\epsilon$, there exists a constant $B_{\epsilon}$ such
-  that
+  The, conditional on $\mathcal{M}_n$, $\{Z_{nj_i}^C(\tau,
+  \mathcal{M}_n), \mathcal{F}_{nj}\}$ is an $L_2$-mixingale of size
+  $-1/2$ with magnitude indices
   \begin{equation}
-    \label{eq:21}
-    \sup_{\tau, m, n} \big\| \big(Y_n(\tau,m)^2 n / \sigma^2 m \big)
-    1\{Y_n(\tau,m)^2 n/ \sigma^2 m  > B_{\epsilon}^2\}\ \big\|_1 \leq \epsilon
+    C D M_{n,j_i}(\tau) n^{-1} \max(1,B) \max(M_{n,j_i}(\tau)^{1/2}
+    \ell_n^{-1/2-\epsilon}, 1)
   \end{equation}
-  with $Y_n(\tau, m)$ defined in~\eqref{eq:28}.  Let $u_{nj}$ be the
-  discrete uniform$(1,\dots,n)$ indicating the beginning of the $j$th
-  block, so that
-  \begin{equation*}
-    (X_{n,u_{nj}},\dots,X_{n,u_{nj} + M_{n,j} - 1}) = (X_{n,K_{n,j-1}+1}^{*},\dots,X_{n,K_{n,j}}^{*})
-  \end{equation*}
-  almost surely, and define
-  \begin{equation*}
-    U_{nj} = Y_{nj}^{*2} \, 1\{Y_{nj}^{*2} \leq B_{\epsilon}^2 \sigma^2 M_{nj} / n d \}
-  \end{equation*}
-  and
-  \begin{equation*}
-    V_{nj} = Y_{nj}^{*2} - U_{nj},
-  \end{equation*}
-  so
-  \begin{multline*}
-    Z_{nj}^{*2} - \E^{*}(Z_{nj}^{*2} \mid \mathcal{G}_{n,j-1}) 
-    = U_{nj} - \E^{*}(U_{nj} \mid \mathcal{G}_{n,j-1}) + V_{nj} - \E^{*}(V_{nj} \mid \mathcal{G}_{n,j-1}) \\ 
-    + \big(Z_{nj}^{*2} - \E^{*}(Z_{nj}^{*2} \mid \mathcal{G}_{n,j-1})\big) - \big(Y_{nj}^{*2} - \E^{*}(Y_{nj}^{*2} \mid \mathcal{G}_{n,j-1})\big)
-  \end{multline*}
-  almost surely.
+  for some $\epsilon > 0$, with $D \geq 2 \max_t(d_{nt}/c_{nt})
+  \max_t(c_{nt})$ and $B$ a finite constant that depends only on the
+  mixingale coefficients of $X_{nt}$.\footnote{See
+    \citet[Theorem~1.6]{Mcl:75} for details.}
+\end{lema}
+\begin{proof}[Proof of Lemma~\ref{res:a5}]
+  Similar to \citet[Lemma 5]{Jon:97}, we'll show that
+  $Z^c_{nj_i}(\tau, \mathcal{M}_n)^2 - Z^c_{nj_i}(\tau,
+  \mathcal{M}_n)^2$ is an $L_2$-mixingale (conditional on
+  $\mathcal{M}_n$) by first showing that it is $L_2$-\ned\ (also
+  conditional on $\mathcal{M}_n$); the conclusion then follows
+  immediately.   By the same argument as in de Jong's
+  Equation~(A.32), for $k > 1$
+  \begin{multline}
+    \E\Big( \Big[Z_{nj_i}^C(\tau, \mathcal{M}_n) - \E(
+    Z_{nj_i}^C(\tau, \mathcal{M}_n) \mid \mathcal{M}_n;
+    W_{n,i-k},\dots,W_{n,i+k}) \Big]^2 \;\big|\; \mathcal{M}_n
+    \Big)^{\frac12}\\ \leq k^{-1/2-\epsilon} \cdot C D
+    M_{n,j_i}(\tau)^{3/2} n^{-1} \ell_n^{-1/2-\epsilon},
+  \end{multline}
+  with $\epsilon > 0$ and (for $k = 0$)
+  \begin{equation}
+    \E\Big(\Big[ Z_{nj_i}^C(\tau, \mathcal{M}_n) - \E (Z_{nj_i}^C(\tau,
+    \mathcal{M}_n) \mid \mathcal{M}_n; W_{n,i}) \Big]^2 \;\big|\; \mathcal{M}_n
+    \Big)^{\frac12} \\ \leq C D B M_{n,j_i} n^{-1}
+  \end{equation}
+  where $B$ is a finite constant that depends only on the mixingale
+  coefficients of $X_{nt}$ \citep[see][for details]{Mcl:75}.  Note
+  that $\{X_{nt}\}$ is a mixingale because it is \ned\ \citep[see,
+  e.g.][Theorem 17.5]{Dav:94}.
 
-  Now, just as in Davidson's proof, we have (with all relationships
-  understood to hold almost surely)
-  \begin{align*}
-    \E\Big(\Big|\tfrac{1}{\eta_n^2} \sum_{j=1}^{J_n} \big(U_{nj} - \E^{*}& (U_{nj} \mid \mathcal{G}_{n,j-1})\big) \Big| \ \Big|\ \mathcal{M}_n\Big)\\
-    &\leq \tfrac{1}{\eta_n^2}\Big[\E\Big( \E^{*} \Big( \Big|\sum_{j=1}^{J_n} \big(U_{nj} 
-     - \E^{*}(U_{nj} \mid \mathcal{G}_{n,j-1})\big) \Big|^2 \ \Big|\ \mathcal{M}_n\Big)\ \Big|\ \mathcal{M}_n\Big)\Big]^{1/2}
-    \\ &= \tfrac{1}{\eta_n^2} \Big(\sum_{j=1}^{J_n} \E\big(\E^{*}\big([U_{nj} - \E^{*}(U_{nj} \mid \mathcal{G}_{n,j-1})]^2\mid \mathcal{M}_{n} \big) \mid \mathcal{M}_n\big) \Big)^{1/2} 
-    \\ &\leq \tfrac{1}{\eta_n^2} \Big(\sum_{j=1}^{J_n} \E \E^{*}(U_{nj}^2 \mid \mathcal{M}_n) \Big)^{1/2} 
-    \\ & \leq \tfrac{B_{\epsilon}}{\eta_n^2} \Big(\sum_{j=1}^{J_n} \tfrac{1}{n} \sum_{\tau=0}^{n-1} \Big[\E(Y_n(\tau, M_{nj})^2 \mid \mathcal{M}_n)\Big]^2\Big)^{1/2}
-    \\ & \leq \tfrac{C_n}{\eta_n^2} \Big(\sum_{j=1}^{J_n} M_{nj}^2 / n^2\Big)^{1/2} \to^{L_1} 0
-  \end{align*}
-  for some $C_n$, with the last inequality a consequence of Lemma~\ref{res:16}
-  and convergence a consequence of Lemma~\ref{res:a1}.  Also,
-  \begin{align*}
-    \E \E^{*}\Big(\Big\lvert &\tfrac{1}{\eta_n^2} \sum_{j=1}^{J_n} (V_{nj} -
-      \E^{*}(V_{nj} \mid \mathcal{G}_{n,j-1})) \Big\rvert \ \Big|\ \mathcal{M}_n \Big)
-    \\ & \leq 2 \E \sum_{j=1}^{J_n} \tfrac{1}{\eta_n^2} \E^{*}(\lvert V_{nj} \rvert \mid \mathcal{M}_n)
-    \\ & \leq 2 \E \sum_{j=1}^{J_n} \tfrac{1}{\eta_n^2} Y_n(u_{nj}, M_{nj})^2
-    1\big\{Y_n(u_{nj}, M_{nj})^2 > B^2_{\epsilon} \sigma^2 M_{nj}/n \big\}
-    \\ & \leq 2 \epsilon \E \sum_{j=1}^{J_n} \tfrac{\sigma^2}{\eta_n^2} M_{nj} / n
-    \\ & \leq \tfrac{2\sigma^2}{\eta_n^2} \epsilon
-  \end{align*}
-  with the second to last inequality holding by the choice of
-  $B_{\epsilon}$ and all of these relationships understood to hold
-  almost surely.
-
-  Finally, 
-  \begin{multline*}
-    \tfrac{1}{\eta_n^2} \sum_{j=1}^{J_n} \big[(Z_{nj}^{*2} - \E(Z_{nj}^{*2} \mid \mathcal{G}_{n,j-1}) - (Y_{nj}^{*2} - \E(Y_{nj}^{*2} \mid \mathcal{G}_{n,j-1}))\big] \\
-    = \tfrac{2}{\eta_n^2} \sum_{j=1}^{J_n} \big[Y_{nj}^{*} - \E^{*}(Y_{nj}^{*} \mid \mathcal{G}_{n,j-1})]
-    \Big[\tfrac{M_{nj}}{\sqrt{n}} (\bar{X}_n - \bar{\mu}_n) + \tfrac{1}{\sqrt{n}} \sum_{t \in I_n(\tau, M_{nj})} (\mu_{nt} - \bar{\mu}_n)\Big]
-  \end{multline*}
-  almost surely, which converges to zero in $L_1$ by the usual arguments, completing the proof.
+  Consequently, $Z_{nj_i}^C(\tau, \mathcal{M}_n) - \E(Z_{nj_i}^C(\tau,
+  \mathcal{M}_n) \mid \mathcal{M}_n)$ is $L_2$-\ned\ of size $-1/2$,
+  and an $L_2$-mixingale of size $-1/2$ as well with magnitude indices
+  \begin{equation}
+    C D \max(M_{j_i}(\tau)^{3/2} n^{-1}
+    \ell_n^{-1/2-\epsilon}, M_{j_i}(\tau) n^{-1}) \max(1, B).
+  \end{equation}
+  So, using \citet[Theorem 1.6]{Mcl:75} again, we have the bound
+  \begin{multline}
+    \E\Bigg(\Bigg[ \sum_{i=1}^{J_n} \big(Z_{nj_i}^c(\tau,
+    \mathcal{M}_n)^2 - \E(Z_{nj_i}^c(\tau, \mathcal{M}_n)^2 \mid
+    \mathcal{M}_n)\big) \Bigg]^2 \;\Big|\; \mathcal{M}_n\Bigg) \\ \leq
+    A^2 C^2 \sum_{i=1}^J \max(M_{j_i}(\tau)^{3/2} n^{-1}
+    \ell_n^{-1/2-\epsilon}, M_{j_i}(\tau) n^{-1})^2 \equiv A^2 C^2 r_n,
+  \end{multline}
+  where $A$ is $D \max(1,B)$ multiplied by a constant that only
+  depends on the mixingale coefficients.  To finish the proof, notice
+  that $r_n \to^p 0$ if $\max_j M_j/n \to^p 0$ and $\max_j M_j /
+  \ell_n^{1+\epsilon} \to^p 0$, which both follow from Lemma~\ref{res:a1}.
 \end{proof}
 
-\begin{lem}\label{res:B}
-  If the conditions of Theorem~\ref{thm:1} hold then
+\begin{lema}\label{res:a6}
+  Define $M_{nj}(\tau)$ and $K_{nj}(\tau)$ as in the proof of
+  Lemma~\ref{res:B}.  Under the conditions of Theorem~\ref{res:C}, 
   \begin{equation}
-    \label{eq:38}
-    \eta_n^2 - \sigma^2 - \tfrac{1}{n^2} \sum_{j=1}^{J_n} \sum_{\tau=0}^{n-1} \Big(\sum_{t \in I_n(\tau, M_{nj})} (\mu_{nt} - \bar{\mu}_n) \Big)^2 = o_p(1),
+    n^{-1} \sum_{j=2}^{\lfloor \gamma n p_n \rfloor} \E \Bigg(
+    \sum_{t=1}^{K_{n,j-1}(\tau)} \sum_{s=K_{n,j-1}(\tau)+1}^{K_{nj}(\tau)}
+    (X_{nt} - \bar{\mu}_n) (X_{ns} - \bar{\mu}_n) \;\Big|\;
+    \mathcal{M}_n\Bigg) \to^p 0
   \end{equation}
+  uniformly in $\gamma$ and $\tau$.
+\end{lema}
+\begin{proof}[Proof of Lemma~\ref{res:a6}]
+  Define $\ell_n = (p_n \log p_n^{-1})^{-1}$.  Then
+  \begin{multline}
+    n^{-1} \sum_{j=2}^{\lfloor \gamma n p_n \rfloor} \E \Bigg(
+    \sum_{t=1}^{K_{n,j-1}(\tau)} \sum_{s=K_{n,j-1}(\tau)+1}^{K_{nj}(\tau)}
+    (X_{nt} - \bar{\mu}_n) (X_{ns} - \bar{\mu}_n) \;\Big|\;
+    \mathcal{M}_n\Bigg) = O_p(\ell_n p_n) \\
+    + n^{-1} \sum_{j=2}^{\lfloor \gamma n p_n \rfloor} \E \Bigg(
+    \sum_{t=1}^{K_{n,j-1}(\tau)}
+    \sum_{s=K_{n,j-1}(\tau)+\ell_n+1}^{K_{nj}(\tau)} (X_{nt} - \bar{\mu}_n)
+    (X_{ns} - \bar{\mu}_n) \;\Bigg|\; \mathcal{M}_n\Bigg)
+  \end{multline}
+  uniformly in $\tau$ and $\gamma$ by \citet[Theorem~1.6]{Mcl:75}.
+  Then $\ell_n p_n \to 0$ by construction and the remainder of the
+  proof follows the same argument as \citepos{Jon:97} Lemma~4.
+\end{proof}
+
+\subsection*{Proof of Theorem~\ref{res:C}}
+By Lemma~\ref{res:A}, it suffices to prove that $\mathbb{B}_n^{**}$
+obeys the \fclt.  We have
+\begin{multline}\label{eq:1}
+  m_n^{-1/2} \sum_{t=1}^{\lfloor \gamma m_n \rfloor} (X_{nt}^{**} -
+  \mu_n^{**}) = (n p)^{-1/2} \sum_{j=1}^{\lfloor \gamma n p_n \rfloor}
+  \Big\{(n p_n/m_n)^{1/2} \sum_{t = K_{n,j-1} + 1}^{K_{nj}}
+  (X_{nt}^{**} - \mu_n^{**})\Big\} \\ + m_n^{-1/2} \sgn(\gamma m_n -
+  K_{n,\lfloor \gamma n p_n \rfloor}) \sum_{t = \min(\lfloor \gamma
+    m_n \rfloor, K_{n,\lfloor \gamma n p_n \rfloor}) +
+    1}^{\max(\lfloor \gamma m_n \rfloor, K_{n,\lfloor \gamma n p_n
+      \rfloor})} (X_{nt}^{**} - \mu_n^{**}).
+\end{multline}
+We can show that the second sum in~(\ref{eq:1}) vanishes
+asymptotically.  To simplify the presentation, assume that $\gamma m_n
+> K_{n,\lfloor \gamma n p_n \rfloor}$; the same argument works for the
+reverse inequality as well.  By Lemma~\ref{res:a4},
 \begin{equation}
-    \label{eq:19}
-    \tfrac{1}{n} \sum_{\tau=0}^{n-1} \sum_{j=1}^{J_n} Z_n(\tau,
-    M_{nj})^2 -\eta_n^2 = o_p(\eta_n^2),
+  \E^{**} m_n^{-1/2} \sum_{t = K_{n,\lfloor \gamma n p_n \rfloor} +
+    1}^{\lfloor \gamma m_n\rfloor} (X_{nt}^{**} - \mu_n^{**})=
+  (\bar X_n - \bar X_n) \E^{**} (\lfloor \gamma m_n
+  \rfloor - K_{n,\lfloor \gamma n p_n \rfloor})/ m_n^{1/2} = 0
 \end{equation}
-  \begin{equation}\label{eq:37}
-    \sigma_n^{*2} - \eta_n^2 = o_p(\eta_n^2),
+(remember that $m_n$ is random) and
+\begin{align}
+  \var^{**}\Big(&m_n^{-1/2} \sum_{t = K_{n,\lfloor \gamma n p_n
+      \rfloor} + 1}^{\lfloor \gamma m_n\rfloor} (X_{nt}^{**} -
+  \mu_n^{**})\Big) \\&= \E^{**} (m_n n)^{-1} \sum_{\tau=1}^n
+  \Bigg\{\sum_{j=\lfloor\gamma n p_n \rfloor + 1}^{\kappa_n - 1}
+  \Bigg(\sum_{t=K_{n,j-1}+1}^{K_{nj}} (X_{nt} - \bar{X}_n)\Bigg)^2 \\
+  &\qquad+ \Bigg(\sum_{t=K_{n,\kappa_n-1}+1}^{\lfloor \gamma m_n
+    \rfloor} (X_{nt} - \bar{X}_n)\Bigg)^2 \Bigg\} \to^p 0
+\end{align}
+uniformly in $\gamma$ by \citet[Theorem~1.6]{Mcl:75}, with $\kappa_n$
+indicating the block containing $\lfloor \gamma m_n \rfloor$, so
+$K_{n,\kappa_n-1} < \lfloor \gamma m_n \rfloor \leq K_{n,\kappa_n}$.
+It now suffices to prove that the first term in~(\ref{eq:1}) satisfies
+an \fclt.
+
+Let $Z_{nj}^{**} = \sqrt{n p_n/ m_n} \sum_{t = K_{n,j-1} + 1}^{K_{nj}}
+(X_{nt}^{**} - \mu_n^{**})$; clearly $Z_{nj}^{**}$ is an \mds\
+conditional on $\mathcal{M}_n$ that has finite variance and is
+globally covariance stationarity condition by Lemma~\ref{res:B}.
+Moreover, $(n p_n)^{-1} \sum_j (Z_{nj}^{**})^2 \to^{p^{**}} 1$ by the
+\lln\ \citep[e.g.][Theorem~19.7]{Dav:94} and $\max_j (Z_{nj}^{**})^2 =
+o_{p^{**}}(n)$ given $\mathcal{M}_n$ by uniform integrability.  Then
+the random functions $\gamma \mapsto (n p_n)^{-1/2}
+\sum_{j=1}^{\lfloor \gamma n p_n \rfloor} Z_{nj}^{**}$ converge in
+distribution to $\mathcal{B}$ conditional on $\mathcal{M}_n$ by the
+\fclt\ \citep[e.g.][Theorem 27.14]{Dav:94}.  Since this limit does not
+depend on $\mathcal{M}_n$, it holds unconditionally as well.\qed
+
+\subsection*{Proof of Lemma~\ref{res:A}}
+We'll use a coupling argument.  If $m_n > n$, then $\bar{X}_n^{*} \eqd
+\bar{Y}_n^{**} \equiv n^{-1} \sum_{t=1}^{n} X_{nt}^{**}$.  Similarly,
+if $m_n < n$, $\bar{X}_n^{**} \eqd \bar{Z}_n^{*} \equiv n^{-1}
+\sum_{t=1}^{m_n} X_{nt}^{*}$.  So the result holds if $m_n^{1/2}
+(\bar{X}_n^{**} - \bar{Y}_n^{**}) \to^p 0$ and $n^{1/2} (\bar{X}_n^{*}
+- \bar{Z}_n^{*}) \to^p 0$; i.e.
+\begin{equation}\label{eq:4}
+  m_n^{-1/2} \sum_{t=\lfloor \gamma m_n \rfloor +
+    1}^{\lfloor \gamma n \rfloor} (X_{nt}^{*} - \mu_n^{*}) \to^{p}
+  0, \qquad (n^{-1/2} - m_n^{-1/2})
+  \sum_{t=1}^{\lfloor \gamma n \rfloor} (X_{nt}^* - \mu_n^*) \to^p 0
 \end{equation}
 and
+\begin{equation}\label{eq:6}
+  n^{-1/2} \sum_{t=\lfloor \gamma n \rfloor +
+    1}^{\lfloor \gamma m_n \rfloor} (X_{nt}^{**} - \mu_n^{**}) \to^{p} 0, \qquad
+  (m_n^{-1/2} - n^{-1/2})
+  \sum_{t=1}^{\lfloor \gamma m_n \rfloor} (X_{nt}^{**} - \mu_n^{**}) \to^p 0
+\end{equation}
+uniformly in $\gamma$, where summations over empty index sets are
+defined to be zero.  I'll prove~\eqref{eq:4} as the argument
+for~\eqref{eq:6} is identical
+
+Now let $\mathcal{N}_n = (M_{n1},\dots,M_{n,N_n})$.  By
+Lemma~\ref{res:a4},
+\begin{gather}\label{eq:17}
+  \E^{*} \Big(m_n^{-1/2} \sum_{t=\lfloor \gamma m_n \rfloor +
+    1}^{\lfloor \gamma n \rfloor} (X_{nt}^{*} - \mu_n^{*}) \;\Big|\;
+  \mathcal{N}_n \Big) = \frac{(\lfloor \gamma n \rfloor - \lfloor
+    \gamma m_n
+    \rfloor)^{+}}{n^{1/2}} (\bar{X}_n - \bar{X}_n) = 0, \\
+  \E^{*} \Big((n^{-1/2} - m_n^{-1/2}) \sum_{t=1}^{\lfloor \gamma n
+    \rfloor} (X_{nt}^* - \mu_n^*) \;\Big|\; \mathcal{N}_n \Big) = 0,
+\end{gather}
+and
+\begin{align}
+  \var^{*} \Big(m_n^{-1/2} & \sum_{t=\lfloor \gamma m_n \rfloor +
+    1}^{\lfloor \gamma n \rfloor} (X_{nt}^{*} - \mu_n^{*}) \;\Big|\;
+  \mathcal{N}_n \Big) \\ &= (m_n n)^{-1} \sum_{\tau=1}^n \Bigg[
+  \Bigg\{ \sum_{t= \lfloor \gamma m_n \rfloor + 1}^{K_{n,\kappa_{n0}}}
+  (X_{n,\alpha_n(\tau + t)} - \bar{X}_n) \Bigg\}^2 \\&\quad +
+  \sum_{j=\kappa_{n0} + 1}^{\kappa_{n1} - 1} \Bigg\{ \sum_{t=K_{n,j-1}
+    + 1}^{K_{nj}} (X_{n, \alpha_n(\tau+t)} - \bar X_n)\Bigg\}^2
+  \\&\quad + \Bigg\{ \sum_{t=K_{n,\kappa_{n1} - 1} + 1}^{\lfloor
+    \gamma n \rfloor} (X_{n, \alpha_n(\tau + t)} - \bar{X}_n)\Bigg\}^2
+  \Bigg].
+\end{align}
+By \citet[Theorem~1.6]{Mcl:75},
+\begin{multline}
+  \E \var^{*} \Big( (\gamma m_n)^{-1/2} \sum_{t=\lfloor \gamma m_n
+    \rfloor + 1}^{\lfloor \gamma n \rfloor} (X_{nt}^* - \mu_n^*)
+  \;\Big|\; \mathcal{N}_n\Big) \\ \leq \gamma^{-1} \E (m_{n} n)^{-1} \sum_{\tau=1}^n
+  \E \Big[ A_{n0} (K_{n,\kappa_{n0}} - \lfloor \gamma m_n \rfloor) \\
+  + \sum_{j=\kappa_{n0} + 1}^{\kappa_{n1} - 1} A_{nj} M_{nj} +
+  A_{n,\kappa_{n1}} (\lfloor \gamma n \rfloor - K_{n,\kappa_{n1}} - 1)
+  \Big] \to 0
+\end{multline}
+uniformly in $\gamma$, since the $A_{nj}$ are uniformly bounded
+constants that only depend on the mixingale magnitude indices of
+$\{X_{nt}\}$.  Also,
 \begin{equation}
-    \label{eq:36}
-    \hat\sigma_n^{*2} - \eta_n^2 = o_p(\eta_n^2).
+  \var^{*} \Big((n^{-1/2} - m_n^{-1/2})
+  \sum_{t=1}^{\lfloor \gamma n \rfloor} (X_{nt}^* - \mu_n^*) \mid
+  \mathcal{N}_n\Big) \to^p 0
 \end{equation}
-\end{lem}
+uniformly by a similar argument.  \citet[Theorem~1.6]{Mcl:75} also
+ensures that the conditional variances are uniformly integrable,
+giving~\eqref{eq:4}.\qed
 
-\begin{proof} 
-  Equation~\eqref{eq:35}, along with Theorem~2 of \citet{Jon:97} and
-  Lemma~\ref{res:a1}, implies that
-  \begin{multline*}
-    \label{eq:52}
-    \sum_{j=1}^{J_n} \tfrac{1}{n} \sum_{\tau=0}^{n-1} Z_n(\tau,
-    M_{nj})^2 = \tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau=0}^{n-1}
-    Y_n(\tau, M_{nj})^2 + \tfrac{1}{n^2} \sum_{j=1}^{J_n}
-    \sum_{\tau=0}^{n-1} \Big(\sum_{t \in I_n(\tau, M_{nj})} (\mu_{nt} - \bar{\mu}_n)\Big)^2 \\
-    + \tfrac{2}{n^{3/2}} \sum_{j=1}^{J_n} \sum_{\tau=0}^{n-1}
-    Y_n(\tau, M_{nj}) \sum_{t\in I_n(\tau, M_{nj})} (\mu_{nt} -
-    \bar{\mu}_n) + o_p(1).
-  \end{multline*}
-  So~\eqref{eq:38} follows directly from Lemma~\ref{res:7}.
-  For~\eqref{eq:19}, it suffices to prove that
+\subsection*{Proof of Lemma~\ref{res:B}}
+For any $\tau$ in $\{1,\dots,n\}$, let $\kappa_n(\tau)$ indicate the
+block containing $\tau$, so $K_{n,\kappa_n(\tau)-1} < \tau \leq
+K_{n,\kappa_n(\tau)}$.  Also let
 \begin{equation}
-    \label{eq:20}
-    \tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau=0}^{n-1} \big\{Y_n(\tau,
-    M_{nj})^2 - \E(Y_n(\tau, M_{nj})^2 \mid \mathcal{M}_n) \big\} \to^p 0,
+  M_{nj}(\tau) = (\min(n, K_{n,\beta_n(\kappa_n(\tau) + j)} - \tau) - \max(1,
+  K_{n,\beta_n(\kappa_n(\tau) - 1 + j)} + 1 - \tau))^{+},
+\end{equation}
+with $\beta_n(x) = (x-1) \mod \lfloor n p_n \rfloor + 1$, and let
+$K_{nj}(\tau) = \sum_{i=1}^j M_{nj}(\tau)$ and $K_{n0}(\tau) = 0$.
+Now define
+\begin{equation}
+  Z_{nj}(\tau,\mathcal{M}_n) = \sum_{t=K_{n,j-1}(\tau)+1}^{K_{nj}(\tau)} n^{-1/2} (X_{nt} - \bar \mu_n), \qquad j = 1,\dots,
+  \lfloor \gamma n p_n \rfloor.
+\end{equation}
+By Lemma~\ref{res:a4},
+\begin{equation}
+  \var^{**}\Big(m_n^{-1/2} \sum_{t=1}^{\lfloor \gamma m_n\rfloor} X_{nt}^{**} \mid \mathcal{M}_n\Big) = n^{-1}
+  \sum_{\tau = 1}^n \sum_{j=1}^{\lfloor \gamma n p_n \rfloor} Z_{nj}(\tau,
+  \mathcal{M}_n)^2 + o_p
+\end{equation}
+uniformly in $\gamma$.  The advantage of this representation is that
+each series $\{Z_{nj}(\tau, \mathcal{M})\}_j$ is formed from
+consecutive blocks of the original series.
+
+Define the lower bound $\ell_n$ on the lengths $M_{ni}$ as $\ell_n =
+(p_n \log p_n^{-1})^{-1}$.  Since
+\begin{multline}
+  \sum_{j=1}^{\lfloor \gamma n p_n \rfloor} \E\big( Z_{nj}(\tau,
+  \mathcal{M}_n)^2 \ind\{M_{nj}(\tau) > \ell_n\}\big) \leq \\ \big((1
+  - p_n)^{1/p_n}\big)^{p_n\ell_n} \sum_{j=1}^{\lfloor \gamma n p_n
+    \rfloor} \E Z_{nj}(\tau, \mathcal{M}_n)^2 = e^{-p_n\ell_n} O(1)
+  \to 0,
+\end{multline}
+with the last equality a consequence of \citet[Theorem~1.6]{Mcl:75},
+we have
+\begin{equation}
+  \var^{**}(m_n^{1/2} \bar{X}^{**}_n \mid \mathcal{M}_n) = n^{-1} \sum_{\tau=1}^n
+  \sum_{j=1}^{\lfloor \gamma n p_n \rfloor} Z_{nj}(\tau, \mathcal{M}_n)^2
+  \ind\{M_{nj}(\tau) > \ell_n\} + o_p.
+\end{equation}
+
+Now, truncate $Z_{nj}(\tau, \mathcal{M}_n)$ similar to
+\citet[Lemma~5]{Jon:97}: define
+\begin{equation}\label{eq:3}
+  Z^C_{nj}(\tau, \mathcal{M}_n) = 
+  \begin{cases}
+    0 & M_{nj}(\tau) \leq \ell_n, \\ Z_{nj}(\tau, \mathcal{M}_n) &
+    M_{nj}(\tau) > \ell_n ,\ |Z_{nj}(\tau, \mathcal{M}_n)| \leq C
+    \sqrt{M_{nj}(\tau)/n} \\ C \sqrt{M_{nj}(\tau)/n} & M_{nj}(\tau) >
+    \ell_n ,\ Z_{nj}(\tau, \mathcal{M}_n) >C \sqrt{M_{nj}(\tau)/n} \\
+    -C \sqrt{M_{nj}(\tau)/n} & M_{nj}(\tau) > \ell_n,\ Z_{nj}(\tau,
+    \mathcal{M}_n) < -C \sqrt{M_{nj}(\tau)/n}.
+  \end{cases}
+\end{equation}
+\citet[Theorem~1.6]{Mcl:75} establishes that the family $\{n
+Z_{nj}(\tau, \mathcal{M})^2 / M_{nj}(\tau); n,j,\tau,\mathcal{M}\}$ is
+uniformly integrable,\footnote{See also \citet[Lemma 3.2]{Dav:92} and
+  \citet[Lemma 5]{Jon:97}} so $Z_{nj}(\tau,\mathcal{M}_n)^2 -
+Z^c_{nj}(\tau,\mathcal{M}_n)^2$ can be made arbitrarily small by
+choosing a large enough $C$.  So it suffices to prove
+\begin{equation}\label{eq:7}
+  \sum_{j=1}^{\lfloor \gamma n p_n \rfloor} \big(Z_{nj}^C(\tau,
+  \mathcal{M}_n)^2 - \E(Z_{nj}^C(\tau,
+  \mathcal{M}_n)^2 \mid \mathcal{M}_n) \big) \to^p 0
 \end{equation}
 and
+\begin{equation}\label{eq:8}
+  n^{-1} \sum_{\tau=1}^n \sum_{j=1}^{\lfloor \gamma n p_n \rfloor}
+  \E(Z_{nj}(\tau, \mathcal{M}_n)^2 \mid \mathcal{M}_n) \to^p
+  \gamma. 
+\end{equation}
+
+\citet[Theorem~1.6]{Mcl:75} and Lemma~\ref{res:a5} imply that, for
+some $\epsilon > 0$,
+\begin{multline}
+  \E\Bigg(\Bigg\{\sum_{j=1}^{\lfloor \gamma n p_n \rfloor}
+  \big(Z_{nj}^C(\tau, \mathcal{M}_n)^2 - \E(Z_{nj}^C(\tau,
+  \mathcal{M}_n)^2 \mid \mathcal{M}_n) \big)\Bigg\}^2 \;\Big|\;
+  \mathcal{M}_n \Bigg) \\ \leq A^2 C^2 \sum_{j=1}^{\lfloor \gamma n
+    p_n \rfloor} (M_{nj}(\tau)/n)^2 \max(1, M_{nj}(\tau) /
+  \ell_n^{1+\epsilon}),
+\end{multline}
+which converges to zero if $\max_j M_{nj}/n \to^p 0$ and $\max_j
+M_{nj}/\ell_n^{1+\epsilon} \to^p 0$.  Both follow from
+Lemma~\ref{res:a1}, proving~\eqref{eq:7}.
+
+To prove~(\ref{eq:8}), let $d_n$ be a sequence of integers such that
+$d_n \to \infty$ and $d_n/n \to \infty$ and let $\zeta_n(\gamma)$ be a
+sequence of functions such that $\zeta_n(x) = \zeta_n(x - 1)$ for all
+$x$ and
 \begin{equation}
-    \label{eq:51}
-    \tfrac{1}{n^{3/2}} \sum_{j=1}^{J_n} \sum_{\tau=0}^{n-1}
-    Y_{n}(\tau, M_{nj})\sum_{t\in I_n(\tau, M_{nj})}(\mu_{nt} -
-    \bar{\mu}_n) = o_p(\eta_n).
+  (2 d_n)^{-1} \sum_{s,t = \lfloor \gamma n \rfloor - d_n +
+    1}^{\lfloor \gamma n \rfloor + d_n} \E (X_{ns} -
+  \bar{\mu}_n)(X_{nt} - \bar{\mu}_n) - \zeta_n(\gamma) \to 0
 \end{equation}
-  Observe that we can express the summation in~\eqref{eq:20} as
-  \begin{multline}\label{eq:47}
-    \tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau=0}^{n-1} \big\{Y_n(\tau,
-    M_{nj})^2 - \E(Y_n(\tau, M_{nj})^2 \mid \mathcal{M}_n) \big\} \\ =
-    \tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau=0}^{M_{nj}-1}
-    \sum_{i=1}^{L_{nj}}\big\{ Y_n(\tau+(i-1)M_{nj}, M_{nj})^2
-    - \E(Y_n(\tau+(i-1)M_{nj}, M_{nj})^2 \mid
-    \mathcal{M}_n)\big\} \\ + \tfrac{1}{n} \sum_{j=1}^{J_n}
-    \sum_{\tau= M_{nj}L_{nj}}^{n-1} \big\{Y_{n}(\tau, M_{nj})^2 -
-    \E(Y_n(\tau, M_{nj})^2 \mid \mathcal{M}_n)\big\}
-  \end{multline}
-  almost surely, where $L_{nj} = \lfloor n/ M_{nj} \rfloor$.  The
-  advantage of this representation is that each summation over
-  $i=1,\dots,L_{nj}$ is formed from adjacent blocks of the original
-  series, so standard blocking arguments can be applied.  Now let
-  $\ell_n = (p_n \log p_n^{-1})^{-1}$. By Lemma~\ref{res:7}, for any
-  $\delta > 0$ there exist positive $C$ and $\epsilon$ such that
-  \begin{multline*}
-    \Big\lVert\tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau=1}^{M_{nj}}
-    \sum_{i=1}^{L_{nj}}\big\{ Y_n(\tau+(i-1)M_{nj}, M_{nj})^2 -
-    \E(Y_n(\tau+(i-1)M_{nj}, M_{nj})^2 \mid
-    \mathcal{M}_n)\big\}\Big\rVert_1 \\ \leq C \tfrac{\ell_n}{n} + 2
-    \delta + C\, \Big\lVert \max_{j =
-      1,\dots,J_n}\big(\tfrac{M_{nj}}{n}\big)^{1/2} \max_{j =
-      1,\dots,J_n}\big(1,
-    \tfrac{M_{nj}}{\ell_n^{1+\epsilon}}\big)^{1/2} \Big\rVert_1
-  \end{multline*} 
-  which converges to $2 \delta$ by Lemma~\ref{res:a1}.  The second
-  term of~\eqref{eq:47} is $O_{p}(1 - M_{nj}/n)$ by Lemma~\ref{res:16},
-  proving~\eqref{eq:20}.
+for all $\gamma \in (0,1]$. It is obvious that \eqref{eq:8} holds for
+$\gamma = 0$.  Lemmas~\ref{res:a5} and~\ref{res:a6} and the fact that
+$\sum_{\tau=1}^n n^{-1} \zeta_n(x + \tau/n) \to 1$ uniformly in $x$ by
+assumption imply that
+\begin{align}
+  n^{-1} \sum_{\tau=1}^n \sum_{j=1}^{\lfloor \gamma n p_n \rfloor}
+  \E(Z_{nj}^2(\tau, \mathcal{M}_n) \mid \mathcal{M}_n) &=
+  \sum_{\tau=1}^n \sum_{j=1}^{\lfloor \gamma n p_n \rfloor}
+  \frac{\zeta_n(\tau/n + j/np_n)}{n^2 p_n} + o_p \\ &= \gamma + o_p,
+\end{align}
+completing the proof.  \qed
 
-  For~\eqref{eq:51}, the Cauchy-Schwarz inequality implies that
-  \begin{multline*}
-    \tfrac{1}{n^{3/2}} \sum_{j=1}^{J_n} \sum_{\tau=0}^{n-1}
-    \Big\lvert Y_{n}(\tau, M_{nj})\sum_{t\in I_n(\tau, M_{nj})}(\mu_{nt} -
-    \bar{\mu}_n)\Big\rvert \\\leq \Big\{\tfrac{1}{n} \sum_{j=1}^{J_n}
-    \sum_{\tau=0}^{n-1} \big(\tfrac{1}{\sqrt{n}} Y_n(\tau,
-    M_{nj})^2\big)\Big\}^{1/2} \Big\{\tfrac{1}{n} \sum_{j=1}^{J_n}
-    \sum_{\tau=0}^{n-1} \Big(\tfrac{1}{\sqrt{n}} \sum_{t \in I_n(\tau,
-      M_{nj})} (\mu_{nt} - \bar{\mu}_{n} )\Big)^2\Big\}^{1/2}.
-  \end{multline*}
-  Lemma~\ref{res:16} implies that
-  \begin{equation}
-    \label{eq:23}
-    \tfrac{1}{n} \sum_{j=1}^{J_n}
-    \sum_{\tau=0}^{n-1} \big(\tfrac{1}{\sqrt{n}} Y_n(\tau,
-    M_{nj})^2\big) \to^p 0
-  \end{equation}
-  and Equation~\eqref{eq:38} that
-  \begin{equation*}
-    \tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau=0}^{n-1}
-    \Big(\tfrac{1}{\sqrt{n}} \sum_{t \in I_n(\tau, M_{nj})} (\mu_{nt} -
-    \bar{\mu}_{n} )\Big)^2 = O_p(\eta_n^2).
-  \end{equation*}
-  completing the proof of~\eqref{eq:19}.
-
-  Result~\eqref{eq:37} is an immediate consequence of~\eqref{eq:19}
-  and Lemma~\ref{res:L}.  Finally, for~\eqref{eq:36}, observe that
-  \begin{equation*}
-    \hat{\sigma}_n^{*2} = \eta_n^2 + (\sigma_n^{*2} - \eta_n^2) + \sum_{j=1}^{J_n}\Big[
-    Z_{nj}^{*2} - \E^*(Z_{nj}^{*2} \mid \mathcal{M}_n)
-    + \tfrac{2 M_{nj}}{\sqrt{n}} (\mu_n^{*} - \bar{X}_n^{*})
-    Z_{nj}^{*} + \tfrac{M_{nj}^2}{n} (\mu_n^{*} - \bar{X}_n^{*})^2 \Big]
-  \end{equation*}
-  implying that $\hat{\sigma}_n^{*2}/\eta_n^2 \to^p 1$
-  by~\eqref{eq:37} along with Lemmas~\ref{res:a1},~\ref{res:L},
-  and~\ref{res:H}.
-\end{proof}
-
-\begin{lem}\label{res:7}
-  Define $Y_n(\tau, m)$ as in Equation~\eqref{eq:28} and $L_{nj} =
-  \lfloor n/M_{nj}\rfloor$. For any positive $\delta$, there exist
-  positive and finite constants $C$, $N$, and $\epsilon$ such that
-\begin{multline}\label{eq:29}
-  \E\Big(\Big\lvert\sum_{i=1}^{L_n} \big[Y_{n}(\tau + (i-1) M_{nj},
-  M_{nj})^2 -  Y_{n}(\tau + (i-1) M_{nj}, M_{nj} -
-  \ell)^2\big]\Big\rvert \ \Big|\
-  \mathcal{M}_n\Big) \leq C \tfrac{\ell}{n},
-\end{multline}
-\begin{multline}\label{eq:16}
-  \E\Big(\Big\lvert\sum_{i=1}^{L_n} \big[Y_{n}(\tau + (i-1) M_{nj},
-  M_{nj} - \ell)^2 \\- \E(Y_{n}(\tau + (i-1) M_{nj}, M_{nj} -
-  \ell)^2 \mid \mathcal{M}_n)\big]\Big\rvert \ \Big|\
-  \mathcal{M}_n\Big)\\ \leq 2 \delta + C \cdot \big(\tfrac{M_{nj}}{n}\big)^{1/2}
-  \max\big(1, \tfrac{M_{nj}}{\ell^{1+\epsilon}}\big)^{1/2},
-\end{multline}
-and
-  \begin{multline}
-    \label{eq:5}
-    \E\Big(\Big\lvert \sum_{i=1}^{L_{n}} \E(Y_n(\tau + (i-1) M_{nj}, M_{nj} - \ell)^2 \mid
-    \mathcal{M}_n) - \sigma^2 \Big\rvert \ \Big|\ \mathcal{M}_n\Big) \leq 
-    \\ C\,  \nu_n^2(0, n) \Big(\ell \log(\ell)^2 \psi(\ell)^2 
-     + \sum_{m=\ell}^{\infty} \log(m)^2 \psi(m)^2 \Big)^{1/2} \Big( \psi(0)^2 + \sum_{v=1}^{\infty} \log(v)^2 \psi(v)^2 \Big)^{1/2}
-  \end{multline}
-  almost surely for all $j = 1,\dots,J_n$, $\tau= 0,\dots,n-1$,
-  $\ell=1,\dots,M_{nj}-1$, and $n > N$.  Moreover, if $\ell_n =
-  (p_n^{-1} \log p_n^{-1})^{-1}$ then
-  \begin{equation}
-    \label{eq:46}
-    \sup_{\tau=0,\dots,n-1} \E\Big(\Big\lvert \sum_{j=1}^{L_{n}} \E(Y_n(\tau + (i-1) M_{nj}, M_{nj} - \ell_n)^2 \mid
-    \mathcal{M}_n) - \sigma^2 \Big\rvert \ \Big|\ \mathcal{M}_n\Big) \to^{L_1} 0.
-  \end{equation}
-\end{lem}
-\begin{proof}
-  Result~\eqref{eq:29} is immediate from Lemma~\ref{res:16}
-  and~\eqref{eq:46} follows directly from~\eqref{eq:5}.
-  Results~\eqref{eq:16} and~\eqref{eq:5} are direct extensions of
-  \citepos[Lemmas 5 and 4, respectively]{Jon:97}, replacing de Jong's
-  implicit use of inequalities with explicit inequalities.
-\end{proof}
-\bibliography{texextra/AllRefs}
+\bibliography{AllRefs}
 \end{document}
@@
 % LocalWords:  de Jong's ns Mcl AllRefs nn th nm ni HaH formulae jn gcalhoun nN
-% LocalWords:  jel PaP DPP np Ames Resampling nonstationary cdf
+% LocalWords:  jel PaP DPP np

### 2015-12-29 subs/ET/reply_editor.txt
Add response letters to referees and editor

Dear Robert,

Thank you again for giving me the opportunity to revise my submission to
Econometric Theory, "Block bootstrap consistency under weak assumptions"
(manuscript #2868).

As you mention in your letter, two of the referees have concerns about the
execution of the proofs in the paper, in particular (in the case of referee
3) technical concerns about uniformity that arise from conditioning on the
sequence of block lengths in the Stationary Bootstrap.  To address these
concerns, I have substantially rewritten the proofs: I had originally used
mixingale arguments to justify the CLT and the FCLT and argued that the
bootstrapped process was a mixingale "conditional on" an additional
information set, but that concept is nonstandard, causing confusion, and
introduces many subtle technical issues that referee 3 alerted me to.  The
revised paper uses instead a martingale difference sequence CLT for the
bootstrapped sample mean and shows that the CLTs assumptions are justified
by deriving the necessary inequalities from NED properties of the original
process.  This change leads to a more direct and more standard logical
argument and I hope addresses the referees' concerns.

The referees also point out that the conclusions of the main results of the
paper could be presented more precisely.  In the revised paper, I present
the CLT and the FCLT results as separate theorems and make my claims about
"convergence in distribution" much more precise: see Theorems 1 and 2 for
the revised statements.  I should point out that referee 1 had the main
concern:

"The above-cited papers, in common with most of this literature, prove
uniform convergence in probability of the difference between the conditional
probability measure of the statistic computed from the resampled data and
the corresponding distribution in the original data.... This is not done
here."

This concern comes from my presentation of the results but not from the
underlying math (in particular, since the limit is continuous, the uniform
convergence that the referee desires is a direct consequence of convergence
in distribution).  I have changed the conclusions to make this uniform
convergence explicit and explain the connection in the proof of Theorem 1.
I should also note that this notion of "uniformity" is distinct from the
technical issues that concern referee #3 (referee #3 is concerned about
uniformity over parameters related to events in the conditioning sigma-field,
not over the domain of the CDF), and the mixingale/MDS changes I mention
above are needed to address referee #3.

Finally, I have made many other changes to the paper's proofs to try to
improve its clarity.  The most substantial of these changes is the removal
of an intermediate approximation: the original version of the paper
approximated the bootstrap process $X_t^*$ with a second bootstrap process
$X_t^{**}$ that was marginally easier to analyze.  Needless to say, this
approach caused some confusion so I removed those intermediate steps,
resulting in a clearer argument.  Other changes in the same vein have
been made as well.

I have included parts of this letter in my replies to individual
referees.  Thank you again for this opportunity.  I look forward to
your response.

### 2015-12-29 subs/ETr1/reply_editor.tex
Add response letters to editor and referees

\documentclass[12pt]{article}
\usepackage[charter]{mathdesign}
\usepackage[margin=1.25in]{geometry}
\frenchspacing
\usepackage{amsmath}

\begin{document}
\hfill 2014-10-06

\noindent
Dear Robert,

Please accept this submission of a revised version of my paper,
``Block bootstrap consistency under weak assumptions.'' I have tried to
address all of the issues raised by the referees. A short summary of
the changes to the paper follows and, as you requested, I have
written detailed letters to referees 2 and 3 addressing their specific
concerns.

\strut

\noindent \textbf{General summary of changes}

\begin{itemize}
\item Several terms were defined in the beginning of the proofs of
  Theorems~1 and~2, but were used repeatedly in the supporting
  lemmas. The paper now defines those terms in a separate subsection
  that proceeds the proofs.

\item I have made some of the arguments in the proof of Theorem~1 more
  explicit, and have tried to explain in detail how conditioning
  affects the intermediate steps of the proof.

\item One referee noticed that the proof of stochastic equicontinuity
  was in error; it has been fixed. Fixing this proof revealed an error
  in our treatment of the expectation terms, $\mu_{nt}$, and we have
  strengthened our assumptions on their dispersion around the grand
  mean, $\bar \mu_n$. We now require
  $\sum_{t=1}^n (\mu_{nt} - \bar \mu_n) \to 0$
  as $n \to \infty$.

  However, our key assumptions on the size and moment conditions that
  the stochastic array $X_{nt}$ satisfies remain unchanged, and the
  paper's main contributions are unchanged.

\item Fixing the stochastic equicontinuity proof also led me to revise
  several of the supporting Lemmas.
  \begin{itemize}
  \item Lemmas 2 and 3 of the last draft have been replaced by Lemmas
    5 and 7. These results are new maximal inequalities.
  \item Lemma 5 of the last draft has been split up; parts of it are
    in Lemma 3 and the remainder is in Lemma 4. Moreover, Lemma 4 of
    the last draft has been incorporated into Lemma 3 of the latest draft.
  \item Lemma 6 of the last draft has been rewritten to use
    unconditional expectations instead of conditional expectations.
  \end{itemize}

\item There is some concern that the inequalities referenced in the
  paper may fail with as complicated of an indexing scheme as used in
  the paper. To address this, I have added a supplemental appendix
  that provides more detail and shows how the original results apply
  to our setting. These results are presented in the main paper as
  Lemmas 6 and 7 of the paper and the supplemental appendix contains
  their proofs. The proof are essentially identical to existing
  results in the literature, and I am not claiming any authorship of
  those particular results. But some readers will probably be
  interested in this explicit demonstration.

  This seemed like the best way to address some of referee 2's
  concerns, and I have added a strong disclaimer to the appendix's
  introduction to avoid the appearance of plagarism. If you have other
  suggestions, or feel that the disclaimer is not clear enough, I am
  happy to remove the supplemental appendix and use a different
  approach.

\item Other minor changes have been made to address points raised by
  the referees.
\end{itemize}

Best,

Gray Calhoun

\end{document}

### 2015-12-29 subs/ETr1/reply_2.tex
Add response letters to editor and referees

\documentclass[12pt]{article}
\usepackage[charter]{mathdesign}
\usepackage[margin=1.25in]{geometry}
\frenchspacing
\usepackage{amsmath}

\begin{document}
\hfill 2014-10-06

\noindent \textbf{Reply to referee 2}

\noindent \textbf{General summary of changes}

\begin{itemize}
\item Several terms were defined in the beginning of the proofs of
  Theorems~1 and~2, but were used repeatedly in the supporting
  lemmas. The paper now defines those terms in a separate subsection
  that proceeds the proofs.

\item I have made some of the arguments in the proof of Theorem~1 more
  explicit, and have tried to explain in detail how conditioning
  affects the intermediate steps of the proof.

\item As you noticed, the proof of stochastic equicontinuity
  was in error; it has been fixed. Fixing this proof revealed an error
  in our treatment of the expectation terms, $\mu_{nt}$, and we have
  strengthened our assumptions on their dispersion around the grand
  mean, $\bar \mu_n$. We now require
  $\sum_{t=1}^n (\mu_{nt} - \bar \mu_n) \to 0$
  as $n \to \infty$.

  However, our key assumptions on the size and moment conditions that
  the stochastic array $X_{nt}$ satisfies remain unchanged, and the
  paper's main contributions are unchanged.

\item Fixing the stochastic equicontinuity proof also led me to revise
  several of the supporting Lemmas.
  \begin{itemize}
  \item Lemmas 2 and 3 of the last draft have been replaced by Lemmas
    5 and 7. These results are new maximal inequalities.
  \item Lemma 5 of the last draft has been split up; parts of it are
    in Lemma 3 and the remainder is in Lemma 4. Moreover, Lemma 4 of
    the last draft has been incorporated into Lemma 3 of the latest draft.
  \item Lemma 6 of the last draft has been rewritten to use
    unconditional expectations instead of conditional expectations.
  \end{itemize}

\item There is some concern that the inequalities referenced in the
  paper may fail with as complicated of an indexing scheme as used in
  the paper. To address this, I have added a supplemental appendix
  that provides more detail and shows how the original results apply
  to our setting. These results are presented in the main paper as
  Lemmas 6 and 7 of the paper and the supplemental appendix contains
  their proofs. The proof are essentially identical to existing
  results in the literature, and I am not claiming any authorship of
  those particular results. But some readers will probably be
  interested in this explicit demonstration.

\item Other minor changes have been made to address points raised by
  the referees.
\end{itemize}

\newpage

\noindent \textbf{Reply to specific points}

\begin{enumerate}

\item \emph{Setup of Theorem 1: it is not clear to me from the text
    how exactly the last block that ranges up to $n$ is dealt with. Is
    $K_{n,J_n} = n$?}

  Yes, thank you for pointing this out. I've clarified that $K_{n,J_n}
  = n$.

\item \emph{Page 7, Equations (16), (17) and (18): I do not understand
    why (16) is implied by Hall and Heyde's CLT by (17) and (18). This
    may be due to my lack of exposure to the bootstrap literature. It
    seems that the author applies a conditional version of a CLT that
    is unconditional; however, the exact argument escapes me. I seem
    to be able to derive the author's result by working directly with
    Hall and Heyde's proof, but I failed to see how the shortcut that
    the author uses works. Some clarification or a good reference may
    be needed here.}

  (These equations are now numbered (21) -- (23))

  I have added some clarification and a reference to the paper; the
  key idea is that the only stochastic components of this conditional
  probability measure are the periods where each block starts; they
  have a discrete uniform distribution over $1,\dots,n$ and are
  independent of the other random variables. This ensures that the
  conditional probability measures are regular and arguments like Hall
  and Heyde's, which implicitly allow the probability space to change
  with $n$, hold without modification. (If it were an irregular
  conditional probability, this would be problematic.)

  Note that Hall and Heyde use the same approach themselves in Remark
  (vi) on p. 63 (for example) in the context of random norming ---
  applying the CLT while conditioning on an auxiliary r.v.

\item \emph{Equation below equation (19): I cannot quite see
    this. There is the issue of the last block, but that must be
    fixable because it is asymptotically negligible; but I also do not
    understand how this formula works overall. Obviously by (12),
    \begin{equation*}
      E^*(g(Z_{nj}^* \mid \mathcal{M}_n) =
      E^*\Big(g\Big(\tfrac{1}{\sqrt{n}} \sum_{t = K_{n,j-1}+1}^{K_{nj}} (X_{nt}^* - \bar X_n)\Big)
      \ \big|\ \mathcal{M}_n\Big)
    \end{equation*}
    and by (14) and (15),
    \begin{align*}
      \tfrac{1}{n} \sum_{\tau = 0}^{n-1} g(Z_n(\tau, M_{nj}))
      &= \tfrac1n \sum_{\tau = 0}^{n-1} g\Big(\tfrac1{\sqrt{n}} \sum_{t \in I_n(\tau, M_{nj})} (X_{nt} - \mu)\Big) \\
      &\approx \tfrac1n \sum_{\tau = 0}^{n-1} g\Big(\tfrac1{\sqrt{n}} \sum_{t = \tau+1}^{\tau + M_{nj}} (X_{nt} - \mu)\Big)
    \end{align*}
    where the $\approx$ indicates that I have ignored the last
    block. However, I could not see why both expressions are
    identical. One odd aspect of the last formula is that it will
    refer to values of $X_{nt}$ for $t > n$ for values of $j$ for
    which $M_{nj} \geq 1$ (this can be seen by choosing $\tau=n-1$).}

  (This equation is now numbered (18))

  $Z_n(\tau, M_{nj})$ should be defined as $\tfrac{1}{\sqrt{n}}
  \sum_{t\in I_n(\tau, m)} (X_{nt} - \bar X_n)$ --- I have corrected
  the definition in the paper. Other uses of $Z_n(\tau, M_{nj})$ in
  the paper had implicitly used the correct definition, fortunately.

  These expressions are now identical because
  \begin{equation*}
    (X_{n, K_{n,j-1}+1}^*,\dots, X_{n, K_{n,j}}^*) =
    \begin{cases}
      (X_{n,1},\dots,X_{n,M_{nj}}) & \text{with probability }1/n \\
      (X_{n,2},\dots,X_{n,M_{nj}+1}) & \text{with probability }1/n \\
      \vdots \\
      (X_{n,n}, X_{n,1}\dots,X_{n,M_{nj}-1}) & \text{with probability }1/n
    \end{cases}
  \end{equation*}

  The ``odd aspect of the last formula'' comes from your ``$\approx$''
  substitution; $I_n(\tau,m)$ is defined in the paper to wrap around
  after the $n$th observation. I.e., when $\tau = n-1$ the index
  defined by $I_n(\tau, m)$ is $(n, 1, 2,\dots, m - 1)$. Since this is
  not obvious, I've now emphasized this aspect of $I$: see Equation~(10).

  Since this argument is so important to my results, I've moved it out
  of the proof of Theorem 1 and discuss it before either proof. I have
  also stated it in a somewhat more general form (i.e. it allows for
  several blocks instead of just one) so that its use in Theorem 2 and
  the supporting lemmas are more clear.

\item \emph{p. 8, middle: ``by definition:'' perhaps explain why the
    expression is $O_{a.s.}(1)$ here.}

  Thank you for alerting me to this source of confusion. I have
  simplified some of the notation in this argument added intermediate
  steps. The relevant line is now between Equations (24) and (25).

\item \emph{p. 8: reference to Van der Vaart's Lemma 2.11: this lemma
    involves convergence of a distribution to a continuous
    distribution, while your setting involves convergence in
    probability. Therefore, perhaps you should indicate how exactly
    the extension can be made to your setting.}

  I have added more details to show how the argument applies in this
  setting.

\item \emph{Lemma 3: usually, uniform integrability of Y n is defined as
    \begin{equation*}
      \limsup_{K \to \infty} \limsup_{n \to \infty} E|X_n(\tau,m)| I(|Y_n| > K) = 0.
    \end{equation*}
    Are you claiming here that for the $X_n(τ, m)$ of Lemma 3, we have
    \begin{equation*}
      \limsup_{K \to \infty} \limsup_{\tau\to\infty} \limsup_{m \to \infty} \limsup_{n \to \infty}
      E|X_n(\tau, m)|I(|X_n(\tau, m)| > K) = 0?
    \end{equation*}
    If so, it is not clear to me that the single-index results from
    Davidson and de Jong have been translated into the triple index
    result needed here; that is, I have trouble with the last sentence
    of the proof of Lemma 3.}

  I have written a supplemental appendix that reproduces some
  inequalities and uniform integrability results. They are referenced
  as Lemmas 6 and 7 in the main text. As you can see, the triple index
  that my paper needs makes the notation more cumbersome, but does not
  change the proof in a meaningful way.

  Lemma 3 has been removed and has been replaced by an analogous but
  somewhat stronger result in Lemma 5.

\item \emph{Start of Theorem 2: I do not see why Lemma 5 has the
    stated implication.}

  I have rephrased this introduction.

\item \emph{p. 9, bottom: this result is an error. Davidson's theorem
    15.14 is a standard maximal inequality in the spirit of
    Kolmogorov's inequality. Therefore, it cannot deliver the stated
    result, because a maximal inequality such as 15.14 only maximizes
    over one index only.}

  Thank you for pointing out this embarrassing error; I have corrected
  the proof.

\item \emph{Lemma 6: this result is obtained from direct reference to
    existing proofs. Therefore as far as I can see, the proof as
    stated leaves open the possibility that $C$, $N$ and $\epsilon$
    depend on $\mathcal{M}_n$.}

  I have changed the statement of these results to rule out that
  possibility, thank you for calling my attention to it.

\end{enumerate}

\end{document}

### 2015-12-29 subs/ETr1/reply_3.tex
Add response letters to editor and referees

--- 2015-12-29 subs/ETr1/reply_2.tex
@@
 \usepackage[margin=1.25in]{geometry}
-\frenchspacing
-\usepackage{amsmath}
 
@@
 
-\noindent \textbf{Reply to referee 2}
+\noindent \textbf{Reply to referee 3}
 
@@
 
-\item As you noticed, the proof of stochastic equicontinuity
+\item One referee noticed that the proof of stochastic equicontinuity
   was in error; it has been fixed. Fixing this proof revealed an error
@@
 
+\begin{description}
+\item[Main comment] \emph{My main comment on the paper relates to the
+    array notation used throughout. Specifically, what is it for?}
+
+  I agree with several of the points raised here. The original array,
+  $\{X_{nt}\}$, is not normalized and so the notation might benefit
+  from using $X_t$ instead of $X_{nt}$. But the theoretical results
+  deal with arrays like $\{Z_{nj}\}$. These arrays are normalized and
+  also depend on the bootstrap lengths $M_{nj}$, which also depend on
+  $n$. Ultimately, I feel that it would be more confusing to the
+  reader if the paper were to use array notation for the various
+  $Z_{nj}$ terms --- where it does seem helpful --- but avoid it for
+  the $X_t$ terms.
+
+  I also think that it is useful to make the normalization explicit in
+  calculating the variance, etc., because it is natural to define the
+  bootstrap in terms of the original $X_{nt}$s and not a normalized or
+  demeaned array.
+
+  I realize that both of these choices make the main text somewhat
+  more cumbersome than it would be otherwise, but I hope that they
+  make the mathematics less ambiguous.
+
+\end{description}
 \begin{enumerate}
+\item[1.] \emph{In the statement of Lemma 2 (p. 13) $\mathcal{G}_n$ is a
+    sigma-field of events, so in what sense are $c_{nt}$ (scalar
+    constant?)  and $\Delta_n$ (real random variable?) elements of
+    $\mathcal{G}_n$ ? I think something else is intended here?}
 
-\item \emph{Setup of Theorem 1: it is not clear to me from the text
-    how exactly the last block that ranges up to $n$ is dealt with. Is
-    $K_{n,J_n} = n$?}
+  I have rewritten the inequalities that depended on this lemma so
+  that they do not require it, so this lemma has been removed from the
+  paper. Originally, the notation was meant to convey that both
+  $c_{nt}$ and $\Delta_n$ are $\mathcal{G}_n$-measurable random
+  variables.
 
-  Yes, thank you for pointing this out. I've clarified that $K_{n,J_n}
-  = n$.
+\item[2.] \emph{It's customary in the this type of work to define the
+    probability space in which the action takes place, say $(\Sigma,
+    \mathcal{F}, P)$, so that subsequently defined sigma fields can be
+    identified as subsets of $\mathcal{F}$. I think that being
+    explicit about this is a convention worth adhering to.}
 
-\item \emph{Page 7, Equations (16), (17) and (18): I do not understand
-    why (16) is implied by Hall and Heyde's CLT by (17) and (18). This
-    may be due to my lack of exposure to the bootstrap literature. It
-    seems that the author applies a conditional version of a CLT that
-    is unconditional; however, the exact argument escapes me. I seem
-    to be able to derive the author's result by working directly with
-    Hall and Heyde's proof, but I failed to see how the shortcut that
-    the author uses works. Some clarification or a good reference may
-    be needed here.}
+  I agree that there are several areas of potential confusion in this
+  paper. With respect to the sigma fields involved, many of our
+  results rely crucially on adding different information sets at
+  different steps of the analysis, often after invoking the L.I.E.;
+  for example, conditioning on the original data set and the random
+  block lengths, but not on the starting position of the blocks; or
+  conditioning on the block lengths, but not on the original data set
+  or the block starting positions; etc. I don't see a way to make
+  those arguments more transparent by explicitly introducing the
+  product of the bootstrap mechanism and the DGP that generated the
+  original dataset as a probability space.
 
-  (These equations are now numbered (21) -- (23))
-
-  I have added some clarification and a reference to the paper; the
-  key idea is that the only stochastic components of this conditional
-  probability measure are the periods where each block starts; they
-  have a discrete uniform distribution over $1,\dots,n$ and are
-  independent of the other random variables. This ensures that the
-  conditional probability measures are regular and arguments like Hall
-  and Heyde's, which implicitly allow the probability space to change
-  with $n$, hold without modification. (If it were an irregular
-  conditional probability, this would be problematic.)
-
-  Note that Hall and Heyde use the same approach themselves in Remark
-  (vi) on p. 63 (for example) in the context of random norming ---
-  applying the CLT while conditioning on an auxiliary r.v.
-
-\item \emph{Equation below equation (19): I cannot quite see
-    this. There is the issue of the last block, but that must be
-    fixable because it is asymptotically negligible; but I also do not
-    understand how this formula works overall. Obviously by (12),
-    \begin{equation*}
-      E^*(g(Z_{nj}^* \mid \mathcal{M}_n) =
-      E^*\Big(g\Big(\tfrac{1}{\sqrt{n}} \sum_{t = K_{n,j-1}+1}^{K_{nj}} (X_{nt}^* - \bar X_n)\Big)
-      \ \big|\ \mathcal{M}_n\Big)
-    \end{equation*}
-    and by (14) and (15),
-    \begin{align*}
-      \tfrac{1}{n} \sum_{\tau = 0}^{n-1} g(Z_n(\tau, M_{nj}))
-      &= \tfrac1n \sum_{\tau = 0}^{n-1} g\Big(\tfrac1{\sqrt{n}} \sum_{t \in I_n(\tau, M_{nj})} (X_{nt} - \mu)\Big) \\
-      &\approx \tfrac1n \sum_{\tau = 0}^{n-1} g\Big(\tfrac1{\sqrt{n}} \sum_{t = \tau+1}^{\tau + M_{nj}} (X_{nt} - \mu)\Big)
-    \end{align*}
-    where the $\approx$ indicates that I have ignored the last
-    block. However, I could not see why both expressions are
-    identical. One odd aspect of the last formula is that it will
-    refer to values of $X_{nt}$ for $t > n$ for values of $j$ for
-    which $M_{nj} \geq 1$ (this can be seen by choosing $\tau=n-1$).}
-
-  (This equation is now numbered (18))
-
-  $Z_n(\tau, M_{nj})$ should be defined as $\tfrac{1}{\sqrt{n}}
-  \sum_{t\in I_n(\tau, m)} (X_{nt} - \bar X_n)$ --- I have corrected
-  the definition in the paper. Other uses of $Z_n(\tau, M_{nj})$ in
-  the paper had implicitly used the correct definition, fortunately.
-
-  These expressions are now identical because
-  \begin{equation*}
-    (X_{n, K_{n,j-1}+1}^*,\dots, X_{n, K_{n,j}}^*) =
-    \begin{cases}
-      (X_{n,1},\dots,X_{n,M_{nj}}) & \text{with probability }1/n \\
-      (X_{n,2},\dots,X_{n,M_{nj}+1}) & \text{with probability }1/n \\
-      \vdots \\
-      (X_{n,n}, X_{n,1}\dots,X_{n,M_{nj}-1}) & \text{with probability }1/n
-    \end{cases}
-  \end{equation*}
-
-  The ``odd aspect of the last formula'' comes from your ``$\approx$''
-  substitution; $I_n(\tau,m)$ is defined in the paper to wrap around
-  after the $n$th observation. I.e., when $\tau = n-1$ the index
-  defined by $I_n(\tau, m)$ is $(n, 1, 2,\dots, m - 1)$. Since this is
-  not obvious, I've now emphasized this aspect of $I$: see Equation~(10).
-
-  Since this argument is so important to my results, I've moved it out
-  of the proof of Theorem 1 and discuss it before either proof. I have
-  also stated it in a somewhat more general form (i.e. it allows for
-  several blocks instead of just one) so that its use in Theorem 2 and
-  the supporting lemmas are more clear.
-
-\item \emph{p. 8, middle: ``by definition:'' perhaps explain why the
-    expression is $O_{a.s.}(1)$ here.}
-
-  Thank you for alerting me to this source of confusion. I have
-  simplified some of the notation in this argument added intermediate
-  steps. The relevant line is now between Equations (24) and (25).
-
-\item \emph{p. 8: reference to Van der Vaart's Lemma 2.11: this lemma
-    involves convergence of a distribution to a continuous
-    distribution, while your setting involves convergence in
-    probability. Therefore, perhaps you should indicate how exactly
-    the extension can be made to your setting.}
-
-  I have added more details to show how the argument applies in this
-  setting.
-
-\item \emph{Lemma 3: usually, uniform integrability of Y n is defined as
-    \begin{equation*}
-      \limsup_{K \to \infty} \limsup_{n \to \infty} E|X_n(\tau,m)| I(|Y_n| > K) = 0.
-    \end{equation*}
-    Are you claiming here that for the $X_n(τ, m)$ of Lemma 3, we have
-    \begin{equation*}
-      \limsup_{K \to \infty} \limsup_{\tau\to\infty} \limsup_{m \to \infty} \limsup_{n \to \infty}
-      E|X_n(\tau, m)|I(|X_n(\tau, m)| > K) = 0?
-    \end{equation*}
-    If so, it is not clear to me that the single-index results from
-    Davidson and de Jong have been translated into the triple index
-    result needed here; that is, I have trouble with the last sentence
-    of the proof of Lemma 3.}
-
-  I have written a supplemental appendix that reproduces some
-  inequalities and uniform integrability results. They are referenced
-  as Lemmas 6 and 7 in the main text. As you can see, the triple index
-  that my paper needs makes the notation more cumbersome, but does not
-  change the proof in a meaningful way.
-
-  Lemma 3 has been removed and has been replaced by an analogous but
-  somewhat stronger result in Lemma 5.
-
-\item \emph{Start of Theorem 2: I do not see why Lemma 5 has the
-    stated implication.}
-
-  I have rephrased this introduction.
-
-\item \emph{p. 9, bottom: this result is an error. Davidson's theorem
-    15.14 is a standard maximal inequality in the spirit of
-    Kolmogorov's inequality. Therefore, it cannot deliver the stated
-    result, because a maximal inequality such as 15.14 only maximizes
-    over one index only.}
-
-  Thank you for pointing out this embarrassing error; I have corrected
-  the proof.
-
-\item \emph{Lemma 6: this result is obtained from direct reference to
-    existing proofs. Therefore as far as I can see, the proof as
-    stated leaves open the possibility that $C$, $N$ and $\epsilon$
-    depend on $\mathcal{M}_n$.}
-
-  I have changed the statement of these results to rule out that
-  possibility, thank you for calling my attention to it.
+  However, I am very concerned about these issues and I have written a
+  separate section that proceeds the proofs and defines many of the
+  derived random variables and sub sigma-fields that are used in our
+  proofs. Hopefully that helps clear up some of the readers' potential
+  confusion.
 

### 2015-12-29 Paper.tex

--- 2015-12-29 Paper.tex
@@
 \documentclass[11pt]{article}
-\usepackage{amsfonts}
-\usepackage{amsmath,amsthm,amssymb,graphicx,setspace,url,booktabs,tabularx,slantsc}
-\usepackage[T1]{fontenc}
-
-% \usepackage[yyyymmdd,hhmmss]{datetime}
-% \usepackage{fancyhdr}
-% \pagestyle{fancy}
-% \lfoot{Page \thepage. Typeset on \today\ at \currenttime}
-% \cfoot{}
-% \rfoot{}
-
-\usepackage[sort,round]{natbib}
-\usepackage[multiple]{footmisc}
-\usepackage{geometry}
-\usepackage[small]{caption}
-
-\bibliographystyle{abbrvnat}
-\newcommand\citepos[2][]{\citeauthor{#2}'s \citeyearpar[#1]{#2}}
-
-\newtheorem{thm}{Theorem}
-\newtheorem{lem}{Lemma}
-\newtheorem{claim}{Claim}
-\newtheorem{cor}{Corollary}
-\newtheorem{res}{Result}
-
-\theoremstyle{definition}
-
-\newtheorem{example}{Example}
-\newtheorem{defn}{Definition}
-\newtheorem{rem}{Remark}
-
-\DeclareMathOperator*{\argmin}{arg\,min}
-\DeclareMathOperator*{\plim}{plim}
-
-\DeclareMathOperator{\dist}{d}
-\DeclareMathOperator{\const}{const}
-\DeclareMathOperator{\cov}{cov}
-\DeclareMathOperator{\E}{E}
-\DeclareMathOperator{\eqd}{\overset{d}{=}}
-\DeclareMathOperator{\ind}{1}
-\DeclareMathOperator{\pr}{Pr}
-\DeclareMathOperator{\sgn}{sgn}
-\DeclareMathOperator{\var}{var}
-\DeclareMathOperator{\vech}{vech}
-
-\renewcommand{\mod}{\operatorname{mod}}
-
-\newcommand{\clt}{\textsc{clt}}
-\newcommand{\fclt}{\textsc{fclt}}
-\newcommand{\hac}{\textsc{hac}}
-\newcommand{\lln}{\textsc{lln}}
-\newcommand{\mds}{\textsc{mds}}
-\newcommand{\ned}{\textsc{ned}}
-
-\frenchspacing
+\input{preamble}
 
@@
     University, Ames, IA 50011. Telephone: (515) 294-6271.  Email:
-    \texttt{gcalhoun@iastate.edu}. Web: \texttt{http://gray.clhn.co}.
-    I would like to thank Helle Bunzel, Dimitris Politis, Robert
-    Taylor, and three anonymous referees for their comments and
-    feedback on earlier versions of this paper.}}
+    \protect\url{gcalhoun@iastate.edu}. Web:
+    http://www.econ.iastate.edu/$\sim$gcalhoun.  I would like to thank
+    Helle Bunzel, Dimitris Politis, Robert Taylor, and three anonymous
+    referees for their comments and feedback on earlier versions of
+    this paper.}}
 
@@
 
-\date{March 25, 2013}
 \maketitle
@@
   This paper weakens the size and moment conditions needed for typical
-  block bootstrap methods (i.e. the Moving Blocks, Circular Blocks,
+  block bootstrap methods (i.e.\ the Moving Blocks, Circular Blocks,
   and Stationary Bootstraps) to be valid for the sample mean of
@@
   random and unequal block lengths.  This paper also proves that
-  bootstrapped partial sums satisfy a Functional CLT under the same
+  bootstrapped partial sums satisfy a Functional \clt\ under the same
   conditions.
@@
 \newpage
-\noindent Block bootstraps, e.g. the Moving Blocks
+\noindent Block bootstraps, e.g.\ the Moving Blocks
 \citep{Kun:89,LiS:92}, Circular Block \citep{PoR:92}, and Stationary
@@
 conditions of the original papers to fit with those commonly used in
-Econometrics based on Near-Epoch-Dependence
-(\ned).\footnote{\citet{GoW:02} show that these bootstrap methods can
-  be applied to heterogeneous $L_{2+\delta}$-\ned\ processes of size
+Econometrics based on Near-Epoch-Dependence (\ned).%
+\footnote{\citet{GoW:02} show that these bootstrap methods can be
+  applied to heterogeneous $L_{2+\delta}$-\ned\ processes of size
   $-2(r-1)/(r-2)$ on a strong mixing sequence of size
@@
   Both papers require that the expected block length grow with $n$ and
-  be $o(n^{1/2})$.  \cite{GoP:11} discuss these issues
-  further.}\footnote{An array $\{X_{nt}\}$ is an $L_{\rho}$-\ned\
-  process on a mixing array $\{V_{nt}\}$ if
+  be $o(n^{1/2})$.  \cite{GoP:11} discuss these issues further.}%
+\footnote{An array $\{X_{nt}\}$ is an $L_{\rho}$-\ned\ process on a
+  mixing array $\{V_{nt}\}$ if
   \begin{equation}
@@
     - \delta})$ for all $\delta>0$.  Dropping the index ``$n$'' gives
-  the series definition.  Note that strong and uniform mixing arrays are
-  not required to be stationary.} But these conditions are still stronger than
+  the series definition.  Note that strong and uniform mixing arrays
+  are not required to be stationary.} %
+But these conditions are still stronger than
 required for a \clt\ to hold; \citet{Jon:97} has established the \clt\
 under $L_2$-\ned\ with smaller size and moment
-restrictions.\footnote{\citet{Jon:97} proves that the \clt\ holds for
-  averages of $L_2$-\ned\ processes of size $-1/2$ on a strong mixing
-  series of size $-r/(r-2)$, $r > 2$ and the original series having
-  bounded $r$-moments.}  This paper shows that these block bootstrap
+restrictions.%
+\footnote{\citet{Jon:97} proves that the \clt\ holds for averages of
+  $L_2$-\ned\ processes of size $-1/2$ on a strong mixing series of
+  size $-r/(r-2)$, $r > 2$ and the original series having bounded
+  $r$-moments.} %
+This paper shows that these block bootstrap
 methods consistently estimate the distribution of the sample mean
 under \citepos{Jon:97} assumptions, and show that an \fclt\ holds as
-well.\footnote{\citet{Rad:96} proves consistency for the Moving Blocks
+well.%
+\footnote{\citet{Rad:96} proves consistency for the Moving Blocks
   Bootstrap for any stationary strong mixing sequence that satisfies
   the \clt. This paper uses a similar method of proof to his, but also
-  accommodates nonstationary sequences and the Stationary Bootstrap.}
+  accommodates nonstationary sequences and the Stationary
+  Bootstrap.} %
 It also relaxes \citepos{GoW:02} and \citepos{GoJ:03} requirement that
@@
 a recent review of the bootstrap for time-series
-processes,\footnote{Also see the discussion papers:
-  \citet{Dah:11,GoP:11,Hor:11,JeM:11,KrP:11b}.} and \citet{GoP:11}
-further discuss recent developments in block-bootstraps.
-
-Theorem~\ref{thm:1} presents the main result, asymptotic normality of
+processes,%
+\footnote{Also see the discussion papers:
+  \citet{Dah:11,GoP:11,Hor:11,JeM:11,KrP:11b}.} %
+and \citet{GoP:11} further discuss recent developments in
+block-bootstraps.
+
+Theorem~\ref{main-bootstrap-clt} presents the main result, asymptotic normality of
 the distribution of bootstrapped partial sums.  This paper adopts the
-standard notation that $\E^{*}$, $\var^{*}$, etc. are the usual
+standard notation that $\E^{*}$, $\var^{*}$, etc.\ are the usual
 operators with respect to the probability measure induced by the
@@
 
-\begin{thm}\label{thm:1}
+\begin{thm}\label{main-bootstrap-clt}
   Suppose the following conditions hold.
@@
     \ned\ magnitude indices are denoted $\{d_{nt}\}$.
-  \item The array $\mu_{nt} - \bar \mu_n$ is uniformly bounded where
-    $\E X_{nt} = \mu_{nt}$ and $\bar{\mu}_n = n^{-1} \sum_{t=1}^n
+  \item The array $\mu_{nt} - \bar \mu_n$ is uniformly bounded
+    and $\sum_{t=1}^n (\mu_{nt} - \bar \mu_n)^2 \to 0$,
+    where $\E X_{nt} = \mu_{nt}$ and $\bar{\mu}_n = n^{-1} \sum_{t=1}^n
     \mu_{nt}$. Moreover, $\sqrt{n} \| \bar{X}_{n} - \bar\mu_n \|_2
-    \to \sigma > 0$.
+    \to \sigma > 0$, with $\bar X_n = (1/n) \sum_{t=1}^n X_{nt}$.
   \item There exists an array of positive real numbers $\{c_{nt}\}$
@@
     block, $i=1,\dots,J_n$, and define $K_{n0} = 0$ and $K_{nj} =
-    \sum_{i=1}^j M_{ni}$.
+    \sum_{i=1}^j M_{ni}$. The last block, $M_{n,J_n}$, is defined as
+    $K_{n,J_n} - K_{n,J_n-1}$, so $K_{n,J_n} = n$ a.s.
   \end{enumerate}
-  Then
-  \begin{equation}\label{eq:30}
-    \sup_x \big\lvert \pr^{*}\big[\sqrt{n}(\bar X_{n}^{*} - \mu_{n}^{*}) \big/
-    \sigma_n^{*} \leq x \big] - \Phi(x) \big\rvert \to^p 0,
+  Then $\hat\sigma^{*2} \to^p \sigma^2$,
+  \begin{equation}\label{eq:36}
+    \sup_x \big\lvert \pr^{*}\big[\sqrt{n}(\bar X_{n}^{*} - \E^* \bar X_n^*) \leq x \big]
+    - \pr \big[\sqrt{n}(\bar X_{n} - \E \bar X_n) \leq x \big] \big\rvert \to^p 0,
   \end{equation}
@@
   \begin{equation}
-    \label{eq:9}
+    \label{eq:2}
     \sup_x \big\lvert \pr^{*}\big[
-    \sqrt{n}(\bar X_{n}^{*} - \mu_{n}^{*}) \big/ \hat\sigma_n^{*}
+    \sqrt{n}(\bar X_{n}^{*} -  \E^* \bar X_n^*) \big/ \hat\sigma_n^{*}
     \leq x \big] - \Phi(x) \big\rvert \to^p 0,
@@
   where $\Phi$ is the \textsc{cdf} of the Standard Normal
-  distribution, $\sigma_n^{*2} = \var^{*}(\sqrt{n} \bar X_n^{*})$, and
-    \begin{equation}
-      \label{eq:12}
+  distribution and
+    \begin{equation}
+      \label{eq:3}
       \hat{\sigma}_n^{*2} = \tfrac{1}{n} \sum_{j=1}^{J_n}
@@
 
-Note that \citet{Jon:97} allows a little bit more flexibility in his
+As mentioned earlier, these are the same size and mixing conditions
+used by \citet{Jon:97}.
+Note that de Jong does allow a little bit more flexibility in the
 conditions on the array $\{c_{nt}\}$ \citep[see also][]{Dav:93};
@@
 Stationary Bootstrap will select the blocks randomly and is similar to
-\citepos{JoD:00b} for the \fclt.
-
-Consistency for the distribution of the sample mean follows as an
-immediate corollary of Theorem~\ref{thm:1} and \citet[Theorem~2]{Jon:97}.
-
-\begin{cor}\label{cor:1} 
-  If the conditions of Theorem~\ref{thm:1} hold and $\hat{\sigma}^2_n$
-  is a consistent estimator of $\sigma^2$ then
-  \begin{equation}
-    \label{eq:31}
-    \sup_{x} \big\lvert \pr^{*}\big[
-    \sqrt{n}(\bar X_{n}^{*} - \mu_{n}^{*}) / \sigma_{n}^{*}
-    \leq x \big]
-    - \pr\big[\sqrt{n}(\bar X_n - \bar{\mu}_n)/\hat{\sigma}_n \leq x \big] \big\rvert \to^p 0.
-  \end{equation}
-  and
-  \begin{equation}
-    \label{eq:11}
-    \sup_{x} \big\lvert \pr^{*}\big[
-    \sqrt{n} (\bar X_{n}^{*} - \mu_{n}^{*}) \big/ \hat\sigma^{*}_{n}
-    \leq x \big]
-    - \pr\big[\sqrt{n}(\bar X_n - \bar{\mu}_n)/\hat{\sigma}_n \leq x \big] \big\rvert \to^p 0.
-  \end{equation}
-\end{cor}
-
-Corollary~\ref{cor:1} justifies using the Stationary Bootstrap to
-conduct inference about $\bar \mu_n$ even though there may be
-considerable heterogeneity.  Unlike \citet{GoW:02} and \citet{GoJ:03},
-we are able to achieve consistency without
-additional assumptions that ensure the heterogeneity is asymptotically
-irrelevant, either because the deviations of $\mu_{nt}$ from $\bar
-\mu_n$ are small or because there are a finite number of breaks that
-occur in a neighborhood of the first observation.
-The additional cost is the assumption that there must be an estimator
-$\hat\sigma^2$ of $\sigma^2$ that is known to be consistent, and such an
-estimator will typically require the heterogeneity in the mean to be
-approximately known.
-
-If the mean \textit{is} approximately constant, we can get a result
-directly comparable to \citepos{GoW:02} and \citet{GoJ:03}, but with
-the weaker size and moment conditions of Theorem~\ref{thm:1}.
-Corollary~\ref{cor:2} formalizes this result and follows from
-Corollary~\ref{cor:1} and Lemma~\ref{res:B}.
-\begin{cor}\label{cor:2}
-  Suppose that the conditions of Theorem~\ref{thm:1} hold and that
-  $\sum_{t=1}^n (\mu_{nt} - \bar{\mu}_n)^2$ is $o(n^{1/2})$.  
-  Then $\sigma_n^{*2} \to^p
-  \sigma^2$, $\hat{\sigma}_n^{*2} \to^p \sigma^2$, and
-\end{cor}
-  \begin{equation}
-    \sup_{x} \big\lvert \pr^{*}\big[
-    \sqrt{n}(\bar X_{n}^{*} - \mu_{n}^{*})
-    \leq x \big]
-    - \pr\big[\sqrt{n}(\bar X_n - \bar{\mu}_n) \leq x \big] \big\rvert \to^p 0.
-  \end{equation}
-
-For some uses, a \clt\ is not enough and an \fclt\ is desired.
-Theorem~\ref{thm:1} can be extended to give an \fclt\ (using
-arguments from \citealp{JoD:00b}), but we will see that extending 
-Corollaries~\ref{cor:1} and~\ref{cor:2} is more problematic.
-Theorem~\ref{thm:2} proves a version of Theorem~\ref{thm:1} for the
-partial sum; under the same assumptions as Theorem~\ref{thm:1}, the
-partial sum of the bootstrapped process obeys an \fclt\ and can be
-used to derive critical values for other test statistics.
-
-\begin{thm}\label{thm:2}
-  Suppose that the conditions of Theorem~\ref{thm:1} hold, let $W$ be
-  standard Brownian Motion, and define
-  \begin{equation}
-    \label{eq:7}
+\citepos{JoD:00b} requirement for the \fclt. Similarly, our assumption
+on the dispersion of the individual means, $(\mu_{nt} - \bar\mu_n)^2$, is
+slightly stronger than \citepos{GoW:02} and \citepos{GoJ:03} to
+accommodate larger block sizes.
+
+Theorem~\ref{main-bootstrap-clt} relies on a general insight about the
+variance of the sample mean under the bootstrap-induced
+distribution. It is well-known that a key step in proving the \clt\
+for arbitrary dependent processes is demonstrating that the squared
+elements converge to a positive and finite limit; i.e.\ if
+$\{Z_{nj};~j=1,\dots,J_n\}$ is a representative stochastic array,
+$\sum_j Z_{nj}^2 \to^p \sigma^2$ is an important necessary condition
+for $\sum_j Z_{nj} \to^d N(0,\sigma^2)$.  (See Section 3.2 of
+\citealp{HaH:80}, for further discussion.)  For martingale difference
+arrays, each $Z_{nj}$ is one of the original random variables $X_{nt}$
+(typically normalized by $1/\sqrt{n}$), but for other forms of
+dependence (\ned\ or mixingale arrays, for example, as in
+\citealp{Jon:97}) each $Z_{nj}$ is a contiguous block of the original
+random variables,
+\begin{equation*}
+  Z_{nj} = \tfrac{1}{\sqrt{n}} \sum_{t=(j-1) M_n +1}^{j M_n} (X_{nt} - \mu_{nt}),
+\end{equation*}
+that adds up to the original summation, plus potentially a negligible
+residual, so $\sum_j Z_{nj}= (1/\sqrt{n}) \sum_t (X_{nt} - \mu_{nt}) +
+o_p(1)$. In \citet{Jon:97}, for example, the \clt\ for mixingale
+arrays assumes that there exists a sequence of blocks such that $\sum_j
+Z_{nj}^2$ converges i.p., and the \ned\ \clt\ establishes conditions
+under which such a $Z_{nj}$ exists.
+
+Our insight is that the expectation of squared blocks of the bootstrap
+process can be expressed as a sequence of \emph{contiguous} blocks of
+the original process, so the arguments that establish convergence of
+the original squared blocks can be applied with only minor changes to
+the bootstrapped blocks. Consider the Moving Blocks Bootstrap,%
+\footnote{To make this presentation as simple as possible, assume for
+  now that $n = M_n J_n$ exactly.} %
+for example, and let
+\begin{equation*}
+  Z_{nj}^* = \tfrac{1}{\sqrt{n}} \sum_{t=(j-1) M_n + 1}^{j M_n} (X_{nt}^* - \bar X_n).
+\end{equation*}
+Then, conditional on the data, the $Z_{nj}^{*2}$ are independent can
+be expected to obey an \lln, so %
+$\sum_j (Z_{nj}^{*2} - \E^* Z_{nj}^{*2}) \to^p 0$ %
+and the CLT for the bootstrapped array requires $\sum_j \E^*
+Z_{nj}^{*2}$ to converge to a positive and finite limit.  But, since
+$\E^*$ only averages over the starting point of each block, we have
+\begin{align*}
+  \E^* Z_{nj}^{*2} &=
+  \tfrac{1}{n} \sum_{\tau = 0}^{n-M_n}
+  \Big(\tfrac{1}{\sqrt{n}}
+  \sum_{t= \tau + 1}^{\tau + M_n} (X_{nt} - \bar X_n) \Big)^2 \\
+  &= \tfrac{1}{n} \sum_{\tau_0 = 0}^{M_n-1}
+  \sum_{j=1}^{J_n-1}
+  \Big(\tfrac{1}{\sqrt{n}}
+  \sum_{t= (j - 1) M_n + \tau_0 + 1}^{j M_n + \tau_0} (X_{nt} - \bar X_n) \Big)^2
+\end{align*}
+after grouping blocks separated by $M_n$ periods. For each $\tau_0$,
+the summation can be expected to converge in probability through the
+same arguments that were used to establish the \clt\ for the original
+array.%
+\footnote{Some of the details of the argument will typically need to
+  change, since the original \clt\ only requires convergence for
+  $\tau_0 = 0$, but these details are often incidental to the original
+  argument.}%
+\footnote{Lemmas~\ref{bootstrap-variance-convergence-lemma} and
+  \ref{bootstrapped-zsq-uniform-integrability-lemma} are particularly
+  strong demonstrations of this argument.} %
+A similar representation is available for the Circular and Stationary
+bootstraps.
+
+In short, the basic approach that we use to prove Theorem~\ref{main-bootstrap-clt}
+is based on a fundamental connection between the second moments of the
+bootstrap process and the sum of squared blocks of the original
+array. Even though the details of our proof rely on specific
+techniques for \ned\ arrays, this connection implies that block
+bootstraps are typically consistent when the original dependent array
+obeys the \clt, and the connection should be useful for proving
+consistency of the bootstrap under other dependence conditions.
+
+For some uses, a \clt\ is inadequate and an \fclt\ is necessary.
+Theorem~\ref{main-bootstrap-clt} can be extended to give an \fclt\
+(using arguments from \citealp{JoD:00b}). We show in
+Theorem~\ref{main-bootstrap-invariance-theorem} that the partial sum
+of the bootstrapped process obeys an \fclt\ and can be used to derive
+critical values for other test statistics under the same assumptions
+as Theorem~\ref{main-bootstrap-clt}.
+
+\begin{thm}\label{main-bootstrap-invariance-theorem}
+  Suppose that the conditions of Theorem~\ref{main-bootstrap-clt}
+  hold, let $W$ be standard Brownian Motion, and define
+  \begin{equation}
+    \label{eq:6}
     W_n^{*}(\gamma) = \tfrac{1}{\sqrt{n}}
@@
   \end{equation}
-  Then $\pr^{*}[\dist(W_n^{*}, W) > \delta] \to 0$ i.p. and
-  $\pr^{*}[\dist(\hat{W}_n^{*}, W) > \delta] \to 0$ i.p. for any
+  Then $\pr^{*}[\dist(W_n^{*}, W) > \delta] \to 0$ i.p.\ and
+  $\pr^{*}[\dist(\hat{W}_n^{*}, W) > \delta] \to 0$ i.p.\ for any
   positive $\delta$ and distance $\dist$ that metricizes weak
@@
 
-Just as with Theorem~\ref{thm:1}, we have natural corollaries using
-Theorem~\ref{thm:2} to approximate the behavior of partial sums of the
-original series.  But applying this corollary requires much stronger
-assumptions.  In Corollary~\ref{cor:1}, the
-heterogeneity in $X_{nt}$ affects inference through the estimator of
-the asymptotic variance, $\hat{\sigma}_n^2$; but if the researcher
-has a consistent estimator of the variance, inference on the grand
-mean, $\bar{\mu}_{n}$, can proceed as normal.
-Assuming negligible heterogeneity in the means was unnecessary unless
-we want to avoid estimating $\sigma^2$ directly.
-
-But for the partial sum, a consistent estimator of the variance is not
-enough.  If the mean is not approximately constant then only the full
-summation is centered at the grand mean---the partial sums are
-centered at partial averages of the $\mu_{nt}$ terms.  If the research
-question concerns the individual $\mu_{nt}$'s then the bootstrap
-approximation can be used, but otherwise it can not.
-
-A second difference is that, if the $\mu_{nt}$ terms are approximately
-constant as in Corollary~\ref{cor:2}, the covariance process must
-still be consistently estimated.  The bootstrapped processes are
+Obviously, Theorem~\ref{main-bootstrap-invariance-theorem}, has
+natural corollaries that allow it to be used to approximate the
+behavior of partial sums of the original series.  But applying this
+result requires stronger assumptions than
+Theorem~\ref{main-bootstrap-clt}. The bootstrapped processes are
 (essentially) homoskedastic, so they are unable to match patterns of
-heteroskedasticity in the original series.  Those patterns must be
-removed by studentizing both the original and bootstrap partial sums.
-Other methods, such
-as the Local Block Bootstrap \citep{PaP:02,DPP:03}, may be able to
-capture this additional heterogeneity, but we do not pursue that
-possibility further.
+heteroskedasticity in the original series and we can not estimate the
+covariance process of the original partial sum in the bootstrap. This
+necessitates a separate consistent estimator of the covariance process, which
+we did not need for the sample mean.  Other methods, such as the Local
+Block Bootstrap \citep{PaP:02,DPP:03}, may be able to capture this
+additional heterogeneity with the bootstrap alone, but we do not
+pursue that possibility further.
 
 \begin{cor}
-  Suppose the conditions of Theorem~\ref{thm:1} hold, define
-  \begin{equation}
-    \label{eq:14}
+  Suppose the conditions of Theorem~\ref{main-bootstrap-clt} hold and
+  that $\sup_{t=1,\dots,n}|\mu_{nt} - \bar \mu_n| = o(1/\sqrt{n})$. Define
+  \begin{equation}
+    \label{eq:8}
     \sigma_n^2(\gamma) = \tfrac{1}{n}
@@
   \begin{equation}
-    \label{eq:8}
+    \label{eq:9}
     \hat{W}_n(\gamma) = \tfrac{1}{\sqrt{n}} \sum_{t=1}^{\lfloor \gamma
-      n \rfloor} (X_{nt} - \mu_{nt}) / \hat{\sigma}_{n}(\gamma).
+      n \rfloor} (X_{nt} - \bar\mu_n) / \hat{\sigma}_{n}(\gamma).
   \end{equation}
@@
   convergence.
-
-  Moreover, define 
-  \begin{align*}
-    \tilde W_n(\gamma) &= \tfrac{1}{\sqrt{n}} \sum_{t=1}^{\lfloor \gamma
-      n \rfloor} (X_{nt} - \bar \mu_{n}) / \hat{\sigma}_{n}(\gamma),
-&    \bar W_n(\gamma) &= \tfrac{1}{\sqrt{n}} \sum_{t=1}^{\lfloor \gamma
-      n \rfloor} (X_{nt} - \bar \mu_{n}) / \hat\sigma_n.
-  \end{align*}
-  If $\sup_t \mu_{nt}$ is $o(n^{-1/2})$ then
-  $\pr^{*}[\dist(\hat{W}_n^{*}, \tilde{W}_n) > \delta] \to^p 0$ and, if 
-  $\sup_\gamma | \sigma_n(\gamma) / \gamma \sigma - 1 | \to 0$, then
-  $\pr^{*}[\dist(\hat{W}_n^{*}, \bar{W}_n) > \delta] \to^p 0$.
 \end{cor}
 
-The rest of the paper presents the mathematical proof in detail.
-The key insight in these proofs is for the Stationary Bootstrap (other
-block bootstraps arise as a special case).  After conditioning on the
-block lengths, proving that the partial sums obey an \fclt\ reduces to
-proving consistency of the bootstrap variance (conditional on the
-block lengths), and the conditional bootstrap variance can be
-expressed in terms of blocks of consecutive observations of the
-original series.\footnote{Although this paper focuses on the Moving Blocks,
-Circular, and Stationary Bootstraps, I expect that the results can be
-extended to other recent block bootstrap methods such as the Tapered Block
-Bootstrap \citep{PaP:01,PaP:02b} and the Extended Tapered Block Bootstrap
-\citep{Sha:10}.  Those extensions are left for future research.}
-Since convergence of these blocks is essential to
-the \clt\ in general,\footnote{See, for example, \citet{Mcl:74},
-  \citet[Chapter 3]{HaH:80}, and \citet[Chapter 24]{Dav:94}.} I
-conjecture that the same approach will hold under most forms of
-dependence that allow for a \clt\ or \fclt.
+The rest of the paper presents the mathematical proofs in detail.
 
 \appendix
-
-\subsection*{Proof of Theorem~\ref{thm:1}}
-I will only present the proof for the Stationary Bootstrap, since it
-is the more difficult of the three.
-We can rewrite the sum of $X_{nt}^{*} - \mu_n^{*}$ as a sum of blocks:
-\begin{equation}\label{eq:1}
-  \tfrac{1}{\sqrt{n}} \sum_{t=1}^n (X_{nt}^{*} - \mu_n^{*}) = \sum_{j=1}^{J_n} \Big\{\tfrac{1}{\sqrt{n}} \sum_{t = K_{n,j-1} +
-    1}^{K_{nj}} (X_{nt}^{*} - \bar X_n)\Big\} \equiv 
-  \sum_{j=1}^{J_n} Z_{nj}^{*}.
-\end{equation}
-Now define $\mathcal{M}_{n}=\sigma(J_{n}, M_{n1},\dots,M_{nJ_n})$,
-$\mathcal{G}_{nj} = \sigma(Z_{n1}^{*},\dots, Z_{nj}^{*},
-X_{n1},\dots,X_{nn}, \mathcal{M}_n)$,
-  \begin{equation}\label{eq:18}
-    Z_n(\tau, m) = \tfrac{1}{\sqrt{n}} \sum_{t\in I_n(\tau, m)} (X_{nt} - \bar \mu_n),
-  \end{equation}
-$\nu_{nj}^2(\tau) = \E(Z_n(\tau, M_{nj})^2 \mid \mathcal M_n)$, and
-  \begin{equation}\label{eq:26}
-    \eta_n^{2} = \tfrac{1}{n} \sum_{\tau=0}^{n-1} \sum_{j=1}^{J_n} \nu_{nj}^2(\tau),
-  \end{equation}
-with
-\begin{equation}
-  \label{eq:3}
+\section{Proof of main results}
+
+For both results, we only present a proof for the stationary
+bootstrap. The moving blocks and circular block bootstrap follow the
+same general argument but are simpler. First we will define some
+notation that will be used repeatedly in our results.
+
+Define the \sigmafield
+\begin{equation}
+  \Ms = \sigma(J_{n}, M_{n1},\dots,M_{nJ_n})
+\end{equation}
+and the conditional probability $\Pm(\cdot) = \pr[\cdot \mid \Ms]$.
+(And define $\Pm^*(\cdot) = \pr^*[\cdot \mid \Ms]$, $\Em(\cdot) =
+\E^*(\cdot \mid \Ms)$, etc.) An important property is
+that $\Ms$ is \emph{independent} of the $X_{nt}$, so we can treat any
+$M_{nj}$ and $J_n$ terms as constants within $\Em(\cdot)$ and
+$\Pm[\cdot]$ and integrate over the unconditional distributions of the
+$X_{nt}$. This property is especially important because it allows us
+to use maximal inequalities and other moment inequalities for
+mixingale arrays without modification to construct almost sure bounds on the
+conditional moments $\Em$.
+
+Also define
+\begin{equation}
+  \label{eq:10}
   I_n(\tau, m) = \begin{cases}
-    \{\tau + 1,\dots, \tau + m\} & 0 \leq \tau \leq n - m \\
-    \{1,\dots, m - n + \tau\} \cup \{\tau + 1,\dots, n\} & n - m < \tau \leq n.
+    \{\tau + 1,\dots, \tau + m\} &
+    \textif\ 0 \leq \tau \leq n - m \text{\ and\ } 1 \leq m \\
+    \{1,\dots, m - n + \tau\} \cup \{\tau + 1,\dots, n\} &
+    \textif\ n - m < \tau \leq n \text{\ and\ } 1 \leq m\\
+    \emptyset & \textif\  m \leq 0,
   \end{cases}
 \end{equation}
-  Consequently $\{Z_{nj}^{*} / \eta_n, \mathcal{G}_{nj}\}$ is a martingale
-  difference array and
-\begin{equation}
-  \label{eq:6}
-  \pr^{*} \Big[ \sum_{j=1}^{J_n}
-  Z_{nj}^{*} / \eta_n \leq x \ \Big|\ \mathcal{M}_{n}\Big] - \Phi(x) \to^p 0
-\end{equation}
-for all $x$ if the following two conditions hold:
-\begin{equation}
-  \label{eq:13}
-  \sum_{j=1}^{J_n} \E^{*}\big( (Z_{nj}^{*2}/\eta_n^{2}) 1\{Z_{nj}^{*2}/\eta_n^{2}  >
-  \epsilon\} \ \big|\ \mathcal{M}_n\big) \to^p 0 \qquad \forall \epsilon > 0
+so each $I_n(\tau, m)$ defines a potential block of length $m$ of the
+original observations that could be chosen by the bootstrap.%
+\footnote{The index sets $I_n(\tau, m)$ are designed to ``wrap
+  around'' and use the first observations when $\tau + m > n$,
+  matching the defining aspect of the stationary and circular block
+  bootstraps.} %
+By convention, summations over empty index sets will be considered
+equal to zero. Also let
+\newcommand{\Zb}[1][j]{{Z^*_{n{#1}}}}
+\begin{align}\label{eq:11}
+  Z_n(\tau, m) &= \tfrac{1}{\sqrt{n}} \sum_{t\in I_n(\tau, m)} (X_{nt} - \bar X_n) \\
+  Z_n^*(\tau,m)&= \tfrac{1}{\sqrt{n}} \sum_{t \in I_n(\tau,m)} (X_{nt}^{*} - \bar X_n) \label{eq:12}
+\intertext{and}
+  \Zb          &= Z_n^*(K_{n,j-1}, M_{nj}),
+\intertext{and define the corresponding demeaned terms}
+  Z_n'(\tau, m) &= \tfrac{1}{\sqrt{n}} \sum_{t\in I_n(\tau, m)} (X_{nt} - \mu_{nt})
+  \label{eq:13}\\
+  Z_n^{\prime*}(\tau,m)&= \tfrac{1}{\sqrt{n}} \sum_{t \in I_n(\tau,m)} (X_{nt}^{*} - \mu_{nt}^*)
+  \label{eq:14}
+\intertext{and}
+  Z_{nj}^{\prime *} &= Z_n^{\prime*}(K_{n,j-1}, M_{nj}), \label{eq:15}
+\end{align}
+where $\mu_{nt}^*$ is the expected value of the observation in the
+original dataset corresponding to the $t$th observation in the
+bootstrapped dataset. Further, define the filtration
+\begin{equation}
+\Gs_{nj} = \sigma(Z^*_{n1},\dots, Z^*_{nj},~X_{n1},\dots,X_{nn},~\Ms)
+\end{equation}
+so that $\{Z_{nj}^* / \sigma_n^*, \Gs_{nj}\}$ is a martingale difference
+array.
+
+By construction,
+\begin{equation}\label{eq:16}
+  \tfrac{1}{\sqrt{n}} \sum_{t=1}^n (X_{nt}^{*} - \bar X_n)
+  = \sum_{j=1}^{J_n} \Zb
 \end{equation}
 and
-\begin{equation}
-  \label{eq:4}
-  \pr^{*}\Big[\ \Big|\sum_{j=1}^{J_n} Z_{nj}^{*2}/ \eta_n^{2} - 1
-  \Big|\ > \epsilon \ \Big|\ \mathcal{M}_n \Big] \to^p 0 \qquad \forall \epsilon > 0,
-\end{equation}
-since~\eqref{eq:13} and~\eqref{eq:4} ensure that $Z_{nj}^{*}/\eta_n$ obeys a
-martingale difference \clt\ \citep[e.g.][Theorem
-3.3]{HaH:80}.
-
-First we will prove
-\begin{equation}\label{eq:41}
-  \E\Big[ \sum_{j=1}^{J_n} \E^{*}\big((Z_{nj}^{*2} / \eta_n^2) 1\{
-  Z_{nj}^{*2} / \eta_n^2 > \epsilon\} \mid \mathcal{M}_n\big) \ \Big|\
-  \mathcal{M}_n\Big] \to^p 0,
-\end{equation}
-which implies~\eqref{eq:13}.  Note that
-\begin{equation*}
-  \E^{*}(g(Z_{nj}^{*}) \mid \mathcal{M}_n) = \tfrac{1}{n}
-  \sum_{\tau=0}^{n-1} g(Z_n(\tau, M_{nj}))
-\end{equation*}
-almost surely for any function $g$.  As a consequence, we can write
-\begin{multline}\label{eq:32}
-  \E\Big( \sum_{j=1}^{J_n} \E^{*}\big( (Z_{nj}^{*2}/\eta_n^{2})
-  1\{Z_{nj}^{*2}/\eta_n^{2} > \epsilon\} \ \big|\ \mathcal{M}_n\big)
-  \ \Big|\ \mathcal{M}_{n} \Big)
-  \\\begin{split}= \tfrac{1}{n} \sum_{\tau=0}^{n-1} \sum_{j=1}^{J_n} &
-     \frac{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n}{\eta_n^2}
-  \E\Bigg( \frac{Z_n(\tau, M_{nj})^2}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n} 
-  \\ & \times 1\Bigg\{\frac{Z_n(\tau, M_{nj})^2}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n} 
-  > \frac{\eta_n^2 \epsilon}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n}\Bigg\} 
-  \ \Bigg|\ \mathcal{M}_n \Bigg)
-\end{split}
-\end{multline}
-almost surely.  Lemma~\ref{res:L} implies that there exists a finite,
+\begin{equation}\label{eq:17}
+  \Em^{*}g(\Zb,\dots,\Zb[k]) = \frac{1}{n^{k-j+1}}
+  \sum_{\tau_1=0}^{n-1} \cdots \sum_{\tau_{k-j+1}=0}^{n-1}
+  g(Z_n(\tau_1, M_{nj}),\dots,Z_n(\tau_{k-j+1}, M_{nk}))
+\end{equation}
+almost surely for any function $g$ and any $j \leq k$. Equation~\eqref{eq:17}
+conditions on the lengths of each block, but averages over their
+starting points.
+
+\subsection*{Proof of Theorem~\ref{main-bootstrap-clt}}
+{%
+\newcommand{\Db}[1][j]{D_{n#1}^{*}}
+\newcommand{\Zsum}{\sum_{j=1}^{J_n} \Zb / \sigma_n}
+First we prove that
+\begin{equation}\label{eq:37}
+  \sup_x \big\lvert \pr^{*}\big[
+  \sqrt{n}(\bar X_{n}^{*} -  \bar X_n) \big/ \sigma_n^{*}
+  \leq x \big] - \Phi(x) \big\rvert \to^p 0
+\end{equation}
+where $\sigma_n^{*2} = n \E^* (\bar X_n^* - \bar X_n)^2$.
+Rewrite $\sqrt{n}(\bar X_{n}^{*} - \bar X_n)$ as in
+Equation~\eqref{eq:16}, so
+\begin{equation*}
+  \tfrac{1}{\sqrt{n}} \sum_{t=1}^n (X_{nt}^* - \bar X_n) =
+  \sum_{j=1}^{J_n} Z_{nj}^*
+\end{equation*}
+and $\{\Zb / \sigma_n^*, \Gs_{nj}\}$ is a martingale difference
+array. Moreover,
+\begin{equation}
+  \label{eq:18}
+  \Pm^{*} \Big[\sum_{j=1}^{J_n} \Zb / \sigma_n^* \leq x \Big] - \Phi(x) \to^p 0,
+\end{equation}
+for all $x$ if $\sigma_n^{*2} \to^p \sigma^2$ (which ensures that
+$\sigma_n^{*2}$ is uniformly a.s.\ positive and holds by
+Lemma~\ref{bootstrap-variance-convergence-lemma}) and the following
+two conditions hold for all positive $\epsilon$:
+\begin{equation}
+  \label{eq:19}
+  \sum_{j=1}^{J_n} \Em^{*} \big(Z_{nj}^{*2} \ind\{Z_{nj}^{*2}  >
+  \epsilon\}\big) \to^p 0
+\end{equation}
+and
+\begin{equation}
+  \label{eq:20}
+  \Pm^{*}\Big[\ \Big|\sum_{j=1}^{J_n} Z_{nj}^{*2} - \sigma_n^{*2}
+  \Big|\ > \epsilon \Big] \to^p 0
+\end{equation}
+since~\eqref{eq:19} and~\eqref{eq:20} ensure that $\Zb/\sigma_n^*$ obeys
+a martingale difference \clt\ \citep[e.g.][Theorem 3.3]{HaH:80}.%
+\footnote{Conditional on $X_{n1},\dots,X_{nn}$, $J_n$, and
+  $M_{n1},\dots,M_{n,J_n}$, the only stochastic components of $\Zsum$
+  are the start periods of each block, which are
+  $\discreteuniform(1,\dots,n)$ and are independent of all of the
+  other random variables in the information set used for conditioning.
+  Consequently, $\Pm^*$ is a regular conditional probability and
+  arguments like Hall and Heyde's (1980) Theorem 3.3
+  apply without modification on this probability measure. See
+  also Section 23.2 of \citet{Vaa:00}.
+
+  Also note that Hall and Heyde's Theorem 3.3 as stated imposes an
+  additional restriction on the sigma-fields. However, as Hall and
+  Heyde discuss on pages 59 and 63--64, that condition is unnecessary
+  here because the $\sigma_n^{*2}$ is measurable with respect to
+  all of the $\Gs_{nj}$.} %
+
+For~\eqref{eq:20}, since $Z_{nj}^*$ and $Z_{nk}^*$ ($k \neq j$) are uncorrelated
+conditional on $X_{n1},\dots,X_{nn},$ and $\Ms$, we have
+\begin{equation*}
+  \sum_{j=1}^{J_n} Z_{nj}^{*2} - \sigma_n^{*2} =
+  \sum_{j=1}^{J_n} \Big( Z_{nj}^{*2} - (1/J_n) \E^* \sum_{j=1}^{J_n} Z_{nj}^{*2} \Big)
+\end{equation*}
+almost surely. But
+\begin{equation*}
+   \Big\{\tfrac{n}{M_{nj}} \Big(Z_{nj}^{*2} - (1/J_n) \E^* \sum_{j=1}^{J_n} Z_{nj}^{*2}\Big),
+   \ \Gs_{nj} \Big\}
+\end{equation*}
+is a uniformly-integrable martingale difference array
+by Lemma~\ref{bootstrapped-zsq-uniform-integrability-lemma},
+and satisfies the \lln\ (e.g., \citealp{Dav:94}, Theorem 19.7), so
+this sum converges to zero in conditional probability, proving~\eqref{eq:20}.
+
+To prove~\eqref{eq:19}, it suffices to show that
+\begin{equation}\label{eq:21}
+  \Em \sum_{j=1}^{J_n} \Em^{*}\big(Z_{nj}^{*2} \ind\{Z_{nj}^{*2} > \epsilon\}\big) \to^p 0.
+\end{equation}
+Lemma~\ref{bootstrapped-zsq-uniform-integrability-lemma} implies that there exists a finite,
 monotone function $B(\cdot)$ such that $B(x) \to 0$ as $x \to \infty$
 and
+\begin{equation*}
+  \Em( (n Z_{nj}^{*2} / M_{nj}) \ind\{n Z_n^{*2} / M_{nj} > \epsilon n / M_{nj}\}) \\
+  \leq B(\epsilon n /M_{nj})
+\end{equation*}
+almost surely for large enough $n$ and all $j$ and $\tau$.  Consequently,
+\begin{align*}
+    \Em \sum_{j=1}^{J_n} \Em^{*}( Z_{nj}^{*2} \ind\{Z_{nj}^{*2} > \epsilon\})
+    & \leq \sum_{j=1}^{J_n} ( M_{nj} / n )\, B(\epsilon n /M_{nj}) \\
+    & \leq \max_{j = 1,\dots,J_n} B(\epsilon n / M_{nj}) \sum_{i=1}^{J_n} M_{ni} / n \\
+    & = B(\epsilon n / \max_{j = 1,\dots,J_n} M_{nj}) \\
+    & \to^p 0 \text{\ as\ } n \to \infty,
+\end{align*}
+where the equality holds by monotonicity of $B$ and convergence in
+probability holds by Lemma~\ref{block-length-convergence-lemma},
+completing the proof of~\eqref{eq:19}.
+The Dominated Convergence Theorem then ensures that
+\begin{equation}\label{eq:22}
+  \pr^{*} \Big[\sum_{j=1}^{J_n}
+  Z_{nj}^{*} / \sigma_n^* \leq x \Big] - \Phi(x) \to^p 0.
+\end{equation}
+follows from~(\ref{eq:18}). (Also see
+Lemma~\ref{equivalent-convergence-from-lie-lemma}.)
+
+Lemma~\ref{bootstrap-variance-convergence-lemma} implies that
+$\sigma_n^{*2}$ and $\hat\sigma_n^{*2}$ both converge to $\sigma^2$ in
+probability. This convergence then implies that
+\begin{equation}
+  \label{eq:23}
+  \pr^{*}\big[\sqrt{n}(\bar X_{n}^{*} - \bar X_n) \leq x\big] \to^p \Phi(x/\sigma)
+\end{equation}
+and
+\begin{equation}
+\label{eq:24}
+  \pr^{*}\big[\sqrt{n}(\bar X_{n}^{*} - \bar X_n) / \hat\sigma_n^{*}
+  \leq x\big] \to^p \Phi(x)
+\end{equation}
+for any $x$.  These results are sufficient for~\eqref{eq:36}
+and~\eqref{eq:2} though an argument attributed to Poly{\`a}
+that proceeds as follows.
+Let $k$ be a finite integer and define $x_i = \sigma \Phi^{-1}(i/k)$ for $i =
+0,\dots,k$ (so $x_0 = -\infty$ and $x_k = +\infty$).
+For any $x \in [x_i, x_{i+1}]$,
+\begin{align*}
+  \pr^*\big[\sqrt{n} (\bar X_n^* - \bar X_n) \leq x] - \Phi(x/\sigma)
+  &\leq \pr^*\big[\sqrt{n} (\bar X_n^* - \bar X_n) \leq x_{i+1}] - \Phi(x_i/\sigma) \\
+  &= \pr^*\big[\sqrt{n} (\bar X_n^* - \bar X_n) \leq x_{i+1}] - \Phi(x_{i+1}/\sigma) + 1/k
+\intertext{and}
+  \pr^*\big[\sqrt{n} (\bar X_n^* - \bar X_n) \leq x] - \Phi(x/\sigma)
+  &\geq \pr^*\big[\sqrt{n} (\bar X_n^* - \bar X_n) \leq x_i] - \Phi(x_{i+1}/\sigma) \\
+  &= \pr^*\big[\sqrt{n} (\bar X_n^* - \bar X_n) \leq x_i] - \Phi(x_i/\sigma) - 1/k
+\end{align*}
+almost surely. Then
 \begin{multline*}
-\E\Bigg( \frac{Z_n(\tau, M_{nj})^2}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n}
-  \times 1\Bigg\{\frac{Z_n(\tau, M_{nj})^2}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n} > \frac{\eta_n^2 \epsilon}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n}\Bigg\} 
-  \ \Bigg|\ \mathcal{M}_n \Bigg) \\
-  \leq B\Bigg(\frac{\eta_n^2\epsilon}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n}\Bigg)
+  \sup_{x \in (-\infty, +\infty)} \big| \pr^*\big[\sqrt{n} (\bar X_n^* - \bar X_n) \leq x] - \Phi(x/\sigma) \big| \\
+  \leq \sup_{i=0,\dots,k} \big|\pr^{*}\big[\sqrt{n}(\bar X_{n}^{*} - \bar X_n) \leq x_i \big] - \Phi(x_i/\sigma) \big| + 1/k
 \end{multline*}
-almost surely for all $n$, $j$, and $\tau$.  Consequently, the right
-side of~\eqref{eq:32} is bounded by
-\begin{equation*}
-\tfrac{1}{n} \sum_{\tau=0}^{n-1} \sum_{j=1}^{J_n} 
-\frac{\nu_{nj}^2(\tau) + \sigma^2 M_{nj}/n}{\eta_n^2} B\Bigg(\frac{\eta_n^2
-  \epsilon}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n}\Bigg)
-\end{equation*}
-a.s., and this quantity is a.s. less than
-\begin{equation*}
-  O_{a.s.}(1) \max_{\tau = 0,\dots,n-1} \max_{j=1,\dots,J_n} B\Bigg(\frac{\eta_n^2\epsilon}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n}\Bigg)
-\end{equation*}
-by definition.  Moreover
-\[\max_{\tau=0,\dots,n-1} \max_{j=1,\dots,J_n} B\Bigg(\frac{\eta_n^2 \epsilon}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n}\Bigg)
-= B\Bigg(\min_{\tau=0,\dots,n-1} \min_{j=1,\dots,J_n} \frac{\eta_n^2 \epsilon}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n}\Bigg)\]
-a.s. by monotonicity, and
-\begin{equation*}
-  \min_{\tau=0,\dots,n-1} \min_{j=1,\dots,J_n} \frac{\eta_n^2}{\nu_{nj}^2(\tau) + \sigma^2 M_{nj} / n} \to^p \infty
-\end{equation*}
-by Lemmas~\ref{res:a1}, \ref{res:16},
-and~\ref{res:B}, completing the proof of \eqref{eq:41}.
-For~\eqref{eq:4},
-\begin{equation*}
-  \sum_{j=1}^{J_n} Z_{nj}^{*2} = \eta_n^2 + \sum_{j=1}^{J_n}
-  \big(Z_{nj}^{*2} - \E^*(Z_{nj}^{*2} \mid \mathcal{M}_n)\big) +
-  \tfrac{1}{n} \sum_{\tau=0}^{n-1} \sum_{j=1}^{J_n} \big(Z_{n}(\tau,
-  M_{nj})^2 - \nu_{nj}^2(\tau)\big) \qquad
-  \text{a.s.}.
-\end{equation*}
-The first summation on the right is $o_p(\eta_n^2)$ by
-Lemma~\ref{res:H} and the second is $o_p(\eta_n^2)$ by
-Lemma~\ref{res:B}.
-
-The Dominated Convergence Theorem then ensures that
-\begin{equation}\label{eq:39}
-  \pr^{*} \Big[\sum_{j=1}^{J_n}
-  Z_{nj}^{*} / \eta_n \leq x \Big] - \Phi(x) \to^p 0.
-\end{equation}
-Lemma~\ref{res:B} proves that $\sigma_n^{*}/\eta_n \to^p 1$ and
-$\hat{\sigma}_n^{*}/\eta_n \to^p 1$, so
-\begin{equation}
-  \label{eq:17}
-  \pr^{*}\big[\sqrt{n}(\bar X_{n}^{*} - \mu_{n}^{*}) / \sigma_n^{*}
-  \leq x\big] \to^p \Phi(x)
-\end{equation}
-and
-\begin{equation}
-  \label{eq:17}
-  \pr^{*}\big[\sqrt{n}(\bar X_{n}^{*} - \mu_{n}^{*}) / \hat\sigma_n^{*}
-  \leq x\big] \to^p \Phi(x)
-\end{equation}
-for any $x$.  These results are sufficient for~\eqref{eq:30}
-and~\eqref{eq:9} since the Normal distribution is continuous
-\citep[see, for example,][Lemma 2.11]{Vaa:00}.\qed
-
-\subsection*{Proof of Theorem~\ref{thm:2}}
-Again, I will only present a proof for the Stationary Bootstrap.
-The proof follows that of \citet{JoD:00b} closely and notation is reused from the
-proof of Theorem~\ref{thm:1}.  Lemma~\ref{res:B} implies that
-$\pr^{*}[\dist(W_n^{*}, W) > \delta] \to^p 0$ is sufficient for all of Theorem~\ref{thm:2}'s
-conclusions
-  \begin{equation*}
-    W_n^{*}(\gamma) = \tfrac{1}{\sqrt{n}} \sum_{t=1}^{\lfloor \gamma n
-      \rfloor} (X^{*}_{nt} - \mu_n^{*})/\eta_{n}.
-  \end{equation*}
-  From Theorem~\ref{thm:1}, we know that
-  \begin{equation*}
-    (W^{*}_n(\gamma_1),\dots, W^{*}_n(\gamma_l)) \to^d
-    (W(\gamma_1),\dots,W(\gamma_l))
-  \end{equation*}
-  in probability for any finite $l$ and $\gamma_1,\dots,\gamma_l \in
-  [0,1]$, so the result holds if $W_n^{*}(\gamma)$ is stochastically
-  equicontinuous and if the increments of $W^{*}_n(\cdot)$ are
-  independent in the limit \citep[Theorems~15.4 and~15.5]{Bil:68}.
-
-  Stochastic equicontinuity requires that
-  \begin{equation}\label{eq:22} 
-    \lim_{\delta \to 0} \limsup_{n \to \infty} \E\Big( \pr^{*}\Big[\sup_{\gamma
-    \in [0,1]} \sup_{\gamma' \in (\gamma-\delta, \gamma+\delta) \cap
-    [0,1]]} |W_n^{*}(\gamma) - W_n^{*}(\gamma')| >
-  \epsilon \ \Big|\ \mathcal{M}_n \Big]\Big) = 0.
-  \end{equation}
-  By construction,
-  \begin{equation*}
-    W_n^*(\gamma) = \sum_{j=1}^{\lfloor \gamma J_n \rfloor} Z_{nj}^*  +
-    \big(1 - 2 \times 1\{ \gamma n \leq K_{n, \lfloor \gamma J_n \rfloor}\}\big)
-    \sum_{t \in L_n(\gamma)} (X_{nt}^* - \mu_{nt}^*)
-  \end{equation*}
-  where 
-  \[L_n(\gamma) =
-  \{\min(K_{n,\lfloor \gamma J_n \rfloor}, \lfloor n \gamma \rfloor) + 1,\dots,
-  \max(K_{n,\lfloor \gamma J_n \rfloor}, \lfloor n \gamma \rfloor)\},
-  \]
-  so we have the upper bound
-  \begin{align}\label{eq:27}
-    \E \Big(\pr^{*}\Big[&\sup_{\gamma \in [0,1]} \sup_{\gamma' \in
-      (\gamma-\delta, \gamma+\delta) \cap [0,1]]}
-    |W_n^{*}(\gamma) - W_n^{*}(\gamma')| > \epsilon \
-    \Big|\ \mathcal{M}_n \Big]\Big) \nonumber \\
-    &\leq \E \Big(\pr^{*} \Big[\sup_{\gamma \in [0,1]} \sup_{\gamma' \in
-      (\gamma, \gamma+2\delta) \cap [0,1]]} \Big\lvert
-    \sum_{j={\lfloor \gamma J_n \rfloor}}^{\lfloor \gamma'J_n \rfloor}
-    Z_{nj}^{*}/ \eta_n \Big\rvert > \epsilon \
-    \Big|\ \mathcal{M}_n \Big]\Big) \nonumber \\
-    &\quad+ 2 \E \Big(\pr^{*} \Big[\sup_{\gamma \in [0,1]} \Big\lvert
-    \tfrac{1}{\sqrt{n}} \sum_{t \in L_n(\gamma)} (X_{nt}^{*} -
-    \mu_n^{*}) / \eta_{n}\Big\rvert > \epsilon \ \Big|\ \mathcal{M}_n \Big]\Big).
-  \end{align}
-  Just as in Theorem~\ref{thm:1}, $Z_{nj}^{*}/\eta_n$ is a martingale
-  difference array conditional on $\mathcal{M}_n$, and so
-  \begin{equation*}
-    \E \Big(\pr^{*} \Big[\sup_{\gamma \in [0,1]} \sup_{\gamma' \in
-      (\gamma, \gamma+2\delta) \cap [0,1]]} \Big\lvert 
-    \sum_{j={\lfloor \gamma J_n \rfloor}}^{\lfloor \gamma'J_n \rfloor}
-    Z_{nj}^{*} / \eta_n \Big\rvert > \epsilon \
-    \Big|\ \mathcal{M}_n \Big]\Big) \leq \tfrac{C \delta}{\epsilon} \E\big(\sigma_n^{*2}/\eta_n^2\big)
-  \end{equation*}
-  for some finite $C$ that does not depend on $n$ \citep[using,
-  e.g.][Theorem~15.14]{Dav:94}. And Lemmas~\ref{res:L} and~\ref{res:B}
-  imply that
-  \begin{equation*}
-    \lim_{\delta \to 0}\limsup_{n\to\infty}  \tfrac{C \delta}{\epsilon} \E(\sigma_n^{*} /
-    \eta_n) = 0.
-  \end{equation*}
-
-  The second term in \eqref{eq:27} is a.s. equal to
-  \begin{equation*}
-    \E\Big( \tfrac{2}{n} \sum_{\tau=0}^{n-1} \pr\Big[\sup_{\gamma \in
-      [0,1]} \Big\lvert \tfrac{1}{\eta_n \sqrt{n}} \sum_{t \in I(\tau, |\lfloor
-      \gamma n \rfloor - K_{n,\lfloor \gamma J_n \rfloor}|)} (X_{nt} -
-    \bar X_n) \Big\rvert > \epsilon \ \Big|\ \mathcal{M}_n\Big]\Big)
-  \end{equation*}
-  since the $X_{nt}^{*}$'s are all in the same ``block'' by
-  construction, and this quantity is a.s. bounded by
-  \begin{multline}\label{eq:24}
-    2 \max_{\tau=0,\dots,n-1} \E \Big(\pr\Big[\sup_{\gamma \in [0,1]} \Big\lvert
-    \tfrac{1}{\eta_n \sqrt{n}} \sum_{t \in I(\tau, |\lfloor \gamma n
-      \rfloor - K_{n,\lfloor \gamma J_n \rfloor}|)} (X_{nt} -
-    \mu_{nt}) \Big\rvert > \epsilon \ \Big|\ \mathcal{M}_n\Big]\Big) \\+ 2
-    \max_{\tau=0,\dots,n-1}\E \Big(\pr\Big[\sup_{\gamma \in [0,1]} \Big\lvert
-    \tfrac{1}{\eta_n \sqrt{n}} \sum_{t \in I(\tau, |\lfloor \gamma n
-      \rfloor - K_{n,\lfloor \gamma J_n \rfloor}|)} (\mu_{nt} - \bar
-    \mu_n) \Big\rvert > \epsilon \ \Big|\ \mathcal{M}_n\Big]\Big) \\+ 2
-    \max_{\tau=0,\dots,n-1}\E\Big( \pr\Big[\sup_{\gamma \in [0,1]} \Big\lvert
-    \tfrac{1}{\eta_n \sqrt{n}} \sum_{t \in I(\tau, |\lfloor \gamma n
-      \rfloor - K_{n,\lfloor \gamma J_n \rfloor}|)} (\bar \mu_{n} -
-    \bar X_n) \Big\rvert > \epsilon \ \Big|\ \mathcal{M}_n\Big]\Big).
-  \end{multline}
-  Lemma~\ref{res:B} implies that $\eta_n^{-1} = O_p(n^{-1/2})$ and the
-  \lln\ implies that $K_{n,\lfloor \gamma J_n\rfloor}/n$ converges
-  i.p.  to $\gamma$.  Consequently, the first term converges to zero
-  i.p. since the partial sums of $X_{nt} - \mu_{nt}$ obey an \fclt, the
-  second term converges to zero i.p. since $\mu_{nt}-\bar{\mu}_n$ is
-  bounded, and the third term converges to zero i.p. since $\bar{X}_n
-  - \bar{\mu}_n = O_p(n^{-1/2})$, proving~\eqref{eq:22}.
-
-  Since the increments of $W_n^{*}$ are asymptotically normal, we can
-  prove asymptotic independence by proving that the covariance between
-  any two distinct increments converges to zero.  Take $i < j$ and
-  define $i'$, $j'$, $i''$, and $j''$ so that
-  \begin{align*}
-    \gamma_{i-1} n &\in [K_{n,i'-1}+1,K_{n,i'}] & \gamma_{i} n &\in [K_{n,i''-1}+1,K_{n,i''}]\\
-    \gamma_{j-1} n &\in [K_{n,j'-1}+1,K_{n,j'}] & \gamma_{j} n &\in [K_{n,j''-1}+1,K_{n,j''}].
-  \end{align*}
-  Then the covariance between $W_n^*(\gamma_i) - W_n^*(\gamma_{i-1})$
-  and $W_n^*(\gamma_j) - W_n^*(\gamma_{j-1})$ equals
-  \begin{multline}\label{eq:15}
-    \E^*((W_n^*(\gamma_i) - W_n^*(\gamma_{i-1}))
-    (W_n^*(\gamma_j) - W_n^*(\gamma_{j-1}))\mid \mathcal{M}_n) =\\
-    \begin{split}
-      \E^*\Big(&\Big(\tfrac{1}{\eta_n\sqrt{n}} \sum_{t=\lfloor \gamma_{i-1} n \rfloor + 1}^{K_{ni'}} (X_{nt}^{*} - \mu_n^{*}) 
-    + \tfrac{1}{\eta_n} \sum_{k=i'+1}^{i''-1} Z_{nk}^{*} + \tfrac{1}{\eta_n \sqrt{n}} \sum_{t=K_{n,i''-1}+1}^{\lfloor \gamma_i n \rfloor} (X_{nt}^{*} - \mu_n^{*})\Big) \\
-    &
-      \times \Big(\tfrac{1}{\eta_n\sqrt{n}} \sum_{t=\lfloor \gamma_{j-1} n \rfloor + 1}^{K_{nj'}} (X_{nt}^{*} - \mu_n^{*}) 
-    + \tfrac{1}{\eta_n} \sum_{k=j'+1}^{j''-1} Z_{nk}^{*} 
-  \end{split}\\
-  + \tfrac{1}{\eta_n \sqrt{n}} \sum_{t=K_{n,j''-1}+1}^{\lfloor
-    \gamma_j n \rfloor} (X_{nt}^{*} - \mu_n^{*})\Big) \ \Big|\
-  \mathcal{M}_n \Big)
-\end{multline}
-  almost surely (with obvious modifications if $i' = i''$ or $j' =
-  j''$).  Since the blocks are independent under the bootstrap-induced
-  probability measure, the right side of~\eqref{eq:15} equals
-  \begin{equation*}
-    \E^{*}\Big( \tfrac{1}{\eta_n^2 n} \sum_{s=K_{n,i''-1}+1}^{\lfloor \gamma_i n \rfloor} (X_{ns}^{*} - \mu_n^{*})
-    \sum_{t=\lfloor \gamma_{j-1} n \rfloor + 1}^{K_{nj'}} (X_{nt}^{*} - \mu_n^{*}) \ \Big|\ \mathcal{M}_n\Big) 1\{K_{ni''} = K_{nj'} \}
-  \end{equation*}
-  which is almost surely bounded in absolute value by
-  \begin{equation*}
-     \E^{*}\Big(\Big( \tfrac{1}{\eta_n \sqrt{n}} \sum_{s=K_{n,i''-1}+1}^{\lfloor \gamma_i n \rfloor} (X_{ns}^{*} - \mu_n^{*})\Big)^2 \ \Big|\ \mathcal{M}_n\Big)^{1/2}
-     \E^{*}\Big(\Big( \tfrac{1}{\eta_n \sqrt{n}} \sum_{t=\lfloor \gamma_{j-1} n \rfloor+1}^{K_{n,j'}} (X_{nt}^{*} - \mu_n^{*})\Big)^2 \ \Big|\ \mathcal{M}_n\Big)^{1/2}.
-  \end{equation*}
-  Each of these terms converges to zero in probability as before, completing the proof.
- \qed
+almost surely, and~\eqref{eq:23} ensures that
+\begin{equation*}
+  \sup_{i=0,\dots,k} \big|\pr^{*}\big[\sqrt{n}(\bar X_{n}^{*} - \bar X_n)
+  \leq x_i \big] - \Phi(x_i/\sigma) \big| + 1/k \to^p 1/k
+\end{equation*}
+for any finite $k$. Since $k$ is arbitrary,~\eqref{eq:37} holds. Since
+Theorem~\ref{main-bootstrap-clt}'s assumptions ensure that the original
+array obeys the \clt,~\eqref{eq:36} holds \citep[Theorem 2]{Jon:97}.
+
+A similar argument applies to the asymptotic distribution of
+$\sqrt{n}(\bar X_n^* - \bar X_n) / \hat\sigma_n^*$, completing the
+proof.\qed
+}
+
+\subsection*{Proof of Theorem~\ref{main-bootstrap-invariance-theorem}}
+\newcommand{\gn}{{\lfloor \gamma n \rfloor}}
+\newcommand{\gJ}{{\lfloor \gamma J_n \rfloor}}
+\newcommand{\lastK}{{K_{n, \gJ}}}
+Define $W_n^{\prime*}$ as
+\begin{equation*}
+  W^{\prime*}_n(\gamma)
+  = \tfrac{1}{\sqrt{n}} \sum_{t=1}^\gn (X_{nt}^* - \bar X_{n})/\sigma
+  = \sum_{j=1}^\gJ \Zb /\sigma + Z_n^*(\lastK, \gn - \lastK) / \sigma.
+\end{equation*}
+Lemma~\ref{bootstrap-variance-convergence-lemma} ensures that
+$\sigma_n^{*2}$ and $\hat\sigma_n^{*2}$ both converge in probability to
+$\sigma^2$, so it suffices to prove that $\pr^*[\dist(W_n^{\prime*}, W) >
+\delta)] \to^p 0$; we can also assume without loss of generality that
+$\sigma^2 = 1$. Moreover,
+Lemma~\ref{equivalent-convergence-from-lie-lemma} ensures that it
+suffices to prove unconditional convergence, so we will establish
+$\pr[\dist(W_n^{\prime *}, W) > \delta] \to 0$.
+
+Theorem~\ref{main-bootstrap-clt} implies that, for any fixed $\gamma$,
+$W_n^{\prime *}(\gamma)$ is asymptotically normal and, as a
+partial sum of an \mds, $W_n^{\prime *}$ has asymptotically independent
+increments. To see this, choose $\gamma, \gamma' \in [0,1]$ and
+$\delta, \delta' > 0$ so that $\delta + \gamma \leq \gamma'$. Since
+the increments of $W_n^{\prime *}$ are uncorrelated conditional on
+$X_{1n},\dots,X_{nn}$, and $\Ms$, we have
+\begin{equation*}
+    \E\big| (W_n^{\prime *}(\delta' + \gamma') - W_n^{\prime *}(\gamma'))
+  (W_n^{\prime *}(\delta + \gamma) - W_n^{\prime *}(\gamma)) \big| = 0
+\end{equation*}
+for large enough $n$ if $\gamma' > \gamma + \delta$ and, if $\gamma' =
+\gamma + \delta$,
+\begin{multline*}
+  \E\big[(W_n^{\prime *}(\delta' + \gamma') - W_n^{\prime *}(\gamma'))
+  (W_n^{\prime *}(\delta + \gamma) - W_n^{\prime *}(\gamma)) \big] = \\
+  \E \Em^*\big\{- Z_n^*(\lfloor \gamma' n \rfloor, K_{n, \lceil \gamma' J_n \rceil }- \lfloor \gamma' n \rfloor)
+  Z_n^*(K_{n,\lfloor (\gamma + \delta) J_n \rfloor},
+  \lfloor (\gamma + \delta) n \rfloor - K_{n,\lfloor (\gamma + \delta) J_n \rfloor}))\big\}.
+\end{multline*}
+But this second quantity can be bounded:
+\begin{align*}
+  \E \Em^*\big\{-& Z_n^*(\lfloor \gamma' n \rfloor,
+  K_{n, \lceil \gamma' J_n \rceil }- \lfloor \gamma' n \rfloor)
+  Z_n^*(K_{n,\lfloor (\gamma + \delta) J_n \rfloor},
+  \lfloor (\gamma + \delta) n \rfloor - K_{n,\lfloor (\gamma + \delta) J_n \rfloor}))\big\} \\
+  &\leq \big\{\E \Em\big[Z_n^*(\lfloor \gamma' n \rfloor, K_{n, \lceil \gamma' J_n \rceil }- \lfloor \gamma' n \rfloor)\big]^2 \\
+  & \quad \times \big\{\E \Em Z_n^*(K_{n,\lfloor (\gamma + \delta) J_n \rfloor},
+  \lfloor (\gamma + \delta) n \rfloor - K_{n,\lfloor (\gamma + \delta) J_n \rfloor}))^2\big\}^{1/2} \\
+  &\leq C \E M_{n, \lfloor (\gamma + \delta) J_n \rfloor} / n
+\end{align*}
+for some constant $C$ by
+Lemma~\ref{bootstrapped-zsq-uniform-integrability-lemma}. This term
+converges to zero by Lemma~\ref{block-length-convergence-lemma}.
+
+Consequently, as in \cite{JoD:00b}, the result follows from stochastic
+equicontinuity \citep[Theorems 15.4 and 15.5]{Bil:68} namely that
+\begin{equation*}
+  \lim_{\delta \to 0} \limsup_{n \to \infty} \pr[\sup_{\gamma \in [0,1]}
+  \sup_{\gamma' \in [\gamma - \delta, \gamma + \delta]}
+    | W_n^{\prime *}(\gamma) - W_n^{\prime *}(\gamma') | > \epsilon] = 0
+\end{equation*}
+for any positive $\epsilon$.  Fix $\delta> 0$ such that $D = 2/\delta$
+is a positive integer and let $\gamma_d = d/D$ for $d =
+0,\dots,D$. Then, mimicking the argument in \cite{JoD:00b},
+\begin{align*}
+  \pr[\sup_{\gamma \in [0,1]} &
+  \sup_{\gamma' \in [\gamma - \delta, \gamma + \delta]}
+  | W_n^{\prime *}(\gamma) - W_n^{\prime *}(\gamma') | > \epsilon] \\
+  &\leq \pr[ \sup_{d = 1,\dots,D} \sup_{\gamma \in [0,\delta]}
+  | W_n^{\prime *}(\gamma + \gamma_d) - W_n^{\prime *}(\gamma_d) | > \epsilon/2] \\
+  &\leq  (4/\epsilon^2) \sum_{d=1}^D \E[\sup_{\gamma \in [0,\delta]}
+  | W_n^{\prime *}(\gamma + \gamma_d) - W_n^{\prime *}(\gamma_d) |^2 \\
+  &\qquad\qquad\qquad \times \ind\{\sup_{\gamma \in [0,\delta]}
+  | W_n^{\prime *}(\gamma + \gamma_d) - W_n^{\prime *}(\gamma_d) |^2 > \epsilon^2/4\}] \\
+  &\leq  (4/\epsilon^2) \max_{d=1,\dots,D} \E[\sup_{\gamma \in [0,\delta]}
+  (1/\delta) | W_n^{\prime *}(\gamma + \gamma_d) - W_n^{\prime *}(\gamma_d) |^2 \\
+  &\qquad\qquad\qquad \times \ind\{\sup_{\gamma \in [0,\delta]}
+  (1/\delta) | W_n^{\prime *}(\gamma + \gamma_d) - W_n^{\prime *}(\gamma_d) |^2 > \epsilon^2/4\delta\}].
+\end{align*}
+Lemma~\ref{bootstrapped-zsq-uniform-integrability-lemma} implies that
+\begin{equation*}
+  \sup_{\gamma \in [0,\delta]}
+  (1/\delta) | W_n^{\prime *}(\gamma + \gamma_d) - W_n^{\prime *}(\gamma_d) |^2
+\end{equation*}
+is uniformly integrable, so there exists a finite and positive
+function $B$ such that $B(x) \to 0$ as $x \to \infty$ and
+\begin{multline*}
+  \E[\sup_{\gamma \in [0,\delta]}
+  (1/\delta) | W_n^{\prime *}(\gamma + \gamma_d) - W_n^{\prime *}(\gamma_d) |^2
+  \ind\{\sup_{\gamma \in [0,\delta]}
+  (1/\delta) | W_n^{\prime *}(\gamma + \gamma_d) - W_n^{\prime *}(\gamma_d) |^2 > x\}] \\
+  \leq B(x)
+\end{multline*}
+for all $d$ and $\delta$ and all large enough $n$.
+
+As a result,
+\begin{align*}
+  \lim_{\delta \to 0} \limsup_{n\to\infty} \pr[\sup_{\gamma \in [0,1]}
+  \sup_{\gamma' \in [\gamma - \delta, \gamma + \delta]}
+  | W_n^{\prime *}(\gamma) - W_n^{\prime *}(\gamma') | > \epsilon] & \leq
+  \lim_{\delta \to 0} (4/\epsilon^2)
+  B(\epsilon^2/4\delta) \\
+  &= 0,
+\end{align*}
+completing the proof.\qed
 
 \section{Supplemental results}
-As in the proofs of Theorems~\ref{thm:1} and~\ref{thm:2}, we only
-present the proofs for the Stationary Bootstrap as those for the
-Circular and Moving Block bootstraps are similar but less complicated.
-
-\begin{lem}\label{res:a1}
-  Suppose that $M_{n1}, M_{n2},\dots$ are i.i.d. geometric random
+
+\begin{lem}\label{block-length-convergence-lemma}
+  Suppose that $M_{n1}, M_{n2},\dots$ are i.i.d.\ geometric random
   variables with success parameter $p_n = c n^{-a}$ with $a, c \in
@@
   \ell_n^{1+\epsilon} \to^p 0$ as $n \to \infty$ for any positive
-  $\epsilon$ and $C$, and
+  $\epsilon$ and $C$,
   \item $\max_{i=1,\dots,J_n} M_{ni} /
   \ell_n^{1+\epsilon} \to^p 0$ as $n \to \infty$ for any positive
-  $\epsilon$.
+  $\epsilon$, and
+  \item $\sum_{i=1}^{J_n} M_{ni}^2 / n^2 \to^p 0$.
   \end{enumerate}
@@
 
-\begin{proof}[Proof of Lemma~\ref{res:a1}]
+\begin{proof}[Proof of Lemma~\ref{block-length-convergence-lemma}]
   To prove part 1, observe that, for any increasing positive sequence
@@
     \pr\Big[\max_{i=1,\dots,J_n} M_{ni} > x\Big] & \leq
-    \pr\Big[\max_{i=1,\dots,\lfloor C n p_n \rfloor} M_{ni} > x \text{ or
-    } J_n > \lfloor C n p_n \rfloor\Big] \\
+    \pr\Big[\max_{i=1,\dots,\lfloor C n p_n \rfloor} M_{ni} > x
+    \text{\ or\ } J_n > \lfloor C n p_n \rfloor\Big] \\
     & \leq \pr\Big[\max_{i=1,\dots,\lfloor C n p_n \rfloor} M_{ni} > x\Big]
@@
   The proof of part 4 is the same as part 2, making the obvious
-  substitutions.
+  substitutions. Part 5 holds because $\sum_{i=1}^{J_n} M_{ni}^2/n^2
+  \leq \max_{i=1,\dots,J_n} M_{ni}/n$ which converges to zero in
+  probability by part 2.
 \end{proof}
 
-The next result is identical to \citepos{Mcl:75} Theorem~1.6, but is
-stated for conditional expectations so that it is relevant for our
-bootstrap results. The proof is identical to the original.
-\begin{lem}\label{res:16}
-  Let $\{\mathcal{G}_n\}$ be a sequence of $\sigma$-fields,
-  $\{\mathcal{F}_{nt}\}$ an array of $\sigma$-fields such that
-  $\mathcal{G}_n \subset \mathcal{F}_{nt}$ for each $n$ and $t$, and
-  suppose that $\{X_{nt}\}$ is an array such that
-  \begin{equation*}
-    \E\big(\big( \E( X_{nt} \mid \mathcal{F}_{n,t-m} \big)^2 \ \big|\
-    \mathcal{G}_n\big)^{1/2} \leq \psi_m c_{nt}
-  \end{equation*}
-  and
-\begin{equation*}
-  \E\big(\big(X_{nt} - \E( X_{nt}\mid F_{n,t+m}) \big)^2 \ \big|\
-  \mathcal{G}_n\big)^{1/2} \leq \psi_{m+1} c_{nt}  
-\end{equation*}
-almost surely, with $\psi_m = O(m^{-1/2-\delta})$ for some positive
-$\delta$ and $c_{nt} \in \mathcal{G}_n$ for every $n$ and $t$.  Then
-there exists a sequence of random variables $\Delta_n \in
-\mathcal{G}_n$ such that $\Delta_n = O_p(1)$ and
-\begin{equation}\label{eq:40}
-  \E\Big( \max_{u \leq s, t \leq v} \Big(\sum_{w=s}^t X_{nw}\Big)^2 \ \Big|\
-  \mathcal{G}_n\Big) \leq \Delta_n \sum_{t=u}^v c_{nt}^2
-\end{equation}
-almost surely.
-\end{lem}
-
-\begin{lem}\label{res:L}
-  Define $Z_n(\tau,m)$ as in Equation~\eqref{eq:18}.  Under the
-  conditions of Theorem~\ref{thm:1}, the family
-  \begin{equation*}
-    \Bigg\{\frac{Z_{n}(\tau,m)^2}{\E
-  Z_n(\tau,m)^2 + \sigma^2 m / n}\ ;\quad \tau, m, n\Bigg\}
-  \end{equation*}
- is uniformly integrable.
+\begin{lem}\label{equivalent-convergence-from-lie-lemma}
+  If $\{A_n\}$ is a sequence of events then the following are equivalent:
+  \begin{align*}
+  \pr[A_n] &\to 0, &
+  \pr^*[A_n] &\to 0 \text{\ in\ }L_1, &
+  &\text{and}&
+  \Pm^*[A_n] &\to 0 \text{\ in\ }L_1.
+  \end{align*}
 \end{lem}
 \begin{proof}
-  We can write 
+  Since $|\pr[A_n]| = \E |\pr^*[A_n]| = \E |\pr^*_{\mathcal{M}}[A_n]|$ these
+  conditions are equivalent by definition.
+\end{proof}
+
+\begin{lem}\label{bootstrap-variance-convergence-lemma}
+Under the conditions of Theorem~\ref{main-bootstrap-clt},
+\begin{gather}
+  \label{eq:25}
+  \sum_{j=1}^{J_n} (Z_{nj}^{*2} - \Em^* Z_{nj}^{*2}) \to^p 0,
+  \\
+  \label{eq:26}
+  \sum_{j=1}^{J_n} (Z_{nj}^{*2} - Z_{nj}^{\prime*2}) \to^p 0,
+\end{gather}
+and $\pr^*[ |\sigma_n^{*2} - \sigma^2| > \epsilon] \to^p 0$.
+If, in addition, $\bar X_n^* - \bar X_n = O_p(1/\sqrt{n})$ then
+$\pr^*[ |\hat\sigma_n^{*2} - \sigma^2| > \epsilon] \to^p 0$.
+\end{lem}
+
+\begin{proof}
+  For~\eqref{eq:26}, $(Z_{nj}^{*2} - \Em^* Z_{nj}^{*2}) \cdot (n /
+  M_{nj})$ is a uniformly integrable martingale difference array, by
+  Lemma~\ref{bootstrapped-zsq-uniform-integrability-lemma}, and
+  satisfies the \lln. (See~\citealp{Dav:94}, Theorem 19.7.)
+  For~\eqref{eq:26}, observe that
+  \begin{equation*}
+    \Big| \sum_{j=1}^{J_n} (Z_{nj}^{*2} - Z_{nj}^{\prime*2}) \Big| \leq
+    2 \Big(\sum_{j=1}^{J_n} Z_{nj}^{*2} \Big)^{1/2}
+    \Big(\tfrac{1}{n} \sum_{t=1}^n (\mu_{nt} - \bar X_n)^2\Big)^{1/2}
+    + \tfrac{1}{n} \sum_{t=1}^n (\mu_{nt} - \bar X_n)^2
+  \end{equation*}
+  after several applications of the Cauchy-Schwarz
+  inequality. Lemma~\ref{lln-for-real-zsq}, along with~\eqref{eq:17}
+  and~\eqref{eq:25}, implies that $\sum_j Z_{nj}^{*2} = O_p(1)$;
+  $(1/n) \sum_t (\mu_{nt} - \bar X)^2$ converges to zero in
+  probability by assumption on $\mu_{nt} - \bar\mu_n$ and because
+  $\bar X$ itself obeys the \lln.
+
+  To show that $\sigma_n^{*2}$ converges, we can write
+  \begin{multline*}
+    \sigma_n^{*2} - \sigma^2 = \E^*\Big\{ \sum_{j=1}^{J_n} (Z_{nj}^{*2} - Z_{nj}^{\prime*2}) \Big\}
+    + \tfrac{1}{n} \sum_{\tau=0}^{n-1} \E^* \Big\{\sum_{j=1}^{J_n}
+    \big( Z_{n}^{\prime}(\tau,M_{nj})^2 - \Em Z_{n}^{\prime}(\tau,M_{nj})^2 \big)\Big\} \\
+    + \tfrac{1}{n} \sum_{\tau=0}^{n-1} \E^* \Big\{\sum_{j=1}^{J_n}
+    \Em Z_{n}^{\prime}(\tau,M_{nj})^2  - \sigma^2\Big\}.
+  \end{multline*}
+  Uniform integrability ensures that the convergence in~(\ref{eq:25})
+  holds in $L_1$ as well and
+  Lemma~\ref{equivalent-convergence-from-lie-lemma} then implies that
+  the first term converges to zero in probability.
+  Lemma~\ref{lln-for-real-zsq} proves that the second and third
+  summation converge to zero in probability as well.
+
+  Next,
+  \begin{equation*}
+    \hat \sigma_n^{*2} - \sigma_n^{*2}
+    = \sum_{j=1}^{J_n} \big( Z_{nj}^* + (M_{nj}/\sqrt{n}) (\bar X_n - \bar X_{n}^*) \big)
+    - \E^*  \sum_{j=1}^{J_n} Z_{nj}^{*2}
+  \end{equation*}
+  so, in light of the previous arguments, $\hat\sigma_n^{*2} \to^p \sigma^2$ if
+  \begin{equation}
+    (\bar X_n - \bar X_n^*)^2 \sum_{j=1}^{J_n} M_{nj}^2/n \to^p 0,
+  \end{equation}
+  which holds by Lemma~\ref{block-length-convergence-lemma} and
+  assumption.
+\end{proof}
+
+\begin{lem}\label{lln-for-real-zsq}
+  If the conditions of Theorem~\ref{main-bootstrap-clt} hold then
+  \begin{gather}
+    \pr\Big[ \Big\lvert
+    \tfrac{1}{n} \sum_{\tau=0}^{n-1} \sum_{j=1}^{J_n}
+    \big[ Z_n'(\tau, M_{nj})^2 - \Em Z_n'(\tau, M_{nj})^2 \big]
+    \Big\rvert > \epsilon \Big] \to 0,\label{eq:27}
+    \intertext{and}
+    \pr\Big[ \Big\lvert
+    \tfrac{1}{n} \sum_{\tau=0}^{n-1} \sum_{j=1}^{J_n}
+    \Em Z_n'(\tau, M_{nj})^2 - \sigma^2
+    \Big\rvert > \epsilon \Big] \to 0.\label{eq:28}
+  \end{gather}
+\end{lem}
+\newcommand{\nMj}{\lfloor n / M_{nj} \rfloor}
+
+\noindent For these two proofs, let $\ell_n = (p_n
+\log p_n^{-1})^{-1}$ and let $L_{nj} = \nMj$; $\ell_n$ represents a
+smaller block size that satisfies $\ell_n J_n / n \to^p 0$.
+
+\begin{proof}[Proof of~(\ref{eq:27})]
+  We can express this summation as
+  \begin{multline}\label{eq:29}
+    \tfrac{1}{n} \sum_{\tau=0}^{n-1}  \sum_{j=1}^{J_n}
+    \big\{Z_n'(\tau, M_{nj})^2 - \Em Z_n'(\tau, M_{nj})^2 \big\}
+    \\ =
+    \tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau=0}^{M_{nj}-1}
+    \sum_{i=0}^{L_{nj}-1}\big\{\big[ Z_n'(\tau + i M_{nj}, M_{nj} - \ell_n) + Z_n'(\tau + (i+1) M_{nj} - \ell_n, \ell_n)\big]^2 \\
+    - \Em\big[ Z_n'(\tau + i M_{nj}, M_{nj} - \ell_n) + Z_n'(\tau + (i+1) M_{nj} - \ell_n, \ell_n)\big]^2 \big\} \\
+    + \tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau= M_{nj}L_{nj}}^{n-1}
+    \big\{Z_{n}'(\tau, M_{nj})^2 - \Em Z_n'(\tau, M_{nj})^2 \big\}
+  \end{multline}
+  almost surely.
+
+  By Lemma~\ref{dejong-restatement-lemma} (Equation~\ref{eq:32}), for
+  any $\delta > 0$ there exist positive $C$ and $\epsilon$ such that
+  \begin{align*}
+    \Big\lVert\tfrac{1}{n} \sum_{j=1}^{J_n} & \sum_{\tau=0}^{M_{nj}-1}
+    \sum_{i=0}^{L_{nj}-1} \big\{ Z_n'(\tau + i M_{nj}, M_{nj} - \ell_n)^2 -
+    \Em \big(Z_n'(\tau + i M_{nj}, M_{nj} - \ell_n)^2\big) \big\}\Big\rVert_1 \\
+    &\leq \E \tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau=0}^{M_{nj}-1}
+    \Em \Big| \sum_{i=0}^{L_{nj}-1} \big\{ Z_n'(\tau + i M_{nj}, M_{nj} - \ell_n)^2 -
+    \Em \big(Z_n'(\tau + i M_{nj}, M_{nj} - \ell_n)^2\big) \big\} \Big|\\
+    &\leq \E \Big(\tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau=0}^{M_{nj}-1} 
+    \big(2 \delta + C \, \tfrac{M_{nj}}{n^{1/2} \ell^{1/2+\epsilon}}\big)\Big)
+  \end{align*}
+  for large enough $n$, which converges to $2 \delta$ by
+  Lemma~\ref{block-length-convergence-lemma}. Also,
+  Lemma~\ref{zsq-uniform-integrability-lemma} ensures that there
+  exists a value $C$ (possibly different from the value above) such
+  that
+  \begin{equation*}
+    \E\Big(\tfrac{1}{n}  \sum_{j=1}^{J_n} \sum_{\tau=0}^{M_{nj}-1} \sum_{i=0}^{L_{nj}-1}
+    Z_n'(\tau + (i+1) M_{nj} - \ell_n, \ell_n)^2 \Big)
+    \leq C \E \Big(\sum_{j=1}^{J_n} L_{nj} \ell_n M_{nj} / n^2\Big)
+  \end{equation*}
+  and
+  \begin{equation*}
+    \E \Big(\tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau= M_{nj}L_{nj}}^{n-1} Z_{n}'(\tau, M_{nj})^2\Big)
+    \leq
+    C \E \Big(\sum_{j=1}^{J_n} M_{nj}^2 / n^2 \Big)
+  \end{equation*}
+  for large enough $n$, both of which converge to zero in $L_1$ as $n
+  \to \infty$ by Lemma~\ref{block-length-convergence-lemma}.  These
+  three convergence results imply that the \textsc{rhs} of
+  (\ref{eq:29}) converges to zero, completing the proof.
+\end{proof}
+
+\begin{proof}[Proof of~(\ref{eq:28})]
+  After using similar arguments to in the previous part of the proof,
+  the conclusion holds if
+  \begin{equation*}
+    \tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau=0}^{M_{nj}-1} \sum_{i=0}^{L_{nj} - 1}
+    \Em Z_n'(\tau + i M_{nj}, M_{nj} - \ell_n)^2 \to^p \sigma^2,
+  \end{equation*}
+  which is a direct implication of Lemma~\ref{dejong-restatement-lemma}.
+\end{proof}
+
+\begin{lem}\label{bootstrapped-zsq-uniform-integrability-lemma}
+  Under the conditions of Theorem~\ref{main-bootstrap-clt},
   \begin{multline}\label{eq:35}
-    Z_n(\tau, m)^2 = \big(Y_n(\tau, m) + \tfrac{m}{\sqrt{n}}
-    (\bar{\mu}_n - \bar{X}_n) \big)^2 + \Big(\tfrac{1}{\sqrt{n}}\sum_{t \in I_n(\tau,m)} (\mu_{nt} - \bar{\mu}_n)\Big)^2\\
-    + 2 \big(Y_n(\tau, m) + \tfrac{m}{\sqrt{n}} (\bar{\mu}_n - \bar{X}_n)\big)
-    \Big(\tfrac{1}{\sqrt{n}}\sum_{t \in I_n(\tau,m)} (\mu_{nt} - \bar{\mu}_n)\Big)
-  \end{multline}
-  almost surely, with 
-  \begin{equation}\label{eq:28}
-    Y_n(\tau, m) = \tfrac{1}{\sqrt{n}} \sum_{t \in
-      I_n(\tau, m)} (X_{nt} - \mu_{nt}).
-  \end{equation}
-  Then the conclusion holds if
-  \begin{equation}\label{eq:34}
-    \frac{\big(\sqrt{n} Y_n(\tau, m) + m (\bar{\mu}_n - \bar{X}_n) \big)^2}
-    {\E \big(\sqrt{n} Y_n(\tau,m) + m (\bar{\mu}_n - \bar{X}_n)\big)^2  
-    + \big(\sum_{t \in I_n(\tau,m)} (\mu_{nt} - \bar{\mu}_n)\big)^2 + m \sigma^2},
-  \end{equation}
-  and
-  \begin{equation}\label{eq:33}
-    \frac{\big(\sum_{t \in I_n(\tau,m)} (\mu_{nt} - \bar{\mu}_n)\big)^2}
-    {\E \big(\sqrt{n} Y_n(\tau,m) + m (\bar{\mu}_n - \bar{X}_n) \big)^2  +\big(\sum_{t \in I_n(\tau,m)} (\mu_{nt} - \bar{\mu}_n)\big)^2 + \sigma^2}
-  \end{equation}
-  are all uniformly integrable.  But $\tfrac{n}{m} Y_n(\tau, m)^2$ and
-  $n (\bar{\mu_n} - \bar X_n)^2$ are uniformly integrable by existing
-  results \citep{Dav:92,Dav:93,Jon:97} and~\eqref{eq:33} is bounded
-  above by construction, completing the proof.
-\end{proof}
-
-\begin{lem}\label{res:H}
-  Suppose the conditions of Theorem~\ref{thm:1} hold and define
-  $Z_{nj}^{*}$ and $\eta_n^2$ as in Equations~\eqref{eq:18}
-  and~\eqref{eq:26}. Then
-  \begin{equation}
-    \label{eq:2}
-    \pr^{*}\Big[\Big| \sum_{j=1}^{J_n} \big(Z_{nj}^{*2} -
-    \E^{*}(Z_{nj}^{*2} \mid \mathcal{M}_n)\big) \Big| \Big/ \eta_n^2
-    > \delta \ \Big|\ \mathcal{M}_n \Big] \to^p 0
-  \end{equation}
-  for any positive $\delta$.
-\end{lem}
-
-\begin{proof}
-  The proof follows the steps of, for example, Davidson's Theorem 19.7
-  using Lemma~\ref{res:L} to establish the necessary inequalities.
-  The same argument behind Lemma~\ref{res:L} ensures that, for any
-  positive $\epsilon$, there exists a constant $B_{\epsilon}$ such
-  that
-  \begin{equation}
-    \label{eq:21}
-    \sup_{\tau, m, n} \big\| \big(Y_n(\tau,m)^2 n / \sigma^2 m \big)
-    1\{Y_n(\tau,m)^2 n/ \sigma^2 m  > B_{\epsilon}^2\}\ \big\|_1 \leq \epsilon
-  \end{equation}
-  with $Y_n(\tau, m)$ defined in~\eqref{eq:28}.  Let $u_{nj}$ be the
-  discrete uniform$(1,\dots,n)$ indicating the beginning of the $j$th
-  block, so that
-  \begin{equation*}
-    (X_{n,u_{nj}},\dots,X_{n,u_{nj} + M_{n,j} - 1}) = (X_{n,K_{n,j-1}+1}^{*},\dots,X_{n,K_{n,j}}^{*})
-  \end{equation*}
-  almost surely, and define
-  \begin{equation*}
-    U_{nj} = Y_{nj}^{*2} \, 1\{Y_{nj}^{*2} \leq B_{\epsilon}^2 \sigma^2 M_{nj} / n d \}
-  \end{equation*}
-  and
-  \begin{equation*}
-    V_{nj} = Y_{nj}^{*2} - U_{nj},
-  \end{equation*}
-  so
-  \begin{multline*}
-    Z_{nj}^{*2} - \E^{*}(Z_{nj}^{*2} \mid \mathcal{G}_{n,j-1}) 
-    = U_{nj} - \E^{*}(U_{nj} \mid \mathcal{G}_{n,j-1}) + V_{nj} - \E^{*}(V_{nj} \mid \mathcal{G}_{n,j-1}) \\ 
-    + \big(Z_{nj}^{*2} - \E^{*}(Z_{nj}^{*2} \mid \mathcal{G}_{n,j-1})\big) - \big(Y_{nj}^{*2} - \E^{*}(Y_{nj}^{*2} \mid \mathcal{G}_{n,j-1})\big)
-  \end{multline*}
-  almost surely.
-
-  Now, just as in Davidson's proof, we have (with all relationships
-  understood to hold almost surely)
-  \begin{align*}
-    \E\Big(\Big|\tfrac{1}{\eta_n^2} \sum_{j=1}^{J_n} \big(U_{nj} - \E^{*}& (U_{nj} \mid \mathcal{G}_{n,j-1})\big) \Big| \ \Big|\ \mathcal{M}_n\Big)\\
-    &\leq \tfrac{1}{\eta_n^2}\Big[\E\Big( \E^{*} \Big( \Big|\sum_{j=1}^{J_n} \big(U_{nj} 
-     - \E^{*}(U_{nj} \mid \mathcal{G}_{n,j-1})\big) \Big|^2 \ \Big|\ \mathcal{M}_n\Big)\ \Big|\ \mathcal{M}_n\Big)\Big]^{1/2}
-    \\ &= \tfrac{1}{\eta_n^2} \Big(\sum_{j=1}^{J_n} \E\big(\E^{*}\big([U_{nj} - \E^{*}(U_{nj} \mid \mathcal{G}_{n,j-1})]^2\mid \mathcal{M}_{n} \big) \mid \mathcal{M}_n\big) \Big)^{1/2} 
-    \\ &\leq \tfrac{1}{\eta_n^2} \Big(\sum_{j=1}^{J_n} \E \E^{*}(U_{nj}^2 \mid \mathcal{M}_n) \Big)^{1/2} 
-    \\ & \leq \tfrac{B_{\epsilon}}{\eta_n^2} \Big(\sum_{j=1}^{J_n} \tfrac{1}{n} \sum_{\tau=0}^{n-1} \Big[\E(Y_n(\tau, M_{nj})^2 \mid \mathcal{M}_n)\Big]^2\Big)^{1/2}
-    \\ & \leq \tfrac{C_n}{\eta_n^2} \Big(\sum_{j=1}^{J_n} M_{nj}^2 / n^2\Big)^{1/2} \to^{L_1} 0
-  \end{align*}
-  for some $C_n$, with the last inequality a consequence of Lemma~\ref{res:16}
-  and convergence a consequence of Lemma~\ref{res:a1}.  Also,
-  \begin{align*}
-    \E \E^{*}\Big(\Big\lvert &\tfrac{1}{\eta_n^2} \sum_{j=1}^{J_n} (V_{nj} -
-      \E^{*}(V_{nj} \mid \mathcal{G}_{n,j-1})) \Big\rvert \ \Big|\ \mathcal{M}_n \Big)
-    \\ & \leq 2 \E \sum_{j=1}^{J_n} \tfrac{1}{\eta_n^2} \E^{*}(\lvert V_{nj} \rvert \mid \mathcal{M}_n)
-    \\ & \leq 2 \E \sum_{j=1}^{J_n} \tfrac{1}{\eta_n^2} Y_n(u_{nj}, M_{nj})^2
-    1\big\{Y_n(u_{nj}, M_{nj})^2 > B^2_{\epsilon} \sigma^2 M_{nj}/n \big\}
-    \\ & \leq 2 \epsilon \E \sum_{j=1}^{J_n} \tfrac{\sigma^2}{\eta_n^2} M_{nj} / n
-    \\ & \leq \tfrac{2\sigma^2}{\eta_n^2} \epsilon
-  \end{align*}
-  with the second to last inequality holding by the choice of
-  $B_{\epsilon}$ and all of these relationships understood to hold
-  almost surely.
-
-  Finally, 
-  \begin{multline*}
-    \tfrac{1}{\eta_n^2} \sum_{j=1}^{J_n} \big[(Z_{nj}^{*2} - \E(Z_{nj}^{*2} \mid \mathcal{G}_{n,j-1}) - (Y_{nj}^{*2} - \E(Y_{nj}^{*2} \mid \mathcal{G}_{n,j-1}))\big] \\
-    = \tfrac{2}{\eta_n^2} \sum_{j=1}^{J_n} \big[Y_{nj}^{*} - \E^{*}(Y_{nj}^{*} \mid \mathcal{G}_{n,j-1})]
-    \Big[\tfrac{M_{nj}}{\sqrt{n}} (\bar{X}_n - \bar{\mu}_n) + \tfrac{1}{\sqrt{n}} \sum_{t \in I_n(\tau, M_{nj})} (\mu_{nt} - \bar{\mu}_n)\Big]
-  \end{multline*}
-  almost surely, which converges to zero in $L_1$ by the usual arguments, completing the proof.
-\end{proof}
-
-\begin{lem}\label{res:B}
-  If the conditions of Theorem~\ref{thm:1} hold then
-  \begin{equation}
-    \label{eq:38}
-    \eta_n^2 - \sigma^2 - \tfrac{1}{n^2} \sum_{j=1}^{J_n} \sum_{\tau=0}^{n-1} \Big(\sum_{t \in I_n(\tau, M_{nj})} (\mu_{nt} - \bar{\mu}_n) \Big)^2 = o_p(1),
-  \end{equation}
-  \begin{equation}
-    \label{eq:19}
-    \tfrac{1}{n} \sum_{\tau=0}^{n-1} \sum_{j=1}^{J_n} Z_n(\tau,
-    M_{nj})^2 -\eta_n^2 = o_p(\eta_n^2),
-  \end{equation}
-  \begin{equation}\label{eq:37}
-    \sigma_n^{*2} - \eta_n^2 = o_p(\eta_n^2),
-  \end{equation}
-  and
-  \begin{equation}
-    \label{eq:36}
-    \hat\sigma_n^{*2} - \eta_n^2 = o_p(\eta_n^2).
-  \end{equation}
-\end{lem}
-
-\begin{proof} 
-  Equation~\eqref{eq:35}, along with Theorem~2 of \citet{Jon:97} and
-  Lemma~\ref{res:a1}, implies that
-  \begin{multline*}
-    \label{eq:52}
-    \sum_{j=1}^{J_n} \tfrac{1}{n} \sum_{\tau=0}^{n-1} Z_n(\tau,
-    M_{nj})^2 = \tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau=0}^{n-1}
-    Y_n(\tau, M_{nj})^2 + \tfrac{1}{n^2} \sum_{j=1}^{J_n}
-    \sum_{\tau=0}^{n-1} \Big(\sum_{t \in I_n(\tau, M_{nj})} (\mu_{nt} - \bar{\mu}_n)\Big)^2 \\
-    + \tfrac{2}{n^{3/2}} \sum_{j=1}^{J_n} \sum_{\tau=0}^{n-1}
-    Y_n(\tau, M_{nj}) \sum_{t\in I_n(\tau, M_{nj})} (\mu_{nt} -
-    \bar{\mu}_n) + o_p(1).
-  \end{multline*}
-  So~\eqref{eq:38} follows directly from Lemma~\ref{res:7}.
-  For~\eqref{eq:19}, it suffices to prove that
-  \begin{equation}
-    \label{eq:20}
-    \tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau=0}^{n-1} \big\{Y_n(\tau,
-    M_{nj})^2 - \E(Y_n(\tau, M_{nj})^2 \mid \mathcal{M}_n) \big\} \to^p 0,
-  \end{equation}
-  and
-  \begin{equation}
-    \label{eq:51}
-    \tfrac{1}{n^{3/2}} \sum_{j=1}^{J_n} \sum_{\tau=0}^{n-1}
-    Y_{n}(\tau, M_{nj})\sum_{t\in I_n(\tau, M_{nj})}(\mu_{nt} -
-    \bar{\mu}_n) = o_p(\eta_n).
-  \end{equation}
-  Observe that we can express the summation in~\eqref{eq:20} as
-  \begin{multline}\label{eq:47}
-    \tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau=0}^{n-1} \big\{Y_n(\tau,
-    M_{nj})^2 - \E(Y_n(\tau, M_{nj})^2 \mid \mathcal{M}_n) \big\} \\ =
-    \tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau=0}^{M_{nj}-1}
-    \sum_{i=1}^{L_{nj}}\big\{ Y_n(\tau+(i-1)M_{nj}, M_{nj})^2
-    - \E(Y_n(\tau+(i-1)M_{nj}, M_{nj})^2 \mid
-    \mathcal{M}_n)\big\} \\ + \tfrac{1}{n} \sum_{j=1}^{J_n}
-    \sum_{\tau= M_{nj}L_{nj}}^{n-1} \big\{Y_{n}(\tau, M_{nj})^2 -
-    \E(Y_n(\tau, M_{nj})^2 \mid \mathcal{M}_n)\big\}
-  \end{multline}
-  almost surely, where $L_{nj} = \lfloor n/ M_{nj} \rfloor$.  The
-  advantage of this representation is that each summation over
-  $i=1,\dots,L_{nj}$ is formed from adjacent blocks of the original
-  series, so standard blocking arguments can be applied.  Now let
-  $\ell_n = (p_n \log p_n^{-1})^{-1}$. By Lemma~\ref{res:7}, for any
-  $\delta > 0$ there exist positive $C$ and $\epsilon$ such that
-  \begin{multline*}
-    \Big\lVert\tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau=1}^{M_{nj}}
-    \sum_{i=1}^{L_{nj}}\big\{ Y_n(\tau+(i-1)M_{nj}, M_{nj})^2 -
-    \E(Y_n(\tau+(i-1)M_{nj}, M_{nj})^2 \mid
-    \mathcal{M}_n)\big\}\Big\rVert_1 \\ \leq C \tfrac{\ell_n}{n} + 2
-    \delta + C\, \Big\lVert \max_{j =
-      1,\dots,J_n}\big(\tfrac{M_{nj}}{n}\big)^{1/2} \max_{j =
-      1,\dots,J_n}\big(1,
-    \tfrac{M_{nj}}{\ell_n^{1+\epsilon}}\big)^{1/2} \Big\rVert_1
-  \end{multline*} 
-  which converges to $2 \delta$ by Lemma~\ref{res:a1}.  The second
-  term of~\eqref{eq:47} is $O_{p}(1 - M_{nj}/n)$ by Lemma~\ref{res:16},
-  proving~\eqref{eq:20}.
-
-  For~\eqref{eq:51}, the Cauchy-Schwarz inequality implies that
-  \begin{multline*}
-    \tfrac{1}{n^{3/2}} \sum_{j=1}^{J_n} \sum_{\tau=0}^{n-1}
-    \Big\lvert Y_{n}(\tau, M_{nj})\sum_{t\in I_n(\tau, M_{nj})}(\mu_{nt} -
-    \bar{\mu}_n)\Big\rvert \\\leq \Big\{\tfrac{1}{n} \sum_{j=1}^{J_n}
-    \sum_{\tau=0}^{n-1} \big(\tfrac{1}{\sqrt{n}} Y_n(\tau,
-    M_{nj})^2\big)\Big\}^{1/2} \Big\{\tfrac{1}{n} \sum_{j=1}^{J_n}
-    \sum_{\tau=0}^{n-1} \Big(\tfrac{1}{\sqrt{n}} \sum_{t \in I_n(\tau,
-      M_{nj})} (\mu_{nt} - \bar{\mu}_{n} )\Big)^2\Big\}^{1/2}.
-  \end{multline*}
-  Lemma~\ref{res:16} implies that
-  \begin{equation}
-    \label{eq:23}
-    \tfrac{1}{n} \sum_{j=1}^{J_n}
-    \sum_{\tau=0}^{n-1} \big(\tfrac{1}{\sqrt{n}} Y_n(\tau,
-    M_{nj})^2\big) \to^p 0
-  \end{equation}
-  and Equation~\eqref{eq:38} that
-  \begin{equation*}
-    \tfrac{1}{n} \sum_{j=1}^{J_n} \sum_{\tau=0}^{n-1}
-    \Big(\tfrac{1}{\sqrt{n}} \sum_{t \in I_n(\tau, M_{nj})} (\mu_{nt} -
-    \bar{\mu}_{n} )\Big)^2 = O_p(\eta_n^2).
-  \end{equation*}
-  completing the proof of~\eqref{eq:19}.
-
-  Result~\eqref{eq:37} is an immediate consequence of~\eqref{eq:19}
-  and Lemma~\ref{res:L}.  Finally, for~\eqref{eq:36}, observe that
-  \begin{equation*}
-    \hat{\sigma}_n^{*2} = \eta_n^2 + (\sigma_n^{*2} - \eta_n^2) + \sum_{j=1}^{J_n}\Big[
-    Z_{nj}^{*2} - \E^*(Z_{nj}^{*2} \mid \mathcal{M}_n)
-    + \tfrac{2 M_{nj}}{\sqrt{n}} (\mu_n^{*} - \bar{X}_n^{*})
-    Z_{nj}^{*} + \tfrac{M_{nj}^2}{n} (\mu_n^{*} - \bar{X}_n^{*})^2 \Big]
-  \end{equation*}
-  implying that $\hat{\sigma}_n^{*2}/\eta_n^2 \to^p 1$
-  by~\eqref{eq:37} along with Lemmas~\ref{res:a1},~\ref{res:L},
-  and~\ref{res:H}.
-\end{proof}
-
-\begin{lem}\label{res:7}
-  Define $Y_n(\tau, m)$ as in Equation~\eqref{eq:28} and $L_{nj} =
-  \lfloor n/M_{nj}\rfloor$. For any positive $\delta$, there exist
-  positive and finite constants $C$, $N$, and $\epsilon$ such that
-\begin{multline}\label{eq:29}
-  \E\Big(\Big\lvert\sum_{i=1}^{L_n} \big[Y_{n}(\tau + (i-1) M_{nj},
-  M_{nj})^2 -  Y_{n}(\tau + (i-1) M_{nj}, M_{nj} -
-  \ell)^2\big]\Big\rvert \ \Big|\
-  \mathcal{M}_n\Big) \leq C \tfrac{\ell}{n},
-\end{multline}
-\begin{multline}\label{eq:16}
-  \E\Big(\Big\lvert\sum_{i=1}^{L_n} \big[Y_{n}(\tau + (i-1) M_{nj},
-  M_{nj} - \ell)^2 \\- \E(Y_{n}(\tau + (i-1) M_{nj}, M_{nj} -
-  \ell)^2 \mid \mathcal{M}_n)\big]\Big\rvert \ \Big|\
-  \mathcal{M}_n\Big)\\ \leq 2 \delta + C \cdot \big(\tfrac{M_{nj}}{n}\big)^{1/2}
-  \max\big(1, \tfrac{M_{nj}}{\ell^{1+\epsilon}}\big)^{1/2},
+    \lim_{C \to 0} \limsup_{n \to \infty} \sup_{m' = 1,\dots,n}
+    \E\Big(\Big(\sum_{\tau=0}^{n-1} \max_{m=1,\dots,m'} Z_n(\tau, m)^2 / m'\Big) \\
+    \times\ind\Big\{\sum_{\tau=0}^{n-1} \max_{m=1,\dots,m'} Z_n(\tau, m)^2 / m' > C\Big\}\Big) = 0.
   \end{multline}
   and
-  \begin{multline}
-    \label{eq:5}
-    \E\Big(\Big\lvert \sum_{i=1}^{L_{n}} \E(Y_n(\tau + (i-1) M_{nj}, M_{nj} - \ell)^2 \mid
-    \mathcal{M}_n) - \sigma^2 \Big\rvert \ \Big|\ \mathcal{M}_n\Big) \leq 
-    \\ C\,  \nu_n^2(0, n) \Big(\ell \log(\ell)^2 \psi(\ell)^2 
-     + \sum_{m=\ell}^{\infty} \log(m)^2 \psi(m)^2 \Big)^{1/2} \Big( \psi(0)^2 + \sum_{v=1}^{\infty} \log(v)^2 \psi(v)^2 \Big)^{1/2}
+  \begin{multline}\label{eq:30}
+    \lim_{C \to \infty} \limsup_{n \to \infty} \sup_{\substack{\tau = 0,\dots,n-1 \\ m'=1,\dots,n}}
+    \E\Big(\max_{m = 1,\dots,m'} (n \, Z^*_n(\tau, m)^2 / m') \\
+    \times \ind\Big\{\max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m' > C\Big\}\Big)
+    = 0,
   \end{multline}
-  almost surely for all $j = 1,\dots,J_n$, $\tau= 0,\dots,n-1$,
-  $\ell=1,\dots,M_{nj}-1$, and $n > N$.  Moreover, if $\ell_n =
-  (p_n^{-1} \log p_n^{-1})^{-1}$ then
-  \begin{equation}
-    \label{eq:46}
-    \sup_{\tau=0,\dots,n-1} \E\Big(\Big\lvert \sum_{j=1}^{L_{n}} \E(Y_n(\tau + (i-1) M_{nj}, M_{nj} - \ell_n)^2 \mid
-    \mathcal{M}_n) - \sigma^2 \Big\rvert \ \Big|\ \mathcal{M}_n\Big) \to^{L_1} 0.
-  \end{equation}
+  making the families of random variables $\{\max_{m=1,\dots,m'}
+  Z_n(\tau, m)^2 n / m'\}$ and $\{\max_{m=1,\dots,m'}
+  Z^{*}_n(\tau, m)^2 n / m'\}$ uniformly integrable.
 \end{lem}
+
 \begin{proof}
-  Result~\eqref{eq:29} is immediate from Lemma~\ref{res:16}
-  and~\eqref{eq:46} follows directly from~\eqref{eq:5}.
-  Results~\eqref{eq:16} and~\eqref{eq:5} are direct extensions of
-  \citepos[Lemmas 5 and 4, respectively]{Jon:97}, replacing de Jong's
-  implicit use of inequalities with explicit inequalities.
+  For \eqref{eq:35}, take $\epsilon > 0$. The sum
+  \[
+  \sum_{\tau=0}^{n-1} \max_{m=1,\dots,m'} Z_n(\tau, m)^2 / m'
+  \]
+  is uniformly integrable if and only if it is uniformly $L_1$-bounded
+  and there exists an $\epsilon'$ such that
+  \[
+  \sup_{n, m} \E\Big( \ind(A) \sum_{\tau=0}^{n-1} \max_{m=1,\dots,m'} Z_n(\tau, m)^2 / m' \Big)
+  < \epsilon
+  \]
+  for every event $A$ satisfying $\pr(A) < \epsilon'$.
+  (\citealp{Dav:94}, 12.9.)
+  Lemma~\ref{zsq-uniform-integrability-lemma} ensures that there is an
+  $\epsilon'$ such that
+  \begin{equation*}
+    \sup_{n, m', \tau} \E\big( \ind(A) \max_{m=1,\dots,m'} Z_n'(\tau, m)^2 n / m' \big) \leq \epsilon / 9
+  \end{equation*}
+  for all $A$ with $\pr(A) \leq \epsilon'$. Then, writing
+  \begin{align*}
+    Z_n(\tau, m) &= Z_n'(\tau, m)
+    + \tfrac{1}{\sqrt{n}} \sum_{t \in I_n(\tau, m)}
+    \big((\mu_{nt} - \bar \mu_n) + (\bar \mu_n - \bar X_n)\big) \\
+    &= Z_n'(\tau, m)
+    + \tfrac{1}{\sqrt{n}} \sum_{t \in I_n(\tau, m)} (\mu_{nt} - \bar \mu_n)
+    - m Z'_n(0, n) \\
+  \end{align*}
+  gives the relations
+  \begin{align*}
+    \E\Big(\ind(A) \sum_{\tau=0}^{n-1} & \max_{m=1,\dots,m'} Z_n(\tau, m)^2/m'\Big) \\
+    &\leq 3 \sum_{\tau=0}^{n-1} \E\big( \ind(A)  \max_{m=1,\dots,m'} Z'_n(\tau, m)^2/m'\big) \\
+    &\quad+(3/n m') \E\Big(\ind(A) \sum_{\tau=0}^{n-1} \max_{m=1,\dots,m'}
+    \Big(\sum_{t \in I_n(\tau, m)} (\mu_{nt} - \bar \mu_n) \Big)^2\Big) \\
+    &\quad+ (3/m') \sum_{\tau=0}^{n-1}
+    \E (\ind(A) \max_{m=1,\dots,m'} m Z'_n(0, n)^2) \\
+    &\leq (2 \epsilon/3) + \pr(A) (3/n)\sum_{t=1}^n (\mu_{nt} - \bar \mu_n)^2
+  \end{align*}
+  where the last inequality holds as a consequence of $A$'s
+  construction. Since $(1/n)\sum_{t=1}^n (\mu_{nt} - \bar \mu_n)^2 \to
+  0$, choose $n$ large enough that this average is less than
+  $\epsilon/9$. The proof that that the first moment is bounded is
+  similar, which completes the proof of~(\ref{eq:35})
+
+  For~(\ref{eq:30}), we'll first show that, for every $\epsilon > 0$,
+  there exists an $\epsilon' > 0$ with the property that
+  \begin{equation}\label{eq:31}
+    \Em \Big(\ind(A) \times \max_{m = 1,\dots,m'} Z^*_n(\tau, m)^2 n / m'\Big) < \epsilon
+  \end{equation}
+  for any event $A \in \Gs \equiv \sigma(X_{11},\dots,X_{nn};\
+  M_{n1},\dots,M_{n,J_n};\ J_n)$ with $\pr(A) \leq \epsilon'$. Then we
+  will show that this property implies uniform integrability.%
+\footnote{The difference between this proof and the proof
+  of~\eqref{eq:35} is the measurability requirement. Here we need to
+  finesse measurability of the sets $A$.} %
+
+  First, take an arbitrary $\epsilon > 0$ and a value of $\epsilon' > 0$
+  so that
+  \begin{equation*}
+    \Em \Big(\ind(A) \sum_{\tau = 0}^{n-1} \tfrac{1}{m'} \max_{m = 1,\dots,m'}
+    Z_n(\tau, m)^2\Big) < \epsilon / 4
+  \end{equation*}
+  for any $A \in \Gs$ with $\pr(A) \leq \epsilon'$, which is shown to
+  exist in the first part of this Lemma. Then define $J(x)$ to be the
+  block index such that $K_{n,J(x) - 1} < x \leq K_{n,J(x)}$. We have
+  the relationships
+  \begin{align*}
+    \Em \Em^* \Big(&\ind(A) \times \max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m'\Big) \\
+    &= \Em \ind(A) \Em^* \Big[ \tfrac{n}{m'}\max_{m = 1,\dots, m'}
+    \Big(\sum_{j=J(\tau)+1}^{J(\tau + m)-1} Z_{nj}^*
+    + Z_n^*(\tau, K_{n,J(\tau)} - \tau) \\
+    &\quad+ Z_n^*(K_{n,J(\tau+m)-1}, m - K_{n,J(\tau + m)-1}) \Big)^2\Big] \\
+    &\leq 4 \Em \ind(A) \tfrac{1}{m'} \sum_{u = 0}^{n-1} \Big( \sum_{j=J(\tau)+1}^{J(\tau + m')-1}
+    Z_n(u, M_{nj})^2 + Z_n(u, K_{n,J(\tau)} - \tau)^2 \\
+    &\quad + Z_n(u, m' - K_{n,J(\tau+m')-1})^2\Big) \\
+    &= (4/m') \sum_{j=J(\tau)+1}^{J(\tau + m')-1} \Em\Big[ \ind(A) \sum_{u = 0}^{n-1} Z_n(u, M_{nj})^2\Big] \\
+    &\quad + (4/m') \Em\Big[\ind(A) \sum_{u = 0}^{n-1} Z_n(\tau_{J(\tau)}, M_{n,J(\tau)})^2\Big] \\
+    &\quad + (4/m') \Em\Big[ \ind(A)  \sum_{u = 0}^{n-1} Z_n(u, m' - K_{n,J(\tau+m')})^2\Big] \\
+    &\leq \epsilon.
+  \end{align*}
+  The first inequality is a consequence of Doob's maximal inequality
+  for martingales \citep[see][Theorem 15.15, for example]{Dav:94},
+  since $Z_{nj}^*$ is a martingale difference array, and the second
+  equality and last inequality follow by construction of $A$. A
+  similar argument also implies that $n Z_n^*(\tau, m)^2 / m'$ has
+  finite first moment.
+
+  Now, for uniform integrability, take $\epsilon > 0$, choose
+  $\epsilon'$ so that~\eqref{eq:31} holds for all $A \in \Gs$
+  s.t. $\pr(A) \leq \epsilon'$, and choose $C_0$ large enough that
+  \begin{equation*}
+    \Pm\Big[ \max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m' > C_0 \Big] \leq \epsilon'.
+  \end{equation*}
+  Markov's inequality guarantees the existence of this $C_0$. Then
+  \begin{equation*}
+    \Em \Big(\max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m'
+    \times \ind\Big\{ \max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m' > C \Big\}\Big) \leq \epsilon
+  \end{equation*}
+  for all $C > C_0$. Since $\epsilon$ is arbitrary, this completes the proof.
 \end{proof}
-\bibliography{texextra/AllRefs}
+
+\begin{lem}\label{dejong-restatement-lemma}
+\newcommand{\isum}{\sum_{i=0}^{\lfloor n/m \rfloor - 1}}
+  Suppose the conditions of Theorem~\ref{main-bootstrap-clt} hold.
+  For any positive $\delta$, there exist positive and finite constants
+  $C$, $n_0$, and $\epsilon$ such that
+  for all $n > n_0$, $m = 1,\dots,n$, $\tau = 0,\dots,m$, and $\ell =
+  1,\dots,m-1$:
+\begin{multline}\label{eq:32}
+    \E \Big\lvert \isum \big[Z_n'(\tau + i m, m - \ell)^2
+    - \E \big(Z_n'(\tau + i m, m - \ell)^2\big) \big]\Big\rvert \\
+    \leq 2 \delta + C \cdot \big(\tfrac{m}{n}\big)^{1/2}
+    \big(\tfrac{m}{\ell^{1+\epsilon}}\big)^{1/2}.
+\end{multline}
+Also, there exists a constant $C$ and a finite function $D(x)$ such
+that $D(x) \to 0$ as $x \to \infty$ such that, for large enough $n$,
+  \begin{equation}
+    \label{eq:33}
+    \E \Big\lvert \isum \E(Z_n'(\tau + i m, m - \ell)^2
+    - \sigma^2 \Big\rvert \leq C\, D(\ell).
+  \end{equation}
+\end{lem}
+
+Results~\eqref{eq:32} and~\eqref{eq:33} are direct extensions of
+\citepos{Jon:97} Lemmas 5 and 4, respectively, replacing de Jong's
+implicit use of inequalities with explicit inequalities. The
+supplemental appendix presents a proof of~\eqref{eq:33} to show the
+basic idea.
+
+\begin{lem}\label{zsq-uniform-integrability-lemma}
+\newcommand{\uiterm}{\max_{m \in 1,\dots,m'} \Big(
+  \sum_{t \in I_n(\tau, m)} (X_{nt} - \mu_{nt})\Big)^2 \Big/
+  \sum_{t\in I_n(\tau, m')} c_{nt}^2}
+\newcommand{\uitermb}{(1/m') \max_{m \in 1,\dots,m'} \Big(
+  \sum_{t \in I_n^*(\tau, m)} (X_{nt} - \mu_{nt})\Big)^2}
+  Under the conditions of Theorem~1,
+  \begin{multline}\label{eq:34}
+    \lim_{C \to 0} \limsup_{n \to \infty} \sup_{\substack{\tau = 0,\dots,n-1 \\  m' = 1,\dots,n}}
+    \E\big(\big(\max_{m=1,\dots,m'} Z'_n(\tau, m)^2 n / m'\big) \\
+    \times\ind\{\max_{m=1,\dots,m'} Z'_n(\tau, m)^2 n / m' > C\}\big)) = 0.
+  \end{multline}
+\end{lem}
+
+\begin{proof}
+  See supplemental appendix for the proof of~\eqref{eq:34}, which
+  follows \citet[Lemma 6.5]{Mcl:75b} and \citet[Lemma 3.5]{Mcl:77}
+  almost exactly and is also presented as Theorem~16.13 in
+  \citet{Dav:94}.
+\end{proof}
+
+\bibliography{texextra/references}
 \end{document}
@@
 % LocalWords:  de Jong's ns Mcl AllRefs nn th nm ni HaH formulae jn gcalhoun nN
-% LocalWords:  jel PaP DPP np Ames Resampling nonstationary cdf
+% LocalWords:  jel PaP DPP np Ames Resampling nonstationary cdf Helle

### 2015-12-31 subs/ETr2/reply_2.tex
[#15] Initialize response letter to referees
This commit adds the text from the referee reports to my (blank)
response letters. It also fixes the makefile rule to prevent
an error in texi2dvi.

Closes #15

\documentclass[12pt]{article}
\frenchspacing
\input{../../preamble.tex}
\usepackage[tiny]{titlesec}

\begin{document}
\section*{\hfill Reply to referee 2\hfill}

\begin{enumerate}
\item \textit{Corollary 1: Assuming there exists an estimator
$\hat{\sigma}_n^2(\gamma)$ such that $\sup_{\gamma}
|\sigma_n^2(\gamma)/\hat{\sigma}_n^2(\gamma) - 1| \to^p 0$ may not be
innocent. After all, for an i.i.d.\ sequence of mean zero, finite
variance $\varepsilon_i$, we could have
\[
\hat{\sigma}_{n}^2(\gamma) = \tfrac{1}{n} \sum_{i=1}^{[\gamma n]} \varepsilon_i^2
\quad\text{and}\quad
\sigma_n^2(\gamma) = [\gamma n] \sigma^2 / n.
\]
Then
\begin{align*}
\sup_{0 \leq \gamma \leq 1} | \sigma_n^2(\gamma) / \hat{\sigma}_n^2(\gamma) - 1 |
& = \sup_{0 \leq \gamma \leq 1} \Big| \sigma^2 \Big/ ([n\gamma])^{-1} \sum_{i=1}^{[\gamma n]} \varepsilon_i^2 - 1 \Big| \\
& = \sup_{k:1 \leq k \leq n} \Big| \sigma^2 \Big/ k^{-1} \sum_{i=1}^{k} \varepsilon_i - 1 \Big|
\end{align*}
and the last expression converges a.s. to a non-degenerate random
variable. It is not clear to me what exactly the author wants to
achieve by dividing by $\hat{\sigma}_n(\gamma)$. Clearly such a
division achieves that the resulting process is $N(0,1)$ and not
$N(0,\gamma)$ for each $\gamma$ which means that the limit is not
Wiener measure, and therefore I did not understand how the resulting
process can end up at $W^{*}$, which is undefined, but is suggested
through the use of the letter $W$ to be some type of Wiener measure.}

\item \textit{p. 11, first equation: there is an expectation of an
    absolute value there; should the absolute value be there?}

\item p. 12, Lemma 1: typo: ``$\sum_{i=1}^{J_n-1} < n$'' should read
  ``$\sum_{i=1}^{J_n-1} M_{ni} < n$''.

\item \textit{On page 7, I could not verify that (18) holds; that is,
    I could not see that none of the $X_{nt}^*$ is not counted twice
    or excluded in the $\sum_{j=1}^{J_n} Z_{nj}^*$.}

\item \textit{At this time, I still do not understand the reasoning of
    the author when it comes to conditioning issues. The author to his
    credit has added explanations, and very likely the problem is
    simply my lack of experience with bootstrap issues. However, on
    page 9 for example, the author says that Lemma 5 implies that
    there exists a finite, monotone function $B(\cdot)$ that has a
    limit of 0. As I read Lemma 5, I would think that this $B(\cdot)$
    depends on $\mathcal{M}$. Similarly, on page 15, the author
    applies Lemma 6, Equation 37; yet that result was derived for an
    unconditional expectation appearing on the spot where the author
    now uses $E_{\mathcal{M}}$. In short, I am still confused by some
    of the conditioning issues, but am willing to assume that the
    problem is with me and not with the author.}

\end{enumerate}
\end{document}

### 2015-12-31 subs/ETr2/reply_3.tex
[#15] Initialize response letter to referees
This commit adds the text from the referee reports to my (blank)
response letters. It also fixes the makefile rule to prevent
an error in texi2dvi.

Closes #15

\documentclass[12pt]{article}
\frenchspacing
\input{../../preamble.tex}
\usepackage[tiny]{titlesec}

\begin{document}
\section*{\hfill Reply to referee 3\hfill}

\begin{enumerate}
\item \textit{The first [issue] concerned the use of array notation,
    in contexts where it appeared to me unnecessary. I asked
    specifically, either for this to be dropped, or for examples to be
    given showing its role in applications.}

\item \textit{The second [issue] concerned the specification of the
    statistical model, in particular, to define the probability space
    appropriately, so as to develop the formal relationships between
    the various sub-sigma fields, and sequences and filtrations of
    same. For example, we need a formal context for objects like the
    sequence defined in equation (9). Clarity and formalism in these
    matters are especially important where random events generated by
    the bootstrap and by nature interact.}

\end{enumerate}
\end{document}

### 2015-12-31 Paper.tex
[#16] Finish correct capitalization of De Jong
This capitalization issue was initially fixed when I updated the
remote submodule; this commit finishes it.

Closes #16

@@
 \documentclass[11pt]{article}
+\IfFileExists{VERSION.tex}{\input{VERSION}}%
+{\date{Pdf compiled \today. (Version unclear; run `make VERSION.tex'.)}}
 \input{preamble}
-
+\input{VERSION}
 \begin{document}
@@
     \protect\url{gcalhoun@iastate.edu}. Web:
-    http://www.econ.iastate.edu/$\sim$gcalhoun.  I would like to thank
+    \protect\url{http://gray.clhn.org}.  I would like to thank
     Helle Bunzel, Dimitris Politis, Robert Taylor, and three anonymous
@@
     of][\textit{Econometric Theory}]{Jon:97}.  In doing so, this paper
-  extends de Jong's method of proof, a blocking argument, to hold with
+  extends De Jong's method of proof, a blocking argument, to hold with
   random and unequal block lengths.  This paper also proves that
@@
 used by \citet{Jon:97}.
-Note that de Jong does allow a little bit more flexibility in the
+Note that De Jong does allow a little bit more flexibility in the
 conditions on the array $\{c_{nt}\}$ \citep[see also][]{Dav:93};
@@
 Results~\eqref{eq:32} and~\eqref{eq:33} are direct extensions of
-\citepos{Jon:97} Lemmas 5 and 4, respectively, replacing de Jong's
+\citepos{Jon:97} Lemmas 5 and 4, respectively, replacing De Jong's
 implicit use of inequalities with explicit inequalities. The
@@
 % LocalWords:  CLT Kun LiS PoR GoW GoJ nt indices eq studentized JoD reindex nj
-% LocalWords:  de Jong's ns Mcl AllRefs nn th nm ni HaH formulae jn gcalhoun nN
+% LocalWords:  De Jong's ns Mcl AllRefs nn th nm ni HaH formulae jn gcalhoun nN
 % LocalWords:  jel PaP DPP np Ames Resampling nonstationary cdf Helle

### 2015-12-31 Paper.tex

@@
 
-  \noindent \textsc{jel} Classification: C12, C15
+  \noindent \allcaps{jel} Classification: C12, C15
 
@@
 \noindent Block bootstraps, e.g.\ the Moving Blocks
-\citep{Kun:89,LiS:92}, Circular Block \citep{PoR:92}, and Stationary
+(\citealp{Kun:89}, and \citealp{LiS:92}), Circular Block \citep{PoR:92}, and Stationary
 Bootstraps \citep{PoR:94}, have become popular in Economics, partly
@@
 general weak dependence and moment conditions.  Some recent papers
-(\citealp{GoW:02}; \citealp{GoJ:03}) relax the dependence and moment
-conditions of the original papers to fit with those commonly used in
-Econometrics based on Near-Epoch-Dependence (\ned).%
+(\citealp{GoW:02}, and \citealp{GoJ:03}) relax the dependence and moment
+conditions of the original papers to fit with the Near-Epoch-Dependence
+(\ned) assumptions commonly used in econometrics.%
 \footnote{\citet{GoW:02} show that these bootstrap methods can be
@@
     - \delta})$ for all $\delta>0$.  Dropping the index ``$n$'' gives
-  the series definition.  Note that strong and uniform mixing arrays
+  the series definition.  Note that the underlying strong and uniform mixing arrays
   are not required to be stationary.} %
@@
 methods consistently estimate the distribution of the sample mean
-under \citepos{Jon:97} assumptions, and show that an \fclt\ holds as
+under \citepos{Jon:97} assumptions and show that an \fclt\ holds as
 well.%
@@
 a recent review of the bootstrap for time-series
-processes,%
-\footnote{Also see the discussion papers:
-  \citet{Dah:11,GoP:11,Hor:11,JeM:11,KrP:11b}.} %
+processes%
+\footnote{Also see the discussion papers by \citet{Dah:11},
+\citet{GoP:11}, \citet{Hor:11}, \citet{JeM:11}, and
+\citet{KrP:11b}.} %
 and \citet{GoP:11} further discuss recent developments in
@@
 Theorem~\ref{main-bootstrap-clt} presents the main result, asymptotic normality of
-the distribution of bootstrapped partial sums.  This paper adopts the
+the distribution of bootstrapped sums. This paper adopts the
 standard notation that $\E^{*}$, $\var^{*}$, etc.\ are the usual
@@
 Bootstrap are presented, since proofs for the other methods are
-similar and easier to follow.  All limits are taken as $n \to \infty$
+similar and easier to construct.  All limits are taken as $n \to \infty$
 unless otherwise noted and $\lVert \cdot \rVert_r$ denotes the
@@
   \item $X_{nt}$ is $L_2$-\ned\ of size $-1/2$ on an array
-    $V_{nt}$ that is either strong mixing of size $-r/(r-2)$ or
+    $\{V_{nt}\}$ that is either strong mixing of size $-r/(r-2)$ or
     uniform mixing of size $-r/2(r-1)$, with $r > 2$.  The
@@
   \end{equation}
-  where $\Phi$ is the \textsc{cdf} of the Standard Normal
+  where $\Phi$ is the \allcaps{cdf} of the Standard Normal
   distribution and
@@
 \end{equation*}
-that adds up to the original summation, plus potentially a negligible
-residual, so $\sum_j Z_{nj}= (1/\sqrt{n}) \sum_t (X_{nt} - \mu_{nt}) +
+that adds up to the original summation (plus potentially a negligible
+residual) so $\sum_j Z_{nj}= (1/\sqrt{n}) \sum_t (X_{nt} - \mu_{nt}) +
 o_p(1)$. In \citet{Jon:97}, for example, the \clt\ for mixingale
@@
 \footnote{Some of the details of the argument will typically need to
-  change, since the original \clt\ only requires convergence for
+  change because the original \clt\ only requires convergence for
   $\tau_0 = 0$, but these details are often incidental to the original
@@
 bootstraps are typically consistent when the original dependent array
-obeys the \clt, and the connection should be useful for proving
+obeys the \clt\ and the connection should be useful for proving
 consistency of the bootstrap under other dependence conditions.
 
-For some uses, a \clt\ is inadequate and an \fclt\ is necessary.
-Theorem~\ref{main-bootstrap-clt} can be extended to give an \fclt\
-(using arguments from \citealp{JoD:00b}). We show in
+Theorem~\ref{main-bootstrap-clt} can be further extended to give an
+\fclt\ using arguments from \citet{JoD:00b}. We show in
 Theorem~\ref{main-bootstrap-invariance-theorem} that the partial sum
@@
 same general argument but are simpler. First we will define some
-notation that will be used repeatedly in our results.
+notation that will be used repeatedly.
 
@@
   also Section 23.2 of \citet{Vaa:00}.
-
   Also note that Hall and Heyde's Theorem 3.3 as stated imposes an
@@
   Heyde discuss on pages 59 and 63--64, that condition is unnecessary
-  here because the $\sigma_n^{*2}$ is measurable with respect to
+  here because $\sigma_n^{*2}$ is measurable with respect to
   all of the $\Gs_{nj}$.} %
 
-For~\eqref{eq:20}, since $Z_{nj}^*$ and $Z_{nk}^*$ ($k \neq j$) are uncorrelated
-conditional on $X_{n1},\dots,X_{nn},$ and $\Ms$, we have
+For~\eqref{eq:20}, $Z_{nj}^*$ and $Z_{nk}^*$ (when $k \neq j$) are
+conditionally uncorrelated given $X_{n1},\dots,X_{nn},$ and $\Ms$, which
+implies
 \begin{equation*}
@@
 is a uniformly-integrable martingale difference array
-by Lemma~\ref{bootstrapped-zsq-uniform-integrability-lemma},
-and satisfies the \lln\ (e.g., \citealp{Dav:94}, Theorem 19.7), so
+by Lemma~\ref{bootstrapped-zsq-uniform-integrability-lemma}
+and satisfies the \lln\ (e.g., \citealp{Dav:94}, Theorem 19.7). So
 this sum converges to zero in conditional probability, proving~\eqref{eq:20}.
@@
 \end{multline*}
-almost surely, and~\eqref{eq:23} ensures that
+almost surely and~\eqref{eq:23} ensures that
 \begin{equation*}
@@
 array obeys the \clt,~\eqref{eq:36} holds \citep[Theorem 2]{Jon:97}.
-
 A similar argument applies to the asymptotic distribution of
@@
 \end{equation*}
-for large enough $n$ if $\gamma' > \gamma + \delta$ and, if $\gamma' =
-\gamma + \delta$,
+for large enough $n$ if $\gamma' > \gamma + \delta$. If $\gamma' =
+\gamma + \delta$ then
 \begin{multline*}
@@
   Lemma~\ref{lln-for-real-zsq} proves that the second and third
-  summation converge to zero in probability as well.
+  summation converge to zero in probability.
 
@@
     \big[ Z_n'(\tau, M_{nj})^2 - \Em Z_n'(\tau, M_{nj})^2 \big]
-    \Big\rvert > \epsilon \Big] \to 0,\label{eq:27}
+    \Big\rvert > \epsilon \Big] \to 0 \label{eq:27}
     \intertext{and}
@@
   almost surely.
-
   By Lemma~\ref{dejong-restatement-lemma} (Equation~\ref{eq:32}), for
@@
   \end{align*}
-  gives the relations
+  gives the relationship
   \begin{align*}
@@
 
-  For~(\ref{eq:30}), we'll first show that, for every $\epsilon > 0$,
+  For~(\ref{eq:30}), we will first show that, for every $\epsilon > 0$,
   there exists an $\epsilon' > 0$ with the property that
@@
 
-  First, take an arbitrary $\epsilon > 0$ and a value of $\epsilon' > 0$
+  Take an arbitrary $\epsilon > 0$ and a value of $\epsilon' > 0$
   so that
@@
 Also, there exists a constant $C$ and a finite function $D(x)$ such
-that $D(x) \to 0$ as $x \to \infty$ such that, for large enough $n$,
+that $D(x) \to 0$ as $x \to \infty$ and, for large enough $n$,
   \begin{equation}
@@
 supplemental appendix presents a proof of~\eqref{eq:33} to show the
-basic idea.
+main idea.
 

### 2015-12-31 Paper.tex
[#5] Fix typo in Lemma 1
This commit fixes a typo pointed out by one of the referees.
Closes #5

@@
   (0,1)$, and that $\ell_n = (p_n \log p_n^{-1})^{-1}$ and define
-  $J_n$ so that $\sum_{i=1}^{J_n-1} < n \leq \sum_{i=1}^{J_n} M_{ni} $
+  $J_n$ so that $\sum_{i=1}^{J_n-1} M_{ni} < n \leq \sum_{i=1}^{J_n} M_{ni} $
   Then

### 2015-12-31 subs/ETr2/reply_ed.tex
[fixup] Add basic response letter to editor

\documentclass[12pt]{article}
\usepackage[margin=1.25in]{geometry}
\frenchspacing
\input{../../preamble.tex}
\usepackage[tiny]{titlesec}

\begin{document}
\noindent Hi Robert,

I have revised my paper, ``Block bootstrap consistency under weak
assumptions'' (ET \#2868) as requested by the referees. The letters to
each referee addresses their requests specifically. As a quick
summary, I've made the following changes:

\input{summary}
\end{document}

### 2015-12-31 Paper.tex
[#1] Add probabilistic infrastructure to appendix
As requested by one of the referees, we've added an explicit
probability infrastructure to the beginning of the appendix.

@@
 
-Define the \sigmafield
+First, the relevant probability infrastructure.  Let
+$(S, \Omega, \pr)$ be a probability space and define the sequence of
+sub-sigma-fields $\Omega_n \subset \Omega$. Assume that each
+$X_{nt}$, $V_{nt}$, $M_{nj}$, and $u_{nj}$ is $\Omega_n$-measurable,
+with $u_{nj}$ the $\operatorname{uniform}(1,\dots,n)$ random variables
+that designate the start period of each bootstrap ``block.'' Also
+define the \sigmafield\ generated by the stationary bootstrap's block
+lengths alone, which will be used repeatedly in our results,
 \begin{equation}
@@
 \E^*(\cdot \mid \Ms)$, etc.) An important property is
-that $\Ms$ is \emph{independent} of the $X_{nt}$, so we can treat any
+that $\Ms$ is \emph{independent} of the $X_{nt}$'s, $V_{nt}$'s, and
+$u_{nj}$'s, so we can treat any
 $M_{nj}$ and $J_n$ terms as constants within $\Em(\cdot)$ and
 $\Pm[\cdot]$ and integrate over the unconditional distributions of the
-$X_{nt}$. This property is especially important because it allows us
+other random variables. This property is especially important because it allows us
 to use maximal inequalities and other moment inequalities for
-mixingale arrays without modification to construct almost sure bounds on the
+mixingale arrays with only small modifications to construct almost sure bounds on the
 conditional moments $\Em$.
@@
 \begin{equation*}
-    \E\big| (W_n^{\prime *}(\delta' + \gamma') - W_n^{\prime *}(\gamma'))
-  (W_n^{\prime *}(\delta + \gamma) - W_n^{\prime *}(\gamma)) \big| = 0
+    \E\big[ (W_n^{\prime *}(\delta' + \gamma') - W_n^{\prime *}(\gamma'))
+  (W_n^{\prime *}(\delta + \gamma) - W_n^{\prime *}(\gamma)) \big] = 0
 \end{equation*}
@@
 \begin{lem}\label{equivalent-convergence-from-lie-lemma}
-  If $\{A_n\}$ is a sequence of events then the following are equivalent:
+  If $\{A_n\}$ is a sequence of events in $\Omega$ then the following
+  are equivalent:
   \begin{align*}

### 2015-12-31 Paper.tex
[#2] Add footnote justifying array notation
One of the referees is concerned about the use of explicit
array notation. I've been unable to find another approach to
writing this paper, so this commit tries to add some additional
justification.

@@
 slightly stronger than \citepos{GoW:02} and \citepos{GoJ:03} to
-accommodate larger block sizes.
+accommodate larger block sizes.%
+\footnote{Note that this is the main reason that we are presenting our
+  results using general triangular-array notation: to allow for the
+  means to change over time for comparison with \citepos{GoW:02} and
+  \citepos{GoJ:03} results.}
 

### 2015-12-31 Paper.tex
[#17] Fix small errors in proof of Lemma 5

@@
   for large enough $n$, which converges to $2 \delta$ by
-  Lemma~\ref{block-length-convergence-lemma}. Also,
+  Lemma~\ref{block-length-convergence-lemma}.
   Lemma~\ref{zsq-uniform-integrability-lemma} ensures that there
@@
   that
-  \begin{equation*}
+  \begin{align*}
     \E\Big(\tfrac{1}{n}  \sum_{j=1}^{J_n} \sum_{\tau=0}^{M_{nj}-1} \sum_{i=0}^{L_{nj}-1}
-    Z_n'(\tau + (i+1) M_{nj} - \ell_n, \ell_n)^2 \Big)
-    \leq C \E \Big(\sum_{j=1}^{J_n} L_{nj} \ell_n M_{nj} / n^2\Big)
-  \end{equation*}
+    & Z_n'(\tau + (i+1) M_{nj} - \ell_n, \ell_n)^2 \Big) \\
+    &= \E \Em \Big(\tfrac{1}{n}  \sum_{j=1}^{J_n} \sum_{\tau=0}^{M_{nj}-1} \sum_{i=0}^{L_{nj}-1}
+    Z_n'(\tau + (i+1) M_{nj} - \ell_n, \ell_n)^2 \Big) \\
+    &\leq C \E \Big(\sum_{j=1}^{J_n} L_{nj} \ell_n M_{nj} / n^2\Big)
+  \end{align*}
   and
@@
   \end{equation*}
-  for large enough $n$, both of which converge to zero in $L_1$ as $n
-  \to \infty$ by Lemma~\ref{block-length-convergence-lemma}.  These
-  three convergence results imply that the \textsc{rhs} of
-  (\ref{eq:29}) converges to zero, completing the proof.
+  for large enough $n$,%
+\footnote{Lemma~\ref{dejong-restatement-lemma}
+  and~\ref{zsq-uniform-integrability-lemma} are stated for the
+  unconditional expectation, which may cause some confusion here. Note
+  that $M_{nj}$ is measurable with respect to $\mathcal{M}_n$ and
+  is treated the same as the constant $m$ in the statement of
+  these Lemmas.  The other random variables in
+  these expressions are independent of $\mathcal{M}_n$. So the only
+  effect of conditioning on $\mathcal{M}_n$ is to prevent integration
+  over the distributions of the $M_{nj}$ and the expectation otherwise
+  behaves exactly like the unconditional expectation.\label{f:1}} %
+  both of which converge to zero in $L_1$ as $n \to \infty$ by
+  Lemma~\ref{block-length-convergence-lemma}.  These three convergence
+  results imply that the \allcaps{rhs} of (\ref{eq:29}) converges to
+  zero in probability, completing the proof.
 \end{proof}
@@
 \begin{proof}[Proof of~(\ref{eq:28})]
-  After using similar arguments to in the previous part of the proof,
+  After using similar arguments to the previous part of the proof,
   the conclusion holds if
@@
   \end{equation*}
-  which is a direct implication of Lemma~\ref{dejong-restatement-lemma}.
+  which is a direct implication of
+  Lemma~\ref{dejong-restatement-lemma}.%
+  \footnote{The discussion in Footnote~\ref{f:1} applies here as well.}
 \end{proof}
@@
   \begin{multline}\label{eq:35}
-    \lim_{C \to 0} \limsup_{n \to \infty} \sup_{m' = 1,\dots,n}
+    \lim_{C \to \infty} \limsup_{n \to \infty} \sup_{m' = 1,\dots,n}
     \E\Big(\Big(\sum_{\tau=0}^{n-1} \max_{m=1,\dots,m'} Z_n(\tau, m)^2 / m'\Big) \\
@@
   \end{multline}
-  making the families of random variables $\{\max_{m=1,\dots,m'}
-  Z_n(\tau, m)^2 n / m'\}$ and $\{\max_{m=1,\dots,m'}
-  Z^{*}_n(\tau, m)^2 n / m'\}$ uniformly integrable.
+  making the family of random variables $\{\max_{m=1,\dots,m'}
+  Z^{*}_n(\tau, m)^2 n / m'; \tau, m', n\}$ uniformly integrable.
 \end{lem}
@@
   \[
-  \sup_{n, m} \E\Big( \ind(A) \sum_{\tau=0}^{n-1} \max_{m=1,\dots,m'} Z_n(\tau, m)^2 / m' \Big)
+  \sup_{n, m'} \E\Big( \ind(A) \sum_{\tau=0}^{n-1} \max_{m=1,\dots,m'} Z_n(\tau, m)^2 / m' \Big)
   < \epsilon
   \]
-  for every event $A$ satisfying $\pr(A) < \epsilon'$.
+  for every event $A \in \Omega_n$ satisfying $\pr(A) < \epsilon'$.
   (\citealp{Dav:94}, 12.9.)
-  Lemma~\ref{zsq-uniform-integrability-lemma} ensures that there is an
+  Lemma~\ref{zsq-uniform-integrability-lemma} ensures uniform integrability of
+  $\max_{m=1,\dots,m'} Z_n'(\tau, m)^2 n/m'$, so there exists an
   $\epsilon'$ such that
@@
   \end{equation*}
-  for all $A$ with $\pr(A) \leq \epsilon'$. Then, writing
+  for all $A \in \Omega_n$ with $\pr(A) \leq \epsilon'$. Then, writing
   \begin{align*}
@@
     + \tfrac{1}{\sqrt{n}} \sum_{t \in I_n(\tau, m)} (\mu_{nt} - \bar \mu_n)
-    - m Z'_n(0, n) \\
+    - (m/n) Z'_n(0, n)
   \end{align*}
@@
     \Big(\sum_{t \in I_n(\tau, m)} (\mu_{nt} - \bar \mu_n) \Big)^2\Big) \\
-    &\quad+ (3/m') \sum_{\tau=0}^{n-1}
-    \E (\ind(A) \max_{m=1,\dots,m'} m Z'_n(0, n)^2) \\
-    &\leq (2 \epsilon/3) + \pr(A) (3/n)\sum_{t=1}^n (\mu_{nt} - \bar \mu_n)^2
+    &\quad+ (3 m' / n) \E (\ind(A) Z'_n(0, n)^2) \\
+    &\leq (2 \epsilon/3) + (3 \epsilon' m' / n)\sum_{t=1}^n (\mu_{nt} - \bar \mu_n)^2
   \end{align*}
   where the last inequality holds as a consequence of $A$'s
-  construction. Since $(1/n)\sum_{t=1}^n (\mu_{nt} - \bar \mu_n)^2 \to
-  0$, choose $n$ large enough that this average is less than
-  $\epsilon/9$. The proof that that the first moment is bounded is
-  similar, which completes the proof of~(\ref{eq:35})
+  construction. Since $\sum_{t=1}^n (\mu_{nt} - \bar \mu_n)^2 \to
+  0$, choose $n$ large enough that this sum is less than
+  $\epsilon/9\epsilon'$. The proof that that the first moment is bounded is
+  similar, which completes the proof of~(\ref{eq:35}).
 
@@
   \end{equation}
-  for any event $A \in \Gs \equiv \sigma(X_{11},\dots,X_{nn};\
-  M_{n1},\dots,M_{n,J_n};\ J_n)$ with $\pr(A) \leq \epsilon'$. Then we
-  will show that this property implies uniform integrability.%
-\footnote{The difference between this proof and the proof
-  of~\eqref{eq:35} is the measurability requirement. Here we need to
-  finesse measurability of the sets $A$.} %
+  for any event $A \in \Fs_n \equiv \sigma(X_{n1},\dots,X_{nn};\,
+  M_{n1},\dots,M_{n,J_n};\, J_n)$ with $\pr(A) \leq
+  \epsilon'$. Then we will show that this property implies uniform
+  integrability.%
+\footnote{The novelty in this part of the proof is the measurability
+  requirement. The sigma-field $\Fs_n$ intentionally exlcudes the
+  block start periods $u_{n1},\dots,u_{n,J_n}$, so
+  $Z_n^{*}(\tau, m)^2$ is not $\Fs_n$-measureable. If we instead
+  proved~\eqref{eq:31} for all $A \in \Omega_n$, as we did for the
+  first part of the proof, then uniform integrebality would be an
+  immediate consequence and would not need to be shown separately. See
+  \citet[Theorem 12.9]{Dav:94}.} %
 
@@
   \begin{equation*}
-    \Em \Big(\ind(A) \sum_{\tau = 0}^{n-1} \tfrac{1}{m'} \max_{m = 1,\dots,m'}
-    Z_n(\tau, m)^2\Big) < \epsilon / 4
-  \end{equation*}
-  for any $A \in \Gs$ with $\pr(A) \leq \epsilon'$, which is shown to
-  exist in the first part of this Lemma. Then define $J(x)$ to be the
-  block index such that $K_{n,J(x) - 1} < x \leq K_{n,J(x)}$. We have
-  the relationships
-  \begin{align*}
-    \Em \Em^* \Big(&\ind(A) \times \max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m'\Big) \\
-    &= \Em \ind(A) \Em^* \Big[ \tfrac{n}{m'}\max_{m = 1,\dots, m'}
-    \Big(\sum_{j=J(\tau)+1}^{J(\tau + m)-1} Z_{nj}^*
-    + Z_n^*(\tau, K_{n,J(\tau)} - \tau) \\
-    &\quad+ Z_n^*(K_{n,J(\tau+m)-1}, m - K_{n,J(\tau + m)-1}) \Big)^2\Big] \\
-    &\leq 4 \Em \ind(A) \tfrac{1}{m'} \sum_{u = 0}^{n-1} \Big( \sum_{j=J(\tau)+1}^{J(\tau + m')-1}
-    Z_n(u, M_{nj})^2 + Z_n(u, K_{n,J(\tau)} - \tau)^2 \\
-    &\quad + Z_n(u, m' - K_{n,J(\tau+m')-1})^2\Big) \\
-    &= (4/m') \sum_{j=J(\tau)+1}^{J(\tau + m')-1} \Em\Big[ \ind(A) \sum_{u = 0}^{n-1} Z_n(u, M_{nj})^2\Big] \\
-    &\quad + (4/m') \Em\Big[\ind(A) \sum_{u = 0}^{n-1} Z_n(\tau_{J(\tau)}, M_{n,J(\tau)})^2\Big] \\
-    &\quad + (4/m') \Em\Big[ \ind(A)  \sum_{u = 0}^{n-1} Z_n(u, m' - K_{n,J(\tau+m')})^2\Big] \\
-    &\leq \epsilon.
-  \end{align*}
-  The first inequality is a consequence of Doob's maximal inequality
-  for martingales \citep[see][Theorem 15.15, for example]{Dav:94},
-  since $Z_{nj}^*$ is a martingale difference array, and the second
-  equality and last inequality follow by construction of $A$. A
+    \sup_{m'=1,\dots,n} \Em \Big(\ind(A) \sum_{\tau = 0}^{n-1} \tfrac{1}{m'} \max_{m = 1,\dots,m'}
+    Z_n(\tau, m)^2\Big) < \epsilon / 6
+  \end{equation*}
+  for any $A \in \Fs_n$ with $\pr(A) \leq \epsilon'$, which is
+  shown to exist in the first part of this Lemma. Then, for any $x$,
+  define $J(x)$ to be the block index such that $K_{n,J(x) - 1} < x
+  \leq K_{n,J(x)}$. For any $m$, we can decompose $Z_n^{*}(\tau, m)$ as
+  \begin{equation*}
+  Z^{*}_n(\tau, m) = Z_n^*(\tau, K_{n,J(\tau)} - \tau) +
+  \sum_{j=J(\tau)+1}^{J(\tau + m)-1} Z_{nj}^* + Z_n^*(K_{n,J(\tau+m)-1}, m - K_{n,J(\tau + m)-1}),
+  \end{equation*}
+  giving
+  \begin{align}
+  \Em \Em^* \Big(&\ind(A) \times \max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m'\Big)
+  \notag \\
+  &\leq 3 \Em \Em^* \Big[\ind(A) \tfrac{n}{m'}\max_{m = 1,\dots, m'}
+  \Big(Z_n^*(\tau, K_{n,J(\tau)} - \tau) + \sum_{j=J(\tau)+1}^{J(\tau + m)-1} Z_{nj}^*\Big)^2\Big]
+  \notag \\
+  &\quad + 3 \Em \Em^* \big[\ind(A) \tfrac{n}{m'}
+  \max_{m=1,\dots,m'} Z_n^*(K_{n,J(\tau+m)-1}, m - K_{n,J(\tau + m)-1})^2 \big]\label{eq:6}
+  \end{align}
+  almost surely.
+
+  Since $Z_{nj}^*$ is a martingale difference array, Doob's maximal
+  inequality for martingales \citep[see][Theorem 15.15, for
+  example]{Dav:94} along with the construction of $Z_{nj}^{*}$ gives
+  a bound for the first term on the \allcaps{RHS} of~\eqref{eq:6},
+  \begin{multline*}
+  \Em \Em^* \Big[\ind(A) \tfrac{n}{m'}\max_{m = 1,\dots, m'}
+  \Big(Z_n^*(\tau, K_{n,J(\tau)} - \tau) + \sum_{j=J(\tau)+1}^{J(\tau + m)-1} Z_{nj}^*\Big)^2\Big] \\
+  \leq \tfrac{1}{m'} \sum_{u = 0}^{n-1} \Big\{\Em\big[\ind(A) Z_n(u, K_{n,J(\tau)} - \tau)^2\big] +
+  \sum_{j=J(\tau)+1}^{J(\tau + m')-1} \Em \big[\ind(A) Z_n(u, M_{nj})^2]\Big\}
+  \end{multline*}
+  and this term is less than $\epsilon/6$ by construction of $A$.
+  For the second term on the \allcaps{RHS}~\eqref{eq:6}, use the sequence of inequalities
+  \begin{align*}
+  \Em \Em^* \big[\ind(A) &\tfrac{n}{m'}
+  \max_{m=1,\dots,m'} Z_n^*(K_{n,J(\tau+m)-1}, m - K_{n,J(\tau + m)-1})^2 \big] \\
+  &\leq \sum_{j=J(\tau) + 1}^{J(\tau+m')-1} \tfrac{n}{m'} \Em \Em^* \big[\ind(A)
+  \max_{m=1,\dots, \min(M_{nj}, m' - K_{n,j-1})} Z_n^*(K_{n,j}, m)^2 \big] \\
+  &\leq \sum_{j=J(\tau) + 1}^{J(\tau+m')} \tfrac{M_{nj}}{m'} \sum_{u=0}^{n-1} \Em \big[\ind(A)
+  \max_{m=1,\dots,\min(M_{nj}, m' - K_{n,j-1})} Z_n(u, m)^2 / M_{nj} \big] \\
+  &\leq \sum_{j=J(\tau) + 1}^{J(\tau+m')} \epsilon \cdot \min(M_{nj}, m' - K_{n,j-1}) / 6 m' \\
+  &\leq \epsilon/6.
+  \end{align*}
+  Together, these bounds imply~(\ref{eq:31}). A
   similar argument also implies that $n Z_n^*(\tau, m)^2 / m'$ has
@@
   Now, for uniform integrability, take $\epsilon > 0$, choose
-  $\epsilon'$ so that~\eqref{eq:31} holds for all $A \in \Gs$
+  $\epsilon'$ so that~\eqref{eq:31} holds for all $A \in \Fs_n$
   s.t. $\pr(A) \leq \epsilon'$, and choose $C_0$ large enough that

### 2015-12-31 Paper.tex
[fixup] Make small wording improvements to appendix intro

@@
 bootstrap. The moving blocks and circular block bootstrap follow the
-same general argument but are simpler. First we will define some
-notation that will be used repeatedly.
+same general argument but are simpler. We will define some additional
+notation here before presenting the proofs.
 
@@
 define the \sigmafield\ generated by the stationary bootstrap's block
-lengths alone, which will be used repeatedly in our results,
+lengths alone,
 \begin{equation}

### 2015-12-31 subs/ETr2/reply_3.tex

@@
 \section*{\hfill Reply to referee 3\hfill}
+\section*{General summary of changes}
+This version of the paper has the following changes from the
+previous submission:
+\input{summary}
+
+\section*{Reply to specific points}
 
@@
 
+  I have added a formal specification of the top-level probability
+  space at the beginning of the mathematical appendix. You are
+  right, this has made it easier to make precise statements in some
+  of the results\,---\,e.g. the statement of Lemma~2 and the proof
+  of Lemma~5. Thank you for this suggestion.  I will also point out
+  that the paper defines several important sub-sigma-fields as they
+  are necessary for the proofs, which gives additional clarity and
+  formalism, and I have tried to improve in this respect in this
+  version of the paper.
+
 \end{enumerate}

### 2015-12-31 Paper.tex

--- 2015-12-31 Paper.tex
@@
 
-First, the relevant probability infrastructure.  Let
-$(S, \Omega, \pr)$ be a probability space and define the sequence of
-sub-sigma-fields $\Omega_n \subset \Omega$. Assume that each
-$X_{nt}$, $V_{nt}$, $M_{nj}$, and $u_{nj}$ is $\Omega_n$-measurable,
-with $u_{nj}$ the $\operatorname{uniform}(1,\dots,n)$ random variables
-that designate the start period of each bootstrap ``block.'' Also
-define the \sigmafield\ generated by the stationary bootstrap's block
-lengths alone, which will be used repeatedly in our results,
+Define the \sigmafield
 \begin{equation}
@@
 \E^*(\cdot \mid \Ms)$, etc.) An important property is
-that $\Ms$ is \emph{independent} of the $X_{nt}$'s, $V_{nt}$'s, and
-$u_{nj}$'s, so we can treat any
+that $\Ms$ is \emph{independent} of the $X_{nt}$, so we can treat any
 $M_{nj}$ and $J_n$ terms as constants within $\Em(\cdot)$ and
 $\Pm[\cdot]$ and integrate over the unconditional distributions of the
-other random variables. This property is especially important because it allows us
+$X_{nt}$. This property is especially important because it allows us
 to use maximal inequalities and other moment inequalities for
-mixingale arrays with only small modifications to construct almost sure bounds on the
+mixingale arrays without modification to construct almost sure bounds on the
 conditional moments $\Em$.
@@
 \begin{lem}\label{equivalent-convergence-from-lie-lemma}
-  If $\{A_n\}$ is a sequence of events in $\Omega$ then the following
-  are equivalent:
+  If $\{A_n\}$ is a sequence of events then the following are equivalent:
   \begin{align*}

### 2015-12-31 subs/ETr2/reply_3.tex

@@
     given showing its role in applications.}
+
+  The aim of the paper is to relax the conditions required by
+  \cite{GoW:02} and \cite{GoJ:03}. A major focus of \cite{GoW:02} is
+  proving consistency of these block bootstraps under some degree of
+  heterogeneity in the means\,---\,one example is, as they put it, ``a
+  finite number of properly behaved breaks in means.'' For our results
+  to be comparable to theirs in this way, even to show that we do not
+  allow as much heterogeneity in the means as those papers do, it's
+  important that we use array notation. So, an example where array
+  notation is important in applciations is when there is a break in
+  the mean at observation $n/2$.
+
+  While I agree with what you wrote in the previous letter, ``it is
+  never a good practice to copy what other authors do, as an
+  alternative to justifying it,'' I also think that readers generally
+  benefit when authors reuse decent notation from other closely
+  related papers, even if a different notation is incrementally
+  better.
+
+  Another question raised in your previous letter was: why explicitly
+  normalize by $1/\sqrt{n}$ and why take means? As mentioned in the
+  previous paragraph, each $X_{nt}$ is allowed to have nonzero mean,
+  so estimates of the variance need to be explicitly demeaned. Making
+  the normalization explicit makes these operations transparent. Once
+  the series is demeaned (either using the sample mean or the
+  population mean), all of the mathematics uses the various $Z_{nj}$
+  terms which have an implicit normalization.
+
+  In any case, I have added an explanation for these choices as
+  Footnote 6 in the paper.
 
@@
 \end{enumerate}
+
+\bibliography{../../texextra/references}
 \end{document}

### 2015-12-31 Paper.tex
[#6] Add further explanation for (old) Equation 18
This commit adds some further explanation for one of the equations
that a referee thought was not obvious.

@@
 bootstrap. The moving blocks and circular block bootstrap follow the
-same general argument but are simpler. First we will define some
-notation that will be used repeatedly.
-
-Define the \sigmafield
+same general argument but are simpler. We will define some additional
+notation here before presenting the proofs.
+
+First, the relevant probability infrastructure.  Let
+$(S, \Omega, \pr)$ be a probability space and define the sequence of
+sub-sigma-fields $\Omega_n \subset \Omega$. Assume that each
+$X_{nt}$, $V_{nt}$, $M_{nj}$, and $u_{nj}$ is $\Omega_n$-measurable,
+with $u_{nj}$ the $\operatorname{uniform}(1,\dots,n)$ random variables
+that designate the start period of each bootstrap ``block.'' Also
+define the \sigmafield\ generated by the stationary bootstrap's block
+lengths alone,
 \begin{equation}
@@
 By convention, summations over empty index sets will be considered
-equal to zero. Also let
+equal to zero. Note that the $I_n$ satisfy
+\begin{align}\label{eq:4}
+   \begin{split}
+   I_n(K_{n0}, M_{n1}) &= \{1,\dots,K_{n1}\} \\
+   I_n(K_{n1}, M_{n2}) &= \{K_{n1}+1,\dots,K_{n2}\} \\
+   \vdots \\
+   I_n(K_{n,J_n-1}, M_{nJ_{n}}) &= \{K_{n,J_{n-1}}+1,\dots,n \},
+   \end{split}
+\end{align}
+so $I_n(K_{n0}, M_{n1}),\dots,I_n(K_{n,J_n-1}, M_{nJ_{n}})$ exactly
+partition the set $\{1,\dots,n\}$ into consecutive blocks with
+lengths determined by the bootstrap.
+
+Let
 \newcommand{\Zb}[1][j]{{Z^*_{n{#1}}}}
@@
 \intertext{and}
-  \Zb          &= Z_n^*(K_{n,j-1}, M_{nj}),
+  \Zb          &= Z_n^*(K_{n,j-1}, M_{nj}) = \tfrac{1}{\sqrt{n}} \sum_{t=K_{n,j-1}+1}^{K_{n,j}} (X_{nt}^* - \bar X_n) \label{eq:1}
 \intertext{and define the corresponding demeaned terms}
@@
 
-By construction,
+By construction, (see Equations~\eqref{eq:4} and~\eqref{eq:1})
 \begin{equation}\label{eq:16}

### 2015-12-31 subs/ETr2/reply_2.tex

@@
 \section*{\hfill Reply to referee 2\hfill}
+
+\section*{General summary of changes}
+This version of the paper has the following changes from the
+previous submission:
+\input{summary}
+
+\section*{Reply to specific points}
 
@@
 
+  No, that was a mistake and it has been fixed. Thank you for pointing
+  it out.
+
 \item p. 12, Lemma 1: typo: ``$\sum_{i=1}^{J_n-1} < n$'' should read
   ``$\sum_{i=1}^{J_n-1} M_{ni} < n$''.
+
+  Thanks!
 
@@
     or excluded in the $\sum_{j=1}^{J_n} Z_{nj}^*$.}
+
+  Each $Z_{nj}^*$ equals $(1/\sqrt{n}) \sum_{t=K_{n,j-1}+1}^{K_{nj}}
+  (X_{nt}^* - \bar X_n)$ since $I_n(K_{n,j-1}, M_{nj}) =
+  \{K_{n,j-1}+1,\dots,K_{nj}\}$. So the summations are taken over
+  sequential and nonoverlapping blocks of the index $\{1,\dots,n\}$,
+  starting with $\{1,\dots,M_{n1}\}$ and ending with
+  $\{K_{n,J_n-1}+1,\dots,n\}$.  I've added some more details after the
+  definition of $I_n(\tau,m)$ and spelled out the
+  definition of $Z_{nj}^*$ a bit more to try to make
+  this point more clearly in the paper. Be aware that the exact
+  Equation number has moved.
 

### 2015-12-31 Paper.tex
[#7] Address conditioning issues raised by referee
This commit tries to expalain some of the conditioning issues that
bother one of the referees.

@@
 \end{equation}
-Lemma~\ref{bootstrapped-zsq-uniform-integrability-lemma} implies that there exists a finite,
-monotone function $B(\cdot)$ such that $B(x) \to 0$ as $x \to \infty$
-and
-\begin{equation*}
-  \Em( (n Z_{nj}^{*2} / M_{nj}) \ind\{n Z_n^{*2} / M_{nj} > \epsilon n / M_{nj}\}) \\
-  \leq B(\epsilon n /M_{nj})
-\end{equation*}
-almost surely for large enough $n$ and all $j$ and $\tau$.  Consequently,
-\begin{align*}
-    \Em \sum_{j=1}^{J_n} \Em^{*}( Z_{nj}^{*2} \ind\{Z_{nj}^{*2} > \epsilon\})
-    & \leq \sum_{j=1}^{J_n} ( M_{nj} / n )\, B(\epsilon n /M_{nj}) \\
+For any $j$ and $m$ and for large enough $n$,
+\begin{align}
+\Em \Em^{*}\big((Z_n(u_{nj}, m)^2n/m) &\ind\{Z_n(u_{nj}, m)^2n/m > \epsilon n/m\}\big) \notag \\
+&= \E \big((Z_n^{*}(0, m)^2n/m) \ind\{Z_n^{*}(0, m)^2n/m > \epsilon n/m\}\big) \notag \\
+&\leq B(\epsilon n/m)\label{eq:5}
+\end{align}
+where $B$ is some finite monotone function such that $B(x) \to 0$ as
+$x \to \infty$; the existence of a function $B$ that satisfies these
+conditions (and does not depend on $n$ or $m$) is a consequence of
+Lemma~\ref{bootstrapped-zsq-uniform-integrability-lemma},
+Equation~\eqref{eq:30}. Since $J_n$ and $M_{nj}$ are both $\Ms$-measureable
+and independent of the $u_{nj}$'s and $X_{nt}$'s,~\eqref{eq:5} implies that
+\begin{align*}
+\Em &\sum_{j=1}^{J_n} \Em^{*}\big(Z_{nj}^{*2} \ind\{Z_{nj}^{*2} > \epsilon\}\big) \\
+& = \sum_{j=1}^{J_n} (M_{nj}/n) \Em \Em^{*}
+\big((Z_n(u_{nj}, M_{nj})^2 n/M_{nj})
+\ind\{Z_n(u_{nj}, M_{nj})^2n/M_{nj} > \epsilon n/M_{nj}\}\big) \\
+& \leq \sum_{j=1}^{J_n} (M_{nj}/n) \, B(\epsilon n/M_{nj}) \\
 & \leq \max_{j = 1,\dots,J_n} B(\epsilon n / M_{nj}) \sum_{i=1}^{J_n} M_{ni} / n \\
 & = B(\epsilon n / \max_{j = 1,\dots,J_n} M_{nj}) \\
-    & \to^p 0 \text{\ as\ } n \to \infty,
-\end{align*}
-where the equality holds by monotonicity of $B$ and convergence in
-probability holds by Lemma~\ref{block-length-convergence-lemma},
-completing the proof of~\eqref{eq:19}.
-The Dominated Convergence Theorem then ensures that
+& \to^p 0 \text{\ as\ } n \to \infty.
+\end{align*}
+The first equality follows from simple algerbra and the definition
+of the $u_{nj}$'s. The first inequality is a
+consequence of~\eqref{eq:5}.  The second equality holds by
+monotonicity of $B$. And convergence in probability holds by
+Lemma~\ref{block-length-convergence-lemma}, completing the proof
+of~\eqref{eq:19}. The Dominated Convergence Theorem and~(\ref{eq:18})
+then ensure that
 \begin{equation}\label{eq:22}
@@
 \end{equation}
-follows from~(\ref{eq:18}). (Also see
+(Also see
 Lemma~\ref{equivalent-convergence-from-lie-lemma}.)
@@
 for any finite $k$. Since $k$ is arbitrary,~\eqref{eq:37} holds. Since
-Theorem~\ref{main-bootstrap-clt}'s assumptions ensure that the original
-array obeys the \clt,~\eqref{eq:36} holds \citep[Theorem 2]{Jon:97}.
-A similar argument applies to the asymptotic distribution of
-$\sqrt{n}(\bar X_n^* - \bar X_n) / \hat\sigma_n^*$, completing the
-proof.\qed
-}
+Theorem~\ref{main-bootstrap-clt}'s assumptions ensure that the
+original array obeys the \clt,~\eqref{eq:36} holds \citep[Theorem
+2]{Jon:97}.  A similar argument applies to the asymptotic distribution
+of $\sqrt{n}(\bar X_n^* - \bar X_n) / \hat\sigma_n^*$, completing the
+proof.\qed }
 
@@
 
+Note that these results apply immediately to the conditional expectation
+$\Em$ because the block lengths $M_{jn}$ do not appear in~\eqref{eq:32}
+and~\eqref{eq:33} and are independent of all of the random variables
+used for these bounds.
+
 \begin{lem}\label{zsq-uniform-integrability-lemma}
@@
 
-\begin{proof}
-  See supplemental appendix for the proof of~\eqref{eq:34}, which
+For proof, see supplemental appendix for the proof of~\eqref{eq:34}, which
 follows \citet[Lemma 6.5]{Mcl:75b} and \citet[Lemma 3.5]{Mcl:77}
 almost exactly and is also presented as Theorem~16.13 in
-  \citet{Dav:94}.
-\end{proof}
+\citet{Dav:94}. The same comment that follows
+Lemma~\ref{dejong-restatement-lemma} applies here as well: the bounds
+apply equally well to $\Em$.
 

### 2015-12-31 subs/ETr2/reply_2.tex

@@
 
+  The important point to keep in mind is that $\mathcal{M}$ only
+  contains information about the block lengths for the stationary
+  bootstrap. Lemmas 5 and 6 present results for the unconditional
+  expectation that hold for \emph{every fixed} block length ($m'$ in
+  Lemma 5, $m$ in Lemma 6). Uniform integrability over the family of
+  block lengths (as in Lemma 5) implies that the same $B(\cdot)$
+  applies to every $m'$ in $1,\dots,n$. Then on page 9, we use the
+  fact that the same $B(\cdot)$ works for every $m'$ implies that it
+  works for a randomly chosen $m'$ as well.
+
+  I've added an intermediate step in that application of Lemma 5 to
+  try to make the argument less opaque.
+
+  The use of Lemma 6 is similar. In that expression, $M_{nj}$ is
+  measurable with respect to $\mathcal{M}_n$, so it is treated the
+  same as the constant $m$ in the statement of Lemma 6, and the other
+  random variables are independent of $\mathcal{M}_n$. I have added
+  some additional explanation that (I hope!) make this point more clear.
+
 \end{enumerate}

### 2015-12-31 Paper.tex
[#3] Resolve variance issue raised by referee
This commit removes corollary 1 and tries to resolve some issues
with the covariance process that one of the referees found confusing.

--- 2015-12-31 Paper.tex
@@
 
-Theorem~\ref{main-bootstrap-clt} can be further extended to give an
-\fclt\ using arguments from \citet{JoD:00b}. We show in
+Theorem~\ref{main-bootstrap-clt} can also be extended to give an \fclt\
+using arguments from \citet{JoD:00b}. We show in
 Theorem~\ref{main-bootstrap-invariance-theorem} that the partial sum
@@
 critical values for other test statistics under the same assumptions
-as Theorem~\ref{main-bootstrap-clt}.
+as Theorem~\ref{main-bootstrap-clt}. For this result, define the
+following partial sums,
+\begin{align*}
+W_n(\gamma) &=
+\tfrac{1}{\sqrt{n}} \sum_{t=1}^{\lfloor \gamma n \rfloor}
+(X_{nt} - \bar\mu_n) &&\text{and}&
+W_n^{*}(\gamma) &= \tfrac{1}{\sqrt{n}}
+\sum_{t=1}^{\lfloor \gamma n \rfloor}
+(X^*_{nt} - \mu_n^{*}).
+\end{align*}
+Also let $W$ denote standard Brownian Motion and $\sigma W$ denote
+Brownian Motion scaled by the constant $\sigma$.
 
 \begin{thm}\label{main-bootstrap-invariance-theorem}
-  Suppose that the conditions of Theorem~\ref{main-bootstrap-clt}
-  hold, let $W$ be standard Brownian Motion, and define
-  \begin{equation}
-    \label{eq:6}
-    W_n^{*}(\gamma) = \tfrac{1}{\sqrt{n}}
-    \sum_{t=1}^{\lfloor \gamma n \rfloor} (X^*_{nt} - \mu_n^{*}) / \sigma_{n}^{*}
-  \end{equation}
-  and
-  \begin{equation}
-    \label{eq:7}
-    \hat{W}_n^{*}(\gamma) = \tfrac{1}{\sqrt{n}}
-    \sum_{t=1}^{\lfloor \gamma n \rfloor} (X^*_{nt} - \mu_n^{*}) / \hat\sigma_n^{*}.
-  \end{equation}
-  Then $\pr^{*}[\dist(W_n^{*}, W) > \delta] \to 0$ i.p.\ and
-  $\pr^{*}[\dist(\hat{W}_n^{*}, W) > \delta] \to 0$ i.p.\ for any
-  positive $\delta$ and distance $\dist$ that metricizes weak
-  convergence.
+Suppose that the conditions of Theorem~\ref{main-bootstrap-clt} hold
+and let $\dist$ be any distance function that metricizes weak
+convergence. Then
+\begin{equation}\label{eq:7}
+\pr^{*}[\dist(W_n^{*}, \sigma W) > \delta] \to^p 0
+\end{equation}
+for any positive  $\delta$.
+If, in addition, $\sup_{t=1,\dots,n}|\mu_{nt} -
+\bar \mu_n| = o(1/\sqrt{n})$ and
+\begin{equation}\label{eq:4}
+n^{-1} \sum_{s,t=1}^{\lfloor \gamma n \rfloor} \cov(X_{ns}, X_{nt}) \to \sigma^2 \gamma
+\end{equation}
+for all $\gamma \in [0,1]$, then
+\begin{equation}\label{eq:8}
+\pr[\dist(W_n, \sigma W) > \delta] \to 0
+\end{equation}
+for any positive $\delta$.
 \end{thm}
-
-Obviously, Theorem~\ref{main-bootstrap-invariance-theorem}, has
-natural corollaries that allow it to be used to approximate the
-behavior of partial sums of the original series.  But applying this
-result requires stronger assumptions than
-Theorem~\ref{main-bootstrap-clt}. The bootstrapped processes are
-(essentially) homoskedastic, so they are unable to match patterns of
-heteroskedasticity in the original series and we can not estimate the
-covariance process of the original partial sum in the bootstrap. This
-necessitates a separate consistent estimator of the covariance process, which
-we did not need for the sample mean.  Other methods, such as the Local
-Block Bootstrap \citep{PaP:02,DPP:03}, may be able to capture this
-additional heterogeneity with the bootstrap alone, but we do not
-pursue that possibility further.
-
-\begin{cor}
-  Suppose the conditions of Theorem~\ref{main-bootstrap-clt} hold and
-  that $\sup_{t=1,\dots,n}|\mu_{nt} - \bar \mu_n| = o(1/\sqrt{n})$. Define
-  \begin{equation}
-    \label{eq:8}
-    \sigma_n^2(\gamma) = \tfrac{1}{n}
-    \sum_{s,t=1}^{\lfloor \gamma n \rfloor} \cov(X_{ns}, X_{nt}),
-  \end{equation}
-  let $\hat\sigma_n^2(\cdot)$ be an estimator of $\sigma_n^2(\cdot)$
-  such that $\sup_{\gamma} |\sigma_n^2(\gamma) /
-  \hat{\sigma}_n^2(\gamma) - 1| \to^p 0$, and let
-  \begin{equation}
-    \label{eq:9}
-    \hat{W}_n(\gamma) = \tfrac{1}{\sqrt{n}} \sum_{t=1}^{\lfloor \gamma
-      n \rfloor} (X_{nt} - \bar\mu_n) / \hat{\sigma}_{n}(\gamma).
-  \end{equation}
-  Then $\pr^{*}[\dist(W_n^{*}, \hat{W}_n) > \delta] \to^p 0$ and
-  $\pr^{*}[\dist(\hat{W}_n^{*}, \hat{W}_n) > \delta] \to^p 0$ for any
-  positive $\delta$ and any distance $\dist$ that metricizes weak
-  convergence.
-\end{cor}
+If both~\eqref{eq:7} and~\eqref{eq:8} hold then the bootstrap can be
+used to approximate the distribution of partial sums.
+Note that Theorem~\ref{main-bootstrap-invariance-theorem} imposes
+stronger assumptions for the original process
+than for the bootstrapped process. Without~\eqref{eq:4}, the
+partial sum of the original observations converges to a transformed
+Brownian Motion with a different covariance process. The bootstrapped
+partial sum, on the other hand, always converges to standard (but
+potentially scaled) Brownian Motion because the resampling strategies
+ensure that the bootstrapped process is globally covariance stationary.
+
+If the original process does not satisfy~\eqref{eq:4}, it would be
+necessary to normalize $W_n$ with a uniformly
+consistent estimator of the true covariance process of the series to
+make use of these results. This would be the case if the variance
+permanently changes partway through the series, for example.  Other
+methods, such as the Local Block Bootstrap \citep{PaP:02,DPP:03}, may
+be able to capture this additional heterogeneity with the bootstrap
+alone, but we do not pursue that possibility further.
 
@@
 \newcommand{\lastK}{{K_{n, \gJ}}}
-Define $W_n^{\prime*}$ as
-\begin{equation*}
-  W^{\prime*}_n(\gamma)
-  = \tfrac{1}{\sqrt{n}} \sum_{t=1}^\gn (X_{nt}^* - \bar X_{n})/\sigma
-  = \sum_{j=1}^\gJ \Zb /\sigma + Z_n^*(\lastK, \gn - \lastK) / \sigma.
-\end{equation*}
-Lemma~\ref{bootstrap-variance-convergence-lemma} ensures that
-$\sigma_n^{*2}$ and $\hat\sigma_n^{*2}$ both converge in probability to
-$\sigma^2$, so it suffices to prove that $\pr^*[\dist(W_n^{\prime*}, W) >
-\delta)] \to^p 0$; we can also assume without loss of generality that
-$\sigma^2 = 1$. Moreover,
-Lemma~\ref{equivalent-convergence-from-lie-lemma} ensures that it
-suffices to prove unconditional convergence, so we will establish
-$\pr[\dist(W_n^{\prime *}, W) > \delta] \to 0$.
-
-Theorem~\ref{main-bootstrap-clt} implies that, for any fixed $\gamma$,
-$W_n^{\prime *}(\gamma)$ is asymptotically normal and, as a
-partial sum of an \mds, $W_n^{\prime *}$ has asymptotically independent
-increments. To see this, choose $\gamma, \gamma' \in [0,1]$ and
+
+We will only present proofs for the bootstrap results, since
+Theorem~3.1 of \cite{JoD:00b} establishes the result for the partial
+sums of the original process.  Theorem~\ref{main-bootstrap-clt}
+implies that, for any fixed $\gamma$, $W_n^{*}(\gamma)$ is
+asymptotically normal with limiting variance $\gamma \sigma^2$, so we
+can assume that $\sigma^2 = 1$ without loss of generality. Moreover,
+Lemma~\ref{equivalent-convergence-from-lie-lemma} shows that it is
+sufficient to prove unconditional convergence, so we will establish
+$\pr^*[\dist(W_n^{*}, W) > \delta)] \to^p 0$. As in \cite{JoD:00b},
+this will hold if we show that $W_n^{*}$ has asymptotically
+independent increments and stochastic equicontinuity, namely
+\begin{equation}\label{eq:9}
+  \lim_{\delta \to 0} \limsup_{n \to \infty} \pr[\sup_{\gamma \in [0,1]}
+  \sup_{\gamma' \in [\gamma - \delta, \gamma + \delta]}
+    | W_n^{*}(\gamma) - W_n^{*}(\gamma') | > \epsilon] = 0
+\end{equation}
+for any positive $\epsilon$.
+
+First observe that we can write $W_n^{*}$ as
+\begin{equation*}
+  W^{*}_n(\gamma)
+  = \tfrac{1}{\sqrt{n}} \sum_{t=1}^\gn (X_{nt}^* - \bar X_{n})
+  = \sum_{j=1}^\gJ \Zb + Z_n^*(\lastK, \gn - \lastK).
+\end{equation*}
+To show that the increments of this process are asymptotically
+independent, choose $\gamma, \gamma' \in [0,1]$ and
 $\delta, \delta' > 0$ so that $\delta + \gamma \leq \gamma'$. Since
-the increments of $W_n^{\prime *}$ are uncorrelated conditional on
+the blocks of $W_n^{*}$ are conditionally uncorrelated given
 $X_{1n},\dots,X_{nn}$, and $\Ms$, we have
 \begin{equation*}
-    \E\big[ (W_n^{\prime *}(\delta' + \gamma') - W_n^{\prime *}(\gamma'))
-  (W_n^{\prime *}(\delta + \gamma) - W_n^{\prime *}(\gamma)) \big] = 0
+  \E\big[ (W_n^{*}(\delta' + \gamma') - W_n^{*}(\gamma'))
+  (W_n^{*}(\delta + \gamma) - W_n^{*}(\gamma)) \big] = 0
 \end{equation*}
@@
 \begin{multline*}
-  \E\big[(W_n^{\prime *}(\delta' + \gamma') - W_n^{\prime *}(\gamma'))
-  (W_n^{\prime *}(\delta + \gamma) - W_n^{\prime *}(\gamma)) \big] = \\
+  \E\big[(W_n^{*}(\delta' + \gamma') - W_n^{*}(\gamma'))
+  (W_n^{*}(\delta + \gamma) - W_n^{*}(\gamma)) \big] = \\
   \E \Em^*\big\{- Z_n^*(\lfloor \gamma' n \rfloor, K_{n, \lceil \gamma' J_n \rceil }- \lfloor \gamma' n \rfloor)
@@
 
-Consequently, as in \cite{JoD:00b}, the result follows from stochastic
-equicontinuity \citep[Theorems 15.4 and 15.5]{Bil:68} namely that
-\begin{equation*}
-  \lim_{\delta \to 0} \limsup_{n \to \infty} \pr[\sup_{\gamma \in [0,1]}
-  \sup_{\gamma' \in [\gamma - \delta, \gamma + \delta]}
-    | W_n^{\prime *}(\gamma) - W_n^{\prime *}(\gamma') | > \epsilon] = 0
-\end{equation*}
-for any positive $\epsilon$.  Fix $\delta> 0$ such that $D = 2/\delta$
-is a positive integer and let $\gamma_d = d/D$ for $d =
-0,\dots,D$. Then, mimicking the argument in \cite{JoD:00b},
+For~\eqref{eq:9}, fix $\delta> 0$ such that $D = 2/\delta$ is a
+positive integer and let $\gamma_d = d/D$ for $d =
+0,\dots,D$. Mimicking the argument in \cite{JoD:00b} gives the bounds
 \begin{align*}
@@
   \sup_{\gamma' \in [\gamma - \delta, \gamma + \delta]}
-  | W_n^{\prime *}(\gamma) - W_n^{\prime *}(\gamma') | > \epsilon] \\
+  | W_n^{*}(\gamma) - W_n^{*}(\gamma') | > \epsilon] \\
   &\leq \pr[ \sup_{d = 1,\dots,D} \sup_{\gamma \in [0,\delta]}
-  | W_n^{\prime *}(\gamma + \gamma_d) - W_n^{\prime *}(\gamma_d) | > \epsilon/2] \\
+  | W_n^{*}(\gamma + \gamma_d) - W_n^{*}(\gamma_d) | > \epsilon/2] \\
   &\leq  (4/\epsilon^2) \sum_{d=1}^D \E[\sup_{\gamma \in [0,\delta]}
-  | W_n^{\prime *}(\gamma + \gamma_d) - W_n^{\prime *}(\gamma_d) |^2 \\
+  | W_n^{*}(\gamma + \gamma_d) - W_n^{*}(\gamma_d) |^2 \\
   &\qquad\qquad\qquad \times \ind\{\sup_{\gamma \in [0,\delta]}
-  | W_n^{\prime *}(\gamma + \gamma_d) - W_n^{\prime *}(\gamma_d) |^2 > \epsilon^2/4\}] \\
+  | W_n^{*}(\gamma + \gamma_d) - W_n^{*}(\gamma_d) |^2 > \epsilon^2/4\}] \\
   &\leq  (4/\epsilon^2) \max_{d=1,\dots,D} \E[\sup_{\gamma \in [0,\delta]}
-  (1/\delta) | W_n^{\prime *}(\gamma + \gamma_d) - W_n^{\prime *}(\gamma_d) |^2 \\
+  (1/\delta) | W_n^{*}(\gamma + \gamma_d) - W_n^{*}(\gamma_d) |^2 \\
   &\qquad\qquad\qquad \times \ind\{\sup_{\gamma \in [0,\delta]}
-  (1/\delta) | W_n^{\prime *}(\gamma + \gamma_d) - W_n^{\prime *}(\gamma_d) |^2 > \epsilon^2/4\delta\}].
+  (1/\delta) | W_n^{*}(\gamma + \gamma_d) - W_n^{*}(\gamma_d) |^2 > \epsilon^2/4\delta\}].
 \end{align*}
@@
   \sup_{\gamma \in [0,\delta]}
-  (1/\delta) | W_n^{\prime *}(\gamma + \gamma_d) - W_n^{\prime *}(\gamma_d) |^2
-\end{equation*}
-is uniformly integrable, so there exists a finite and positive
-function $B$ such that $B(x) \to 0$ as $x \to \infty$ and
+  (1/\delta) | W_n^{*}(\gamma + \gamma_d) - W_n^{*}(\gamma_d) |^2
+\end{equation*}
+is uniformly integrable, so an argument similar to that used in the
+proof of Theorem~\ref{main-bootstrap-clt} shows that there exists a
+finite and monotone function $B$ such that $B(x) \to 0$ as
+$x \to \infty$ and
 \begin{multline*}
   \E[\sup_{\gamma \in [0,\delta]}
-  (1/\delta) | W_n^{\prime *}(\gamma + \gamma_d) - W_n^{\prime *}(\gamma_d) |^2
+  (1/\delta) | W_n^{*}(\gamma + \gamma_d) - W_n^{*}(\gamma_d) |^2 \times \\
   \ind\{\sup_{\gamma \in [0,\delta]}
-  (1/\delta) | W_n^{\prime *}(\gamma + \gamma_d) - W_n^{\prime *}(\gamma_d) |^2 > x\}] \\
+  (1/\delta) | W_n^{*}(\gamma + \gamma_d) - W_n^{*}(\gamma_d) |^2 > x\}]
   \leq B(x)
@@
   \sup_{\gamma' \in [\gamma - \delta, \gamma + \delta]}
-  | W_n^{\prime *}(\gamma) - W_n^{\prime *}(\gamma') | > \epsilon] & \leq
+  | W_n^{*}(\gamma) - W_n^{*}(\gamma') | > \epsilon] & \leq
   \lim_{\delta \to 0} (4/\epsilon^2)

### 2015-12-31 subs/ETr2/reply_2.tex

@@
 through the use of the letter $W$ to be some type of Wiener measure.}
+
+$\hat{W}_n(\gamma)$ should have been defined as
+\begin{equation*}
+\hat{W}_n(\gamma) = \sqrt{\tfrac{\gamma}{n}} \sum_{t=1}^{\lfloor \gamma n \rfloor}
+(X_{nt} - \bar{\mu}_n) / \hat{\sigma}_n(\gamma),
+\end{equation*}
+would make the limit a Wiener process and (I think) would have
+prevented a lot of your confusion. In any case, I have merged this
+corollary with the previous theorem (Theorem 2) and have edited the
+surrounding text to make this part more clear. I have also removed the
+conditions for normalizing partial sums that would not converge to a
+Wiener processes and left that element implicit.
 

### 2015-12-31 Paper.tex
[fixup] Make small corrections to the main paper

--- 2015-12-31 Paper.tex
@@
   &= \tfrac{1}{n} \sum_{\tau_0 = 0}^{M_n-1}
-  \sum_{j=1}^{J_n-1}
+  \sum_{j=1}^{J_n}
   \Big(\tfrac{1}{\sqrt{n}}
@@
   To show that $\sigma_n^{*2}$ converges, we can write
-  \begin{multline*}
+  \begin{multline}\label{eq:38}
     \sigma_n^{*2} - \sigma^2 = \E^*\Big\{ \sum_{j=1}^{J_n} (Z_{nj}^{*2} - Z_{nj}^{\prime*2}) \Big\}
@@
     \Em Z_{n}^{\prime}(\tau,M_{nj})^2  - \sigma^2\Big\}.
-  \end{multline*}
+  \end{multline}
   Uniform integrability ensures that the convergence in~(\ref{eq:25})
@@
   Lemma~\ref{equivalent-convergence-from-lie-lemma} then implies that
-  the first term converges to zero in probability.
+  the first term in \eqref{eq:38} converges to zero in probability.
   Lemma~\ref{lln-for-real-zsq} proves that the second and third
@@
     \hat \sigma_n^{*2} - \sigma_n^{*2}
-    = \sum_{j=1}^{J_n} \big( Z_{nj}^* + (M_{nj}/\sqrt{n}) (\bar X_n - \bar X_{n}^*) \big)
+    = \sum_{j=1}^{J_n} \big( Z_{nj}^* + (M_{nj}/\sqrt{n}) (\bar X_n - \bar X_{n}^*) \big)^2
     - \E^*  \sum_{j=1}^{J_n} Z_{nj}^{*2}

### 2015-12-31 version_git.sh
[fixup] Change date presentation for untagged commits
For the 'public' branch of this repository, I don't really need to use
tags. I can just expose the date and the commit SHA and that should be
fine. Tags can be reserved for submissions or other versions that *I*
want to release and keep track of on a private branch.

@@ -40,5 +40,5 @@ esac
 if [ $(git describe --tags --exact-match 2> /dev/null) ]; then
     echo $(git describe --tags --exact-match)
 else
-    echo "$commit_short on $date_string ($branch)"
+    echo "$date_string, commit $commit_short"
 fi

### 2015-12-31 Paper.tex

--- 2015-12-31 Paper.tex
@@
 accommodate larger block sizes.%
-\footnote{Note that this is the main reason that we are presenting our
+\footnote{Note that this is one reason that we are presenting our
   results using general triangular-array notation: to allow for the

### 2016-05-16 subs/ETr3/reply_3.tex
[#19] Add empty letter for response to referee 3
This commit adds a letter with referee 3's specific concerns, so that I
can fill out a response for the referee. This commit closes #19.

\documentclass[12pt]{article}
\frenchspacing
\input{../../preamble.tex}
\usepackage[tiny]{titlesec}

\begin{document}
\section*{\hfill Reply to referee 3\hfill}

In your letter, you wrote,
\begin{quotation}
  \noindent\textit{``Yes, your array notation is of course needed to
    accommodate the assumption of mean heterogeneity. However, what I
    was really hoping for was some additional transparency in the form
    of an example of a mean array which would satisfy Assumption 2 of
    Theorem 1, and also perhaps a case which would fail to satisfy
    it.}

  \textit{``Array notation has commonly been used in asymptotic
    analysis to increase the generality of results, especially by
    allowing flexible scaling by sample size such as
    $X_{nt} = X_t/a_n$ where $a_n$ can be either $\sqrt{n}$ or
    something else. The object here is quite different, such cases
    would not satisfy Assumption 2 and are ruled out. It would
    therefore help the general reader, who is not inside your head at
    the outset, to explain the role of the arrays in this context,
    most helpfully by quoting an example or two. Footnote 6 is not
    helpful in this respect. Lots of people like to read papers in ET
    even when they are not particularly familiar with the precedent
    literature. Giving such readers the relevant background is just a
    courtesy. We are only talking 2 or 3 extra sentences at most.''}
\end{quotation}

You also wrote,
\begin{quotation}
  \noindent\textit{``Just one additional comment on the text. On page
    5, line --7, should $\mu_n^*$ read $\bar{\mu}_n^*$?''}
\end{quotation}
\end{document}

### 2016-05-23 Paper.tex
[#21] remove duplicated VERSION.tex input
The LaTeX file loaded VERSION.tex a second time, after some code that
checks whether the file exists and loads it if it does. This
duplication was either (1) unnecessary, if the file exists, or (2)
causes an error, if the file doesn't.

This commit closes #21.
[#24] Add AucTeX variables to LaTeX files
This will make life slightly easier. The commit closes #24
[#23] Fix incorrect equation reference in Proof of Lemma 3
Closes #23.

@@
 \input{preamble}
-\input{VERSION}
 \begin{document}
@@
 \begin{proof}
-  For~\eqref{eq:26}, $(Z_{nj}^{*2} - \Em^* Z_{nj}^{*2}) \cdot (n /
+  For~\eqref{eq:25}, $(Z_{nj}^{*2} - \Em^* Z_{nj}^{*2}) \cdot (n /
   M_{nj})$ is a uniformly integrable martingale difference array, by
@@
 % LocalWords:  jel PaP DPP np Ames Resampling nonstationary cdf Helle
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2016-06-07 Paper.tex
[#18] Relax assumption on dispersion of mu_t in Theorem 1
This commit makes a fairly large change to the results. The assumption on
the mu_t's turns out to be very restrictive, so I've relaxed it. To do this,
I've added a separate lemma that shows that the dispersion component of X*-bar
converges to zero at the right rate to not affect the asymptotic distribution.
Then I've added a small part at the beginning of Theorem 1's proof, which
basically points to Lemma 3, and modified the proof of (old numbering) Lemma 5,
which proves uniform integrability of the bootstrapped blocks.

@@
 
-Theorem~\ref{main-bootstrap-clt} presents the main result, asymptotic normality of
+Theorem~\ref{T1} presents the main result, asymptotic normality of
 the distribution of bootstrapped sums. This paper adopts the
@@
 
-\begin{thm}\label{main-bootstrap-clt}
+\begin{thm}\label{T1}
   Suppose the following conditions hold.
@@
   \item The array $\mu_{nt} - \bar \mu_n$ is uniformly bounded
-    and $\sum_{t=1}^n (\mu_{nt} - \bar \mu_n)^2 \to 0$,
-    where $\E X_{nt} = \mu_{nt}$ and $\bar{\mu}_n = n^{-1} \sum_{t=1}^n
-    \mu_{nt}$. Moreover, $\sqrt{n} \| \bar{X}_{n} - \bar\mu_n \|_2
+    and $\sum_{t=1}^n (\mu_{nt} - \bar \mu_n)^2 = o(n p_n^2)$ (for
+    the Stationary Bootstrap) or
+    $\sum_{t=1}^n (\mu_{nt} - \bar \mu_n)^2 = o(n/M_n^2)$ (for
+    the Moving or Circular Block Bootstraps),
+    where $\E X_{nt} = \mu_{nt}$, $\bar{\mu}_n = n^{-1} \sum_{t=1}^n
+    \mu_{nt}$, and $p_n$ and $M_n$ are further defined in item 4.
+    Moreover, $\sqrt{n} \| \bar{X}_{n} - \bar\mu_n \|_2
     \to \sigma > 0$, with $\bar X_n = (1/n) \sum_{t=1}^n X_{nt}$.
@@
   \end{enumerate}
-  Then $\hat\sigma^{*2} \to^p \sigma^2$,
+  Then $\sigma^{*2} \to^p \sigma^2$, $\hat\sigma^{*2} \to^p \sigma^2$,
   \begin{equation}\label{eq:36}
@@
 
-Theorem~\ref{main-bootstrap-clt} relies on a general insight about the
+Theorem~\ref{T1} relies on a general insight about the
 variance of the sample mean under the bootstrap-induced
@@
   argument.}%
-\footnote{Lemmas~\ref{bootstrap-variance-convergence-lemma} and
-  \ref{bootstrapped-zsq-uniform-integrability-lemma} are particularly
+\footnote{Lemmas~\ref{L4} and
+  \ref{L6} are particularly
   strong demonstrations of this argument.} %
@@
 
-In short, the basic approach that we use to prove Theorem~\ref{main-bootstrap-clt}
+In short, the basic approach that we use to prove Theorem~\ref{T1}
 is based on a fundamental connection between the second moments of the
@@
 
-Theorem~\ref{main-bootstrap-clt} can also be extended to give an \fclt\
+Theorem~\ref{T1} can also be extended to give an \fclt\
 using arguments from \citet{JoD:00b}. We show in
-Theorem~\ref{main-bootstrap-invariance-theorem} that the partial sum
+Theorem~\ref{T2} that the partial sum
 of the bootstrapped process obeys an \fclt\ and can be used to derive
 critical values for other test statistics under the same assumptions
-as Theorem~\ref{main-bootstrap-clt}. For this result, define the
+as Theorem~\ref{T1}. For this result, define the
 following partial sums,
@@
 
-\begin{thm}\label{main-bootstrap-invariance-theorem}
-Suppose that the conditions of Theorem~\ref{main-bootstrap-clt} hold
+\begin{thm}\label{T2}
+Suppose that the conditions of Theorem~\ref{T1} hold
 and let $\dist$ be any distance function that metricizes weak
@@
 \end{equation}
-for any positive  $\delta$.
-If, in addition, $\sup_{t=1,\dots,n}|\mu_{nt} -
-\bar \mu_n| = o(1/\sqrt{n})$ and
+for any positive $\delta$. If, in addition,
 \begin{equation}\label{eq:4}
@@
 used to approximate the distribution of partial sums.
-Note that Theorem~\ref{main-bootstrap-invariance-theorem} imposes
+Note that Theorem~\ref{T2} imposes
 stronger assumptions for the original process
@@
 equal to zero. Note that the $I_n$ satisfy
-\begin{align}\label{eq:4}
+\begin{align}\label{eq:39}
    \begin{split}
@@
 
-By construction, (see Equations~\eqref{eq:4} and~\eqref{eq:1})
+By construction, (see Equations~\eqref{eq:39} and~\eqref{eq:1})
 \begin{equation}\label{eq:16}
@@
 
-\subsection*{Proof of Theorem~\ref{main-bootstrap-clt}}
+\subsection*{Proof of Theorem~\ref{T1}}
 {%
@@
 \newcommand{\Zsum}{\sum_{j=1}^{J_n} \Zb / \sigma_n}
+Observe that
+\[
+\sqrt{n}(\bar X_{n}^{*} -  \E^{*} \bar X_n^{*})
+= \sqrt{n}((\bar{X}_{n}^{*} - \bar{\mu}_{n}^{*}) - \E^{*} (\bar X_n^{*} - \bar{\mu}_n^{*}))
++ \sqrt{n}(\bar{\mu}_{n}^{*} - \E^{*} \bar{\mu}_n^{*}).
+\]
+Lemma~\ref{L3} implies that the last term is $o_{L_2}(1)$, so we can assume that
+$\mu_{nt}$ is constant in $t$ for each $n$ for the proof of normality. Convergence
+in probability of the bootstrap variance and the bootstrap variance estimator
+holds by Lemma~\ref{L4}.
+
 First we prove that
@@
 $\sigma_n^{*2}$ is uniformly a.s.\ positive and holds by
-Lemma~\ref{bootstrap-variance-convergence-lemma}) and the following
+Lemma~\ref{L4}) and the following
 two conditions hold for all positive $\epsilon$:
@@
 is a uniformly-integrable martingale difference array
-by Lemma~\ref{bootstrapped-zsq-uniform-integrability-lemma}
+by Lemma~\ref{L6}
 and satisfies the \lln\ (e.g., \citealp{Dav:94}, Theorem 19.7). So
@@
 conditions (and does not depend on $n$ or $m$) is a consequence of
-Lemma~\ref{bootstrapped-zsq-uniform-integrability-lemma},
-Equation~\eqref{eq:30}. Since $J_n$ and $M_{nj}$ are both $\Ms$-measureable
+Lemma~\ref{L6},
+Equation~\eqref{eq:30}. Since $J_n$ and $M_{nj}$ are both $\Ms$-measurable
 and independent of the $u_{nj}$'s and $X_{nt}$'s,~\eqref{eq:5} implies that
@@
 \end{align*}
-The first equality follows from simple algerbra and the definition
+The first equality follows from simple algebra and the definition
 of the $u_{nj}$'s. The first inequality is a
@@
 monotonicity of $B$. And convergence in probability holds by
-Lemma~\ref{block-length-convergence-lemma}, completing the proof
+Lemma~\ref{L1}, completing the proof
 of~\eqref{eq:19}. The Dominated Convergence Theorem and~(\ref{eq:18})
@@
 (Also see
-Lemma~\ref{equivalent-convergence-from-lie-lemma}.)
-
-Lemma~\ref{bootstrap-variance-convergence-lemma} implies that
+Lemma~\ref{L2}.)
+
+Lemma~\ref{L4} implies that
 $\sigma_n^{*2}$ and $\hat\sigma_n^{*2}$ both converge to $\sigma^2$ in
@@
 for any finite $k$. Since $k$ is arbitrary,~\eqref{eq:37} holds. Since
-Theorem~\ref{main-bootstrap-clt}'s assumptions ensure that the
-original array obeys the \clt,~\eqref{eq:36} holds \citep[Theorem
-2]{Jon:97}.  A similar argument applies to the asymptotic distribution
-of $\sqrt{n}(\bar X_n^* - \bar X_n) / \hat\sigma_n^*$, completing the
+Theorem~\ref{T1}'s assumptions ensure that the original array obeys
+the \clt,~\eqref{eq:36} holds \citep[Theorem 2]{Jon:97}.  A similar
+argument applies to the asymptotic distribution of
+$\sqrt{n}(\bar X_n^* - \bar X_n) / \hat\sigma_n^*$, completing the
 proof.\qed }
 
-\subsection*{Proof of Theorem~\ref{main-bootstrap-invariance-theorem}}
+\subsection*{Proof of Theorem~\ref{T2}}
 \newcommand{\gn}{{\lfloor \gamma n \rfloor}}
@@
 Theorem~3.1 of \cite{JoD:00b} establishes the result for the partial
-sums of the original process.  Theorem~\ref{main-bootstrap-clt}
+sums of the original process.  Theorem~\ref{T1}
 implies that, for any fixed $\gamma$, $W_n^{*}(\gamma)$ is
@@
 can assume that $\sigma^2 = 1$ without loss of generality. Moreover,
-Lemma~\ref{equivalent-convergence-from-lie-lemma} shows that it is
+Lemma~\ref{L2} shows that it is
 sufficient to prove unconditional convergence, so we will establish
@@
 for some constant $C$ by
-Lemma~\ref{bootstrapped-zsq-uniform-integrability-lemma}. This term
-converges to zero by Lemma~\ref{block-length-convergence-lemma}.
+Lemma~\ref{L6}. This term
+converges to zero by Lemma~\ref{L1}.
 
@@
 \end{align*}
-Lemma~\ref{bootstrapped-zsq-uniform-integrability-lemma} implies that
+Lemma~\ref{L6} implies that
 \begin{equation*}
@@
 is uniformly integrable, so an argument similar to that used in the
-proof of Theorem~\ref{main-bootstrap-clt} shows that there exists a
+proof of Theorem~\ref{T1} shows that there exists a
 finite and monotone function $B$ such that $B(x) \to 0$ as
@@
 
-\begin{lem}\label{block-length-convergence-lemma}
+\begin{lem}\label{L1}
   Suppose that $M_{n1}, M_{n2},\dots$ are i.i.d.\ geometric random
@@
   $\epsilon$, and
-  \item $\sum_{i=1}^{J_n} M_{ni}^2 / n^2 \to^p 0$.
+  \item $\E\big(\sum_{i=1}^{J_n} M_{ni}^2\big) = (2 n - 1) / p_n - n + 1$.
   \end{enumerate}
@@
 
-\begin{proof}[Proof of Lemma~\ref{block-length-convergence-lemma}]
+\begin{proof}[Proof of Lemma~\ref{L1}]
   To prove part 1, observe that, for any increasing positive sequence
@@
   as well.
-
   The proof of part 4 is the same as part 2, making the obvious
-  substitutions. Part 5 holds because $\sum_{i=1}^{J_n} M_{ni}^2/n^2
-  \leq \max_{i=1,\dots,J_n} M_{ni}/n$ which converges to zero in
-  probability by part 2.
+  substitutions.
+
+  For part 5, write
+  \begin{equation}\label{eq:41}
+    \sum_{i=1}^{J_n} M_{ni}^2 =
+    \sum_{i=1}^{J_n} (M_{ni} - \tfrac{1}{p_n})^2
+    + \tfrac{2}{p_n} \sum_{i=1}^{J_n} (M_{ni} - \tfrac{1}{p_n})
+    + \tfrac{J_n}{p_n^2}
+  \end{equation}
+  so
+  \begin{equation*}
+    \E \Big( \sum_{i=1}^{J_n} M_{ni}^2 \Big)
+    = \E\Big( \sum_{i=1}^{J_n} (M_{ni} - \tfrac{1}{p_n})^2 \Big)
+    + \tfrac{2 n}{p_n} - \E \tfrac{J_n}{p_n^2}.
+  \end{equation*}
+  Since $J_n$ is a stopping time and $\sum_{i=1}^j (M_{ni} - 1/p_n)$
+  is a martingale, we have the equality \citep[Lemma 6]{CRT:65}
+  \begin{align*}
+    \E\Big( \sum_{i=1}^{J_n} (M_{ni} - \tfrac{1}{p_n})^2 \Big)
+    &= \E\Big( \sum_{i=1}^{J_n} \E((M_{ni} - \tfrac{1}{p_n})^2 \mid M_{n1},\dots,M_{n,i-1})\Big)\\
+    &= \tfrac{1 - p_n}{p_n^2} \E J_n.
+  \end{align*}
+  Then $\E J_n = (n-1) p_n + 1$, completing the proof.
 \end{proof}
 
-\begin{lem}\label{equivalent-convergence-from-lie-lemma}
+\begin{lem}\label{L2}
   If $\{A_n\}$ is a sequence of events in $\Omega$ then the following
@@
 
-\begin{lem}\label{bootstrap-variance-convergence-lemma}
-Under the conditions of Theorem~\ref{main-bootstrap-clt},
+\begin{lem}\label{L3}
+Under the conditions of Theorem~\ref{T1},
+\begin{equation}\label{eq:40}
+  \E \Big(\sum_{j=1}^{J_n} \Big( \sum_{t = K_{n,j-1}+1}^{K_{nj}}
+  (\mu_{nt}^{*} - \bar \mu_n)\Big)^2\Big) = o(n p_n)
+\end{equation}
+and $\bar \mu_n^{*} = \E^{*} \bar \mu_n^{*} + o_{L_2}(n^{-1/2})$.
+\end{lem}
+\begin{proof}
+  Since the blocks are independent and
+  $\E^{*} \bar\mu_n^{*} = \bar\mu_n$ under the stationary bootstrap,
+  the result on $\bar\mu_n^{*}$ follows from~\eqref{eq:40}. To
+  show~\eqref{eq:40}, observe that
+  \begin{align*}
+    \E \Big(\sum_{j=1}^{J_n} &\Big( \sum_{t= K_{n,j-1} +1}^{K_{nj}}
+    (\mu_{nt}^{*} - \bar \mu_n)\Big)^2\Big)= \\
+    &= \E\Big(\sum_{j=1}^{J_n}\sum_{s,t = K_{n,j-1}+1}^{K_{nj}}
+    \E \big((\mu_{ns}^{*} - \bar{\mu}_n)
+    (\mu_{nt}^{*} - \bar{\mu}_n) \mid \Ms \big)\Big)\\
+    &= \E\Big( \sum_{j=1}^{J_n}
+    \sum_{k,l = -n}^{n} \tfrac{1}{n} \sum_{\tau=0}^{n-1}
+    (\mu_{n,\tau+k} - \bar{\mu}_n) (\mu_{n,\tau+l} - \bar{\mu}_n) \;
+    1\{ \tau + k, \tau + l \in I_n(\tau, M_{nj})\}\Big)\\
+    &\leq \E\Big(\sum_{j=1}^{J_n}
+    \Big(\sum_{k = -n}^{n} \Big(\tfrac{1}{n} \sum_{\tau=0}^{n-1}
+    (\mu_{n,\tau+k} - \bar{\mu}_n)^2
+    1\{ \tau + k \in I_n(\tau, M_{nj})\}\Big)^{1/2}\Big)^{2}\Big)\\
+    &= \E\Big(\sum_{j=1}^{J_n}
+    M_{nj}^2 \Big\lvert \tfrac{1}{n} \sum_{\tau=0}^{n-1}
+    (\mu_{n,\tau} - \bar{\mu}_n)^2 \Big\lvert\Big)\\
+    &= o(n p_n).
+  \end{align*}
+  The first line follows from the LIE. The second exploits the
+  fact that the conditional expectation in the previous line
+  just averages over the block's starting period. The
+  inequality is an application of the Cauchy-Schwarz inequality.
+  The next line holds because the summation
+  \[
+    \sum_{\tau=0}^{n-1} (\mu_{n,\tau+k} - \bar{\mu}_n)^2
+    1\{ \tau + k \in I_n(\tau, M_{nj})\}
+  \]
+  is zero for all but $M_{nj}$ values of $k$ and is a nonzero constant
+  for those $k$. The last line holds by Lemma~\ref{L1} and assumption.
+\end{proof}
+
+\begin{lem}\label{L4}
+Under the conditions of Theorem~\ref{T1},
 \begin{gather}
@@
   M_{nj})$ is a uniformly integrable martingale difference array, by
-  Lemma~\ref{bootstrapped-zsq-uniform-integrability-lemma}, and
+  Lemma~\ref{L6}, and
   satisfies the \lln. (See~\citealp{Dav:94}, Theorem 19.7.)
   For~\eqref{eq:26}, observe that
-  \begin{equation*}
-    \Big| \sum_{j=1}^{J_n} (Z_{nj}^{*2} - Z_{nj}^{\prime*2}) \Big| \leq
-    2 \Big(\sum_{j=1}^{J_n} Z_{nj}^{*2} \Big)^{1/2}
-    \Big(\tfrac{1}{n} \sum_{t=1}^n (\mu_{nt} - \bar X_n)^2\Big)^{1/2}
-    + \tfrac{1}{n} \sum_{t=1}^n (\mu_{nt} - \bar X_n)^2
-  \end{equation*}
-  after several applications of the Cauchy-Schwarz
-  inequality. Lemma~\ref{lln-for-real-zsq}, along with~\eqref{eq:17}
-  and~\eqref{eq:25}, implies that $\sum_j Z_{nj}^{*2} = O_p(1)$;
-  $(1/n) \sum_t (\mu_{nt} - \bar X)^2$ converges to zero in
-  probability by assumption on $\mu_{nt} - \bar\mu_n$ and because
-  $\bar X$ itself obeys the \lln.
+  \begin{multline*}
+    \Big| \sum_{j=1}^{J_n} (Z_{nj}^{*2} - Z_{nj}^{\prime*2}) \Big|
+    \leq 2 \Big(\sum_{j=1}^{J_n} Z_{nj}^{*2} \Big)^{1/2}
+    \Big(\tfrac{1}{n} \sum_{j=1}^{J_n} \Big( \sum_{t= K_{n,j-1} + 1}^{K_{nj}}
+    (\mu_{nt}^{*} - \bar X_n)\Big)^2 \Big)^{1/2} \\
+    + \tfrac{1}{n} \sum_{j=1}^{J_n} \Big( \sum_{t= K_{n,j-1} + 1}^{K_{nj}}
+    (\mu_{nt}^{*} - \bar X_n)\Big)^2
+  \end{multline*}
+  from the Cauchy-Schwarz inequality. Lemma~\ref{L5}, along
+  with~\eqref{eq:17} and~\eqref{eq:25}, implies that
+  $\sum_j Z_{nj}^{*2} = O_p(1)$. Lemma~\ref{L3} implies that
+  \[
+    \tfrac{1}{n} \sum_{j=1}^{J_n} \Big( \sum_{t= K_{n,j-1} + 1}^{K_{nj}}
+    (\mu_{nt}^{*} - \bar X_n)\Big)^2 \to^p 0
+  \]
+  since $\bar X$ itself obeys the \lln.
 
@@
   Uniform integrability ensures that the convergence in~(\ref{eq:25})
-  holds in $L_1$ as well and
-  Lemma~\ref{equivalent-convergence-from-lie-lemma} then implies that
+  holds in $L_1$ and Lemma~\ref{L2} then implies that
   the first term in \eqref{eq:38} converges to zero in probability.
-  Lemma~\ref{lln-for-real-zsq} proves that the second and third
+  Lemma~\ref{L5} proves that the second and third
   summation converge to zero in probability.
@@
   \end{equation}
-  which holds by Lemma~\ref{block-length-convergence-lemma} and
+  which holds by Lemma~\ref{L1} and
   assumption.
@@
 
-\begin{lem}\label{lln-for-real-zsq}
-  If the conditions of Theorem~\ref{main-bootstrap-clt} hold then
+\begin{lem}\label{L5}
+  If the conditions of Theorem~\ref{T1} hold then
   \begin{gather}
@@
   almost surely.
-  By Lemma~\ref{dejong-restatement-lemma} (Equation~\ref{eq:32}), for
+  By Lemma~\ref{L7} (Equation~\ref{eq:32}), for
   any $\delta > 0$ there exist positive $C$ and $\epsilon$ such that
@@
   for large enough $n$, which converges to $2 \delta$ by
-  Lemma~\ref{block-length-convergence-lemma}.
-  Lemma~\ref{zsq-uniform-integrability-lemma} ensures that there
+  Lemma~\ref{L1}.
+  Lemma~\ref{L8} ensures that there
   exists a value $C$ (possibly different from the value above) such
@@
   for large enough $n$,%
-\footnote{Lemma~\ref{dejong-restatement-lemma}
-  and~\ref{zsq-uniform-integrability-lemma} are stated for the
+\footnote{Lemma~\ref{L7}
+  and~\ref{L8} are stated for the
   unconditional expectation, which may cause some confusion here. Note
@@
   both of which converge to zero in $L_1$ as $n \to \infty$ by
-  Lemma~\ref{block-length-convergence-lemma}.  These three convergence
+  Lemma~\ref{L1}.  These three convergence
   results imply that the \allcaps{rhs} of (\ref{eq:29}) converges to
@@
   which is a direct implication of
-  Lemma~\ref{dejong-restatement-lemma}.%
+  Lemma~\ref{L7}.%
   \footnote{The discussion in Footnote~\ref{f:1} applies here as well.}
@@
 
-\begin{lem}\label{bootstrapped-zsq-uniform-integrability-lemma}
-  Under the conditions of Theorem~\ref{main-bootstrap-clt},
-  \begin{multline}\label{eq:35}
-    \lim_{C \to \infty} \limsup_{n \to \infty} \sup_{m' = 1,\dots,n}
-    \E\Big(\Big(\sum_{\tau=0}^{n-1} \max_{m=1,\dots,m'} Z_n(\tau, m)^2 / m'\Big) \\
-    \times\ind\Big\{\sum_{\tau=0}^{n-1} \max_{m=1,\dots,m'} Z_n(\tau, m)^2 / m' > C\Big\}\Big) = 0.
-  \end{multline}
-  and
+\begin{lem}\label{L6}
+  Under the conditions of Theorem~\ref{T1},
   \begin{multline}\label{eq:30}
@@
 \begin{proof}
-  For \eqref{eq:35}, take $\epsilon > 0$. The sum
-  \[
-  \sum_{\tau=0}^{n-1} \max_{m=1,\dots,m'} Z_n(\tau, m)^2 / m'
-  \]
-  is uniformly integrable if and only if it is uniformly $L_1$-bounded
-  and there exists an $\epsilon'$ such that
-  \[
-  \sup_{n, m'} \E\Big( \ind(A) \sum_{\tau=0}^{n-1} \max_{m=1,\dots,m'} Z_n(\tau, m)^2 / m' \Big)
-  < \epsilon
-  \]
-  for every event $A \in \Omega_n$ satisfying $\pr(A) < \epsilon'$.
-  (\citealp{Dav:94}, 12.9.)
-  Lemma~\ref{zsq-uniform-integrability-lemma} ensures uniform integrability of
-  $\max_{m=1,\dots,m'} Z_n'(\tau, m)^2 n/m'$, so there exists an
-  $\epsilon'$ such that
-  \begin{equation*}
-    \sup_{n, m', \tau} \E\big( \ind(A) \max_{m=1,\dots,m'} Z_n'(\tau, m)^2 n / m' \big) \leq \epsilon / 9
-  \end{equation*}
-  for all $A \in \Omega_n$ with $\pr(A) \leq \epsilon'$. Then, writing
+  We will first show that, for every $\epsilon > 0$ and large enough
+  $n$, there exists an $\epsilon' > 0$ with the property that
+  \begin{equation}\label{eq:31}
+    \E \Big(\ind(A) \times \max_{m = 1,\dots,m'} Z^*_n(\tau, m)^2 n / m'\Big) < \epsilon
+  \end{equation}
+  for any event $A \in \Fs_n \equiv \sigma(X_{n1},\dots,X_{nn})$ with
+  $\pr(A) \leq \epsilon'$. Then we will show that this property
+  implies uniform integrability.\footnote{%
+    The novelty in this part of the proof is the measurability
+    requirement. The sigma-field $\Fs_n$ intentionally excludes the
+    random variables that define the bootstrap (block length and block
+    start periods) and any $A \in \Fs_n$ is independent of those
+    variables, so $Z_n^{*}(\tau, m)^2$ is not $\Fs_n$-measurable. If
+    $\Fs_n$ were enlarged to include those variables then uniform
+    integrability would be an immediate consequence and would not need
+    to be shown separately. See \citet[Theorem 12.9]{Dav:94}.} %
+
+  Take an arbitrary $\delta > 0$ and a value of $\delta' > 0$
+  so that
+  \begin{equation}\label{eq:35}
+    \sup_{m'=1,\dots,n} \E \Big(\ind(A) \max_{m = 1,\dots,m'}
+    Z_n'(\tau, m)^2 n / m' \Big) < \delta
+  \end{equation}
+  for any $A \in \Fs_n$ with $\pr(A) \leq \delta'$; the existence
+  of $\delta'$ is ensured by Lemma~\ref{L8}. For any $x$,
+  define $J(x)$ to be the block index such that $K_{n,J(x) - 1} < x
+  \leq K_{n,J(x)}$. For any $m$, we can decompose $Z_n^{*}(\tau, m)$
+  into a summation of conditionally independent blocks
+  \begin{equation*}
+  Z^{*}_n(\tau, m) = Z_n^*(\tau, K_{n,J(\tau)} - \tau) +
+  \sum_{j=J(\tau)+1}^{J(\tau + m)-1} Z_{nj}^* + Z_n^*(K_{n,J(\tau+m)-1}, m - K_{n,J(\tau + m)-1}),
+  \end{equation*}
+  giving
+  \begin{align}
+  \E  \Big(&\ind(A) \times \max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m'\Big)
+  \notag \\
+  &\leq 3 \E\Big[ \Em^{*} \Big[\ind(A) \tfrac{n}{m'}\max_{m = 1,\dots, m'}
+  \Big(Z_n^*(\tau, K_{n,J(\tau)} - \tau) + \sum_{j=J(\tau)+1}^{J(\tau + m)-1} Z_{nj}^*\Big)^2\Big]
+  \notag \\
+  &\quad + 3 \Em^{*} \big[\ind(A) \tfrac{n}{m'}
+  \max_{m=1,\dots,m'} Z_n^*(K_{n,J(\tau+m)-1}, m - K_{n,J(\tau + m)-1})^2 \big]\Big]\label{eq:6}
+  \end{align}
+  almost surely.
+
+  Since $Z_{nj}^*$ is a martingale difference array, Doob's maximal
+  inequality for martingales \citep[see][Theorem 15.15, for
+  example]{Dav:94} along with the construction of $Z_{nj}^{*}$ gives
+  a bound for the first term on the \allcaps{RHS} of~\eqref{eq:6},
+  \begin{align*}
+  \E \Em^* & \Big[\ind(A) \tfrac{n}{m'}\max_{m = 1,\dots, m'}
+  \Big(Z_n^*(\tau, K_{n,J(\tau)} - \tau)
+  + \sum_{j=J(\tau)+1}^{J(\tau + m)-1} Z_{nj}^*\Big)^2\Big] \\
+  &\leq \tfrac{1}{m'} \sum_{u = 0}^{n-1} \E \Big[\Em \big[
+  \ind(A) Z_n(u, K_{n,J(\tau)} - \tau)^2\big] +
+  \sum_{j=J(\tau)+1}^{J(\tau + m')-1} \Em \big[\ind(A) Z_n(u, M_{nj})^2]\Big] \\
+  &\leq \tfrac{3}{m'} \sum_{u = 0}^{n-1} \E\Big[\Em\big[
+  \ind(A) Z'_n(u, K_{n,J(\tau)} - \tau)^2\big]
+  + \tfrac{1}{n} \Pm[A] \Big(\sum_{t \in I_n(u, K_{n,J(\tau)} - \tau)}
+  (\mu_{nt} - \bar \mu_n)\Big)^2 \\
+  & \quad+ \sum_{j=J(\tau)+1}^{J(\tau + m')-1}
+  \Em \big[\ind(A) Z_n'(u, M_{nj})^2]
+  + \tfrac{1}{n} \Pm[A]
+  \sum_{j=J(\tau)+1}^{J(\tau + m')-1}\Big( \sum_{t \in I_n(u,M_{nj})}
+  (\mu_{nt} - \bar{\mu}_n) \Big)^2 \\
+  & \quad+ \Em\big( \ind(A) Z_n'(u, n)^2 \big)
+  \sum_{j=J(\tau)}^{J(\tau+m')-1} M_{nj}^2/n^2 \Big] \\
+  &\leq (3\delta/m') \E (K_{n,J(\tau+m')-1} - \tau)
+    + 3\delta \E\Big(\sum_{j=J(\tau)}^{J(\tau+m')-1} M_{nj}^2/n^2 \Big) \\
+  &\quad+ 3(\delta'/n) \E\Big( \Big(\sum_{t \in I_n(u, K_{n,J(\tau)} - \tau)}
+  (\mu_{nt} - \bar \mu_n)\Big)^2 +
+  \sum_{j=J(\tau)+1}^{J(\tau + m')-1}\Big( \sum_{t \in I_n(u,M_{nj})}
+  (\mu_{nt} - \bar{\mu}_n) \Big)^2 \Big) \\
+  & < C_1 \delta + C_2 p_n \delta'
+  \end{align*}
+  for some finite constants $C_1$ and $C_2$.
+  The second inequality comes from writing
   \begin{align*}
@@
     + \tfrac{1}{\sqrt{n}} \sum_{t \in I_n(\tau, m)} (\mu_{nt} - \bar \mu_n)
-    - (m/n) Z'_n(0, n)
-  \end{align*}
-  gives the relationship
-  \begin{align*}
-    \E\Big(\ind(A) \sum_{\tau=0}^{n-1} & \max_{m=1,\dots,m'} Z_n(\tau, m)^2/m'\Big) \\
-    &\leq 3 \sum_{\tau=0}^{n-1} \E\big( \ind(A)  \max_{m=1,\dots,m'} Z'_n(\tau, m)^2/m'\big) \\
-    &\quad+(3/n m') \E\Big(\ind(A) \sum_{\tau=0}^{n-1} \max_{m=1,\dots,m'}
-    \Big(\sum_{t \in I_n(\tau, m)} (\mu_{nt} - \bar \mu_n) \Big)^2\Big) \\
-    &\quad+ (3 m' / n) \E (\ind(A) Z'_n(0, n)^2) \\
-    &\leq (2 \epsilon/3) + (3 \epsilon' m' / n)\sum_{t=1}^n (\mu_{nt} - \bar \mu_n)^2
-  \end{align*}
-  where the last inequality holds as a consequence of $A$'s
-  construction. Since $\sum_{t=1}^n (\mu_{nt} - \bar \mu_n)^2 \to
-  0$, choose $n$ large enough that this sum is less than
-  $\epsilon/9\epsilon'$. The proof that that the first moment is bounded is
-  similar, which completes the proof of~(\ref{eq:35}).
-
-  For~(\ref{eq:30}), we will first show that, for every $\epsilon > 0$,
-  there exists an $\epsilon' > 0$ with the property that
-  \begin{equation}\label{eq:31}
-    \Em \Big(\ind(A) \times \max_{m = 1,\dots,m'} Z^*_n(\tau, m)^2 n / m'\Big) < \epsilon
-  \end{equation}
-  for any event $A \in \Fs_n \equiv \sigma(X_{n1},\dots,X_{nn};\,
-  M_{n1},\dots,M_{n,J_n};\, J_n)$ with $\pr(A) \leq
-  \epsilon'$. Then we will show that this property implies uniform
-  integrability.%
-\footnote{The novelty in this part of the proof is the measurability
-  requirement. The sigma-field $\Fs_n$ intentionally exlcudes the
-  block start periods $u_{n1},\dots,u_{n,J_n}$, so
-  $Z_n^{*}(\tau, m)^2$ is not $\Fs_n$-measureable. If we instead
-  proved~\eqref{eq:31} for all $A \in \Omega_n$, as we did for the
-  first part of the proof, then uniform integrebality would be an
-  immediate consequence and would not need to be shown separately. See
-  \citet[Theorem 12.9]{Dav:94}.} %
-
-  Take an arbitrary $\epsilon > 0$ and a value of $\epsilon' > 0$
-  so that
-  \begin{equation*}
-    \sup_{m'=1,\dots,n} \Em \Big(\ind(A) \sum_{\tau = 0}^{n-1} \tfrac{1}{m'} \max_{m = 1,\dots,m'}
-    Z_n(\tau, m)^2\Big) < \epsilon / 6
-  \end{equation*}
-  for any $A \in \Fs_n$ with $\pr(A) \leq \epsilon'$, which is
-  shown to exist in the first part of this Lemma. Then, for any $x$,
-  define $J(x)$ to be the block index such that $K_{n,J(x) - 1} < x
-  \leq K_{n,J(x)}$. For any $m$, we can decompose $Z_n^{*}(\tau, m)$ as
-  \begin{equation*}
-  Z^{*}_n(\tau, m) = Z_n^*(\tau, K_{n,J(\tau)} - \tau) +
-  \sum_{j=J(\tau)+1}^{J(\tau + m)-1} Z_{nj}^* + Z_n^*(K_{n,J(\tau+m)-1}, m - K_{n,J(\tau + m)-1}),
-  \end{equation*}
-  giving
-  \begin{align}
-  \Em \Em^* \Big(&\ind(A) \times \max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m'\Big)
-  \notag \\
-  &\leq 3 \Em \Em^* \Big[\ind(A) \tfrac{n}{m'}\max_{m = 1,\dots, m'}
-  \Big(Z_n^*(\tau, K_{n,J(\tau)} - \tau) + \sum_{j=J(\tau)+1}^{J(\tau + m)-1} Z_{nj}^*\Big)^2\Big]
-  \notag \\
-  &\quad + 3 \Em \Em^* \big[\ind(A) \tfrac{n}{m'}
-  \max_{m=1,\dots,m'} Z_n^*(K_{n,J(\tau+m)-1}, m - K_{n,J(\tau + m)-1})^2 \big]\label{eq:6}
-  \end{align}
-  almost surely.
-
-  Since $Z_{nj}^*$ is a martingale difference array, Doob's maximal
-  inequality for martingales \citep[see][Theorem 15.15, for
-  example]{Dav:94} along with the construction of $Z_{nj}^{*}$ gives
-  a bound for the first term on the \allcaps{RHS} of~\eqref{eq:6},
-  \begin{multline*}
-  \Em \Em^* \Big[\ind(A) \tfrac{n}{m'}\max_{m = 1,\dots, m'}
-  \Big(Z_n^*(\tau, K_{n,J(\tau)} - \tau) + \sum_{j=J(\tau)+1}^{J(\tau + m)-1} Z_{nj}^*\Big)^2\Big] \\
-  \leq \tfrac{1}{m'} \sum_{u = 0}^{n-1} \Big\{\Em\big[\ind(A) Z_n(u, K_{n,J(\tau)} - \tau)^2\big] +
-  \sum_{j=J(\tau)+1}^{J(\tau + m')-1} \Em \big[\ind(A) Z_n(u, M_{nj})^2]\Big\}
-  \end{multline*}
-  and this term is less than $\epsilon/6$ by construction of $A$.
-  For the second term on the \allcaps{RHS}~\eqref{eq:6}, use the sequence of inequalities
-  \begin{align*}
-  \Em \Em^* \big[\ind(A) &\tfrac{n}{m'}
+    - (m/n) Z'_n(\tau, n),
+  \end{align*}
+  the third follows by construction of $A$
+  and fourth follows from an argument similar to Lemma~\ref{L3}.
+
+  For the second term on the \allcaps{RHS} of~\eqref{eq:6}, use the
+  sequence of inequalities
+  \begin{align*}
+  \E \Em^* \big[\ind(A) &\tfrac{n}{m'}
   \max_{m=1,\dots,m'} Z_n^*(K_{n,J(\tau+m)-1}, m - K_{n,J(\tau + m)-1})^2 \big] \\
-  &\leq \sum_{j=J(\tau) + 1}^{J(\tau+m')-1} \tfrac{n}{m'} \Em \Em^* \big[\ind(A)
-  \max_{m=1,\dots, \min(M_{nj}, m' - K_{n,j-1})} Z_n^*(K_{n,j}, m)^2 \big] \\
-  &\leq \sum_{j=J(\tau) + 1}^{J(\tau+m')} \tfrac{M_{nj}}{m'} \sum_{u=0}^{n-1} \Em \big[\ind(A)
-  \max_{m=1,\dots,\min(M_{nj}, m' - K_{n,j-1})} Z_n(u, m)^2 / M_{nj} \big] \\
-  &\leq \sum_{j=J(\tau) + 1}^{J(\tau+m')} \epsilon \cdot \min(M_{nj}, m' - K_{n,j-1}) / 6 m' \\
-  &\leq \epsilon/6.
-  \end{align*}
-  Together, these bounds imply~(\ref{eq:31}). A
-  similar argument also implies that $n Z_n^*(\tau, m)^2 / m'$ has
-  finite first moment.
+  &\leq \E \Big(\sum_{j=J(\tau) + 1}^{J(\tau+m')-1} \tfrac{n}{m'} \Em^* \big[\ind(A)
+  \max_{m=1,\dots, \min(M_{nj}, m' - K_{n,j-1})} Z_n^*(K_{n,j}, m)^2 \big]\Big) \\
+  &\leq \E \Big(\sum_{j=J(\tau) + 1}^{J(\tau+m')} \tfrac{1}{m'} \sum_{u=0}^{n-1} \Em \big[\ind(A)
+  \max_{m=1,\dots,\min(M_{nj}, m' - K_{n,j-1})} Z_n(u, m)^2 \big]\Big) \\
+  &\leq \E \Big(\sum_{j=J(\tau) + 1}^{J(\tau+m')} \tfrac{3}{m'} \sum_{u=0}^{n-1} \Big\{
+  \Em \big[\ind(A)
+  \max_{m=1,\dots,\min(M_{nj}, m' - K_{n,j-1})} Z_n'(u, m)^2 \big] \\
+  &\quad +
+  \tfrac{1}{n} \Pm[A] \max_{m = 1,\dots,\min(M_{nj}, m'-K_{n,j-1})}
+  \Big(\sum_{t \in I_n(u,m)} (\mu_{nt} - \bar{\mu}_n)\Big)^2 \\
+  &\quad+ \tfrac{\min(M_{nj},m'-K_{n,j-1})^2}{n^2} \Em( \ind(A) Z_n'(u, n)^2 ) \Big\}\Big)\\
+  &\leq C'_1 \delta + C_2' \delta' p_n
+  \end{align*}
+  for constants $C_1'$ and $C_2'$. To express these bounds in the form
+  of~\eqref{eq:31}, let $\epsilon > 0$ be arbitrary, choose $\delta'$
+  such that~\eqref{eq:35} holds for $\delta = \epsilon/(2C_1+2C_1')$,
+  and let $\epsilon' = \min(\delta', \epsilon/(2 C_2 + 2C_2'))$.
+  A similar argument also
+  implies that $n Z_n^*(\tau, m)^2 / m'$ has finite first moment.
 
@@
   \begin{equation*}
-    \Pm\Big[ \max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m' > C_0 \Big] \leq \epsilon'.
+    \Pr\Big[ \max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m' > C_0 \Big] \leq \epsilon'.
   \end{equation*}
@@
   \begin{equation*}
-    \Em \Big(\max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m'
+    \E \Big(\max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m'
     \times \ind\Big\{ \max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m' > C \Big\}\Big) \leq \epsilon
@@
 
-\begin{lem}\label{dejong-restatement-lemma}
+\begin{lem}\label{L7}
 \newcommand{\isum}{\sum_{i=0}^{\lfloor n/m \rfloor - 1}}
-  Suppose the conditions of Theorem~\ref{main-bootstrap-clt} hold.
+  Suppose the conditions of Theorem~\ref{T1} hold.
   For any positive $\delta$, there exist positive and finite constants
@@
 
-\begin{lem}\label{zsq-uniform-integrability-lemma}
+\begin{lem}\label{L8}
 \newcommand{\uiterm}{\max_{m \in 1,\dots,m'} \Big(
@@
 \citet{Dav:94}. The same comment that follows
-Lemma~\ref{dejong-restatement-lemma} applies here as well: the bounds
+Lemma~\ref{L7} applies here as well: the bounds
 apply equally well to $\Em$.

### 2016-06-08 Paper.tex
[#18] Add examples of heterogeneity allowed under assumption 2
This commit adds several paragraphs that explain the sort of hetergoeneity
in the means that Theorem 1's assumptions allow. This explanation is in
response to one of the referees on the paper.

@@
 Stationary Bootstrap will select the blocks randomly and is similar to
-\citepos{JoD:00b} requirement for the \fclt. Similarly, our assumption
-on the dispersion of the individual means, $(\mu_{nt} - \bar\mu_n)^2$, is
-slightly stronger than \citepos{GoW:02} and \citepos{GoJ:03} to
-accommodate larger block sizes.%
-\footnote{Note that this is one reason that we are presenting our
-  results using general triangular-array notation: to allow for the
-  means to change over time for comparison with \citepos{GoW:02} and
-  \citepos{GoJ:03} results.}
+\citepos{JoD:00b} requirement for the \fclt.
+
+The assumption on the dispersion of the individual means,
+$(\mu_{nt} - \bar\mu_n)^2$, is the same as \citepos{GoW:02} and
+\citepos{GoJ:03} when the expected block length is $o(\sqrt{n})$. When
+the blocks are longer than $o(\sqrt{n})$, a case that \citet{GoW:02}
+and \citet{GoJ:03} do not consider, the dispersion must be smaller.
+To see these implications of this assumption, it is helpful to
+consider a simple example: a stochastic process with a single break of
+size $\Delta_n$ at time $T_n$,
+\begin{equation*}
+\mu_{nt} =
+\begin{cases}
+  \mu & \text{if } t \leq T_n \\
+  \mu + \Delta_n & \text{otherwise}
+\end{cases}
+\end{equation*}
+A small amount of algebra gives the relationship,
+\begin{equation*}
+  \sum_{t=1}^n (\mu_{nt} - \bar \mu_n)^2
+  = T_n (n - T_n) \Delta_n^2 / n \equiv D_n;
+\end{equation*}
+we have defined $D_n$ to minimize notation in the subsequent
+discussion.  For the Moving and Circular Block Bootstraps,
+Theorem~\ref{T1}'s Assumption 2 holds if $D_n = o(n / M_n^2)$, and for
+the Stationary Bootstrap the same relationship must hold for the
+expected block length. If $\Delta_n = \Delta_0$ and $T_n = \pi n$ for
+some constants $\Delta_0$ and $\pi$ and for all $n$, then
+$D_n \approx \Delta_0^2 \, c (1 - c) \, n$ and Assumption~2 fails to
+hold. These values of $\Delta_n$ and $T_n$ describe a scenario where
+there is a break large enough that its timing could be precisely
+estimated \citep[as in][]{Bai:94}, but the break is ignored and the
+bootstrap is applied to the entire dataset.
+
+We can also use the same DGP to produce scenarios where
+Theorem~\ref{T1}'s Assumption~2 is satisfied.  The first mimics a
+setting where the break is estimated and the bootstrap is applied to
+the post-break sample, but a small number of pre-break observations
+are accidentally included in the data set as well. Here
+$\Delta_n = \Delta_0$ and $T_n = T_0$ for some finite $T_0$. In this
+case, Assumption 2 holds hold as long as $M_n = o(\sqrt{n})$.
+Similarly, if the break is moderate with unknown timing in the sense
+of \citet{ElM:07}, so $\Delta_n = \Delta / \sqrt{n}$ and
+$T_n = \pi n$, then $D_n \approx \Delta c (1 - c)$ and Assumption 2
+again holds as long as $M_n = o(\sqrt{n})$. Consequently, block sizes
+of length $o(\sqrt{n})$ ensure that the conditions of
+Theorem~\ref{T1}'s when there is a moderate amount of
+heterogeneity---either because the sample is chosen to lie after a
+large break estimated break or because any breaks are smaller in
+magnitude and, consequently, potentially difficult to detect. When the
+degree of heterogeneity is very small or nonexistent, so
+$\sum_t (\mu_{nt} - \bar \mu_n)^2$ grows even slower, then larger
+block lengths can also satisfy Assumption 2.
 

### 2016-06-09 Paper.tex
[#18] Strengthen one component of Lemma 1
The last part of Lemma 1 deals with convergence of \sum M_j^2 / n^2. To
relax the strong assumption on near homogeneity of the means that I'm
currently making, I need a slightly different version of this convergence;
I want the rate that \sum M_j^2 diverges. This commit changes the result
to give this stronger conclusion.

--- 2016-05-23 Paper.tex
@@
   argument.}%
-\footnote{Lemmas~\ref{bootstrap-variance-convergence-lemma} and
-  \ref{bootstrapped-zsq-uniform-integrability-lemma} are particularly
+\footnote{Lemmas~\ref{L3} and
+  \ref{L5} are particularly
   strong demonstrations of this argument.} %
@@
 $\sigma_n^{*2}$ is uniformly a.s.\ positive and holds by
-Lemma~\ref{bootstrap-variance-convergence-lemma}) and the following
+Lemma~\ref{L3}) and the following
 two conditions hold for all positive $\epsilon$:
@@
 is a uniformly-integrable martingale difference array
-by Lemma~\ref{bootstrapped-zsq-uniform-integrability-lemma}
+by Lemma~\ref{L5}
 and satisfies the \lln\ (e.g., \citealp{Dav:94}, Theorem 19.7). So
@@
 conditions (and does not depend on $n$ or $m$) is a consequence of
-Lemma~\ref{bootstrapped-zsq-uniform-integrability-lemma},
+Lemma~\ref{L5},
 Equation~\eqref{eq:30}. Since $J_n$ and $M_{nj}$ are both $\Ms$-measureable
@@
 (Also see
-Lemma~\ref{equivalent-convergence-from-lie-lemma}.)
-
-Lemma~\ref{bootstrap-variance-convergence-lemma} implies that
+Lemma~\ref{L2}.)
+
+Lemma~\ref{L3} implies that
 $\sigma_n^{*2}$ and $\hat\sigma_n^{*2}$ both converge to $\sigma^2$ in
@@
 for any finite $k$. Since $k$ is arbitrary,~\eqref{eq:37} holds. Since
-Theorem~\ref{main-bootstrap-clt}'s assumptions ensure that the
+Theorem~\ref{T1}'s assumptions ensure that the
 original array obeys the \clt,~\eqref{eq:36} holds \citep[Theorem
@@
 
-\subsection*{Proof of Theorem~\ref{main-bootstrap-invariance-theorem}}
+\subsection*{Proof of Theorem~\ref{T2}}
 \newcommand{\gn}{{\lfloor \gamma n \rfloor}}
@@
 for some constant $C$ by
-Lemma~\ref{bootstrapped-zsq-uniform-integrability-lemma}. This term
-converges to zero by Lemma~\ref{block-length-convergence-lemma}.
+Lemma~\ref{L5}. This term
+converges to zero by Lemma~\ref{L1}.
 
@@
 \end{align*}
-Lemma~\ref{bootstrapped-zsq-uniform-integrability-lemma} implies that
+Lemma~\ref{L5} implies that
 \begin{equation*}
@@
   $\epsilon$, and
-  \item $\sum_{i=1}^{J_n} M_{ni}^2 / n^2 \to^p 0$.
+  \item $\sum_{i=1}^{J_n} M_{ni}^2 = O_p(n/p_n)$.
   \end{enumerate}
@@
   The proof of part 4 is the same as part 2, making the obvious
-  substitutions. Part 5 holds because $\sum_{i=1}^{J_n} M_{ni}^2/n^2
-  \leq \max_{i=1,\dots,J_n} M_{ni}/n$ which converges to zero in
-  probability by part 2.
+  substitutions.
+  Using the same argument as in part 2 of this Lemma, it suffices to
+  prove that
+  $\sum\nolimits_{i=1}^{\lfloor C n p_n \rfloor} M_{ni}^2 =
+  O_p(n/p_n)$ where $C$ is an arbitrary constant greater than 1.  The
+  LLN implies that
+  \begin{equation*}
+    \tfrac{1}{C n p_n} \sum\nolimits_{i=1}^{\lfloor C n p_n \rfloor}
+    M_{ni}^2 = \tfrac{2 - p_n}{p_n^2} + o_p(\tfrac{2 - p_n}{p_n^2})
+  \end{equation*}
+  and the result follows immediately.
 \end{proof}
 
-\begin{lem}\label{equivalent-convergence-from-lie-lemma}
+\begin{lem}\label{L2}
   If $\{A_n\}$ is a sequence of events in $\Omega$ then the following
@@
 
-\begin{lem}\label{bootstrap-variance-convergence-lemma}
-Under the conditions of Theorem~\ref{main-bootstrap-clt},
+\begin{lem}\label{L3}
+Under the conditions of Theorem~\ref{T1},
 \begin{gather}
@@
   M_{nj})$ is a uniformly integrable martingale difference array, by
-  Lemma~\ref{bootstrapped-zsq-uniform-integrability-lemma}, and
+  Lemma~\ref{L5}, and
   satisfies the \lln. (See~\citealp{Dav:94}, Theorem 19.7.)
@@
   after several applications of the Cauchy-Schwarz
-  inequality. Lemma~\ref{lln-for-real-zsq}, along with~\eqref{eq:17}
+  inequality. Lemma~\ref{L4}, along with~\eqref{eq:17}
   and~\eqref{eq:25}, implies that $\sum_j Z_{nj}^{*2} = O_p(1)$;
@@
   holds in $L_1$ as well and
-  Lemma~\ref{equivalent-convergence-from-lie-lemma} then implies that
+  Lemma~\ref{L2} then implies that
   the first term in \eqref{eq:38} converges to zero in probability.
-  Lemma~\ref{lln-for-real-zsq} proves that the second and third
+  Lemma~\ref{L4} proves that the second and third
   summation converge to zero in probability.
@@
 
-\begin{lem}\label{lln-for-real-zsq}
-  If the conditions of Theorem~\ref{main-bootstrap-clt} hold then
+\begin{lem}\label{L4}
+  If the conditions of Theorem~\ref{T1} hold then
   \begin{gather}
@@
   almost surely.
-  By Lemma~\ref{dejong-restatement-lemma} (Equation~\ref{eq:32}), for
+  By Lemma~\ref{L6} (Equation~\ref{eq:32}), for
   any $\delta > 0$ there exist positive $C$ and $\epsilon$ such that
@@
   for large enough $n$, which converges to $2 \delta$ by
-  Lemma~\ref{block-length-convergence-lemma}.
-  Lemma~\ref{zsq-uniform-integrability-lemma} ensures that there
+  Lemma~\ref{L1}.
+  Lemma~\ref{L7} ensures that there
   exists a value $C$ (possibly different from the value above) such
@@
   for large enough $n$,%
-\footnote{Lemma~\ref{dejong-restatement-lemma}
-  and~\ref{zsq-uniform-integrability-lemma} are stated for the
+\footnote{Lemma~\ref{L6}
+  and~\ref{L7} are stated for the
   unconditional expectation, which may cause some confusion here. Note
@@
   which is a direct implication of
-  Lemma~\ref{dejong-restatement-lemma}.%
+  Lemma~\ref{L6}.%
   \footnote{The discussion in Footnote~\ref{f:1} applies here as well.}
@@
 
-\begin{lem}\label{bootstrapped-zsq-uniform-integrability-lemma}
-  Under the conditions of Theorem~\ref{main-bootstrap-clt},
+\begin{lem}\label{L5}
+  Under the conditions of Theorem~\ref{T1},
   \begin{multline}\label{eq:35}
@@
   (\citealp{Dav:94}, 12.9.)
-  Lemma~\ref{zsq-uniform-integrability-lemma} ensures uniform integrability of
+  Lemma~\ref{L7} ensures uniform integrability of
   $\max_{m=1,\dots,m'} Z_n'(\tau, m)^2 n/m'$, so there exists an
@@
 
-\begin{lem}\label{dejong-restatement-lemma}
+\begin{lem}\label{L6}
 \newcommand{\isum}{\sum_{i=0}^{\lfloor n/m \rfloor - 1}}
-  Suppose the conditions of Theorem~\ref{main-bootstrap-clt} hold.
+  Suppose the conditions of Theorem~\ref{T1} hold.
   For any positive $\delta$, there exist positive and finite constants
@@
 
-\begin{lem}\label{zsq-uniform-integrability-lemma}
+\begin{lem}\label{L7}
 \newcommand{\uiterm}{\max_{m \in 1,\dots,m'} \Big(
@@
 \citet{Dav:94}. The same comment that follows
-Lemma~\ref{dejong-restatement-lemma} applies here as well: the bounds
+Lemma~\ref{L6} applies here as well: the bounds
 apply equally well to $\Em$.

### 2016-06-10 Paper.tex
[#25] Fix duplicate equation refernce in Theorem 1
Closes #25.

@@
 
-Theorem~\ref{T1} presents the main result, asymptotic normality of
+Theorem~\ref{main-bootstrap-clt} presents the main result, asymptotic normality of
 the distribution of bootstrapped sums. This paper adopts the
@@
 
-\begin{thm}\label{T1}
+\begin{thm}\label{main-bootstrap-clt}
   Suppose the following conditions hold.
@@
 
-Theorem~\ref{T1} relies on a general insight about the
+Theorem~\ref{main-bootstrap-clt} relies on a general insight about the
 variance of the sample mean under the bootstrap-induced
@@
   argument.}%
-\footnote{Lemmas~\ref{L3} and
-  \ref{L5} are particularly
+\footnote{Lemmas~\ref{bootstrap-variance-convergence-lemma} and
+  \ref{bootstrapped-zsq-uniform-integrability-lemma} are particularly
   strong demonstrations of this argument.} %
@@
 
-In short, the basic approach that we use to prove Theorem~\ref{T1}
+In short, the basic approach that we use to prove Theorem~\ref{main-bootstrap-clt}
 is based on a fundamental connection between the second moments of the
@@
 
-Theorem~\ref{T1} can also be extended to give an \fclt\
+Theorem~\ref{main-bootstrap-clt} can also be extended to give an \fclt\
 using arguments from \citet{JoD:00b}. We show in
-Theorem~\ref{T2} that the partial sum
+Theorem~\ref{main-bootstrap-invariance-theorem} that the partial sum
 of the bootstrapped process obeys an \fclt\ and can be used to derive
 critical values for other test statistics under the same assumptions
-as Theorem~\ref{T1}. For this result, define the
+as Theorem~\ref{main-bootstrap-clt}. For this result, define the
 following partial sums,
@@
 
-\begin{thm}\label{T2}
-Suppose that the conditions of Theorem~\ref{T1} hold
+\begin{thm}\label{main-bootstrap-invariance-theorem}
+Suppose that the conditions of Theorem~\ref{main-bootstrap-clt} hold
 and let $\dist$ be any distance function that metricizes weak
@@
 used to approximate the distribution of partial sums.
-Note that Theorem~\ref{T2} imposes
+Note that Theorem~\ref{main-bootstrap-invariance-theorem} imposes
 stronger assumptions for the original process
@@
 
-\subsection*{Proof of Theorem~\ref{T1}}
+\subsection*{Proof of Theorem~\ref{main-bootstrap-clt}}
 {%
@@
 $\sigma_n^{*2}$ is uniformly a.s.\ positive and holds by
-Lemma~\ref{L3}) and the following
+Lemma~\ref{bootstrap-variance-convergence-lemma}) and the following
 two conditions hold for all positive $\epsilon$:
@@
 is a uniformly-integrable martingale difference array
-by Lemma~\ref{L5}
+by Lemma~\ref{bootstrapped-zsq-uniform-integrability-lemma}
 and satisfies the \lln\ (e.g., \citealp{Dav:94}, Theorem 19.7). So
@@
 conditions (and does not depend on $n$ or $m$) is a consequence of
-Lemma~\ref{L5},
+Lemma~\ref{bootstrapped-zsq-uniform-integrability-lemma},
 Equation~\eqref{eq:30}. Since $J_n$ and $M_{nj}$ are both $\Ms$-measureable
@@
 monotonicity of $B$. And convergence in probability holds by
-Lemma~\ref{L1}, completing the proof
+Lemma~\ref{block-length-convergence-lemma}, completing the proof
 of~\eqref{eq:19}. The Dominated Convergence Theorem and~(\ref{eq:18})
@@
 (Also see
-Lemma~\ref{L2}.)
-
-Lemma~\ref{L3} implies that
+Lemma~\ref{equivalent-convergence-from-lie-lemma}.)
+
+Lemma~\ref{bootstrap-variance-convergence-lemma} implies that
 $\sigma_n^{*2}$ and $\hat\sigma_n^{*2}$ both converge to $\sigma^2$ in
@@
 for any finite $k$. Since $k$ is arbitrary,~\eqref{eq:37} holds. Since
-Theorem~\ref{T1}'s assumptions ensure that the
+Theorem~\ref{main-bootstrap-clt}'s assumptions ensure that the
 original array obeys the \clt,~\eqref{eq:36} holds \citep[Theorem
@@
 
-\subsection*{Proof of Theorem~\ref{T2}}
+\subsection*{Proof of Theorem~\ref{main-bootstrap-invariance-theorem}}
 \newcommand{\gn}{{\lfloor \gamma n \rfloor}}
@@
 Theorem~3.1 of \cite{JoD:00b} establishes the result for the partial
-sums of the original process.  Theorem~\ref{T1}
+sums of the original process.  Theorem~\ref{main-bootstrap-clt}
 implies that, for any fixed $\gamma$, $W_n^{*}(\gamma)$ is
@@
 can assume that $\sigma^2 = 1$ without loss of generality. Moreover,
-Lemma~\ref{L2} shows that it is
+Lemma~\ref{equivalent-convergence-from-lie-lemma} shows that it is
 sufficient to prove unconditional convergence, so we will establish
@@
 for some constant $C$ by
-Lemma~\ref{L5}. This term
-converges to zero by Lemma~\ref{L1}.
+Lemma~\ref{bootstrapped-zsq-uniform-integrability-lemma}. This term
+converges to zero by Lemma~\ref{block-length-convergence-lemma}.
 
@@
 \end{align*}
-Lemma~\ref{L5} implies that
+Lemma~\ref{bootstrapped-zsq-uniform-integrability-lemma} implies that
 \begin{equation*}
@@
 is uniformly integrable, so an argument similar to that used in the
-proof of Theorem~\ref{T1} shows that there exists a
+proof of Theorem~\ref{main-bootstrap-clt} shows that there exists a
 finite and monotone function $B$ such that $B(x) \to 0$ as
@@
 
-\begin{lem}\label{L1}
+\begin{lem}\label{block-length-convergence-lemma}
   Suppose that $M_{n1}, M_{n2},\dots$ are i.i.d.\ geometric random
@@
   $\epsilon$, and
-  \item $\sum_{i=1}^{J_n} M_{ni}^2 = O_p(n/p_n)$.
+  \item $\sum_{i=1}^{J_n} M_{ni}^2 / n^2 \to^p 0$.
   \end{enumerate}
@@
 
-\begin{proof}[Proof of Lemma~\ref{L1}]
+\begin{proof}[Proof of Lemma~\ref{block-length-convergence-lemma}]
   To prove part 1, observe that, for any increasing positive sequence
@@
   The proof of part 4 is the same as part 2, making the obvious
-  substitutions.
-  Using the same argument as in part 2 of this Lemma, it suffices to
-  prove that
-  $\sum\nolimits_{i=1}^{\lfloor C n p_n \rfloor} M_{ni}^2 =
-  O_p(n/p_n)$ where $C$ is an arbitrary constant greater than 1.  The
-  LLN implies that
-  \begin{equation*}
-    \tfrac{1}{C n p_n} \sum\nolimits_{i=1}^{\lfloor C n p_n \rfloor}
-    M_{ni}^2 = \tfrac{2 - p_n}{p_n^2} + o_p(\tfrac{2 - p_n}{p_n^2})
-  \end{equation*}
-  and the result follows immediately.
+  substitutions. Part 5 holds because $\sum_{i=1}^{J_n} M_{ni}^2/n^2
+  \leq \max_{i=1,\dots,J_n} M_{ni}/n$ which converges to zero in
+  probability by part 2.
 \end{proof}
 
-\begin{lem}\label{L2}
+\begin{lem}\label{equivalent-convergence-from-lie-lemma}
   If $\{A_n\}$ is a sequence of events in $\Omega$ then the following
@@
 
-\begin{lem}\label{L3}
-Under the conditions of Theorem~\ref{T1},
+\begin{lem}\label{bootstrap-variance-convergence-lemma}
+Under the conditions of Theorem~\ref{main-bootstrap-clt},
 \begin{gather}
@@
   M_{nj})$ is a uniformly integrable martingale difference array, by
-  Lemma~\ref{L5}, and
+  Lemma~\ref{bootstrapped-zsq-uniform-integrability-lemma}, and
   satisfies the \lln. (See~\citealp{Dav:94}, Theorem 19.7.)
@@
   after several applications of the Cauchy-Schwarz
-  inequality. Lemma~\ref{L4}, along with~\eqref{eq:17}
+  inequality. Lemma~\ref{lln-for-real-zsq}, along with~\eqref{eq:17}
   and~\eqref{eq:25}, implies that $\sum_j Z_{nj}^{*2} = O_p(1)$;
@@
   holds in $L_1$ as well and
-  Lemma~\ref{L2} then implies that
+  Lemma~\ref{equivalent-convergence-from-lie-lemma} then implies that
   the first term in \eqref{eq:38} converges to zero in probability.
-  Lemma~\ref{L4} proves that the second and third
+  Lemma~\ref{lln-for-real-zsq} proves that the second and third
   summation converge to zero in probability.
@@
   \end{equation}
-  which holds by Lemma~\ref{L1} and
+  which holds by Lemma~\ref{block-length-convergence-lemma} and
   assumption.
@@
 
-\begin{lem}\label{L4}
-  If the conditions of Theorem~\ref{T1} hold then
+\begin{lem}\label{lln-for-real-zsq}
+  If the conditions of Theorem~\ref{main-bootstrap-clt} hold then
   \begin{gather}
@@
   almost surely.
-  By Lemma~\ref{L6} (Equation~\ref{eq:32}), for
+  By Lemma~\ref{dejong-restatement-lemma} (Equation~\ref{eq:32}), for
   any $\delta > 0$ there exist positive $C$ and $\epsilon$ such that
@@
   for large enough $n$, which converges to $2 \delta$ by
-  Lemma~\ref{L1}.
-  Lemma~\ref{L7} ensures that there
+  Lemma~\ref{block-length-convergence-lemma}.
+  Lemma~\ref{zsq-uniform-integrability-lemma} ensures that there
   exists a value $C$ (possibly different from the value above) such
@@
   for large enough $n$,%
-\footnote{Lemma~\ref{L6}
-  and~\ref{L7} are stated for the
+\footnote{Lemma~\ref{dejong-restatement-lemma}
+  and~\ref{zsq-uniform-integrability-lemma} are stated for the
   unconditional expectation, which may cause some confusion here. Note
@@
   both of which converge to zero in $L_1$ as $n \to \infty$ by
-  Lemma~\ref{L1}.  These three convergence
+  Lemma~\ref{block-length-convergence-lemma}.  These three convergence
   results imply that the \allcaps{rhs} of (\ref{eq:29}) converges to
@@
   which is a direct implication of
-  Lemma~\ref{L6}.%
+  Lemma~\ref{dejong-restatement-lemma}.%
   \footnote{The discussion in Footnote~\ref{f:1} applies here as well.}
@@
 
-\begin{lem}\label{L5}
-  Under the conditions of Theorem~\ref{T1},
+\begin{lem}\label{bootstrapped-zsq-uniform-integrability-lemma}
+  Under the conditions of Theorem~\ref{main-bootstrap-clt},
   \begin{multline}\label{eq:35}
@@
   (\citealp{Dav:94}, 12.9.)
-  Lemma~\ref{L7} ensures uniform integrability of
+  Lemma~\ref{zsq-uniform-integrability-lemma} ensures uniform integrability of
   $\max_{m=1,\dots,m'} Z_n'(\tau, m)^2 n/m'$, so there exists an
@@
 
-\begin{lem}\label{L6}
+\begin{lem}\label{dejong-restatement-lemma}
 \newcommand{\isum}{\sum_{i=0}^{\lfloor n/m \rfloor - 1}}
-  Suppose the conditions of Theorem~\ref{T1} hold.
+  Suppose the conditions of Theorem~\ref{main-bootstrap-clt} hold.
   For any positive $\delta$, there exist positive and finite constants
@@
 
-\begin{lem}\label{L7}
+\begin{lem}\label{zsq-uniform-integrability-lemma}
 \newcommand{\uiterm}{\max_{m \in 1,\dots,m'} \Big(
@@
 \citet{Dav:94}. The same comment that follows
-Lemma~\ref{L6} applies here as well: the bounds
+Lemma~\ref{dejong-restatement-lemma} applies here as well: the bounds
 apply equally well to $\Em$.

### 2016-06-10 Paper.tex
[#26] Relabel lemmas and theorems in LaTeX source
Closes #26.

--- 2016-06-09 Paper.tex
@@
   The proof of part 4 is the same as part 2, making the obvious
-  substitutions.
-  Using the same argument as in part 2 of this Lemma, it suffices to
-  prove that
-  $\sum\nolimits_{i=1}^{\lfloor C n p_n \rfloor} M_{ni}^2 =
-  O_p(n/p_n)$ where $C$ is an arbitrary constant greater than 1.  The
-  LLN implies that
-  \begin{equation*}
-    \tfrac{1}{C n p_n} \sum\nolimits_{i=1}^{\lfloor C n p_n \rfloor}
-    M_{ni}^2 = \tfrac{2 - p_n}{p_n^2} + o_p(\tfrac{2 - p_n}{p_n^2})
-  \end{equation*}
-  and the result follows immediately.
+  substitutions. Part 5 holds because $\sum_{i=1}^{J_n} M_{ni}^2/n^2
+  \leq \max_{i=1,\dots,J_n} M_{ni}/n$ which converges to zero in
+  probability by part 2.
 \end{proof}

### 2016-06-11 subs/ETr3/reply_3.tex
[#18] Draft response to referee 3 re: heterogeneous means

@@
 
+Thank you for clarifying this. I have added new material that explains
+when these assumptions are satisfied when there is a single break in
+the mean of the stochastic process. Specifically, it explains how the
+break size and break timing can affect whether the assumptions
+hold. This section starts half-way through page 4 and is a bit more
+than half a page long.
+
+Working through this example convinced me that the original assumption
+on the means was too restrictive, so I have also relaxed the
+assumption from $\sum_t (\mu_{nt} - \bar \mu_n)^2) \to 0$ to
+$\sum_t (\mu_{nt} - \bar \mu_n)^2) = o(n p_n^2)$ (using notation for
+the stationary bootstrap; the assumption has been relaxed for all
+three of the block bootstraps considered).  This change does not
+affect the mathematical proofs very much: I have added a very simple
+Lemma 3 that shows that the contribution of the $\mu_{nt}$'s to the
+second moment of $\bar X^*$ remains asymptotically negligible under
+this assumption and strengthened one of the components of Lemma 1.
+
+The proofs of Lemmas 4 and 6 (which were labeled Lemmas 3 and 5 in the
+last version of the paper) have to be changed a little as well to
+reflect the new assumption on $\mu_{nt}$. The previous version of
+Lemma 6 established that (suitably normalized) $Z_i^2$s are uniformly
+integrable and used that as an intermediate result to show that the
+$Z_i^{*2}$s are also u.i. under the right normalization. The new
+version skips that intermediate step (the family of $Z_i^2s$ are no
+longer u.i.) but uses components of the original proof to show that
+the $Z_i^{*2}$s are u.i. directly. Changing the proof in this way
+essentially amounts to rearranging the elements of the original proof,
+and invoking the new Lemma 3.
+
+To help make the changes as clear as possible, I have uploaded a
+pdf based on `latexdiff' that highlights the differences in the
+two versions as a supplemental document.
+
 You also wrote,
@@
 \end{document}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2016-06-16 Paper.tex
[#18] Make small text changes to reflect new assumption on means

@@
 the expected block length be $o(n^{1/2})$ to the original papers'
-requirement that it be $o(n)$.
+requirement that it be $o(n)$, although their stronger assumption is
+necessary for the bootstrap to be consistent under some forms of
+heterogeneity.
 
@@
   argument.}%
-\footnote{Lemmas~\ref{L3} and
-  \ref{L5} are particularly
+\footnote{Lemmas~\ref{L4} and
+  \ref{L6} are particularly
   strong demonstrations of this argument.} %
@@
 $\sigma_n^{*2}$ is uniformly a.s.\ positive and holds by
-Lemma~\ref{L3}) and the following
+Lemma~\ref{L4}) and the following
 two conditions hold for all positive $\epsilon$:
@@
 is a uniformly-integrable martingale difference array
-by Lemma~\ref{L5}
+by Lemma~\ref{L6}
 and satisfies the \lln\ (e.g., \citealp{Dav:94}, Theorem 19.7). So
@@
 conditions (and does not depend on $n$ or $m$) is a consequence of
-Lemma~\ref{L5},
-Equation~\eqref{eq:30}. Since $J_n$ and $M_{nj}$ are both $\Ms$-measureable
+Lemma~\ref{L6},
+Equation~\eqref{eq:30}. Since $J_n$ and $M_{nj}$ are both $\Ms$-measurable
 and independent of the $u_{nj}$'s and $X_{nt}$'s,~\eqref{eq:5} implies that
@@
 
-Lemma~\ref{L3} implies that
+Lemma~\ref{L4} implies that
 $\sigma_n^{*2}$ and $\hat\sigma_n^{*2}$ both converge to $\sigma^2$ in
@@
 for any finite $k$. Since $k$ is arbitrary,~\eqref{eq:37} holds. Since
-Theorem~\ref{T1}'s assumptions ensure that the
-original array obeys the \clt,~\eqref{eq:36} holds \citep[Theorem
-2]{Jon:97}.  A similar argument applies to the asymptotic distribution
-of $\sqrt{n}(\bar X_n^* - \bar X_n) / \hat\sigma_n^*$, completing the
+Theorem~\ref{T1}'s assumptions ensure that the original array obeys
+the \clt,~\eqref{eq:36} holds \citep[Theorem 2]{Jon:97}.  A similar
+argument applies to the asymptotic distribution of
+$\sqrt{n}(\bar X_n^* - \bar X_n) / \hat\sigma_n^*$, completing the
 proof.\qed }
@@
 for some constant $C$ by
-Lemma~\ref{L5}. This term
+Lemma~\ref{L6}. This term
 converges to zero by Lemma~\ref{L1}.
@@
 \end{align*}
-Lemma~\ref{L5} implies that
+Lemma~\ref{L6} implies that
 \begin{equation*}
@@
   as well.
-
   The proof of part 4 is the same as part 2, making the obvious
-  substitutions. Part 5 holds because $\sum_{i=1}^{J_n} M_{ni}^2/n^2
-  \leq \max_{i=1,\dots,J_n} M_{ni}/n$ which converges to zero in
-  probability by part 2.
+  substitutions.
+
+  For part 5, write
+  \begin{equation}\label{eq:41}
+    \sum_{i=1}^{J_n} M_{ni}^2 =
+    \sum_{i=1}^{J_n} (M_{ni} - \tfrac{1}{p_n})^2
+    + \tfrac{2}{p_n} \sum_{i=1}^{J_n} (M_{ni} - \tfrac{1}{p_n})
+    + \tfrac{J_n}{p_n^2}
+  \end{equation}
+  so
+  \begin{equation*}
+    \E \Big( \sum_{i=1}^{J_n} M_{ni}^2 \Big)
+    = \E\Big( \sum_{i=1}^{J_n} (M_{ni} - \tfrac{1}{p_n})^2 \Big)
+    + \tfrac{2 n}{p_n} - \E \tfrac{J_n}{p_n^2}.
+  \end{equation*}
+  Since $J_n$ is a stopping time and $\sum_{i=1}^j (M_{ni} - 1/p_n)$
+  is a martingale, we have the equality \citep[Lemma 6]{CRT:65}
+  \begin{align*}
+    \E\Big( \sum_{i=1}^{J_n} (M_{ni} - \tfrac{1}{p_n})^2 \Big)
+    &= \E\Big( \sum_{i=1}^{J_n} \E((M_{ni} - \tfrac{1}{p_n})^2 \mid M_{n1},\dots,M_{n,i-1})\Big)\\
+    &= \tfrac{1 - p_n}{p_n^2} \E J_n.
+  \end{align*}
+  Then $\E J_n = (n-1) p_n + 1$, completing the proof.
 \end{proof}
@@
 \begin{lem}\label{L3}
+Under the conditions of Theorem~\ref{T1},
+\begin{equation}\label{eq:40}
+  \E \Big(\sum_{j=1}^{J_n} \Big( \sum_{t = K_{n,j-1}+1}^{K_{nj}}
+  (\mu_{nt}^{*} - \bar \mu_n)\Big)^2\Big) = o(n p_n)
+\end{equation}
+and $\bar \mu_n^{*} = \E^{*} \bar \mu_n^{*} + o_{L_2}(n^{-1/2})$.
+\end{lem}
+\begin{proof}
+  Since the blocks are independent and
+  $\E^{*} \bar\mu_n^{*} = \bar\mu_n$ under the stationary bootstrap,
+  the result on $\bar\mu_n^{*}$ follows from~\eqref{eq:40}. To
+  show~\eqref{eq:40}, observe that
+  \begin{align*}
+    \E \Big(\sum_{j=1}^{J_n} &\Big( \sum_{t= K_{n,j-1} +1}^{K_{nj}}
+    (\mu_{nt}^{*} - \bar \mu_n)\Big)^2\Big)= \\
+    &= \E\Big(\sum_{j=1}^{J_n}\sum_{s,t = K_{n,j-1}+1}^{K_{nj}}
+    \E \big((\mu_{ns}^{*} - \bar{\mu}_n)
+    (\mu_{nt}^{*} - \bar{\mu}_n) \mid \Ms \big)\Big)\\
+    &= \E\Big( \sum_{j=1}^{J_n}
+    \sum_{k,l = -n}^{n} \tfrac{1}{n} \sum_{\tau=0}^{n-1}
+    (\mu_{n,\tau+k} - \bar{\mu}_n) (\mu_{n,\tau+l} - \bar{\mu}_n) \;
+    1\{ \tau + k, \tau + l \in I_n(\tau, M_{nj})\}\Big)\\
+    &\leq \E\Big(\sum_{j=1}^{J_n}
+    \Big(\sum_{k = -n}^{n} \Big(\tfrac{1}{n} \sum_{\tau=0}^{n-1}
+    (\mu_{n,\tau+k} - \bar{\mu}_n)^2
+    1\{ \tau + k \in I_n(\tau, M_{nj})\}\Big)^{1/2}\Big)^{2}\Big)\\
+    &= \E\Big(\sum_{j=1}^{J_n}
+    M_{nj}^2 \Big\lvert \tfrac{1}{n} \sum_{\tau=0}^{n-1}
+    (\mu_{n,\tau} - \bar{\mu}_n)^2 \Big\lvert\Big)\\
+    &= o(n p_n).
+  \end{align*}
+  The first line follows from the LIE. The second exploits the
+  fact that the conditional expectation in the previous line
+  just averages over the block's starting period. The
+  inequality is an application of the Cauchy-Schwarz inequality.
+  The next line holds because the summation
+  \[
+    \sum_{\tau=0}^{n-1} (\mu_{n,\tau+k} - \bar{\mu}_n)^2
+    1\{ \tau + k \in I_n(\tau, M_{nj})\}
+  \]
+  is zero for all but $M_{nj}$ values of $k$ and is a nonzero constant
+  for those $k$. The last line holds by Lemma~\ref{L1} and assumption.
+\end{proof}
+
+\begin{lem}\label{L4}
 Under the conditions of Theorem~\ref{T1},
@@
   M_{nj})$ is a uniformly integrable martingale difference array, by
-  Lemma~\ref{L5}, and
+  Lemma~\ref{L6}, and
   satisfies the \lln. (See~\citealp{Dav:94}, Theorem 19.7.)
   For~\eqref{eq:26}, observe that
-  \begin{equation*}
-    \Big| \sum_{j=1}^{J_n} (Z_{nj}^{*2} - Z_{nj}^{\prime*2}) \Big| \leq
-    2 \Big(\sum_{j=1}^{J_n} Z_{nj}^{*2} \Big)^{1/2}
-    \Big(\tfrac{1}{n} \sum_{t=1}^n (\mu_{nt} - \bar X_n)^2\Big)^{1/2}
-    + \tfrac{1}{n} \sum_{t=1}^n (\mu_{nt} - \bar X_n)^2
-  \end{equation*}
-  after several applications of the Cauchy-Schwarz
-  inequality. Lemma~\ref{L4}, along with~\eqref{eq:17}
-  and~\eqref{eq:25}, implies that $\sum_j Z_{nj}^{*2} = O_p(1)$;
-  $(1/n) \sum_t (\mu_{nt} - \bar X)^2$ converges to zero in
-  probability by assumption on $\mu_{nt} - \bar\mu_n$ and because
-  $\bar X$ itself obeys the \lln.
+  \begin{multline*}
+    \Big| \sum_{j=1}^{J_n} (Z_{nj}^{*2} - Z_{nj}^{\prime*2}) \Big|
+    \leq 2 \Big(\sum_{j=1}^{J_n} Z_{nj}^{*2} \Big)^{1/2}
+    \Big(\tfrac{1}{n} \sum_{j=1}^{J_n} \Big( \sum_{t= K_{n,j-1} + 1}^{K_{nj}}
+    (\mu_{nt}^{*} - \bar X_n)\Big)^2 \Big)^{1/2} \\
+    + \tfrac{1}{n} \sum_{j=1}^{J_n} \Big( \sum_{t= K_{n,j-1} + 1}^{K_{nj}}
+    (\mu_{nt}^{*} - \bar X_n)\Big)^2
+  \end{multline*}
+  from the Cauchy-Schwarz inequality. Lemma~\ref{L5}, along
+  with~\eqref{eq:17} and~\eqref{eq:25}, implies that
+  $\sum_j Z_{nj}^{*2} = O_p(1)$. Lemma~\ref{L3} implies that
+  \[
+    \tfrac{1}{n} \sum_{j=1}^{J_n} \Big( \sum_{t= K_{n,j-1} + 1}^{K_{nj}}
+    (\mu_{nt}^{*} - \bar X_n)\Big)^2 \to^p 0
+  \]
+  since $\bar X$ itself obeys the \lln.
 
@@
   Uniform integrability ensures that the convergence in~(\ref{eq:25})
-  holds in $L_1$ as well and
-  Lemma~\ref{L2} then implies that
+  holds in $L_1$ and Lemma~\ref{L2} then implies that
   the first term in \eqref{eq:38} converges to zero in probability.
-  Lemma~\ref{L4} proves that the second and third
+  Lemma~\ref{L5} proves that the second and third
   summation converge to zero in probability.
@@
 
-\begin{lem}\label{L4}
+\begin{lem}\label{L5}
   If the conditions of Theorem~\ref{T1} hold then
@@
   almost surely.
-  By Lemma~\ref{L6} (Equation~\ref{eq:32}), for
+  By Lemma~\ref{L7} (Equation~\ref{eq:32}), for
   any $\delta > 0$ there exist positive $C$ and $\epsilon$ such that
@@
   Lemma~\ref{L1}.
-  Lemma~\ref{L7} ensures that there
+  Lemma~\ref{L8} ensures that there
   exists a value $C$ (possibly different from the value above) such
@@
   for large enough $n$,%
-\footnote{Lemma~\ref{L6}
-  and~\ref{L7} are stated for the
+\footnote{Lemma~\ref{L7}
+  and~\ref{L8} are stated for the
   unconditional expectation, which may cause some confusion here. Note
@@
   which is a direct implication of
-  Lemma~\ref{L6}.%
+  Lemma~\ref{L7}.%
   \footnote{The discussion in Footnote~\ref{f:1} applies here as well.}
@@
 
-\begin{lem}\label{L5}
+\begin{lem}\label{L6}
   Under the conditions of Theorem~\ref{T1},
-  \begin{multline}\label{eq:35}
-    \lim_{C \to \infty} \limsup_{n \to \infty} \sup_{m' = 1,\dots,n}
-    \E\Big(\Big(\sum_{\tau=0}^{n-1} \max_{m=1,\dots,m'} Z_n(\tau, m)^2 / m'\Big) \\
-    \times\ind\Big\{\sum_{\tau=0}^{n-1} \max_{m=1,\dots,m'} Z_n(\tau, m)^2 / m' > C\Big\}\Big) = 0.
-  \end{multline}
-  and
   \begin{multline}\label{eq:30}
@@
 \begin{proof}
-  For \eqref{eq:35}, take $\epsilon > 0$. The sum
-  \[
-  \sum_{\tau=0}^{n-1} \max_{m=1,\dots,m'} Z_n(\tau, m)^2 / m'
-  \]
-  is uniformly integrable if and only if it is uniformly $L_1$-bounded
-  and there exists an $\epsilon'$ such that
-  \[
-  \sup_{n, m'} \E\Big( \ind(A) \sum_{\tau=0}^{n-1} \max_{m=1,\dots,m'} Z_n(\tau, m)^2 / m' \Big)
-  < \epsilon
-  \]
-  for every event $A \in \Omega_n$ satisfying $\pr(A) < \epsilon'$.
-  (\citealp{Dav:94}, 12.9.)
-  Lemma~\ref{L7} ensures uniform integrability of
-  $\max_{m=1,\dots,m'} Z_n'(\tau, m)^2 n/m'$, so there exists an
-  $\epsilon'$ such that
-  \begin{equation*}
-    \sup_{n, m', \tau} \E\big( \ind(A) \max_{m=1,\dots,m'} Z_n'(\tau, m)^2 n / m' \big) \leq \epsilon / 9
-  \end{equation*}
-  for all $A \in \Omega_n$ with $\pr(A) \leq \epsilon'$. Then, writing
+  We will first show that, for every $\epsilon > 0$ and large enough
+  $n$, there exists an $\epsilon' > 0$ with the property that
+  \begin{equation}\label{eq:31}
+    \E \Big(\ind(A) \times \max_{m = 1,\dots,m'} Z^*_n(\tau, m)^2 n / m'\Big) < \epsilon
+  \end{equation}
+  for any event $A \in \Fs_n \equiv \sigma(X_{n1},\dots,X_{nn})$ with
+  $\pr(A) \leq \epsilon'$. Then we will show that this property
+  implies uniform integrability.\footnote{%
+    The novelty in this part of the proof is the measurability
+    requirement. The sigma-field $\Fs_n$ intentionally excludes the
+    random variables that define the bootstrap (block length and block
+    start periods) and any $A \in \Fs_n$ is independent of those
+    variables, so $Z_n^{*}(\tau, m)^2$ is not $\Fs_n$-measurable. If
+    $\Fs_n$ were enlarged to include those variables then uniform
+    integrability would be an immediate consequence and would not need
+    to be shown separately. See \citet[Theorem 12.9]{Dav:94}.} %
+
+  Take an arbitrary $\delta > 0$ and a value of $\delta' > 0$
+  so that
+  \begin{equation}\label{eq:35}
+    \sup_{m'=1,\dots,n} \E \Big(\ind(A) \max_{m = 1,\dots,m'}
+    Z_n'(\tau, m)^2 n / m' \Big) < \delta
+  \end{equation}
+  for any $A \in \Fs_n$ with $\pr(A) \leq \delta'$; the existence
+  of $\delta'$ is ensured by Lemma~\ref{L8}. For any $x$,
+  define $J(x)$ to be the block index such that $K_{n,J(x) - 1} < x
+  \leq K_{n,J(x)}$. For any $m$, we can decompose $Z_n^{*}(\tau, m)$
+  into a summation of conditionally independent blocks
+  \begin{equation*}
+  Z^{*}_n(\tau, m) = Z_n^*(\tau, K_{n,J(\tau)} - \tau) +
+  \sum_{j=J(\tau)+1}^{J(\tau + m)-1} Z_{nj}^* + Z_n^*(K_{n,J(\tau+m)-1}, m - K_{n,J(\tau + m)-1}),
+  \end{equation*}
+  giving
+  \begin{align}
+  \E  \Big(&\ind(A) \times \max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m'\Big)
+  \notag \\
+  &\leq 3 \E\Big[ \Em^{*} \Big[\ind(A) \tfrac{n}{m'}\max_{m = 1,\dots, m'}
+  \Big(Z_n^*(\tau, K_{n,J(\tau)} - \tau) + \sum_{j=J(\tau)+1}^{J(\tau + m)-1} Z_{nj}^*\Big)^2\Big]
+  \notag \\
+  &\quad + 3 \Em^{*} \big[\ind(A) \tfrac{n}{m'}
+  \max_{m=1,\dots,m'} Z_n^*(K_{n,J(\tau+m)-1}, m - K_{n,J(\tau + m)-1})^2 \big]\Big]\label{eq:6}
+  \end{align}
+  almost surely.
+
+  Since $Z_{nj}^*$ is a martingale difference array, Doob's maximal
+  inequality for martingales \citep[see][Theorem 15.15, for
+  example]{Dav:94} along with the construction of $Z_{nj}^{*}$ gives
+  a bound for the first term on the \allcaps{RHS} of~\eqref{eq:6},
+  \begin{align*}
+  \E \Em^* & \Big[\ind(A) \tfrac{n}{m'}\max_{m = 1,\dots, m'}
+  \Big(Z_n^*(\tau, K_{n,J(\tau)} - \tau)
+  + \sum_{j=J(\tau)+1}^{J(\tau + m)-1} Z_{nj}^*\Big)^2\Big] \\
+  &\leq \tfrac{1}{m'} \sum_{u = 0}^{n-1} \E \Big[\Em \big[
+  \ind(A) Z_n(u, K_{n,J(\tau)} - \tau)^2\big] +
+  \sum_{j=J(\tau)+1}^{J(\tau + m')-1} \Em \big[\ind(A) Z_n(u, M_{nj})^2]\Big] \\
+  &\leq \tfrac{3}{m'} \sum_{u = 0}^{n-1} \E\Big[\Em\big[
+  \ind(A) Z'_n(u, K_{n,J(\tau)} - \tau)^2\big]
+  + \tfrac{1}{n} \Pm[A] \Big(\sum_{t \in I_n(u, K_{n,J(\tau)} - \tau)}
+  (\mu_{nt} - \bar \mu_n)\Big)^2 \\
+  & \quad+ \sum_{j=J(\tau)+1}^{J(\tau + m')-1}
+  \Em \big[\ind(A) Z_n'(u, M_{nj})^2]
+  + \tfrac{1}{n} \Pm[A]
+  \sum_{j=J(\tau)+1}^{J(\tau + m')-1}\Big( \sum_{t \in I_n(u,M_{nj})}
+  (\mu_{nt} - \bar{\mu}_n) \Big)^2 \\
+  & \quad+ \Em\big( \ind(A) Z_n'(u, n)^2 \big)
+  \sum_{j=J(\tau)}^{J(\tau+m')-1} M_{nj}^2/n^2 \Big] \\
+  &\leq (3\delta/m') \E (K_{n,J(\tau+m')-1} - \tau)
+    + 3\delta \E\Big(\sum_{j=J(\tau)}^{J(\tau+m')-1} M_{nj}^2/n^2 \Big) \\
+  &\quad+ 3(\delta'/n) \E\Big( \Big(\sum_{t \in I_n(u, K_{n,J(\tau)} - \tau)}
+  (\mu_{nt} - \bar \mu_n)\Big)^2 +
+  \sum_{j=J(\tau)+1}^{J(\tau + m')-1}\Big( \sum_{t \in I_n(u,M_{nj})}
+  (\mu_{nt} - \bar{\mu}_n) \Big)^2 \Big) \\
+  & < C_1 \delta + C_2 p_n \delta'
+  \end{align*}
+  for some finite constants $C_1$ and $C_2$.
+  The second inequality comes from writing
   \begin{align*}
@@
 
-\begin{lem}\label{L6}
+\begin{lem}\label{L7}
 \newcommand{\isum}{\sum_{i=0}^{\lfloor n/m \rfloor - 1}}
@@
 
-\begin{lem}\label{L7}
+\begin{lem}\label{L8}
 \newcommand{\uiterm}{\max_{m \in 1,\dots,m'} \Big(
@@
 \citet{Dav:94}. The same comment that follows
-Lemma~\ref{L6} applies here as well: the bounds
+Lemma~\ref{L7} applies here as well: the bounds
 apply equally well to $\Em$.

### 2016-06-17 Paper.tex
[#20] Tweak notation for centered bootstrap BM
The referee suggested using \bar{\mu}^*_n instead of using no bar.
This commit makes the change.
[#27] Tweak wording in paper

@@
 $(\mu_{nt} - \bar\mu_n)^2$, is the same as \citepos{GoW:02} and
-\citepos{GoJ:03} when the expected block length is $o(\sqrt{n})$. When
-the blocks are longer than $o(\sqrt{n})$, a case that \citet{GoW:02}
+\citepos{GoJ:03} under their additional requirement that the
+expected block length be $o(\sqrt{n})$. When
+the blocks are larger than $o(\sqrt{n})$, a case that \citet{GoW:02}
 and \citet{GoJ:03} do not consider, the dispersion must be smaller.
@@
 consider a simple example: a stochastic process with a single break of
-size $\Delta_n$ at time $T_n$,
+size $\Delta_n$ at time $T_n$, implying
 \begin{equation*}
@@
 $T_n = \pi n$, then $D_n \approx \Delta c (1 - c)$ and Assumption 2
-again holds as long as $M_n = o(\sqrt{n})$. Consequently, block sizes
-of length $o(\sqrt{n})$ ensure that the conditions of
-Theorem~\ref{T1}'s when there is a moderate amount of
+again holds as long as $M_n = o(\sqrt{n})$. Consequently, using block sizes
+of length $o(\sqrt{n})$ ensures that Theorem 1's assumptions on the
+dispersion of the $\mu_{nt}$ hold when there is a moderate amount of
 heterogeneity---either because the sample is chosen to lie after a
@@
 $\sum_t (\mu_{nt} - \bar \mu_n)^2$ grows even slower, then larger
-block lengths can also satisfy Assumption 2.
+block lengths can also satisfy this condition.
 
@@
 \sum_{t=1}^{\lfloor \gamma n \rfloor}
-(X^*_{nt} - \mu_n^{*}).
+(X^*_{nt} - \bar\mu_n^{*}).
 \end{align*}

### 2016-09-14 Paper.tex
[#27] Tweak centering term in Brownian Motion
Related to issue #20, I think it makes sense to center on a different
variable. This commit changes the centering term and revises my letter
to the referee.
[#27] Make small changes to wording in main paper

@@
 the expected block length be $o(n^{1/2})$ to the original papers'
-requirement that it be $o(n)$, although their stronger assumption is
-necessary for the bootstrap to be consistent under some forms of
-heterogeneity.
+requirement that it be $o(n)$, although, as we will show, their
+stronger assumption is necessary for the bootstrap to be consistent
+under some forms of heterogeneity.
 
@@
 the blocks are larger than $o(\sqrt{n})$, a case that \citet{GoW:02}
-and \citet{GoJ:03} do not consider, the dispersion must be smaller.
+and \citet{GoJ:03} do not consider, the dispersion must be smaller
+than they require.
 To see these implications of this assumption, it is helpful to
 consider a simple example: a stochastic process with a single break of
-size $\Delta_n$ at time $T_n$, implying
+size $\Delta_n$ at time $T_n$:
 \begin{equation*}
@@
   \mu & \text{if } t \leq T_n \\
-  \mu + \Delta_n & \text{otherwise}
+  \mu + \Delta_n & \text{otherwise}.
 \end{cases}
@@
 Theorem~\ref{T1}'s Assumption 2 holds if $D_n = o(n / M_n^2)$, and for
-the Stationary Bootstrap the same relationship must hold for the
-expected block length. If $\Delta_n = \Delta_0$ and $T_n = \pi n$ for
+the same relationship must hold for the expected block length for the
+Stationary Bootstrap. If $\Delta_n = \Delta_0$ and $T_n = \pi n$ for
 some constants $\Delta_0$ and $\pi$ and for all $n$, then
@@
 
-We can also use the same DGP to produce scenarios where
-Theorem~\ref{T1}'s Assumption~2 is satisfied.  The first mimics a
-setting where the break is estimated and the bootstrap is applied to
-the post-break sample, but a small number of pre-break observations
-are accidentally included in the data set as well. Here
-$\Delta_n = \Delta_0$ and $T_n = T_0$ for some finite $T_0$. In this
-case, Assumption 2 holds hold as long as $M_n = o(\sqrt{n})$.
-Similarly, if the break is moderate with unknown timing in the sense
-of \citet{ElM:07}, so $\Delta_n = \Delta / \sqrt{n}$ and
-$T_n = \pi n$, then $D_n \approx \Delta c (1 - c)$ and Assumption 2
-again holds as long as $M_n = o(\sqrt{n})$. Consequently, using block sizes
-of length $o(\sqrt{n})$ ensures that Theorem 1's assumptions on the
-dispersion of the $\mu_{nt}$ hold when there is a moderate amount of
+To see when Theorem~\ref{T1}'s Assumption~2 is satisfied, consider two
+other parametrizations of this DGP. First, let $\Delta_n = \Delta_0$
+and $T_n = T_0$ for some finite $T_0$. This mimics a setting where a
+researcher intends to apply the bootstrap to a post-break sample, but
+mistakenly includes a small number of pre-break observations as
+well. In this case, Assumption 2 holds hold as long as
+$M_n = o(\sqrt{n})$.  Similarly, suppose
+$\Delta_n = \Delta / \sqrt{n}$ and $T_n = \pi n$, which mimics a
+setting with a moderate break with unknown timing.  Then
+$D_n \approx \Delta c (1 - c)$ and Assumption 2 again holds as long as
+$M_n = o(\sqrt{n})$. Consequently, using block sizes of length
+$o(\sqrt{n})$ ensures that Theorem 1's assumptions on the dispersion
+of the $\mu_{nt}$ hold when there is a moderate amount of
 heterogeneity---either because the sample is chosen to lie after a
@@
 \sum_{t=1}^{\lfloor \gamma n \rfloor}
-(X^*_{nt} - \bar\mu_n^{*}).
+(X^*_{nt} - \E^* \bar X_n^*).
 \end{align*}

### 2016-09-14 Paper.tex
[#28] Tweak intro to proof of theorem 1

@@
 \newcommand{\Zsum}{\sum_{j=1}^{J_n} \Zb / \sigma_n}
-Observe that
-\[
-\sqrt{n}(\bar X_{n}^{*} -  \E^{*} \bar X_n^{*})
-= \sqrt{n}((\bar{X}_{n}^{*} - \bar{\mu}_{n}^{*}) - \E^{*} (\bar X_n^{*} - \bar{\mu}_n^{*}))
-+ \sqrt{n}(\bar{\mu}_{n}^{*} - \E^{*} \bar{\mu}_n^{*}).
-\]
-Lemma~\ref{L3} implies that the last term is $o_{L_2}(1)$, so we can assume that
-$\mu_{nt}$ is constant in $t$ for each $n$ for the proof of normality. Convergence
-in probability of the bootstrap variance and the bootstrap variance estimator
-holds by Lemma~\ref{L4}.
 
@@
 conditions (and does not depend on $n$ or $m$) is a consequence of
-Lemma~\ref{L6},
-Equation~\eqref{eq:30}. Since $J_n$ and $M_{nj}$ are both $\Ms$-measurable
+Lemma~\ref{L6}. Since $J_n$ and $M_{nj}$ are both $\Ms$-measurable
 and independent of the $u_{nj}$'s and $X_{nt}$'s,~\eqref{eq:5} implies that
@@
   \end{align*}
-  Then $\E J_n = (n-1) p_n + 1$, completing the proof.
+  Finally, $\E J_n = (n-1) p_n + 1$, completing the proof.
 \end{proof}
@@
 \begin{proof}
-  Since the blocks are independent and
-  $\E^{*} \bar\mu_n^{*} = \bar\mu_n$ under the stationary bootstrap,
-  the result on $\bar\mu_n^{*}$ follows from~\eqref{eq:40}. To
-  show~\eqref{eq:40}, observe that
+  The second result, on $\bar\mu_n^*$ is an immediate implication of
+  Equation~\eqref{eq:40}. To show~\eqref{eq:40}, observe that
   \begin{align*}
@@
     (\mu_{nt}^{*} - \bar \mu_n)\Big)^2\Big)= \\
-    &= \E\Big(\sum_{j=1}^{J_n}\sum_{s,t = K_{n,j-1}+1}^{K_{nj}}
+    &= \E\Big(\sum_{j=1}^{J_n} \big\lvert \sum_{s,t = K_{n,j-1}+1}^{K_{nj}}
     \E \big((\mu_{ns}^{*} - \bar{\mu}_n)
-    (\mu_{nt}^{*} - \bar{\mu}_n) \mid \Ms \big)\Big)\\
-    &= \E\Big( \sum_{j=1}^{J_n}
-    \sum_{k,l = -n}^{n} \tfrac{1}{n} \sum_{\tau=0}^{n-1}
+    (\mu_{nt}^{*} - \bar{\mu}_n) \mid \Ms \big) \big\rvert \Big)\\
+    &\leq \E\Big( \sum_{j=1}^{J_n}
+    \sum_{k,l = -n}^{n} \tfrac{1}{n} \sum_{\tau=0}^{n-1} \big\lvert
     (\mu_{n,\tau+k} - \bar{\mu}_n) (\mu_{n,\tau+l} - \bar{\mu}_n) \;
-    1\{ \tau + k, \tau + l \in I_n(\tau, M_{nj})\}\Big)\\
-    &\leq \E\Big(\sum_{j=1}^{J_n}
-    \Big(\sum_{k = -n}^{n} \Big(\tfrac{1}{n} \sum_{\tau=0}^{n-1}
+    1\{ \tau + k, \tau + l \in I_n(\tau, M_{nj})\} \big\rvert \Big)\\
+    &\leq \E\Big(\sum_{j=1}^{J_n} \Big[
+    \sum_{k = -n}^{n} \big(\tfrac{1}{n} \sum_{\tau=0}^{n-1}
     (\mu_{n,\tau+k} - \bar{\mu}_n)^2
-    1\{ \tau + k \in I_n(\tau, M_{nj})\}\Big)^{1/2}\Big)^{2}\Big)\\
+    1\{ \tau + k \in I_n(\tau, M_{nj})\}\big)^{1/2}\Big]^{2}\Big)\\
     &= \E\Big(\sum_{j=1}^{J_n}
@@
   \end{align*}
-  The first line follows from the LIE. The second exploits the
-  fact that the conditional expectation in the previous line
-  just averages over the block's starting period. The
-  inequality is an application of the Cauchy-Schwarz inequality.
-  The next line holds because the summation
+  The first equality follows from the LIE. The first inequality
+  exploits the fact that the conditional expectation in the previous
+  expression averages over the block's starting period but treats
+  every other random variable as contstant. (The argument of the
+  indicator function and the indices of the summations are
+  deliberately chosen to accomodate blocks that include observations
+  from both the beginning and the end of the series.) The second
+  inequality is an application of the Cauchy-Schwarz inequality to the
+  inner-most summation. The next equality holds because the
+  summation
   \[
@@
   For~\eqref{eq:26}, observe that
-  \begin{multline*}
+  \begin{align*}
     \Big| \sum_{j=1}^{J_n} (Z_{nj}^{*2} - Z_{nj}^{\prime*2}) \Big|
-    \leq 2 \Big(\sum_{j=1}^{J_n} Z_{nj}^{*2} \Big)^{1/2}
+    &= \Big| \sum_{j=1}^{J_n} \big(Z_{nj}^{*} - \big[Z_{nj}^{*} + \tfrac{1}{\sqrt{n}} \sum_{t=K_{n,j-1}+1}^{K_{nj}} (\bar X_n - \mu_{nt}^*)\big]^2\big) \Big| \\
+    &\leq 2 \Big(\sum_{j=1}^{J_n} Z_{nj}^{*2} \Big)^{1/2}
     \Big(\tfrac{1}{n} \sum_{j=1}^{J_n} \Big( \sum_{t= K_{n,j-1} + 1}^{K_{nj}}
-    (\mu_{nt}^{*} - \bar X_n)\Big)^2 \Big)^{1/2} \\
-    + \tfrac{1}{n} \sum_{j=1}^{J_n} \Big( \sum_{t= K_{n,j-1} + 1}^{K_{nj}}
+    (\mu_{nt}^{*} - \bar X_n)\Big)^2 \Big)^{1/2}\\
+    &\quad + \tfrac{1}{n} \sum_{j=1}^{J_n} \Big( \sum_{t= K_{n,j-1} + 1}^{K_{nj}}
     (\mu_{nt}^{*} - \bar X_n)\Big)^2
-  \end{multline*}
+  \end{align*}
   from the Cauchy-Schwarz inequality. Lemma~\ref{L5}, along
@@
     $\Fs_n$ were enlarged to include those variables then uniform
-    integrability would be an immediate consequence and would not need
-    to be shown separately. See \citet[Theorem 12.9]{Dav:94}.} %
+    integrability would be an immediate consequence of~\eqref{eq:31}
+    and would not need to be shown separately. See \citet[Theorem
+    12.9]{Dav:94}.} %
 

### 2016-09-19 Paper.tex
[#27] Make minor change in Lemma 1 proof
[#27] Add details to proof of Lemma 3

--- 2016-09-14 Paper.tex
@@
 \newcommand{\Zsum}{\sum_{j=1}^{J_n} \Zb / \sigma_n}
+Observe that
+\[
+\sqrt{n}(\bar X_{n}^{*} -  \E^{*} \bar X_n^{*})
+= \sqrt{n}((\bar{X}_{n}^{*} - \bar{\mu}_{n}^{*}) - \E^{*} (\bar X_n^{*} - \bar{\mu}_n^{*}))
++ \sqrt{n}(\bar{\mu}_{n}^{*} - \E^{*} \bar{\mu}_n^{*}).
+\]
+Lemma~\ref{L3} implies that the last term is $o_{L_2}(1)$, so we can assume that
+$\mu_{nt}$ is constant in $t$ for each $n$ for the proof of normality. Convergence
+in probability of the bootstrap variance and the bootstrap variance estimator
+holds by Lemma~\ref{L4}.
 
@@
   For~\eqref{eq:26}, observe that
-  \begin{align*}
+  \begin{multline*}
     \Big| \sum_{j=1}^{J_n} (Z_{nj}^{*2} - Z_{nj}^{\prime*2}) \Big|
-    &= \Big| \sum_{j=1}^{J_n} \big(Z_{nj}^{*} - \big[Z_{nj}^{*} + \tfrac{1}{\sqrt{n}} \sum_{t=K_{n,j-1}+1}^{K_{nj}} (\bar X_n - \mu_{nt}^*)\big]^2\big) \Big| \\
-    &\leq 2 \Big(\sum_{j=1}^{J_n} Z_{nj}^{*2} \Big)^{1/2}
+    \leq 2 \Big(\sum_{j=1}^{J_n} Z_{nj}^{*2} \Big)^{1/2}
     \Big(\tfrac{1}{n} \sum_{j=1}^{J_n} \Big( \sum_{t= K_{n,j-1} + 1}^{K_{nj}}
-    (\mu_{nt}^{*} - \bar X_n)\Big)^2 \Big)^{1/2}\\
-    &\quad + \tfrac{1}{n} \sum_{j=1}^{J_n} \Big( \sum_{t= K_{n,j-1} + 1}^{K_{nj}}
+    (\mu_{nt}^{*} - \bar X_n)\Big)^2 \Big)^{1/2} \\
+    + \tfrac{1}{n} \sum_{j=1}^{J_n} \Big( \sum_{t= K_{n,j-1} + 1}^{K_{nj}}
     (\mu_{nt}^{*} - \bar X_n)\Big)^2
-  \end{align*}
+  \end{multline*}
   from the Cauchy-Schwarz inequality. Lemma~\ref{L5}, along
@@
     $\Fs_n$ were enlarged to include those variables then uniform
-    integrability would be an immediate consequence of~\eqref{eq:31}
-    and would not need to be shown separately. See \citet[Theorem
-    12.9]{Dav:94}.} %
+    integrability would be an immediate consequence and would not need
+    to be shown separately. See \citet[Theorem 12.9]{Dav:94}.} %
 

### 2016-09-26 Paper.tex
[#28] Modify statement of 'uniform integrability' lemma for M_j
The previous version of Lemma 6 did not *really* prove that the
bootstrapped Z_j's are uniformly integrable because of the
randomness in the block lengths. The proof follows from a similar
argument to the existing one, so I've added a statement to the
Lemma.

@@
     \times \ind\Big\{\max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m' > C\Big\}\Big)
-    = 0,
+    = 0.
   \end{multline}
-  making the family of random variables $\{\max_{m=1,\dots,m'}
-  Z^{*}_n(\tau, m)^2 n / m'; \tau, m', n\}$ uniformly integrable.
+  Moreover, the families of random variables
+  $\{\max_{m=1,\dots,m'} Z^{*}_n(\tau, m)^2 n / m'; \tau, m', n\}$ and
+  $\{\max_{m=1,\dots,M_{nj}} Z^{*}_{nj}(u_{nj}, m)^2 n / M_{nj}; j, n\}$ are uniformly integrable.
 \end{lem}
@@
 \begin{proof}
-  We will first show that, for every $\epsilon > 0$ and large enough
+  We will just present a proof of~\eqref{eq:30}. Uniform integrability
+  of the first family of random variables is simply a restatement of
+  that expression and unifom integrability of $Z_{nj}^{*2} n / M_{nj}$
+  follows an abbreviated version of the proof of~\eqref{eq:30}.
+
+  First we will show that, for every $\epsilon > 0$ and large enough
   $n$, there exists an $\epsilon' > 0$ with the property that

### 2016-09-27 Paper.tex
[#27] Make very small wording changes in the paper

--- 2016-09-26 Paper.tex
@@
 \end{equation*}
-we have defined $D_n$ to minimize notation in the subsequent
+we have introduced $D_n$ to minimize notation in the subsequent
 discussion.  For the Moving and Circular Block Bootstraps,
@@
 hold. These values of $\Delta_n$ and $T_n$ describe a scenario where
-there is a break large enough that its timing could be precisely
+there is a break large enough that $\pi$ could be precisely
 estimated \citep[as in][]{Bai:94}, but the break is ignored and the
@@
   Uniform integrability ensures that the convergence in~(\ref{eq:25})
-  holds in $L_1$ and Lemma~\ref{L2} then implies that
+  holds in $L_1$ as well and Lemma~\ref{L2} then implies that
   the first term in \eqref{eq:38} converges to zero in probability.
@@
 \begin{proof}
-  We will just present a proof of~\eqref{eq:30}. Uniform integrability
+  We will only present a proof of~\eqref{eq:30}. Uniform integrability
   of the first family of random variables is simply a restatement of

### 2016-09-27 Paper.tex
[#27] Make very small grammar fixes in paper

@@
 mistakenly includes a small number of pre-break observations as
-well. In this case, Assumption 2 holds hold as long as
+well. In this case, Assumption 2 holds as long as
 $M_n = o(\sqrt{n})$.  Similarly, suppose
@@
 \begin{proof}
-  The second result, on $\bar\mu_n^*$ is an immediate implication of
+  The second result, on $\bar\mu_n^*$, is an immediate implication of
   Equation~\eqref{eq:40}. To show~\eqref{eq:40}, observe that
@@
   of the first family of random variables is simply a restatement of
-  that expression and unifom integrability of $Z_{nj}^{*2} n / M_{nj}$
+  that expression and uniform integrability of $Z_{nj}^{*2} n / M_{nj}$
   follows an abbreviated version of the proof of~\eqref{eq:30}.
@@
   the third follows by construction of $A$
-  and fourth follows from an argument similar to Lemma~\ref{L3}.
+  and the fourth follows from an argument similar to Lemma~\ref{L3}.
 

### 2016-09-28 subs/ETr3/reply_3.tex
[#24] Add AucTeX variables to referee 3 letter
[#20] Draft reply to referee re: notation
[#27] Tweak centering term in Brownian Motion
Related to issue #20, I think it makes sense to center on a different
variable. This commit changes the centering term and revises my letter
to the referee.
Make small changes to referee letter

--- 2016-05-16 subs/ETr3/reply_3.tex
@@
 
-In your letter, you wrote,
+In your report, you wrote,
 \begin{quotation}
@@
 
+Thank you for clarifying this. I have added new material that explains
+when these assumptions are satisfied when there is a single break in
+the mean of the stochastic process. Specifically, it explains how the
+break size and break timing can affect whether the assumptions
+hold. This section starts half-way through page 4 and is a bit more
+than half a page long.
+
+Working through this example revealed that the original assumption
+on the means was too restrictive, so I have also relaxed the
+assumption on the the dispersion of the means from
+$\sum_t (\mu_{nt} - \bar \mu_n)^2) \to 0$ to
+$\sum_t (\mu_{nt} - \bar \mu_n)^2) = o(n p_n^2)$ (using notation for
+the stationary bootstrap; the assumption has been relaxed for all
+three of the block bootstraps considered).  This change does not
+affect the mathematical proofs very much: I have added a very simple
+result (Lemma 3) that shows that the contribution of the $\mu_{nt}$'s to the
+second moment of $\bar X^*$ remains asymptotically negligible under
+this assumption and strengthened one of the components of Lemma 1.
+
+The proofs of Lemmas 4 and 6 (which were labeled Lemmas 3 and 5 in the
+last version of the paper) have to be changed a little as well to
+reflect the new assumption on $\mu_{nt}$. The previous version of
+Lemma 6 established that (suitably normalized) $Z_i^2$s are uniformly
+integrable and used that as an intermediate result to show that the
+$Z_i^{*2}$s are also u.i.\ under the right normalization. The new
+version skips that intermediate step (the family of $Z_i^2s$ are no
+longer u.i.) but uses components of the original proof to show that
+the $Z_i^{*2}$s are u.i. directly. The relaxed assumption on the
+dispersion of the $\mu_{nt}$s ensures that the blocks are short
+enough that the stronger assumption continues to hold for the
+$\mu_{nt}^*$s.
+Changing the proof in this way essentially amounts to rearranging the
+elements of the original proof and invoking the new Lemma 3.
+
+To help make the changes as clear as possible, I have uploaded a
+pdf based on `latexdiff' that highlights the differences in the
+two versions as a supplemental document. I have also made a few
+spelling and wording corrections that will be apparent as well.
+
 You also wrote,
 \begin{quotation}
-  \noindent\textit{``Just one additional comment on the text. On page
+  \noindent%
+  \textit{``Just one additional comment on the text. On page
     5, line --7, should $\mu_n^*$ read $\bar{\mu}_n^*$?''}
 \end{quotation}
+\noindent%
+Yes, thank you, this was an error. I've changed $\mu_n^*$ to
+$E^* \bar X_n^*$ to highlight the connection with Theorem 1's results.
+
 \end{document}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2016-09-28 subs/ETr3/reply_ed.tex
Draft cover letter to editor

--- 2016-09-28 subs/ETr3/reply_3.tex
@@
 \begin{document}
-\section*{\hfill Reply to referee 3\hfill}
+\section*{\hfill Cover letter for the editor\hfill}
 
-In your report, you wrote,
-\begin{quotation}
-  \noindent\textit{``Yes, your array notation is of course needed to
-    accommodate the assumption of mean heterogeneity. However, what I
-    was really hoping for was some additional transparency in the form
-    of an example of a mean array which would satisfy Assumption 2 of
-    Theorem 1, and also perhaps a case which would fail to satisfy
-    it.}
+Hi Robert,
 
-  \textit{``Array notation has commonly been used in asymptotic
-    analysis to increase the generality of results, especially by
-    allowing flexible scaling by sample size such as
-    $X_{nt} = X_t/a_n$ where $a_n$ can be either $\sqrt{n}$ or
-    something else. The object here is quite different, such cases
-    would not satisfy Assumption 2 and are ruled out. It would
-    therefore help the general reader, who is not inside your head at
-    the outset, to explain the role of the arrays in this context,
-    most helpfully by quoting an example or two. Footnote 6 is not
-    helpful in this respect. Lots of people like to read papers in ET
-    even when they are not particularly familiar with the precedent
-    literature. Giving such readers the relevant background is just a
-    courtesy. We are only talking 2 or 3 extra sentences at most.''}
-\end{quotation}
-
-Thank you for clarifying this. I have added new material that explains
-when these assumptions are satisfied when there is a single break in
-the mean of the stochastic process. Specifically, it explains how the
-break size and break timing can affect whether the assumptions
-hold. This section starts half-way through page 4 and is a bit more
-than half a page long.
+I have made the changes that referee 3 requested. In particular, I
+have added new material that explains when the paper's assumptions are
+satisfied when there is a single break in the mean of the stochastic
+process. It explains how the break size and break timing can affect
+whether the assumptions hold. This section starts half-way through
+page 4 and is a bit more than half a page long.
 
@@
 assumption on the the dispersion of the means from
-$\sum_t (\mu_{nt} - \bar \mu_n)^2) \to 0$ to
-$\sum_t (\mu_{nt} - \bar \mu_n)^2) = o(n p_n^2)$ (using notation for
+$\sum_t (\mu_{NM} - \bar \mu_n)^2 \to 0$ to
+$\sum_t (\mu_{nt} - \bar \mu_n)^2 = o(n p_n^2)$ (using notation for
 the stationary bootstrap; the assumption has been relaxed for all
@@
 spelling and wording corrections that will be apparent as well.
+Thanks!
 
-You also wrote,
-\begin{quotation}
-  \noindent%
-  \textit{``Just one additional comment on the text. On page
-    5, line --7, should $\mu_n^*$ read $\bar{\mu}_n^*$?''}
-\end{quotation}
-\noindent%
-Yes, thank you, this was an error. I've changed $\mu_n^*$ to
-$E^* \bar X_n^*$ to highlight the connection with Theorem 1's results.
+\strut
 
+\noindent --- Gray Calhoun
 \end{document}

### 2016-09-28 subs/ETr3/reply_3.tex
Add statement to letters explaining why there are no changes to supplemental appendix
Fix minor typos in replies

@@
 assumption on the the dispersion of the means from
-$\sum_t (\mu_{nt} - \bar \mu_n)^2) \to 0$ to
-$\sum_t (\mu_{nt} - \bar \mu_n)^2) = o(n p_n^2)$ (using notation for
+$\sum_t (\mu_{nt} - \bar \mu_n)^2 \to 0$ to
+$\sum_t (\mu_{nt} - \bar \mu_n)^2 = o(n p_n^2)$ (using notation for
 the stationary bootstrap; the assumption has been relaxed for all
@@
 
+The results in the supplemental appendix are unaffected because they
+only address random variables whose means have been explicitly
+subtracted out.
+
 To help make the changes as clear as possible, I have uploaded a

### 2016-09-28 subs/ETr3/reply_ed.tex
Add statement to letters explaining why there are no changes to supplemental appendix
Fix minor typos in replies

@@
 assumption on the the dispersion of the means from
-$\sum_t (\mu_{NM} - \bar \mu_n)^2 \to 0$ to
+$\sum_t (\mu_{nt} - \bar \mu_n)^2 \to 0$ to
 $\sum_t (\mu_{nt} - \bar \mu_n)^2 = o(n p_n^2)$ (using notation for

### 2017-01-10 Paper.tex
[#30] Change hardcoded reference to Theorem 1 to use LaTeX reference

@@
 some constants $\Delta_0$ and $\pi$ and for all $n$, then
-$D_n \approx \Delta_0^2 \, c (1 - c) \, n$ and Assumption~2 fails to
+$D_n \approx \Delta_0^2 \, \pi (1 - \pi) \, n$ and Assumption~2 fails to
 hold. These values of $\Delta_n$ and $T_n$ describe a scenario where
@@
 To see when Theorem~\ref{T1}'s Assumption~2 is satisfied, consider two
-other parametrizations of this DGP. First, let $\Delta_n = \Delta_0$
+other parametrizations of this DGP\@. First, let $\Delta_n = \Delta_0$
 and $T_n = T_0$ for some finite $T_0$. This mimics a setting where a
@@
 setting with a moderate break with unknown timing.  Then
-$D_n \approx \Delta c (1 - c)$ and Assumption 2 again holds as long as
+$D_n \approx \Delta \pi (1 - \pi)$ and Assumption 2 again holds as long as
 $M_n = o(\sqrt{n})$. Consequently, using block sizes of length
-$o(\sqrt{n})$ ensures that Theorem 1's assumptions on the dispersion
+$o(\sqrt{n})$ ensures that Theorem~\ref{T1}'s assumptions on the dispersion
 of the $\mu_{nt}$ hold when there is a moderate amount of
@@
   argument.}%
-\footnote{Lemmas~\ref{L4} and
-  \ref{L6} are particularly
+\footnote{Lemmas~\ref{L4} and~\ref{L6} are particularly
   strong demonstrations of this argument.} %
@@
 \end{equation}
-for any positive $\delta$. If, in addition,
+for any positive  $\delta$.
+If, in addition, $\sup_{t=1,\dots,n}|\mu_{nt} -
+\bar \mu_n| = o(1/\sqrt{n})$ and
 \begin{equation}\label{eq:4}
@@
   \end{align*}
-  The first equality follows from the LIE. The first inequality
+  The first equality follows from the LIE\@. The first inequality
   exploits the fact that the conditional expectation in the previous
   expression averages over the block's starting period but treats
-  every other random variable as contstant. (The argument of the
+  every other random variable as constant. (The argument of the
   indicator function and the indices of the summations are
-  deliberately chosen to accomodate blocks that include observations
+  deliberately chosen to accommodate blocks that include observations
   from both the beginning and the end of the series.) The second
@@
   which is a direct implication of
-  Lemma~\ref{L7}.%
-  \footnote{The discussion in Footnote~\ref{f:1} applies here as well.}
+  Lemma~\ref{L7}.\footnote{%
+    The discussion in Footnote~\ref{f:1} applies here as well.}
 \end{proof}
@@
   \ind(A) Z_n(u, K_{n,J(\tau)} - \tau)^2\big] +
-  \sum_{j=J(\tau)+1}^{J(\tau + m')-1} \Em \big[\ind(A) Z_n(u, M_{nj})^2]\Big] \\
+  \sum_{j=J(\tau)+1}^{J(\tau + m')-1} \Em \big[\ind(A) Z_n(u, M_{nj})^2\big]\Big] \\
   &\leq \tfrac{3}{m'} \sum_{u = 0}^{n-1} \E\Big[\Em\big[
@@
     + 3\delta \E\Big(\sum_{j=J(\tau)}^{J(\tau+m')-1} M_{nj}^2/n^2 \Big) \\
-  &\quad+ 3(\delta'/n) \E\Big( \Big(\sum_{t \in I_n(u, K_{n,J(\tau)} - \tau)}
+  &\quad+ \tfrac{3\delta'}{nm'} \sum_{u=0}^{n-1}\E\Big( \Big(\sum_{t \in I_n(u, K_{n,J(\tau)} - \tau)}
   (\mu_{nt} - \bar \mu_n)\Big)^2 +
@@
 %%% End:
+%  LocalWords:  mixingale Heyde's

### 2017-01-10 Paper.tex
[#31/grammar] Fix minor wording errors in paper

@@
 discussion.  For the Moving and Circular Block Bootstraps,
-Theorem~\ref{T1}'s Assumption 2 holds if $D_n = o(n / M_n^2)$, and for
+Theorem~\ref{T1}'s Assumption 2 holds if $D_n = o(n / M_n^2)$, and
 the same relationship must hold for the expected block length for the
@@
 heterogeneity---either because the sample is chosen to lie after a
-large break estimated break or because any breaks are smaller in
+large estimated break or because any breaks are smaller in
 magnitude and, consequently, potentially difficult to detect. When the
@@
 \end{equation*}
-Then, conditional on the data, the $Z_{nj}^{*2}$ are independent can
+Then, conditional on the data, the $Z_{nj}^{*2}$ are independent and can
 be expected to obey an \lln, so %

### 2017-01-10 Paper.tex
[#32/Ems] Fix minor typo in defining the bootstrap conditional expectations
[#33/lem1] Clean up first component of Lemma 1

@@
 and the conditional probability $\Pm(\cdot) = \pr[\cdot \mid \Ms]$.
-(And define $\Pm^*(\cdot) = \pr^*[\cdot \mid \Ms]$, $\Em(\cdot) =
+(And define $\Pm^*(\cdot) = \pr^*[\cdot \mid \Ms]$, $\Em^*(\cdot) =
 \E^*(\cdot \mid \Ms)$, etc.) An important property is
@@
 $\Pm[\cdot]$ and integrate over the unconditional distributions of the
-other random variables. This property is especially important because it allows us
-to use maximal inequalities and other moment inequalities for
-mixingale arrays with only small modifications to construct almost sure bounds on the
-conditional moments $\Em$.
+other random variables.\footnote{%
+  A referee suggested the following clarification:
+  \begin{itemize}
+  \item[$\circ$] $\Em^*(\cdot)$ denotes the expectation over the $u_{ni}$, holding
+    the sample and $M_{ni}$ fixed.
+  \item[$\circ$] $\Em(\cdot)$ denotes the expectation over the sample and
+    $u_{ni}$, holding only the $M_{ni}$ fixed.
+  \item[$\circ$] $\E^*(\cdot)$ denotes the expectation over the $u_{ni}$ and
+    $M_{ni}$, holding the sample fixed.
+  \end{itemize}
+  The same distinctions hold for the probabilities as well.} %
+This property is especially important because it allows us to use
+maximal inequalities and other moment inequalities for mixingale
+arrays with only small modifications to construct almost sure bounds
+on the conditional moments $\Em$.
 
@@
 for any $x$.  These results are sufficient for~\eqref{eq:36}
-and~\eqref{eq:2} though an argument attributed to Poly{\`a}
-that proceeds as follows.
+and~\eqref{eq:2} since the limiting distribution is continuous,
+a standard argument that proceeds as follows \citep[see][Lemma 2.11, for example]{Vaa:00}.
 Let $k$ be a finite integer and define $x_i = \sigma \Phi^{-1}(i/k)$ for $i =
@@
 \begin{proof}[Proof of Lemma~\ref{L1}]
-  To prove part 1, observe that, for any increasing positive sequence
-  $x_n$ such that $x_n p_n \to \infty$,
-  \begin{equation*}
-    \pr\Big[\max_{i=1,\dots, \lfloor C n p_n \rfloor} M_{ni} \leq x_n\Big] =
-    (1 - (1 - p_n)^{x_n})^{\lfloor C n p_n \rfloor} \to \lim \exp(-C n p_n (1 - p_n)^{x_n})
-  \end{equation*}
-  and $C n p_n (1 - p_n)^{x_n} \to \lim C n p_n e^{-x_n p_n}$. Now, let
-  $x_n = n x$ for any positive number $x$.  Then
-  \begin{equation*}
-    \pr\Big[\max_{i=1,\dots,\lfloor C n p_n \rfloor} M_{ni}/n \leq x \Big] \to
-    \lim \exp(-C n p_n e^{-n p_n x}) =
-    \exp(0) = 1.
-  \end{equation*}
-  Since $x$ is arbitrary, $\max_{i=1,\dots,\lfloor C n p_n \rfloor} M_{ni} / n \to^p 0$.
+  To prove part 1, take $x$ to be an arbitrary positive number. Then
+  \begin{equation*}
+    \pr\Big[\max_{i=1,\dots, \lfloor C n p_n \rfloor} M_{ni} \leq n x \Big]
+    = (1 - (1 - p_n)^{n x})^{\lfloor C n p_n \rfloor}
+    = \exp(-C n p_n e^{-x n p_n}) \times (1 + o(1))
+  \end{equation*}
+  since $(1 - p_n)^{x/p_n} \to e^{-x}$. In addition, $n p_n e^{-n p_n} \to 0$
+  by assumption, so
+  \begin{align*}
+    \pr\Big[\max_{i=1,\dots, \lfloor C n p_n \rfloor} M_{ni}/n \leq x \Big]
+    \to \exp(0) = 1.
+  \end{align*}
+  Since $x$ is arbitrary, this completes the proof.
 
@@
 \begin{proof}
-  Since $|\pr[A_n]| = \E |\pr^*[A_n]| = \E |\pr^*_{\mathcal{M}}[A_n]|$ these
+  Since $\pr[A_n] = \E |\pr^*[A_n]| = \E |\pr^*_{\mathcal{M}}[A_n]|$ these
   conditions are equivalent by definition.

### 2017-01-10 Paper.tex
[#34/abs] Remove some absolute value signs requested by referee

@@
 for any $x$.  These results are sufficient for~\eqref{eq:36}
-and~\eqref{eq:2} since the limiting distribution is continuous,
-a standard argument that proceeds as follows \citep[see][Lemma 2.11, for example]{Vaa:00}.
+and~\eqref{eq:2} though an argument attributed to Poly{\`a}
+that proceeds as follows.
 Let $k$ be a finite integer and define $x_i = \sigma \Phi^{-1}(i/k)$ for $i =
@@
 \begin{proof}[Proof of Lemma~\ref{L1}]
-  To prove part 1, take $x$ to be an arbitrary positive number. Then
-  \begin{equation*}
-    \pr\Big[\max_{i=1,\dots, \lfloor C n p_n \rfloor} M_{ni} \leq n x \Big]
-    = (1 - (1 - p_n)^{n x})^{\lfloor C n p_n \rfloor}
-    = \exp(-C n p_n e^{-x n p_n}) \times (1 + o(1))
-  \end{equation*}
-  since $(1 - p_n)^{x/p_n} \to e^{-x}$. In addition, $n p_n e^{-n p_n} \to 0$
-  by assumption, so
-  \begin{align*}
-    \pr\Big[\max_{i=1,\dots, \lfloor C n p_n \rfloor} M_{ni}/n \leq x \Big]
-    \to \exp(0) = 1.
-  \end{align*}
-  Since $x$ is arbitrary, this completes the proof.
+  To prove part 1, observe that, for any increasing positive sequence
+  $x_n$ such that $x_n p_n \to \infty$,
+  \begin{equation*}
+    \pr\Big[\max_{i=1,\dots, \lfloor C n p_n \rfloor} M_{ni} \leq x_n\Big] =
+    (1 - (1 - p_n)^{x_n})^{\lfloor C n p_n \rfloor} \to \lim \exp(-C n p_n (1 - p_n)^{x_n})
+  \end{equation*}
+  and $C n p_n (1 - p_n)^{x_n} \to \lim C n p_n e^{-x_n p_n}$. Now, let
+  $x_n = n x$ for any positive number $x$.  Then
+  \begin{equation*}
+    \pr\Big[\max_{i=1,\dots,\lfloor C n p_n \rfloor} M_{ni}/n \leq x \Big] \to
+    \lim \exp(-C n p_n e^{-n p_n x}) =
+    \exp(0) = 1.
+  \end{equation*}
+  Since $x$ is arbitrary, $\max_{i=1,\dots,\lfloor C n p_n \rfloor} M_{ni} / n \to^p 0$.
 

### 2017-01-10 subs/ETr4/reply_3.tex
Add new LaTeX files for response to referees and editor

\documentclass[12pt]{article}
\frenchspacing
\input{../../preamble.tex}
\usepackage[tiny]{titlesec}

\begin{document}
\section*{\hfill Reply to referee 3\hfill}

\begin{enumerate}
\item \emph{$\pi$ or $c$? Which is it?} (page 4, lines --10 and --1)

\item \emph{``independent \underline{and} can\dots''} (Page 5 line --3)

\item \emph{Should $\Em(\cdot)$ read $\Em^*(\cdot)$ here? Similarly
    for $\Em(\cdot)$ and $\Pm(\cdot)$ on the next line.}

  \emph{Just to clarify:
    \begin{itemize}
    \item $\Em^*(\cdot)$ denotes the expectation over the $u$, holding
      sample and the $M_{ni}$ fixed?
    \item $\Em(\cdot)$ denotes the expectation over sample and
      $u_{ni}$, holding only $M_{ni}$ fixed?
    \item $\E^*(\cdot)$ denotes the expectation over $u_{ni}$ and
      $M_{ni}$, holding sample fixed?
    \end{itemize} 
    (Ditto for the probabilities.) This could all be spelt out more
    clearly.}  (Page 7. Line --6)

\item \emph{``any function $g$\dots.'' Are there no restrictions of any
    kind on $g$? If so, this deserves comment.} (Page 9)

\item \emph{I assume $\Em \Em^* = \Em$, law of iterated
    expectations. Yes?  Same on the following page.} (Page 10, equation (25))

\item \emph{``Attributed to Polya ...''. If this is worth saying, it
    is worth providing a citation.} (Page 11, line --5)

\item \emph{Having $n$ on both sides of the limit is untidy, to say
    the least. If what is meant is that the two functions of n have
    the same limit, as it appears, there must be a neater way to write
    this?} (Page 14, lines --8 and --7)

\item \emph{Since these arguments are nonnegative (they're
    probabilities), what is the purpose of enclosing them in absolute
    value bars?} (Page 15, line --5) 
\end{enumerate}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2017-01-10 subs/ETr4/reply_4.tex
Add new LaTeX files for response to referees and editor

--- 2017-01-10 subs/ETr4/reply_3.tex
@@
 \begin{document}
-\section*{\hfill Reply to referee 3\hfill}
+\section*{\hfill Reply to referee 4\hfill}
 
-\begin{enumerate}
-\item \emph{$\pi$ or $c$? Which is it?} (page 4, lines --10 and --1)
-
-\item \emph{``independent \underline{and} can\dots''} (Page 5 line --3)
-
-\item \emph{Should $\Em(\cdot)$ read $\Em^*(\cdot)$ here? Similarly
-    for $\Em(\cdot)$ and $\Pm(\cdot)$ on the next line.}
-
-  \emph{Just to clarify:
-    \begin{itemize}
-    \item $\Em^*(\cdot)$ denotes the expectation over the $u$, holding
-      sample and the $M_{ni}$ fixed?
-    \item $\Em(\cdot)$ denotes the expectation over sample and
-      $u_{ni}$, holding only $M_{ni}$ fixed?
-    \item $\E^*(\cdot)$ denotes the expectation over $u_{ni}$ and
-      $M_{ni}$, holding sample fixed?
-    \end{itemize} 
-    (Ditto for the probabilities.) This could all be spelt out more
-    clearly.}  (Page 7. Line --6)
-
-\item \emph{``any function $g$\dots.'' Are there no restrictions of any
-    kind on $g$? If so, this deserves comment.} (Page 9)
-
-\item \emph{I assume $\Em \Em^* = \Em$, law of iterated
-    expectations. Yes?  Same on the following page.} (Page 10, equation (25))
-
-\item \emph{``Attributed to Polya ...''. If this is worth saying, it
-    is worth providing a citation.} (Page 11, line --5)
-
-\item \emph{Having $n$ on both sides of the limit is untidy, to say
-    the least. If what is meant is that the two functions of n have
-    the same limit, as it appears, there must be a neater way to write
-    this?} (Page 14, lines --8 and --7)
-
-\item \emph{Since these arguments are nonnegative (they're
-    probabilities), what is the purpose of enclosing them in absolute
-    value bars?} (Page 15, line --5) 
-\end{enumerate}
+\emph{On page 10, I did not understand Equation (25)\dots}
 

### 2017-01-10 subs/ETr4/reply_ed.tex
Add new LaTeX files for response to referees and editor

--- 2016-09-28 subs/ETr3/reply_ed.tex
@@
 
-I have made the changes that referee 3 requested. In particular, I
-have added new material that explains when the paper's assumptions are
-satisfied when there is a single break in the mean of the stochastic
-process. It explains how the break size and break timing can affect
-whether the assumptions hold. This section starts half-way through
-page 4 and is a bit more than half a page long.
-
-Working through this example revealed that the original assumption
-on the means was too restrictive, so I have also relaxed the
-assumption on the the dispersion of the means from
-$\sum_t (\mu_{NM} - \bar \mu_n)^2 \to 0$ to
-$\sum_t (\mu_{nt} - \bar \mu_n)^2 = o(n p_n^2)$ (using notation for
-the stationary bootstrap; the assumption has been relaxed for all
-three of the block bootstraps considered).  This change does not
-affect the mathematical proofs very much: I have added a very simple
-result (Lemma 3) that shows that the contribution of the $\mu_{nt}$'s to the
-second moment of $\bar X^*$ remains asymptotically negligible under
-this assumption and strengthened one of the components of Lemma 1.
-
-The proofs of Lemmas 4 and 6 (which were labeled Lemmas 3 and 5 in the
-last version of the paper) have to be changed a little as well to
-reflect the new assumption on $\mu_{nt}$. The previous version of
-Lemma 6 established that (suitably normalized) $Z_i^2$s are uniformly
-integrable and used that as an intermediate result to show that the
-$Z_i^{*2}$s are also u.i.\ under the right normalization. The new
-version skips that intermediate step (the family of $Z_i^2s$ are no
-longer u.i.) but uses components of the original proof to show that
-the $Z_i^{*2}$s are u.i. directly. The relaxed assumption on the
-dispersion of the $\mu_{nt}$s ensures that the blocks are short
-enough that the stronger assumption continues to hold for the
-$\mu_{nt}^*$s.
-Changing the proof in this way essentially amounts to rearranging the
-elements of the original proof and invoking the new Lemma 3.
-
-To help make the changes as clear as possible, I have uploaded a
-pdf based on `latexdiff' that highlights the differences in the
-two versions as a supplemental document. I have also made a few
-spelling and wording corrections that will be apparent as well.
-Thanks!
-
 \strut

### 2017-01-10 subs/ETr4/reply_3.tex
[#29/typo] Add response to referee
[#31/grammar] Add response to referee
[#33/lem1] Add reply to referee

@@
 
+It should be $\pi$. Thanks for catching this error.
+
 \item \emph{``independent \underline{and} can\dots''} (Page 5 line --3)
+
+Fixed, thanks.
 
@@
     for $\Em(\cdot)$ and $\Pm(\cdot)$ on the next line.}
+
+  Yes, for $\Em(\cdot)$. The other terms look correct, though.
 
@@
 
+  This is correct. I have also added your clarification to the paper
+  (if you don't mind, of course) to help other readers see these
+  essential differences.
+
 \item \emph{``any function $g$\dots.'' Are there no restrictions of any
@@
 
+  Ok. My primary motivation in writing that statement was to avoid
+  appearing to take credit for a standard argument in this
+  literature. (I was asked to include these steps explicitly by an
+  earlier referee.)  I have added a reference to van der Vaart's
+  (2000) textbook instead, since I've been unable to track down a
+  specific citation for Poly\'a.
+
 \item \emph{Having $n$ on both sides of the limit is untidy, to say
@@
 
+  This first result has been cleaned up a little bit.
+
 \item \emph{Since these arguments are nonnegative (they're
@@
     value bars?} (Page 15, line --5)
+
+  They are enclosed in absolute value bars to make the connection to the
+  $L_{1}$-norm explicit. I've removed the absolute value sign from the first
+  probability to reduce confusion.
+
 \end{enumerate}

### 2017-01-10 subs/ETr4/reply_3.tex
[#34/abs] Add reply to referee

@@
 
-  Ok. My primary motivation in writing that statement was to avoid
-  appearing to take credit for a standard argument in this
-  literature. (I was asked to include these steps explicitly by an
-  earlier referee.)  I have added a reference to van der Vaart's
-  (2000) textbook instead, since I've been unable to track down a
-  specific citation for Poly\'a.
-
 \item \emph{Having $n$ on both sides of the limit is untidy, to say
@@
     this?} (Page 14, lines --8 and --7)
-
-  This first result has been cleaned up a little bit.
 

### 2017-02-05 Paper.tex
[#35/gfn] Address referee's snarky comment on functional assumptions
[#40/check] Tweak LaTeX code after lacheck

--- 2017-01-10 Paper.tex
@@
 discussion.  For the Moving and Circular Block Bootstraps,
-Theorem~\ref{T1}'s Assumption 2 holds if $D_n = o(n / M_n^2)$, and
+Theorem~\ref{T1}'s Assumption 2 holds if $D_n = o(n / M_n^2)$, and for
 the same relationship must hold for the expected block length for the
@@
 some constants $\Delta_0$ and $\pi$ and for all $n$, then
-$D_n \approx \Delta_0^2 \, \pi (1 - \pi) \, n$ and Assumption~2 fails to
+$D_n \approx \Delta_0^2 \, c (1 - c) \, n$ and Assumption~2 fails to
 hold. These values of $\Delta_n$ and $T_n$ describe a scenario where
@@
 setting with a moderate break with unknown timing.  Then
-$D_n \approx \Delta \pi (1 - \pi)$ and Assumption 2 again holds as long as
+$D_n \approx \Delta c (1 - c)$ and Assumption 2 again holds as long as
 $M_n = o(\sqrt{n})$. Consequently, using block sizes of length
-$o(\sqrt{n})$ ensures that Theorem~\ref{T1}'s assumptions on the dispersion
+$o(\sqrt{n})$ ensures that Theorem 1's assumptions on the dispersion
 of the $\mu_{nt}$ hold when there is a moderate amount of
 heterogeneity---either because the sample is chosen to lie after a
-large estimated break or because any breaks are smaller in
+large break estimated break or because any breaks are smaller in
 magnitude and, consequently, potentially difficult to detect. When the
@@
 \end{equation*}
-Then, conditional on the data, the $Z_{nj}^{*2}$ are independent and can
+Then, conditional on the data, the $Z_{nj}^{*2}$ are independent can
 be expected to obey an \lln, so %
@@
 and the conditional probability $\Pm(\cdot) = \pr[\cdot \mid \Ms]$.
-(And define $\Pm^*(\cdot) = \pr^*[\cdot \mid \Ms]$, $\Em^*(\cdot) =
+(And define $\Pm^*(\cdot) = \pr^*[\cdot \mid \Ms]$, $\Em(\cdot) =
 \E^*(\cdot \mid \Ms)$, etc.) An important property is
@@
 $\Pm[\cdot]$ and integrate over the unconditional distributions of the
-other random variables.\footnote{%
-  A referee suggested the following clarification:
-  \begin{itemize}
-  \item[$\circ$] $\Em^*(\cdot)$ denotes the expectation over the $u_{ni}$, holding
-    the sample and $M_{ni}$ fixed.
-  \item[$\circ$] $\Em(\cdot)$ denotes the expectation over the sample and
-    $u_{ni}$, holding only the $M_{ni}$ fixed.
-  \item[$\circ$] $\E^*(\cdot)$ denotes the expectation over the $u_{ni}$ and
-    $M_{ni}$, holding the sample fixed.
-  \end{itemize}
-  The same distinctions hold for the probabilities as well.} %
-This property is especially important because it allows us to use
-maximal inequalities and other moment inequalities for mixingale
-arrays with only small modifications to construct almost sure bounds
-on the conditional moments $\Em$.
+other random variables. This property is especially important because it allows us
+to use maximal inequalities and other moment inequalities for
+mixingale arrays with only small modifications to construct almost sure bounds on the
+conditional moments $\Em$.
 
@@
 \begin{proof}
-  Since $\pr[A_n] = \E |\pr^*[A_n]| = \E |\pr^*_{\mathcal{M}}[A_n]|$ these
+  Since $|\pr[A_n]| = \E |\pr^*[A_n]| = \E |\pr^*_{\mathcal{M}}[A_n]|$ these
   conditions are equivalent by definition.
@@
   expression averages over the block's starting period but treats
-  every other random variable as constant. (The argument of the
+  every other random variable as contstant. (The argument of the
   indicator function and the indices of the summations are
-  deliberately chosen to accommodate blocks that include observations
+  deliberately chosen to accomodate blocks that include observations
   from both the beginning and the end of the series.) The second
@@
   \ind(A) Z_n(u, K_{n,J(\tau)} - \tau)^2\big] +
-  \sum_{j=J(\tau)+1}^{J(\tau + m')-1} \Em \big[\ind(A) Z_n(u, M_{nj})^2\big]\Big] \\
+  \sum_{j=J(\tau)+1}^{J(\tau + m')-1} \Em \big[\ind(A) Z_n(u, M_{nj})^2]\Big] \\
   &\leq \tfrac{3}{m'} \sum_{u = 0}^{n-1} \E\Big[\Em\big[
@@
 %%% End:
-%  LocalWords:  mixingale Heyde's

### 2017-02-06 Paper.tex
[#40/check] Spellcheck documents

@@
   expression averages over the block's starting period but treats
-  every other random variable as contstant. (The argument of the
+  every other random variable as constant. (The argument of the
   indicator function and the indices of the summations are
-  deliberately chosen to accomodate blocks that include observations
+  deliberately chosen to accommodate blocks that include observations
   from both the beginning and the end of the series.) The second

### 2017-03-10 Paper.tex
[#38/ui] replace proof of 'maximal' ui result (Lemma 6)
The old version of the proof of Lemma 6 was incorrect -- there were
insurmountable measurability issues that I'd missed in earlier versions
of the paper. This commit replaces it with a proof based on McLeish's
proof for mixingales.

--- 2017-01-13 Paper.tex
@@
 \end{equation}
-almost surely for any function $g$ and any $j \leq k$. Equation~\eqref{eq:17}
+almost surely for any function $g$ such that both
+expressions are well-defined and any $j \leq k$. Equation~\eqref{eq:17}
 conditions on the lengths of each block, but averages over their
@@
 \begin{proof}[Proof of Lemma~\ref{L1}]
-  To prove part 1, observe that, for any increasing positive sequence
-  $x_n$ such that $x_n p_n \to \infty$,
-  \begin{equation*}
-    \pr\Big[\max_{i=1,\dots, \lfloor C n p_n \rfloor} M_{ni} \leq x_n\Big] =
-    (1 - (1 - p_n)^{x_n})^{\lfloor C n p_n \rfloor} \to \lim \exp(-C n p_n (1 - p_n)^{x_n})
-  \end{equation*}
-  and $C n p_n (1 - p_n)^{x_n} \to \lim C n p_n e^{-x_n p_n}$. Now, let
-  $x_n = n x$ for any positive number $x$.  Then
-  \begin{equation*}
-    \pr\Big[\max_{i=1,\dots,\lfloor C n p_n \rfloor} M_{ni}/n \leq x \Big] \to
-    \lim \exp(-C n p_n e^{-n p_n x}) =
-    \exp(0) = 1.
-  \end{equation*}
+  To prove part 1, take any positive number $x$. Then
+  \begin{equation*}
+    \pr\Big[\max_{i=1,\dots, \lfloor C n p_n \rfloor} M_{ni}/n \leq x \Big]
+    = (1 - (1 - p_n)^{n x})^{\lfloor C n p_n \rfloor}
+    = \exp(-C n p_n e^{-x n p_n}) \times (1 + o(1))
+  \end{equation*}
+  since $(1 - p_n)^{x/p_n} \to e^{-x}$. In addition, $n p_n e^{-n p_n} \to 0$
+  by assumption, so
+  \begin{align*}
+    \pr\Big[\max_{i=1,\dots, \lfloor C n p_n \rfloor} M_{ni}/n \leq x \Big]
+    \to \exp(0) = 1.
+  \end{align*}
   Since $x$ is arbitrary, $\max_{i=1,\dots,\lfloor C n p_n \rfloor} M_{ni} / n \to^p 0$.
@@
 \begin{lem}\label{L6}
-  Under the conditions of Theorem~\ref{T1},
+  Under the conditions of Theorem~\ref{T1}, for any positive
+  $\epsilon$ and $\epsilon'$ there exist constants $C_0$ and $n_0$
+  such that
   \begin{multline}\label{eq:30}
-    \lim_{C \to \infty} \limsup_{n \to \infty} \sup_{\substack{\tau = 0,\dots,n-1 \\ m'=1,\dots,n}}
-    \E\Big(\max_{m = 1,\dots,m'} (n \, Z^*_n(\tau, m)^2 / m') \\
+    \pr \Big [ \sup_{\substack{\tau = 0,\dots,n-1 \\ m'=1,\dots,n}}
+    \Em \Big ( \max_{ m = 1, \dots, m' } (n \, Z^*_n(\tau, m)^2 / m' ) \\
     \times \ind\Big\{\max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m' > C\Big\}\Big)
-    = 0.
+    > \epsilon \Big ] < \epsilon'
   \end{multline}
-  Moreover, the families of random variables
+  for all $n > n_0$ and $C > C_0$.
+  Moreover, the families of random variables \\
   $\{\max_{m=1,\dots,m'} Z^{*}_n(\tau, m)^2 n / m'; \tau, m', n\}$ and
-  $\{\max_{m=1,\dots,M_{nj}} Z^{*}_{nj}(u_{nj}, m)^2 n / M_{nj}; j, n\}$ are uniformly integrable.
+  $\{Z^{*2}_{nj} n / M_{nj}; \tau, j, n\}$ are
+  uniformly integrable for $n$ larger than some threshold $n_0$.
 \end{lem}
@@
 \begin{proof}
-  We will only present a proof of~\eqref{eq:30}. Uniform integrability
-  of the first family of random variables is simply a restatement of
-  that expression and uniform integrability of $Z_{nj}^{*2} n / M_{nj}$
-  follows an abbreviated version of the proof of~\eqref{eq:30}.
-
-  First we will show that, for every $\epsilon > 0$ and large enough
-  $n$, there exists an $\epsilon' > 0$ with the property that
-  \begin{equation}\label{eq:31}
-    \E \Big(\ind(A) \times \max_{m = 1,\dots,m'} Z^*_n(\tau, m)^2 n / m'\Big) < \epsilon
-  \end{equation}
-  for any event $A \in \Fs_n \equiv \sigma(X_{n1},\dots,X_{nn})$ with
-  $\pr(A) \leq \epsilon'$. Then we will show that this property
-  implies uniform integrability.\footnote{%
-    The novelty in this part of the proof is the measurability
-    requirement. The sigma-field $\Fs_n$ intentionally excludes the
-    random variables that define the bootstrap (block length and block
-    start periods) and any $A \in \Fs_n$ is independent of those
-    variables, so $Z_n^{*}(\tau, m)^2$ is not $\Fs_n$-measurable. If
-    $\Fs_n$ were enlarged to include those variables then uniform
-    integrability would be an immediate consequence of~\eqref{eq:31}
-    and would not need to be shown separately. See \citet[Theorem
-    12.9]{Dav:94}.} %
-
-  Take an arbitrary $\delta > 0$ and a value of $\delta' > 0$
-  so that
-  \begin{equation}\label{eq:35}
-    \sup_{m'=1,\dots,n} \E \Big(\ind(A) \max_{m = 1,\dots,m'}
-    Z_n'(\tau, m)^2 n / m' \Big) < \delta
-  \end{equation}
-  for any $A \in \Fs_n$ with $\pr(A) \leq \delta'$; the existence
-  of $\delta'$ is ensured by Lemma~\ref{L8}. For any $x$,
-  define $J(x)$ to be the block index such that $K_{n,J(x) - 1} < x
+  We will only present a proof of~\eqref{eq:30}.  Uniform
+  integrability of $Z^{*2}_{nj} \, n / M_{nj}$ and
+  $\{\max_{m=1,\dots,m'} Z^{*}_n(\tau, m)^2 n / m'; \tau, m', n\}$
+  follow essentially the same arguments, replacing the conditional
+  with the unconditional expectation, and are omitted.
+
+  For any $x$, define $J(x)$ to be the block index such that $K_{n,J(x) - 1} < x
   \leq K_{n,J(x)}$. For any $m$, we can decompose $Z_n^{*}(\tau, m)$
-  into a summation of conditionally independent blocks
-  \begin{equation*}
+  into a summation of conditionally independent blocks, giving
+  \begin{multline} \label{eq:42}
     Z^{*}_n(\tau, m) = Z_n^*(\tau, K_{n,J(\tau)} - \tau) +
-  \sum_{j=J(\tau)+1}^{J(\tau + m)-1} Z_{nj}^* + Z_n^*(K_{n,J(\tau+m)-1}, m - K_{n,J(\tau + m)-1}),
-  \end{equation*}
-  giving
-  \begin{align}
-  \E  \Big(&\ind(A) \times \max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m'\Big)
-  \notag \\
-  &\leq 3 \E\Big[ \Em^{*} \Big[\ind(A) \tfrac{n}{m'}\max_{m = 1,\dots, m'}
-  \Big(Z_n^*(\tau, K_{n,J(\tau)} - \tau) + \sum_{j=J(\tau)+1}^{J(\tau + m)-1} Z_{nj}^*\Big)^2\Big]
-  \notag \\
-  &\quad + 3 \Em^{*} \big[\ind(A) \tfrac{n}{m'}
-  \max_{m=1,\dots,m'} Z_n^*(K_{n,J(\tau+m)-1}, m - K_{n,J(\tau + m)-1})^2 \big]\Big]\label{eq:6}
-  \end{align}
+    \sum_{j=J(\tau)+1}^{J(\tau + m)-1} Z_{nj}^* \\
+    + Z_n^*(K_{n,J(\tau+m)-1}, m - K_{n,J(\tau + m)-1}).
+  \end{multline}
+  Since the distribution of $Z_n^*(\tau, m)$ does not depend on
+  $\tau$, \eqref{eq:30} holds if, for any positive $\epsilon$ and
+  $\epsilon'$, there exist $n_0$ and $C_0$ such that
+  \begin{multline} \label{eq:31}
+    \Pr \big [ \max_{\tau=0,\dots,n-1}
+    \Em \big ( ( \max_{ m = 1, \dots, K_{n,J(\tau)} - \tau} n \, Z^*_n(\tau, m)^2 / M_{n,J(\tau)} ) \\
+    \times \ind \{ \max_{ m = 1, \dots, K_{n,J(\tau)} - \tau} n \, Z^*_n(\tau, m)^2 / M_{n,J(\tau)} > C \}
+    \big ) > \epsilon \big ] < \epsilon',
+  \end{multline}
+  \begin{multline} \label{eq:44}
+    \pr \Big [
+    \max_{m'=1,\dots,n}
+    \Em \Big (
+    \tfrac{n}{m'} \max_{k=1,\dots,J(m')} \Big\lvert \sum_{j=1}^{k} Z_{nj}^* \Big\rvert^2 \\
+    \times \ind \Big \{
+    \tfrac{n}{m'} \max_{k=1,\dots,J(m')} \Big\lvert \sum_{j=1}^{k} Z_{nj}^* \Big\rvert^2
+    > C \Big \} \Big ) > \epsilon \Big ] < \epsilon'
+  \end{multline}
+  and
+  \begin{multline} \label{eq:5}
+    \Pr \big [ \max_{j=1,\dots,J_n}
+    \Em \big ( ( \max_{ m = 1, \dots, M_{nj}} n \, Z^*_n(K_{n,j-1}, m)^2 / M_{nj} ) \\
+    \times \ind \{ \max_{ m = 1, \dots, M_{nj}} n \, Z^*_n(K_{n,j-1}, m)^2 / M_{nj} > C \}
+    \big ) > \epsilon \big ] < \epsilon',
+  \end{multline}
+  for all $n > n_0$ and $C > C_0$.
+
+  For~\eqref{eq:5}, use the equality
+  \begin{equation}
+    Z_n(\tau, m) = Z_n'(\tau, m)
+    + \tfrac{1}{\sqrt{n}} \sum_{t \in I_n(\tau, m)} (\mu_{nt} - \bar \mu_n)
+    - (m/n) Z'_n(\tau, n), \label{eq:35}
+  \end{equation}
+  to get the upper bound
+  \begin{align*}
+    \Em \big ( & ( \max_{ m = 1, \dots, M_{nj} } n \, Z^*_n(K_{n,j-1},m)^2 / M_{nj} )
+    \ind \{ \max_{ m = 1, \dots, M_{nj} } n \, Z^*_n(K_{n,j-1}, m) ^2 / M_{nj} > C \} \big ) \\
+    & \leq 3 \Em \big ( ( \max_{ m = 1, \dots, M_{nj} } n \, Z'_n(u_n,m)^2 / M_{nj} )
+    \ind \{ \max_{ m = 1, \dots, M_{nj} } n \, Z'_n(u_n,m)^2 / M_{nj} > C / 3 \} \big ) \\
+    & \quad + 3 \Em \big ( ( M_{nj} Z'_n(0,n)^2 / n )
+    \ind \{ M_{nj} Z'_n(0,n)^2 / n > C / 3 \} \big )
+    + 3 \tfrac{M_{nj}}{n} \sum_{t=1}^n ( \mu_{nt} - \bar \mu_n ) ^2,
+  \end{align*}
+  where $u_n$ has the discrete uniform distribution over $0,\dots,n-1$.
+  Lemmas~\ref{L1}, \ref{L3}, and \ref{L8} ensure that there exist
+  $n_0$ and $C_0$ such that, for all $n > n_0$ and $C > C_0$,
+  \begin{equation*}
+    \Em \big ( (\max_{ m = 1, \dots, M_{nj} } n \, Z'_n(u_n,m)^2 / M_{nj} )
+    \ind \{\max_{ m = 1, \dots, M_{nj} } n \, Z'_n(u_n,m)^2 / M_{nj} > C / 3 \}
+    \big ) < \epsilon / 9
+  \end{equation*}
+  and
+  \begin{equation*}
+    \Em \big ( ( M_{nj} \, Z'_n(0,n)^2 / n )
+    \ind \{ M_{nj} \, Z'_n(0,n)^2 / n > C / 3 \} \big )
+    < \epsilon / 9
+  \end{equation*}
+  for all $j = 1,\dots,J_n - 1$ almost surely, and
+  \begin{equation*}
+    \pr \Big [ \max_{j=1,\dots,J_n-1}
+    \tfrac{M_{nj}}{n} \sum_{t=1}^n ( \mu_{nt} - \bar \mu_n )^2 > \epsilon / 9 \Big ]
+    < \epsilon' / 3,
+  \end{equation*}
+  proving~\eqref{eq:5}. The proof of~\eqref{eq:31} is essentially the same.
+
+  The proof of~\eqref{eq:44} follows a streamlined version of \citet[Lemma
+  6.5]{Mcl:75b} and \citet[Lemma 3.5]{Mcl:77}. (Those results are
+  presented as Theorem~16.13 in \citealp{Dav:94}, and are largely
+  reproduced in the proof of this paper's Lemma~\ref{L8}.)
+
+  Separate $Z_{nj}^*$ into two components,
+  \begin{align*}
+    U_{nj}^* &= (\tfrac{n}{m'})^{1/2} \, Z_{nj}^*
+    \ind\{\tfrac{n}{M_{nj}} \, Z_{nj}^{*2} > C' \} -
+    (\tfrac{n}{m'})^{1/2} \Em^*( Z_{nj}^*
+    \ind\{\tfrac{n}{M_{nj}} Z_{nj}^{*2} > C' \}) \\
+    Y_{nj}^* &= (\tfrac{n}{m'})^{1/2} \, Z_{nj}^*
+    \ind\{\tfrac{n}{M_{nj}} \, Z_{nj}^{*2} \leq C' \} -
+    (\tfrac{n}{m'})^{1/2} \Em^*( Z_{nj}^*
+    \ind\{\tfrac{n}{M_{nj}} Z_{nj}^{*2} \leq C'\}),
+    \intertext{making}
+    Z_{nj}^* &= (\tfrac{m'}{n})^{1/2} U_{nj}^* + (\tfrac{m'}{n})^{1/2} Y_{nj}^*
+  \end{align*}
+  where $C'$ is a constant that will be constrained later in the
+  proof. For any $C$, $\tau$, $m'$, and $n$, standard probabilistic
+  inequalities~(e.g. Theorem 2.29 of \citealp{Dav:94}, along with
+  maximal inequalities for martingale difference sequences) imply that
+  \begin{multline}
+    \Em \Big ( \tfrac{n}{m'} \max_{k=1,\dots,J(m')}
+    \Big \lvert \sum_{j=1}^{k} Z_{nj}^* \Big \rvert^2 \ind \Big \{
+    \tfrac{n}{m'} \max_{k=1,\dots,J(m')} \Big \lvert \sum_{j=1}^{k}
+    Z_{nj}^* \Big \rvert^2 > C \Big \} \Big ) \leq \\
+    \tfrac{6}{C} \tfrac{4^4}{3^4}
+    \Em \Big \lvert \sum_{j=1}^{J(m')} Y_{nj}^* \Big \rvert^4
+    + 24 \Em \Big \lvert \sum_{j=1}^{J(m')} U_{nj}^* \Big \rvert^2
+    \label{eq:43}
+  \end{multline}
   almost surely.
 
-  Since $Z_{nj}^*$ is a martingale difference array, Doob's maximal
-  inequality for martingales \citep[see][Theorem 15.15, for
-  example]{Dav:94} along with the construction of $Z_{nj}^{*}$ gives
-  a bound for the first term on the \allcaps{RHS} of~\eqref{eq:6},
-  \begin{align*}
-  \E \Em^* & \Big[\ind(A) \tfrac{n}{m'}\max_{m = 1,\dots, m'}
-  \Big(Z_n^*(\tau, K_{n,J(\tau)} - \tau)
-  + \sum_{j=J(\tau)+1}^{J(\tau + m)-1} Z_{nj}^*\Big)^2\Big] \\
-  &\leq \tfrac{1}{m'} \sum_{u = 0}^{n-1} \E \Big[\Em \big[
-  \ind(A) Z_n(u, K_{n,J(\tau)} - \tau)^2\big] +
-  \sum_{j=J(\tau)+1}^{J(\tau + m')-1} \Em \big[\ind(A) Z_n(u, M_{nj})^2\big]\Big] \\
-  &\leq \tfrac{3}{m'} \sum_{u = 0}^{n-1} \E\Big[\Em\big[
-  \ind(A) Z'_n(u, K_{n,J(\tau)} - \tau)^2\big]
-  + \tfrac{1}{n} \Pm[A] \Big(\sum_{t \in I_n(u, K_{n,J(\tau)} - \tau)}
-  (\mu_{nt} - \bar \mu_n)\Big)^2 \\
-  & \quad+ \sum_{j=J(\tau)+1}^{J(\tau + m')-1}
-  \Em \big[\ind(A) Z_n'(u, M_{nj})^2]
-  + \tfrac{1}{n} \Pm[A]
-  \sum_{j=J(\tau)+1}^{J(\tau + m')-1}\Big( \sum_{t \in I_n(u,M_{nj})}
-  (\mu_{nt} - \bar{\mu}_n) \Big)^2 \\
-  & \quad+ \Em\big( \ind(A) Z_n'(u, n)^2 \big)
-  \sum_{j=J(\tau)}^{J(\tau+m')-1} M_{nj}^2/n^2 \Big] \\
-  &\leq (3\delta/m') \E (K_{n,J(\tau+m')-1} - \tau)
-    + 3\delta \E\Big(\sum_{j=J(\tau)}^{J(\tau+m')-1} M_{nj}^2/n^2 \Big) \\
-  &\quad+ \tfrac{3\delta'}{nm'} \sum_{u=0}^{n-1}\E\Big( \Big(\sum_{t \in I_n(u, K_{n,J(\tau)} - \tau)}
-  (\mu_{nt} - \bar \mu_n)\Big)^2 +
-  \sum_{j=J(\tau)+1}^{J(\tau + m')-1}\Big( \sum_{t \in I_n(u,M_{nj})}
-  (\mu_{nt} - \bar{\mu}_n) \Big)^2 \Big) \\
-  & < C_1 \delta + C_2 p_n \delta'
-  \end{align*}
-  for some finite constants $C_1$ and $C_2$.
-  The second inequality comes from writing
-  \begin{align*}
-    Z_n(\tau, m) &= Z_n'(\tau, m)
-    + \tfrac{1}{\sqrt{n}} \sum_{t \in I_n(\tau, m)}
-    \big((\mu_{nt} - \bar \mu_n) + (\bar \mu_n - \bar X_n)\big) \\
-    &= Z_n'(\tau, m)
-    + \tfrac{1}{\sqrt{n}} \sum_{t \in I_n(\tau, m)} (\mu_{nt} - \bar \mu_n)
-    - (m/n) Z'_n(\tau, n),
-  \end{align*}
-  the third follows by construction of $A$
-  and the fourth follows from an argument similar to Lemma~\ref{L3}.
-
-  For the second term on the \allcaps{RHS} of~\eqref{eq:6}, use the
-  sequence of inequalities
-  \begin{align*}
-  \E \Em^* \big[\ind(A) &\tfrac{n}{m'}
-  \max_{m=1,\dots,m'} Z_n^*(K_{n,J(\tau+m)-1}, m - K_{n,J(\tau + m)-1})^2 \big] \\
-  &\leq \E \Big(\sum_{j=J(\tau) + 1}^{J(\tau+m')-1} \tfrac{n}{m'} \Em^* \big[\ind(A)
-  \max_{m=1,\dots, \min(M_{nj}, m' - K_{n,j-1})} Z_n^*(K_{n,j}, m)^2 \big]\Big) \\
-  &\leq \E \Big(\sum_{j=J(\tau) + 1}^{J(\tau+m')} \tfrac{1}{m'} \sum_{u=0}^{n-1} \Em \big[\ind(A)
-  \max_{m=1,\dots,\min(M_{nj}, m' - K_{n,j-1})} Z_n(u, m)^2 \big]\Big) \\
-  &\leq \E \Big(\sum_{j=J(\tau) + 1}^{J(\tau+m')} \tfrac{3}{m'} \sum_{u=0}^{n-1} \Big\{
-  \Em \big[\ind(A)
-  \max_{m=1,\dots,\min(M_{nj}, m' - K_{n,j-1})} Z_n'(u, m)^2 \big] \\
-  &\quad +
-  \tfrac{1}{n} \Pm[A] \max_{m = 1,\dots,\min(M_{nj}, m'-K_{n,j-1})}
-  \Big(\sum_{t \in I_n(u,m)} (\mu_{nt} - \bar{\mu}_n)\Big)^2 \\
-  &\quad+ \tfrac{\min(M_{nj},m'-K_{n,j-1})^2}{n^2} \Em( \ind(A) Z_n'(u, n)^2 ) \Big\}\Big)\\
-  &\leq C'_1 \delta + C_2' \delta' p_n
-  \end{align*}
-  for constants $C_1'$ and $C_2'$. To express these bounds in the form
-  of~\eqref{eq:31}, let $\epsilon > 0$ be arbitrary, choose $\delta'$
-  such that~\eqref{eq:35} holds for $\delta = \epsilon/(2C_1+2C_1')$,
-  and let $\epsilon' = \min(\delta', \epsilon/(2 C_2 + 2C_2'))$.
-  A similar argument also
-  implies that $n Z_n^*(\tau, m)^2 / m'$ has finite first moment.
-
-  Now, for uniform integrability, take $\epsilon > 0$, choose
-  $\epsilon'$ so that~\eqref{eq:31} holds for all $A \in \Fs_n$
-  s.t. $\pr(A) \leq \epsilon'$, and choose $C_0$ large enough that
-  \begin{equation*}
-    \Pr\Big[ \max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m' > C_0 \Big] \leq \epsilon'.
-  \end{equation*}
-  Markov's inequality guarantees the existence of this $C_0$. Then
-  \begin{equation*}
-    \E \Big(\max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m'
-    \times \ind\Big\{ \max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m' > C \Big\}\Big) \leq \epsilon
-  \end{equation*}
-  for all $C > C_0$. Since $\epsilon$ is arbitrary, this completes the proof.
+  The first term on the RHS of~\eqref{eq:43} can be
+  expanded recursively to give the following upper bound
+  \begin{align*}
+    \tfrac{1}{C} \Em \Big\lvert \sum_{j=1}^{J(m')} Y_{nj}^* \Big\rvert^4
+    & \leq \Em \Big[ \tfrac{1}{C} \Em^* \Big\lvert \sum_{j=1}^{J(m')-1} Y_{nj}^* \Big\rvert^4
+    + \tfrac{6}{C} \Em^* \Big( Y_{n,J(m')}^{*2} \Big\lvert
+    \sum_{j=1}^{J(m')-1} Y_{nj}^* \Big\rvert^2 \Big) \\
+    & \quad + \tfrac{4}{C} \Em^* \Big\lvert Y_{n,J(m')}^{*3} \sum_{j=1}^{J(m')-1} Y_{nj}^* \Big\rvert
+    + \tfrac{1}{C} \Em^* \lvert Y_{n,J(m')}^{*4} \rvert \Big] \\
+    & \leq \tfrac{1}{C} \Em^* \Big ( \sum_{j=1}^{J(m')-1} Y_{nj}^* \Big ) ^4
+    + \tfrac{1}{C} (\tfrac{4 C'}{m'})^2
+    \Big( 6 M_{n,J(m')} \sum_{j=1}^{J(m')-1} M_{nj} \\
+    & \quad + 4 M_{n,J(m')}^{3/2} \Big [ \sum_{j=1}^{J(m')-1} M_{n,J(m')} \Big ] ^{1/2}
+    + M_{n,J(m')}^2 \Big ) \\
+    & \leq \tfrac{ 1 }{ C } ( \tfrac{ 4 C' }{ m' } )^2 \sum_{j=2}^{J(m')}
+      \Big ( 6 M_{nj} \sum_{ k = 1 }^{ j - 1 } M_{nk}
+      + 4 M_{nj}^{3/2} \Big [ \sum_{ k = 1 }^{ j - 1 } M_{ nk } \Big ] ^{1/2}
+      + M_{nj}^2 \Big ) \\
+    & \leq \tfrac{11}{C} \tfrac{ K _{ n, J(m') } }{ m' } (4 C')^2
+  \end{align*}
+  with all inequalities holding almost surely.
+  The second to last inequality holds by recursively applying the previous
+  two inequalities, first for $J(m')-1$, then for $J(m')-2$, etc.
+
+  The second term on the RHS of~\eqref{eq:43} satisfies
+  \begin{align*}
+    \Em \Big \lvert \sum_{j=1}^{J(m')} U_{nj}^* \Big \rvert^2
+    & = \sum_{j=1}^{J(m')} \Em \lvert U_{nj}^* \rvert^2 \\
+    & \leq \max_{j=1,\dots,J(m')} \Em \big(
+      \tfrac{n}{M_{nj}} Z_{nj}^{*2}
+      \ind\{ \tfrac{n}{M_{nj}} Z_{nj}^{*2} > C' \} \big) .
+  \end{align*}
+  Equation~\eqref{eq:5} ensures that we can choose $C'$ and $n'$ such that
+  \begin{equation*}
+    \pr \Big [
+    \max_{j=1,\dots,J(m')} \Em \big(
+      \tfrac{n}{M_{nj}} Z_{nj}^{*2}
+      \ind\{ \tfrac{n}{M_{nj}} Z_{nj}^{*2} > C \} > \epsilon / 2 \big) \Big ]
+    < \epsilon' / 2
+  \end{equation*}
+  for all $n > n'$ and $C > C'$. We can then choose $n_0 > n'$ and $C_0 > C'$
+  such that
+  \begin{equation*}
+    \pr \Big [
+    \max_{ m' = 1, \dots, n }
+    \tfrac{11}{C} \tfrac{ K _{ n, J(m') } }{ m' } (4 C')^2
+    > \epsilon / 2 \Big ] < \epsilon' / 2
+  \end{equation*}
+  for all $n > n_0$ and $C > C_0$,
+  completing the proof.
 \end{proof}

### 2017-03-13 Paper.tex
[#38/ui] make small adjustment to statement of Lemma 6

--- 2017-02-06 Paper.tex
@@
 setting with a moderate break with unknown timing.  Then
-$D_n \approx \Delta c (1 - c)$ and Assumption 2 again holds as long as
+$D_n \approx \Delta \pi (1 - \pi)$ and Assumption 2 again holds as long as
 $M_n = o(\sqrt{n})$. Consequently, using block sizes of length
-$o(\sqrt{n})$ ensures that Theorem 1's assumptions on the dispersion
+$o(\sqrt{n})$ ensures that Theorem~\ref{T1}'s assumptions on the dispersion
 of the $\mu_{nt}$ hold when there is a moderate amount of
 heterogeneity---either because the sample is chosen to lie after a
-large break estimated break or because any breaks are smaller in
+large estimated break or because any breaks are smaller in
 magnitude and, consequently, potentially difficult to detect. When the

### 2017-03-14 Paper.tex
[#40/check] Fix small error in matching bracket sizes

--- 2017-02-06 Paper.tex
@@
 setting with a moderate break with unknown timing.  Then
-$D_n \approx \Delta c (1 - c)$ and Assumption 2 again holds as long as
+$D_n \approx \Delta \pi (1 - \pi)$ and Assumption 2 again holds as long as
 $M_n = o(\sqrt{n})$. Consequently, using block sizes of length

### 2017-03-14 Paper.tex

--- 2017-03-13 Paper.tex
@@
 \end{equation}
-almost surely for any function $g$ such that both
-expressions are well-defined and any $j \leq k$. Equation~\eqref{eq:17}
+almost surely for any function $g$ and any $j \leq k$. Equation~\eqref{eq:17}
 conditions on the lengths of each block, but averages over their
@@
 \begin{proof}[Proof of Lemma~\ref{L1}]
-  To prove part 1, take any positive number $x$. Then
-  \begin{equation*}
-    \pr\Big[\max_{i=1,\dots, \lfloor C n p_n \rfloor} M_{ni}/n \leq x \Big]
-    = (1 - (1 - p_n)^{n x})^{\lfloor C n p_n \rfloor}
-    = \exp(-C n p_n e^{-x n p_n}) \times (1 + o(1))
-  \end{equation*}
-  since $(1 - p_n)^{x/p_n} \to e^{-x}$. In addition, $n p_n e^{-n p_n} \to 0$
-  by assumption, so
-  \begin{align*}
-    \pr\Big[\max_{i=1,\dots, \lfloor C n p_n \rfloor} M_{ni}/n \leq x \Big]
-    \to \exp(0) = 1.
-  \end{align*}
+  To prove part 1, observe that, for any increasing positive sequence
+  $x_n$ such that $x_n p_n \to \infty$,
+  \begin{equation*}
+    \pr\Big[\max_{i=1,\dots, \lfloor C n p_n \rfloor} M_{ni} \leq x_n\Big] =
+    (1 - (1 - p_n)^{x_n})^{\lfloor C n p_n \rfloor} \to \lim \exp(-C n p_n (1 - p_n)^{x_n})
+  \end{equation*}
+  and $C n p_n (1 - p_n)^{x_n} \to \lim C n p_n e^{-x_n p_n}$. Now, let
+  $x_n = n x$ for any positive number $x$.  Then
+  \begin{equation*}
+    \pr\Big[\max_{i=1,\dots,\lfloor C n p_n \rfloor} M_{ni}/n \leq x \Big] \to
+    \lim \exp(-C n p_n e^{-n p_n x}) =
+    \exp(0) = 1.
+  \end{equation*}
   Since $x$ is arbitrary, $\max_{i=1,\dots,\lfloor C n p_n \rfloor} M_{ni} / n \to^p 0$.
@@
 \begin{lem}\label{L6}
-  Under the conditions of Theorem~\ref{T1}, for any positive
-  $\epsilon$ and $\epsilon'$ there exist constants $C_0$ and $n_0$
-  such that
+  Under the conditions of Theorem~\ref{T1},
   \begin{multline}\label{eq:30}
-    \pr \Big [ \sup_{\substack{\tau = 0,\dots,n-1 \\ m'=1,\dots,n}}
-    \Em \Big ( \max_{ m = 1, \dots, m' } (n \, Z^*_n(\tau, m)^2 / m' ) \\
+    \lim_{C \to \infty} \limsup_{n \to \infty} \sup_{\substack{\tau = 0,\dots,n-1 \\ m'=1,\dots,n}}
+    \E\Big(\max_{m = 1,\dots,m'} (n \, Z^*_n(\tau, m)^2 / m') \\
     \times \ind\Big\{\max_{m = 1,\dots,m'} n \, Z^*_n(\tau, m)^2 / m' > C\Big\}\Big)
-    > \epsilon \Big ] < \epsilon'
+    = 0.
   \end{multline}
-  for all $n > n_0$ and $C > C_0$.
-  Moreover, the families of random variables \\
+  Moreover, the families of random variables
   $\{\max_{m=1,\dots,m'} Z^{*}_n(\tau, m)^2 n / m'; \tau, m', n\}$ and
-  $\{Z^{*2}_{nj} n / M_{nj}; \tau, j, n\}$ are
-  uniformly integrable for $n$ larger than some threshold $n_0$.
+  $\{\max_{m=1,\dots,M_{nj}} Z^{*}_{nj}(u_{nj}, m)^2 n / M_{nj}; j, n\}$ are uniformly integrable.
 \end{lem}

### 2017-03-27 Paper.tex
[#38/ui] Update usage of Lemma 6 in Theorem 1

--- 2017-03-13 Paper.tex
@@
 
-To prove~\eqref{eq:19}, it suffices to show that
-\begin{equation}\label{eq:21}
-  \Em \sum_{j=1}^{J_n} \Em^{*}\big(Z_{nj}^{*2} \ind\{Z_{nj}^{*2} > \epsilon\}\big) \to^p 0.
-\end{equation}
-For any $j$ and $m$ and for large enough $n$,
-\begin{align}
-\Em \Em^{*}\big((Z_n(u_{nj}, m)^2n/m) &\ind\{Z_n(u_{nj}, m)^2n/m > \epsilon n/m\}\big) \notag \\
-&= \E \big((Z_n^{*}(0, m)^2n/m) \ind\{Z_n^{*}(0, m)^2n/m > \epsilon n/m\}\big) \notag \\
-&\leq B(\epsilon n/m)\label{eq:5}
-\end{align}
-where $B$ is some finite monotone function such that $B(x) \to 0$ as
-$x \to \infty$; the existence of a function $B$ that satisfies these
-conditions (and does not depend on $n$ or $m$) is a consequence of
-Lemma~\ref{L6}. Since $J_n$ and $M_{nj}$ are both $\Ms$-measurable
-and independent of the $u_{nj}$'s and $X_{nt}$'s,~\eqref{eq:5} implies that
-\begin{align*}
-\Em &\sum_{j=1}^{J_n} \Em^{*}\big(Z_{nj}^{*2} \ind\{Z_{nj}^{*2} > \epsilon\}\big) \\
-& = \sum_{j=1}^{J_n} (M_{nj}/n) \Em \Em^{*}
-\big((Z_n(u_{nj}, M_{nj})^2 n/M_{nj})
-\ind\{Z_n(u_{nj}, M_{nj})^2n/M_{nj} > \epsilon n/M_{nj}\}\big) \\
-& \leq \sum_{j=1}^{J_n} (M_{nj}/n) \, B(\epsilon n/M_{nj}) \\
-& \leq \max_{j = 1,\dots,J_n} B(\epsilon n / M_{nj}) \sum_{i=1}^{J_n} M_{ni} / n \\
-& = B(\epsilon n / \max_{j = 1,\dots,J_n} M_{nj}) \\
-& \to^p 0 \text{\ as\ } n \to \infty.
-\end{align*}
-The first equality follows from simple algebra and the definition
-of the $u_{nj}$'s. The first inequality is a
-consequence of~\eqref{eq:5}.  The second equality holds by
-monotonicity of $B$. And convergence in probability holds by
-Lemma~\ref{L1}, completing the proof
-of~\eqref{eq:19}. The Dominated Convergence Theorem and~(\ref{eq:18})
+To prove~\eqref{eq:19}, it suffices (via the LIE and Lemma~\ref{L2})
+to show that
+\begin{equation*}
+  \sum_{j=1}^{J_n} \Em \big ( Z_{nj}^{*2} \ind \{ Z_{nj}^{*2} > \epsilon \} \big ) \to^p 0.
+\end{equation*}
+But note that
+\begin{equation*}
+  \sum_{j=1}^{J_n} \Em \big ( Z_{nj}^{*2} \ind \{ Z_{nj}^{*2} > \epsilon \} \big )
+  \leq \max_{j=1,\dots,J_n} \Em \big ( \tfrac{ n }{ M_{nj} } Z_{nj}^{*2}
+  \ind \{ \tfrac{ n }{ M_{nj} } Z_{nj}^{*2} >
+  \min_{k=1,\dots,J_n} \tfrac{ n }{ M_{nk} } \epsilon \} \big )
+\end{equation*}
+almost surely. Lemmas~\ref{L1} and~\ref{L6} imply that the RHS converges to
+zero in probability as $n \to \infty$
+proving~\eqref{eq:19}. The Dominated Convergence Theorem and~(\ref{eq:18})
 then ensure that

### 2017-04-05 subs/ETr4/reply_3.tex
[#35/gfn] Address referee's snarky functional comments in response letter
[#32/Ems] Add response to referees
[#37/cite] add statement about attribution to referee letter
[#38/ui] Address referee 3's comment on LIE
Write up summary of changes for resubmission

@@
 \section*{\hfill Reply to referee 3\hfill}
+
+In addition to the changes listed below, I have rewritten the proof of
+Lemma 6 and changed the part of the proof of Theorems 1 and 2 where
+the lemma was invoked. Lemma 6's proof had ignored a key measurability
+requirement that conflicted with the martingale difference sequence
+arguments used in some of the key inequalities.
+
+\section*{\hfill Specific points\hfill}
 
@@
 
+  I have added a disclaimer. Thanks.
+
 \item \emph{I assume $\Em \Em^* = \Em$, law of iterated
@@
 
+  Yes; this part of the proof has been rewritten in response to
+  another referee's comment, however.
+
 \item \emph{``Attributed to Polya ...''. If this is worth saying, it
     is worth providing a citation.} (Page 11, line --5)
+
+  Ok. My primary motivation in writing that statement was to avoid
+  appearing to take credit for a standard argument in this
+  literature. (I was asked to include these steps explicitly by an
+  earlier referee.)  I have added a reference to Van der Vaart's
+  (2000) textbook instead, since I've been unable to track down a
+  specific citation for Poly\'a.
 
@@
     this?} (Page 14, lines --8 and --7)
+
+  This first result has been cleaned up a little bit.
 

### 2017-04-05 subs/ETr4/reply_4.tex
[#38/ui] Address referee 4's comment on UI in theorem 1
Write up summary of changes for resubmission

@@
 
+\strut
+
+\noindent I have rewritten this part of the proof as well as a similar
+construction in the proof of Theorem 2. Lemma 6's proof had ignored
+one key measurability requirement and has been entirely rewritten as
+well.
+
+In addition, I have corrected several typos and made minor changes
+suggested by the other referees.
+
 \end{document}

### 2017-04-05 subs/ETr4/reply_ed.tex
Write up summary of changes for resubmission

@@
 
+I have made the changes requested by the referees. In addition,
+referee 4's concerns led me to reexamine Lemma 6 and I found a subtle
+error in its proof --- the measurability requirements of some of the
+variables used in the proof were inconsistent with the martingale
+difference sequence arguments I was using. So I have substantially
+rewritten the proof to use a different argument.
+
+To make the review process easier, I have also included a pdf of the
+paper with the changes since the last version highlighted. Thanks
+again for the opportunity to revise this paper.
+
+\strut
+
+\noindent Best,
+
 \strut

### 2017-04-05 Paper.tex
Make very minor tweaks to wording during review

--- 2017-03-27 Paper.tex
@@
 almost surely. Lemmas~\ref{L1} and~\ref{L6} imply that the RHS converges to
-zero in probability as $n \to \infty$
+zero in probability as $n \to \infty$,
 proving~\eqref{eq:19}. The Dominated Convergence Theorem and~(\ref{eq:18})
@@
   &\qquad\qquad\qquad \times \ind\{\sup_{\gamma \in [0,\delta]}
-  (1/\delta) | W_n^{*}(\gamma + \gamma_d) - W_n^{*}(\gamma_d) |^2 > \epsilon^2/4\delta\}].
-\end{align*}
-Lemma~\ref{L6} implies that
+  (1/\delta) | W_n^{*}(\gamma + \gamma_d) - W_n^{*}(\gamma_d) |^2 > \epsilon^2/4\delta\}]
+\end{align*}
+for large enough $n$. Lemma~\ref{L6} implies that
 \begin{equation*}
@@
 \end{equation*}
-is uniformly integrable, so an argument similar to that used in the
-proof of Theorem~\ref{T1} shows that there exists a
-finite and monotone function $B$ such that $B(x) \to 0$ as
-$x \to \infty$ and
+is uniformly integrable, so
 \begin{multline*}
-  \E[\sup_{\gamma \in [0,\delta]}
-  (1/\delta) | W_n^{*}(\gamma + \gamma_d) - W_n^{*}(\gamma_d) |^2 \times \\
+  \lim_{\delta \to 0} \limsup_{n\to\infty}\
+  \max_{d=1,\dots,D}
+  \E[\sup_{\gamma \in [0,\delta]} (1/\delta) | W_n^{*}(\gamma + \gamma_d) - W_n^{*}(\gamma_d) |^2
+  \times \\
   \ind\{\sup_{\gamma \in [0,\delta]}
-  (1/\delta) | W_n^{*}(\gamma + \gamma_d) - W_n^{*}(\gamma_d) |^2 > x\}]
-  \leq B(x)
+  (1/\delta) | W_n^{*}(\gamma + \gamma_d) - W_n^{*}(\gamma_d) |^2 > \epsilon^2/4\delta\}]
+  = 0,
 \end{multline*}
-for all $d$ and $\delta$ and all large enough $n$.
-
-As a result,
-\begin{align*}
-  \lim_{\delta \to 0} \limsup_{n\to\infty} \pr[\sup_{\gamma \in [0,1]}
-  \sup_{\gamma' \in [\gamma - \delta, \gamma + \delta]}
-  | W_n^{*}(\gamma) - W_n^{*}(\gamma') | > \epsilon] & \leq
-  \lim_{\delta \to 0} (4/\epsilon^2)
-  B(\epsilon^2/4\delta) \\
-  &= 0,
-\end{align*}
 completing the proof.\qed
@@
   \leq K_{n,J(x)}$. For any $m$, we can decompose $Z_n^{*}(\tau, m)$
-  into a summation of conditionally independent blocks, giving
+  into a summation of conditionally independent blocks
   \begin{multline} \label{eq:42}

### 2017-11-05 Paper.tex
Make minor text changes requested for resubmission

@@
 \maketitle
+\nocite{Jon:97}
 
@@
   This paper weakens the size and moment conditions needed for typical
-  block bootstrap methods (i.e.\ the Moving Blocks, Circular Blocks,
-  and Stationary Bootstraps) to be valid for the sample mean of
+  block bootstrap methods (i.e.\ the moving blocks, circular blocks,
+  and stationary bootstraps) to be valid for the sample mean of
   Near-Epoch-Dependent (\ned) functions of mixing processes; they are
   consistent under the weakest conditions that ensure the original
-  \ned\ process obeys a Central Limit Theorem \citep[those
-    of][\textit{Econometric Theory}]{Jon:97}.  In doing so, this paper
+  \ned\ process obeys a central limit theorem (CLT),
+    established by \citet[\textit{Econometric Theory}]{Jon:97}.  In doing so, this paper
   extends De Jong's method of proof, a blocking argument, to hold with
   random and unequal block lengths.  This paper also proves that
-  bootstrapped partial sums satisfy a Functional \clt\ under the same
+  bootstrapped partial sums satisfy a functional \clt\ (\fclt) under the same
   conditions.
@@
 \newpage
-\noindent Block bootstraps, e.g.\ the Moving Blocks
-(\citealp{Kun:89}, and \citealp{LiS:92}), Circular Block \citep{PoR:92}, and Stationary
-Bootstraps \citep{PoR:94}, have become popular in Economics, partly
+\noindent Block bootstraps, e.g.\ the moving blocks
+(\citealp{Kun:89}, and \citealp{LiS:92}), circular block \citep{PoR:92}, and stationary
+bootstraps \citep{PoR:94}, have become popular in economics, partly
 because they do not require the researcher to make parametric
@@
 well.%
-\footnote{\citet{Rad:96} proves consistency for the Moving Blocks
-  Bootstrap for any stationary strong mixing sequence that satisfies
+\footnote{\citet{Rad:96} proves consistency for the moving blocks
+  bootstrap for any stationary strong mixing sequence that satisfies
   the \clt. This paper uses a similar method of proof to his, but also
-  accommodates nonstationary sequences and the Stationary
-  Bootstrap.} %
+  accommodates nonstationary sequences and the stationary
+  bootstrap.} %
 It also relaxes \citepos{GoW:02} and \citepos{GoJ:03} requirement that
@@
 pasting these blocks together to create the new bootstrap time series.
-The Moving Blocks bootstrap does exactly that; the Circular Block
+The moving blocks bootstrap does exactly that; the circular block
 bootstrap ``wraps'' the observations, so that $(X_{n-1}, X_n, X_1,
 X_2)$, for example, is a possible block of length four (letting $X_t$
-denote the original time series).  The Stationary Bootstrap wraps the
+denote the original time series).  The stationary bootstrap wraps the
 observations and also draws $M$ at random for each block;
 \citet{PoR:94} suggest drawing $M$ from the geometric distribution.
-As the name suggests, the series produced by the Stationary Bootstrap
+As the name suggests, the series produced by the stationary bootstrap
 are strictly stationary, while those produced by the other methods are
-not.  Although the Stationary Bootstrap was believed to be much less
+not.  Although the stationary bootstrap was believed to be much less
 efficient than other block bootstrap methods due to results of
@@
 block bootstrap.  Consequently, there has been renewed interest in the
-Stationary Bootstrap since stationarity of the bootstrap samples can
+stationary bootstrap since stationarity of the bootstrap samples can
 be a useful property in theoretical research.  \cite{KrP:11} provides
@@
 scalar case but generalize immediately to random vectors.  All of the
-proofs are presented in the appendix; only proofs for the Stationary
-Bootstrap are presented, since proofs for the other methods are
-similar and easier to construct.  All limits are taken as $n \to \infty$
-unless otherwise noted and $\lVert \cdot \rVert_r$ denotes the
-$L_r$-norm.
+proofs are presented after the main text of the paper; only proofs for
+the stationary bootstrap are given, since proofs for the other methods
+are similar and easier to construct.  All limits are taken as
+$n \to \infty$ unless otherwise noted and $\lVert \cdot \rVert_r$
+denotes the $L_r$-norm.
 
@@
     and $\sum_{t=1}^n (\mu_{nt} - \bar \mu_n)^2 = o(n p_n^2)$ (for
-    the Stationary Bootstrap) or
+    the stationary bootstrap) or
     $\sum_{t=1}^n (\mu_{nt} - \bar \mu_n)^2 = o(n/M_n^2)$ (for
-    the Moving or Circular Block Bootstraps),
+    the moving or circular block bootstraps),
     where $\E X_{nt} = \mu_{nt}$, $\bar{\mu}_n = n^{-1} \sum_{t=1}^n
@@
     and~$t$.
-  \item $X_{nt}^{*}$ is generated by the Stationary Bootstrap with
+  \item $X_{nt}^{*}$ is generated by the stationary bootstrap with
     geometric block lengths with success probability $p_n$, $p_n = c
-    n^{-a}$ and $a,c \in (0,1)$, or by the Moving or Circular Block
+    n^{-a}$ and $a,c \in (0,1)$, or by the moving or circular block
     bootstrap with block length $M_n$ such that $M_n \sim n^a$ for
@@
 used by \citet{Jon:97}.
-Note that De Jong does allow a little bit more flexibility in the
+Note that De Jong does allow a little more flexibility in the
 conditions on the array $\{c_{nt}\}$ \citep[see also][]{Dav:93};
@@
 blocks.  This additional restriction is required because the
-Stationary Bootstrap will select the blocks randomly and is similar to
+stationary bootstrap will select the blocks randomly and is similar to
 \citepos{JoD:00b} requirement for the \fclt.
@@
 we have introduced $D_n$ to minimize notation in the subsequent
-discussion.  For the Moving and Circular Block Bootstraps,
+discussion.  For the moving and circular block bootstraps,
 Theorem~\ref{T1}'s Assumption 2 holds if $D_n = o(n / M_n^2)$, and
 the same relationship must hold for the expected block length for the
-Stationary Bootstrap. If $\Delta_n = \Delta_0$ and $T_n = \pi n$ for
+stationary bootstrap. If $\Delta_n = \Delta_0$ and $T_n = \pi n$ for
 some constants $\Delta_0$ and $\pi$ and for all $n$, then
@@
 the original squared blocks can be applied with only minor changes to
-the bootstrapped blocks. Consider the Moving Blocks Bootstrap,%
+the bootstrapped blocks. Consider the moving blocks bootstrap,%
 \footnote{To make this presentation as simple as possible, assume for
@@
   strong demonstrations of this argument.} %
-A similar representation is available for the Circular and Stationary
+A similar representation is available for the circular and stationary
 bootstraps.
@@
 \end{align*}
-Also let $W$ denote standard Brownian Motion and $\sigma W$ denote
-Brownian Motion scaled by the constant $\sigma$.
+Also let $W$ denote standard Brownian motion and $\sigma W$ denote
+Brownian motion scaled by the constant $\sigma$.
 
@@
 partial sum of the original observations converges to a transformed
-Brownian Motion with a different covariance process. The bootstrapped
+Brownian motion with a different covariance process. The bootstrapped
 partial sum, on the other hand, always converges to standard (but
-potentially scaled) Brownian Motion because the resampling strategies
+potentially scaled) Brownian motion because the resampling strategies
 ensure that the bootstrapped process is globally covariance stationary.
@@
 permanently changes partway through the series, for example.  Other
-methods, such as the Local Block Bootstrap \citep{PaP:02,DPP:03}, may
+methods, such as the local block bootstrap \citep{PaP:02,DPP:03}, may
 be able to capture this additional heterogeneity with the bootstrap
@@
 
-To prove~\eqref{eq:19}, it suffices (via the LIE and Lemma~\ref{L2})
+To prove~\eqref{eq:19}, it suffices (via the law of iterated expectations and Lemma~\ref{L2})
 to show that
@@
 
-\section{Supplemental results}
+\section{Supporting results}
 
@@
   \end{align*}
-  The first equality follows from the LIE\@. The first inequality
+  The first equality follows from the law of iterated expectations. The first inequality
   exploits the fact that the conditional expectation in the previous
@@
 \citepos{Jon:97} Lemmas 5 and 4, respectively, replacing De Jong's
-implicit use of inequalities with explicit inequalities. The
-supplemental appendix presents a proof of~\eqref{eq:33} to show the
-main idea.
+implicit use of inequalities with explicit inequalities. Since the
+proof follows De Jong's very closely, it is presented in a
+supplementary online appendix.\footnote{%
+  Supplementary material to this article is provided in
+  ``Supplementary Appendix for `Block bootstrap consistency under weak
+  assumptions,'{}'' which is available at Cambridge Journals Online
+  (\url{journals.cambridge.org/ect}).}
 
@@
 
-For proof, see supplemental appendix for the proof of~\eqref{eq:34}, which
-follows \citet[Lemma 6.5]{Mcl:75b} and \citet[Lemma 3.5]{Mcl:77}
+See the supplementary online appendix for the proof of~\eqref{eq:34},
+which follows \citet[Lemma 6.5]{Mcl:75b} and \citet[Lemma 3.5]{Mcl:77}
 almost exactly and is also presented as Theorem~16.13 in
-\citet{Dav:94}. The same comment that follows
-Lemma~\ref{L7} applies here as well: the bounds
-apply equally well to $\Em$.
+\citet{Dav:94}. The same comment that follows Lemma~\ref{L7} applies
+here as well: the bounds apply equally well to $\Em$.
 
